---
title: "Lengths of Philosophy Articles"
abstract: |
    Are articles getting longer? Yes, yes they are. A lot longer.
date: February 7 2025
author:
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
categories:
  - citations
execute:
  echo: false
  warning: false
draft: true
format:
  html:
    fig-format: svg
    fig-height: 9
    fig-width: 12
    fig-dpi: 300
    fig-responsive: true
    fontsize: 1.1rem
---

In an [earlier post](https://brian.weatherson.org/quarto/blog/word-count/count-graphs.html) I went over changes in word usage in philosophy articles. Here I want to do something a bit simpler. I'm going to graph out how much longer articles are getting.

The wordcounts that I get from the JSTOR databases and pdftools are a bit longer than what you're probably used to, because they include everything. That means the body text, the footnotes, the bibliography, the abstract, the running head, and so on. In practice, that means they are about 10-20% longer than what you'd normally think if you were just looking at body text and footnotes.^[So for some of you, that means about 100% longer than body text alone.]

The things like the running head are annoying to include, but they haven't changed much over time. So the trends in the graphs here would be the same even if we used a more normal measure.

```{r}
#| label: loader
#| cache: false

require(tidyverse)
require(slider)
require(stringr)
require(knitr)
require(scico)
require(wesanderson)

if(knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = 'cairo_pdf')
}

# Graph Themes
old <- theme_set(theme_minimal())
theme_set(old)
theme_update(plot.title = element_text(family = "Scala Pro", size = 24, face = "bold"),
             plot.subtitle = element_text(family = "Scala Sans Pro", size = 30),
             axis.text = element_text(family = "Scala Sans Pro", size = 18),
             title = element_text(family = "Scala Sans Pro", size = 18),
             plot.background = element_rect(fill = "#F9FFFF"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "#F9FFFF"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "Scala Sans Pro", size = 20),
             strip.text = element_text(family = "Scala Sans Pro", size = 20),
             legend.key.spacing.y = unit(0.5, 'lines'),
             legend.key.spacing.x = unit(1, 'cm')
  )

if(knitr::is_latex_output()) {
theme_update(plot.title = element_text(family = "Europa-Bold", size = 14),
             plot.subtitle = element_text(family = "EB Garamond", size = 11),
             axis.text = element_text(family = "EB Garamond", size = 10),
             plot.background = element_rect(fill = "white"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "white"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "EB Garamond", size = 11),
             strip.text = element_text(family = "EB Garamond", size = 12),
             legend.key.spacing.y = unit(-0.3, 'lines'),
             legend.key.spacing.x = unit(0, 'cm')
  )
}

load("/Users/weath/Documents/jstor-dfr-2025/all_join.RData")
load("/Users/weath/Documents/citations-2025/philo_bib.RData")

main_tibble <- all_join |>
  inner_join(
    select(
      philo_bib,
      id,
      journal,
      year), by = "id"
    )
  
```

```{r}
#| label: work-out-quartiles

word_quartile_by_year <- main_tibble |>
  group_by(journal, year) |>
  summarise(Q1 = round(quantile(wordcount, 0.25),1),
            Q2 = round(quantile(wordcount, 0.5),1),
            Q3 = round(quantile(wordcount, 0.75),1),
            .groups = "drop") |>
  pivot_longer(cols = starts_with("Q"),
               names_to = "statistic",
               values_to = "value") |>
  ungroup() |>
  group_by(journal, statistic) |>
  mutate(rolling = slide_dbl(value, mean, .before = 2, .after = 2)) |>
  ungroup()

overall_word_quartile_by_year <- main_tibble |>
  group_by(year) |>
  summarise(Q1 = round(quantile(wordcount, 0.25),1),
            Q2 = round(quantile(wordcount, 0.5),1),
            Q3 = round(quantile(wordcount, 0.75),1),
            .groups = "drop") |>
  pivot_longer(cols = starts_with("Q"),
               names_to = "statistic",
               values_to = "value") |>
  ungroup() |>
  group_by(statistic) |>
  mutate(rolling = slide_dbl(value, mean, .before = 2, .after = 2)) |>
  ungroup()
```

We'll start, in @fig-word-quartiles, with a look at all twenty journals.^[See the [earlier post](https://brian.weatherson.org/quarto/blog/word-count/count-graphs.html) for the list of journals.] I haven't used mean lengths, because it can get thrown off too much by single long articles. Instead, for each year I'm plotting the 25th, 50th, and 75th percentile word lengths. So the lowest line is the length such that a quarter of articles are shorter, the middle line is the length where just as many articles are longer than it as shorter, and the top line is the length such that 25% of articles are longer.

I won't go over it here because it's a bit of a mess, but I'm *mostly* taking Web of Science's classification of what's an *article* at face value. This excludes book reviews, and it excludes most things listed as 'Discussion' or 'Note' in the journal, and it's somewhat random whether it includes or excludes book symposia and critical notices. (They don't seem to do this consistently, and I don't know a good way to correct it.) Including any of these would bring the lengths down a bit. That said, @fig-word-quartiles is the big story.^[The lines here are five year moving averages, with the window centered on the year in question. So above 2006, the lines show the 25th, 50th, and 75th percentiles for the window 2004-2008.]

```{r}
#| label: fig-word-quartiles
#| fig-cap: "25th, 50th, and 75th percentile word lengths each year."
#| fig-asp: 0.4

ggplot(overall_word_quartile_by_year,
       aes(x = year, y = value, color = statistic)) +
  geom_point(size = 1.5) +
  theme(legend.position = "none") +
  labs(x = element_blank(),
       y = "Word Count") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::label_comma()) +
  geom_line(aes(x = year, y = rolling, color = statistic)) +
  scale_color_manual(values=wes_palette(n=3, name="AsteroidCity1"))
```

The trends here are remarkable. In every year from 2015-2019, the 25th percentile article, by length, was longer than the median article in any year from 1980-1984. There is a little less movement at the top end, but the disappearance of short articles is rather stunning.

You can see more or less the same trends across all of the journals in @fig-word-quartiles-by-journal. The dots here bounce around a lot more, and even the moving averages are fairly noisy.

```{r}
#| label: fig-word-quartiles-by-journal
#| fig-cap: "25th, 50th, and 75th percentile word lengths each year for each journal."
#| fig-height: 80

ggplot(word_quartile_by_year,
       aes(x = year, y = value, color = statistic)) +
  geom_point(size = 1.5) +
  theme(legend.position = "none") +
  labs(x = element_blank(),
       y = "Word Count") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::label_comma()) +
  geom_line(aes(x = year, y = rolling, color = statistic)) +
  scale_color_manual(values=wes_palette(n=3, name="AsteroidCity1")) + 
  facet_wrap(~journal, ncol = 1, scales = "free")
```

There are some journals which look like the overall trend. In this respect, _Philosophical Studies_ looks most like the discipline as a whole. (This is true in several other respects as well, but that's a story for another day.) But the steady march upwards we saw in @fig-word-quartiles isn't always apparent in @fig-word-quartiles-by-journal. What is somewhat more common among the individual journals is *compression*. For several journals, the gap between the three lines is much closer in 2019 than it was throughout the previous four decades. There are some journals where that gap has stayed steady; the only one where it has really expanded is _Philosophy of Science_.

There is a natural story to explain this. Journals which previous just published articles at the length that people wrote them had to start imposing word limits, and then enforcing them tightly. As philosophers wanted to write longer and longer articles, they started sending papers to journals where they were just under the limit. And so we get situations like with the _Australasian Journal of Philosophy_ where the word limit is tightly enforced, but practically every published article is butting against that limit.