---
title: "Consistency and Resoluteness"
abstract: |
  When does a little story in which a character loses money, or at least comes out with less money than they might easily have had, reveal a defect in that character's rationality? We argue that these stories are less philosophically revealing than is often assumed. In particular, we argue the story can only be used in this kind of argument if the character has firm beliefs about what they will do later in the story. This constraint is, we argue, violated in recent arguments against imprecise credences and incomparable values.
author:
  - name: Harvey Lederman
    url: https://www.harveylederman.com
    affiliation: University of Texas
    affiliation_url: https://utexas.edu
    orcid_id: 0000-0001-9438-097X
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
date: 02-15-2025
categories:
  - epistemology
  - games and decisions
draft: true
format:
  html:
    css: ../trad_defn.css
  pdf:
    output-file: "Consistency and Resoluteness"
    include-in-header:
      - file: ../quarto2024.tex
      - text: |
         \cehead{
                 Lederman and Weatherson
                 }
    include-after-body: 
        text: |
          \noindent Draft of February 2025.
---

One genre of parable has played a key role in philosophical theorizing about rationality. In some respects, the conventions of the genre are simple: A character is portrayed, presented with certain choices, and, in response, loses something of value, with no compensatory gain. The inevitable moral is then drawn: the protagonist displays a rational defect.

Recently this kind of parable has been deployed by Adam @Elga2010, to argue against imprecise credences, and by Johan Gustaffsson [-@Gustafsson2022; @Gustafsson2025], to argue against incomplete preferences. We argue that these parables fail to ground convincing arguments. This is interesting both for debates about the nature of credences and values, but also for more general debates about the role of these parables in philosophy.

Let's start with three such parables that we hope you'll agree are not persuasive.

Dylan owns _B_, but has a slight preference for _A_. So they trade _B_ plus ε for _A_. The next day they wake up with the opposite preference, and trade _A_ plus ε for _B_. At the end they are back where they started, minus 2ε. Should this story make us think that rational people never change their tastes? Hopefully not.

Blake has credence 0.6 in _p_. They pay 0.55 for a bet that pays 1 if _p_, and 0 otherwise. The next morning, they wake up and find, much to their surprise, that they now have credence 0.4 in _p_. They sell the bet for 0.45, netting a loss of 0.1. This one is a little more controversial, but we also don't think that this shows that changing one's beliefs is irrational.^[Two important caveats here. One is that believers in various uniqueness theses will think that Blake is not perfectly rational; see @KopecTitelbaum2016 for a survey of the issues here. But note that uniqueness is a theory of substantive rationality, and these stories are meant to reveal violations of structural rationality. So we think uniqueness shouldn't be assumed here. Another is that there is an argument from David @Lewis1999b that not conditionalising will lead to a money pump, and Blake doesn't conditionalise. But as several authors have pointed out (e.g., @Bradley2005), Lewis's argument shows at most that any policy other than conditionalisation leads to a money pump. And Blake has no such policy; they just find themselves with new beliefs.]

Leslie is offered the following trade: If they pay 5, they will receive a bet that pays 8 if this fair coin lands heads, and 0 if it lands tails. Also, they have the option of paying 1 to put off their decision until after the coin is flipped. Textbook theories of rationality say that they should pay the 1 and take this option. But whatever way the coin lands, and whatever they do, they would have been better off doing that without paying 1. Here we think everyone will agree that Leslie does nothing irrational by paying to delay the decision, even though whatever happens, they could have done better. In general, paying for options is not always irrational. Anyone who pays extra for a cancellable flight or hotel does that, and these payments are not always irrational.

These cases show, we think, that stories involving money pumps don't reveal irrationality on the part of the protagonist if the story involves changes of desire, or changes of belief, either through 'fickle' change (@Woodard2022) or through learning. We want to suggest a similar constraint in the same neighbourhood. The protagonist must have beliefs about what they will do at future nodes, and these beliefs must update by conditionalisation. If that's not true, we will argue, the money pump parable doesn't show anything.

So consider a canonical money-pump argument against incomplete preferences, often called the "Single Souring Moneypump" [@Chang1997 11; @Gustafsson2022 26]. The tree for this is shown in @fig-single-souring.

```{r}
#| echo: FALSE
#| output: FALSE

require(Rcpp)
require(tidyverse)
font_opts <- list(extra.preamble=c("\\usepackage{fontspec}", 
                                   "\\setmainfont{EB Garamond}"))

if(knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = 'tikz')
}
options(tinytex.engine = "xelatex")
```

```{r, engine='tikz', engine.opts=font_opts}
#| label: fig-single-souring
#| fig.cap: "The Single Souring Moneypump"
#| cache: FALSE
#| echo: FALSE

\usetikzlibrary{calc}

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5},
square node/.style={rectangle,draw, inner sep = 1, fill = black}
}

% Specify spacing for each level of the tree
%\tikzstyle{level 1}=[level distance=12mm,sibling distance=15mm]
%\tikzstyle{level 2}=[level distance=15mm,sibling distance=15mm]
%\tikzstyle{level 3}=[level distance=13mm,sibling distance=11mm]


\begin{tikzpicture}[grow=right, sloped]
\node[hollow node, draw] {}
    child {
        node[solid node, draw] {}
        child {
            node[square node, fill, inner sep=1.5pt, label=right:{\emph{B}}] {}
            edge from parent
            node[above] {}
        }
        child {
            node[square node, fill, inner sep=1.5pt, label=right:{\emph{A}-}] {}
            edge from parent
            node[below] {}
        }
        edge from parent
        node[below] {}
    }
        child {
        node[square node, fill, inner sep=1.5pt, label=right:{\emph{A}}] {}
        edge from parent
        node[above] {}
    };
\end{tikzpicture}
```