% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod,
  twoside]{scrartcl}
\usepackage{xcolor}
\usepackage[left=1.1in, right=1in, top=0.8in, bottom=0.8in,
paperheight=9.5in, paperwidth=7in, includemp=TRUE, marginparwidth=0in,
marginparsep=0in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmathfont[]{Garamond-Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0ex}
\usepackage[automark]{scrlayer-scrpage}
\clearpairofpagestyles
\cehead{
  Brian Weatherson
  }
\cohead{
  Books, Schools, and Restaurants
  }
\ohead{\bfseries \pagemark}
\cfoot{}
\makeatletter
\newcommand*\NoIndentAfterEnv[1]{%
  \AfterEndEnvironment{#1}{\par\@afterindentfalse\@afterheading}}
\makeatother
\NoIndentAfterEnv{itemize}
\NoIndentAfterEnv{enumerate}
\NoIndentAfterEnv{description}
\NoIndentAfterEnv{quote}
\NoIndentAfterEnv{equation}
\NoIndentAfterEnv{longtable}
\NoIndentAfterEnv{abstract}
\renewenvironment{abstract}
 {\vspace{-1.25cm}
 \quotation\small\noindent\emph{Abstract}:}
 {\endquotation}
\newfontfamily\tfont{EB Garamond}
\addtokomafont{disposition}{\rmfamily}
\addtokomafont{title}{\normalfont\itshape}
\let\footnoterule\relax

\makeatletter
\renewcommand{\@maketitle}{%
  \newpage
  \null
  \vskip 2em%
  \begin{center}%
  \let \footnote \thanks
    {\itshape\huge\@title \par}%
    \vskip 0.5em%  % Reduced from default
    {\large
      \lineskip 0.3em%  % Reduced from default 0.5em
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%  % Reduced from default
    {\large \@date}%
  \end{center}%
  \par
  }
\makeatother
\RequirePackage{lettrine}

\renewenvironment{abstract}
 {\quotation\small\noindent\emph{Abstract}:}
 {\endquotation\vspace{-0.02cm}}

\setmainfont{EB Garamond Math}[
  BoldFont = {EB Garamond SemiBold},
  ItalicFont = {EB Garamond Italic},
  RawFeature = {+smcp},
]

\newfontfamily\scfont{EB Garamond Regular}[RawFeature=+smcp]
\renewcommand{\textsc}[1]{{\scfont #1}}

\renewcommand{\LettrineTextFont}{\scfont}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Books{,} Schools{,} and Restaurants},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}


\title{Books, Schools, and Restaurants}
\author{}
\date{2026}
\begin{document}
\maketitle
\begin{abstract}
This is a contribution to a symposium on David Liebesman and Ofra
Magidor's book \emph{Property Versatility and Copredication}. It was
originally presented, in compressed version, at the 2026 Eastern APA. I
agree with their big picture metaphysical view, but quibble at several
points about its application to social metaphysics. The common thread to
my quibbles is that they understate the importance of the physical to
the metaphysics of the social world.
\end{abstract}


\setstretch{1.1}
The first thing to say is that this is a great book.\footnote{The book,
  of course, is Liebesman and Magidor (\citeproc{ref-LM2025}{2025}).} I
loved reading it, working through the examples, and thinking about the
puzzles, and I strongly recommend it to anyone reading this symposium.
It's obviously relevant to lots of people working in, or teaching,
metaphysics and philosophy of language. But there also turn out to be
things relevant to philosophy of mind, to aesthetics, and, this is what
I'll be talking about, philosophy of social science.

I'm not much of a critic since I'm sympathetic to the overall view. One
background theme to these remarks is that Liebesman and Magidor aren't
sufficiently radical. There will be two foreground themes. One is that
they need to get more physical; they give physical objects short shrift
at a couple of points. Another is that once we have abstracta like
i-books, plenitude results a la Fairchild
(\citeproc{ref-Fairchild2019}{2019}) are inevitable. And then things get
weird. Not that there's anything wrong with that; the social world is
weirder than it looks. But cataloging the weirdness is valuable.

\section{Example 1: Box on Knox}\label{example-1-box-on-knox}

One guiding puzzle is explaining (1). (Imagine that I'm pointing at a
nondescript copy of a Ned Kelly Award winning book.)

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  There's a famous book on the shelf.
\end{enumerate}

The puzzle which gets \emph{Property Versatility and Copredication}
going is fairly simple. The following four claims are inconsistent.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  If `book' in (1) denotes a physical object, then (1) is false, since
  none of the physical objects on the shelf are famous.
\item
  If `book' in (1) denotes an abstract object, the book-type which won
  the Ned Kelly award, then (1) is also false, since no abstracta is on
  the shelf.
\item
  In (1), `book' denotes either a physical object, or an abstract
  object.
\item
  As uttered in that context, (1) is true.
\end{enumerate}

These are inconsistent, so something has to give. Liebesman and Magidor
want to keep (5), largely because of methodological conservatism, and I
think they're right to do so.

They argue that (4) is true, and non-redundant. In English, `book'
sometimes picks out a physical object, and sometimes an abstract object.
They call the former p-books, and the latter i-books, and I'll follow
suit. The argument for the ambiguity turns on various counting sentences
that I'll discuss in much more length in the rest of this note. The
argument that there is no other reading comes from careful study of the
alternatives, which they find wanting.

So we're left with (2) and (3) as being the possible culprits. They want
to reject (3); abstracta, they say, can be on shelves. I think their
arguments here are fairly compelling, even if surprising. That would
solve the problem, so we don't have any further reason from this problem
to reject (2). I'm going to argue that we have independent reason,
however, to reject it, and that Liebesman and Magidor's solution is
insufficiently radical.

Liebesman and Magidor say that i-books often inherit properties of
p-books. The abstract book is on shelf because a physical copy of it is.
They resist the idea that p-books quite as often inherit properties that
are grounded\footnote{For the record, I doubt Liebesman and Magidor
  would be happy with expressing the point here in terms of grounding.
  It's not the language they use. But it fits smoothly into the picture
  they have, and it's easy enough to translate what I say into less
  metaphysically loaded language.} in facts about i-books. The evidence
for this is that (6) is defective. If p-books automatically inherited
properties of i-books, it should be easy for it to be true when the
shelf contains three wrinkled copies of, say, Jane Harper's latest
novel.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{5}
\tightlist
\item
  Three wrinkled books on the shelf are bestselling.
\end{enumerate}

I'm sceptical how much this shows. (6) just seems like an awkward
locution to me, and not evidence especially about p-books. (7) is just
as defective, even though it's clearly about i-books.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{6}
\tightlist
\item
  Three books featuring Aaron Falk are bestselling.
\end{enumerate}

We can give an independent argument that p-books can inherit properties
freely. Imagine my wife and I are moving house. There are plenty of
books that we both have copies of in virtue of being cultured people, so
our joint collection has some duplicates. The books go in boxes, and
each box has 50 p-books and 40 i-books. Now how should we arrange the
boxes? There are boring options, like sorting them by genre, sorting
them chronologically, sorting them alphabetically by author,
alphabetically by title, etc. But it's more fun to sort them by sales
figures, or by fame, or by comedic value. Depending on what sort order
we choose, one of (8) to (10) will be true of the first box.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  This box has 50 bestselling books.
\item
  This box has 50 famous books.
\item
  This box has 50 funny books.
\end{enumerate}

In those sentences, `book' must be p-book, because there are only 40
i-books per box. But really any feature of i-book could be used in the
penultimate word. So p-books inherit i-book features generally. So there
is a sense in which (2) is false; it's the sense we get when we read
`famous' the same way it is read in (9).

\section{Example 2: Lost in
Translations}\label{example-2-lost-in-translations}

Another core example of \emph{Property Versatility and Co-Predication}
involves duplicate books. My teenager's Homer shelf has two copies of
the \emph{Odyssey} and one of the \emph{Iliad}. Intuitively both (11)
and (12) have true readings.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{10}
\tightlist
\item
  Their shelf has exactly two books on it.
\item
  Their shelf has exactly three books on it.
\end{enumerate}

My Homer shelf is a more complicated case. It only has the
\emph{Odyssey}, but it has two copies of the Fagles translation and one
of the Wilson. It seems to me that all of (13) to (15) have true
readings, and I think from what Liebesman and Magidor say in §9.3 they
agree.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{12}
\tightlist
\item
  My shelf has exactly one book on it, the \emph{Odyssey}.
\item
  My shelf has exactly two books on it, the Fagles translation and the
  Wilson translation.
\item
  My shelf has exactly three books on it, which I can throw at those
  beer bottles.
\end{enumerate}

The solution is to say that the \emph{Odyssey} is an i-book, and so are
the translations of it. That seems like a good step to me, but there are
two questions.

One concerns my wife's Homer shelf, which has one p-book on it, the
Wilson translation of the \emph{Odyssey}. Now (16) is true, but (17) is
false, even though there are two i-books, the \emph{Odyssey} and the
Wilson translation of the \emph{Odyssey} on her shelf.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{15}
\tightlist
\item
  Her shelf has exactly one book on it.
\item
  Her shelf has exactly two books on it.
\end{enumerate}

Here's a challenge. It's not immediately an objection, but if it can't
be answered it would be. Given Liebesman and Magidor's theory of
i-books, why don't we get a true reading of (17)? This is related to an
argument Sider (\citeproc{ref-Sider1996-SIDATW}{1996}) gives against
Lewis's theory of continuants.

The other question concerns how many variants we can get that are like
(13) to (15).

Does it apply to editions? My Jeffrey shelf has two copies of the first
edition of \emph{Logic of Decision} and one copy of the second edition.
Can we get a reading of (18) on which it's true?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{17}
\tightlist
\item
  My Jeffrey shelf has exactly two books on it.
\end{enumerate}

Here's a slightly harder case. My Keynes shelf at the office has four
p-books on it. It has both volumes of \emph{Treatise on Money} and two
copies of the \emph{General Theory}. It's easy to get readings where we
get two and four books, but can we get a reading where (19) is true?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{18}
\tightlist
\item
  My Keynes shelf at the office has exactly three books on it.
\end{enumerate}

I think we can. It has volumes 5 to 7 of the Collected Works, i.e.,
three books. Compare my Beatles shelf. It has seven pieces of vinyl on
it; \emph{Revolver} and three copies of the White Album. Do we get true
readings of each of (20) through (23)?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{19}
\tightlist
\item
  My Beatles shelf has two records on it.
\item
  My Beatles shelf has three records on it.
\item
  My Beatles shelf has four records on it.
\item
  My Beatles shelf has seven records on it.
\end{enumerate}

I think so\footnote{For (20) \emph{Revolver} and the White Album; for
  (21), \emph{Revolver} and both discs of the White Album; for (22), the
  four spines; for (23), the seven discs.}, but I'm getting less
certain. I'll end this with two cases where I think we really don't get
the readings, though again I'm not certain.

My home Keynes shelf is cleaner than its counterpart at the office. It
has the 30 volume Collected Works of John Maynard Keynes, and nothing
else. I think (24) is false; the collected works is not a book.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{23}
\tightlist
\item
  My Keynes shelf at home has exactly one book on it.
\end{enumerate}

It's a bit odd why we don't get that as a reading. The two volume
\emph{Treatise on Money} could be a book, but not the thirty volume
\emph{Collected Works}. If I'm right about those claims, it would be
nice to know why. Here are three hypotheses:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{24}
\tightlist
\item
  There is a cap on how many volumes can make up a book, and that cap is
  more than 2, but less than 30.
\item
  Books are published at a time, or at least in a short space of time,
  and \emph{Collected Works} contains material published over 40 years.
\item
  Books are meant to be read as a single entity, and the \emph{Collected
  Works} is not.
\end{enumerate}

The problem is that none of these are particularly plausible. (25) seems
arbitrary, and besides there are some books with many, many volumes.
There are books which are composed of essays from many different times,
contra (26). Indeed, volumes IX and X, i.e., \emph{Essays in Persuasion}
and \emph{Essays in Biography}, would not count as books under this
criteria. Nor would \emph{The Adventures of Sherlock Holmes}, which
seems to me clearly a book. Against (27), there are reference books that
are not meant to be read as coherent wholes, and multi-volume works that
are coherent, but arguably not books. It would be useful to know how
many people would be willing to count \emph{La Comédie humaine} or
\emph{Om udregning af rumfang} (\emph{On the Calculation of Volume}) as
books. I don't have a good answer here; the boundary between the books
and the non-books is much messier than I had expected.

Let's return to the \emph{Collected Works}, and note a few other strange
things about it. I feel in theory we should be able to get (28),
counting the two volumes of the \emph{Treatise on Money} as one book, or
even (29), doing that and also not counting the index, volume 30, as a
book. Personally I can't hear them as true, but I don't fully trust my
judgments on this.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{27}
\tightlist
\item
  My Keynes shelf at home has exactly 29 books on it.
\item
  My Keynes shelf at home has exactly 28 books on it.
\end{enumerate}

So far I've talked about cases where we might wonder whether there are
fewer books than spines on the shelf. As Liebesman and Magidor note,
there are cases that push the other way. I'm currently looking at a
volume of works by Dashiel Hammett, memorably titled \emph{Five Complete
Novels}. They say, and I agree, that it could count for five books on
the shelf. But what's the limit of that kind of consideration.

My bible shelf has a modern King James bible, and nothing else. (So it
doesn't have the apocrypha.) So here are some books on that shelf:
Genesis, Exodus, Leviticus, etc. Still, I can't hear (30) as true.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{29}
\tightlist
\item
  My bible shelf has 66 books on it.
\end{enumerate}

Maybe I'm just not sufficiently holy, but this seems like another
mystery about what is a book. Why does \emph{The Thin Man} count as a
book, when bundled with \emph{The Maltese Falcon} etc, but not Genesis?
I don't have good answers here, and I don't even know what the data is
in the general public.

None of these are objections; any number of answers are compatible with
the metaphysical picture that Liebesman and Magidor offer. I just think
it's worth getting clear on just when we have i-books made of i-books,
and it's surprising how unclear the data are.

\section{Example 3: Schools of
schools}\label{example-3-schools-of-schools}

Liebesman and Magidor say that `school' is not semantically variable. I
think that can't be right, because of what they say about the variable
granularity of i-books.

Their discussion of schools starts with an argument against theorists
who say that sometimes `school' means `school building'. I agree that
can't be right. One problem is that schools typically, at least in my
schooling, have multiple buildings. (This might be a matter of
geographic variation. In colder climates having a school, even a large
school, in a single building seems more common. It's also become common
in the United States because of the unfortunate need for more security.)
Another problem is that the hypothesis that schools are buildings
doesn't capture the data it was meant to capture, namely that schools
can be vandalized. If one sets fire to the school football field, as I
definitely did not do on April 17th 1986, one has vandalized the school
but not any building.

But the problem is that schools can come in different granularities, or
have different persistence conditions, and that makes `school'
semantically variable. Just in Ann Arbor there are a bunch of cases of
this. Was the University of Michigan founded in 1817, when something
like its closest continuant was founded in Detroit, or in 1837, when a
university was first founded in Ann Arbor? (It had bicentential
celebrations in 2017, and maybe that settles it, since I'm sympathetic
to letting institutions make their own decisions about their vague
boundaries.) In 2025, the interim President of the University of
Michigan was Domenico Grasso, who was previously Chancellor of the
University of Michigan at Dearborn. Did President Grasso change schools
when he `moved' from University of Michigan, Dearborn to University of
Michigan, Ann Arbor to become President? It feels like there could be
multiple correct answers here, which is some evidence of variable
granularity. There are even sharper cases in the elementary schools in
Ann Arbor.

Back in the bad old days of segregation, there were two elementary
schools in southeast Ann Arbor: Bryant and Pattengill. One of these was
predominantly Black, the other predominantly white. As a desegregation
move, the school district was reorganised. Bryant became a K-2 school,
and Pattengill a 3-5 school. This was, and remains, different to the
typical K-5 structure of elementary schools. The catchment area was (and
is) the same for `each' school. This was a kind of bussing, and it
basically worked; a Worthwhile Ann Arbor initiative that persists to
this day. These days there is a level of common organisation to Bryant
and Pattengill, but also some independence. The messiness is nicely
reflected in their websites, where they have their own name, but also
the logo for Bryant-Pattengill.

So here's a hard question: are these the same school? I think it's vague
in a way that reveals semantic indeterminacy. Imagine two parents whose
children just moved from grade 2 at Bryant to grade 3 at Pattengill are
asked if their child has changed school. One says (31); the other says
(32).

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{30}
\tightlist
\item
  Yes, they moved from Bryant to Pattengill.
\item
  No, though they moved campus from Bryant to Pattengill.
\end{enumerate}

Both of these seem like they could be correct in some contexts. If a
parent is talking about how their morning routine changed now that their
eldest is in 3rd grade, then (31) could be reasonable. But if there is a
conversation with some parents of 6th graders who are talking about how
hard it has been to move to a new school with all these new people and
different ways of doing things, saying (31) as a way of indicating that
you are going through something similar is highly misleading at the very
best. This all seems like evidence of semantic variability.

There is another more complicated case that makes a similar point. Ann
Arbor has had for several decades something it calls an Open school.
This doesn't have a catchment area, and it has an idiosyncratic
curriculum. From 1986 to 1999 the Open school was at a campus called
Bach. Since then the Open school has been at a campus called Mack. These
are only about half a mile apart, closer than Bryant and Pattengill, but
they are administratively separate. When Open wasn't at those campuses,
they were normal K-5 schools.

Now we have three characters, Betty, Mary and Gauri. Betty and Mary were
elementary school students in the early 1990s, while Open was still at
the Bach campus. Betty went to Bach, i.e., to Open. Mary went to Mack
Elementary. They each, separately, talk to Gauri, who is a current
student at the Open School at Mack. I'm pretty confident that it's fine
in local dialect for each of them to say (33) to Gauri.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{32}
\tightlist
\item
  I went to the same school you're going to.
\end{enumerate}

But it's not fine (again in local dialect) for them to say (34) to each
other.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{33}
\tightlist
\item
  We went to the same school.
\end{enumerate}

Unless we abandon transitivity of identity, the only way to square those
responses is to say that `school' is semantically variable. Should we
worry about that last caveat? Might someone insist that `school' is
univocal, and make the two instances of (33) consistent with (34) by
denying the transitivity of identity. Liebesman and Magidor say in
places that they have a particularist approach to metaphysics, staying
away from big generalisations. Is transitivity of identity one of those
big generalisations that they will be happy to give up to get the
simplest explanation of the data? I hope not, but it is a possible way
out here.

\section{Example Four: Breakfast at
Sweethearts}\label{example-four-breakfast-at-sweethearts}

On the face of it, restaurants look like they should have a similar
metaphysics to books. Liebesman and Magidor deny this, but I'm going to
argue it's actually correct. Actually I'll do this for coffee shops,
where I'm a little more confident, but I think the arguments carries
over. If they think I'm right about coffee shops, but the metaphysics of
coffee shops is different to that of restaurants, well that would be a
fun outcome.

Both coffee shops and books both have the kinda-abstract/kinda-physical
features that generated the i-books/p-books distinction. If in a
particular terminal there are three Starbucks locations, and no other
places to get coffee, then both of (35) and (36) seem like they have
true readings.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{34}
\tightlist
\item
  There is one coffee shop in the terminal, Starbucks.
\item
  There are three coffee shops in the terminal, the Starbuckses by C8,
  C14, and C20.
\end{enumerate}

That looks like we should have an i-shop that makes (35) true, namely
Starbucks, and three p-shops that make (36) true. But Liebesman and
Magidor deny this. They say the witnesses for (36) are finer grained
i-shops, and p-shops aren't really shops. This is a reasonable
hypothesis to investigate. It isn't something we can rule out by general
principles. Indeed, it's parallel to what I think the right story about
schools is. I agree with them that there are no p-school. The
disagreement was that I think there can be different i-schools of
different granularity. If that's my story about schools, I can hardly
say it's an incoherent hypothesis about restaurants and coffee shops.
Still, coherence only means it is worth investigating, not that it's
true. And I'll argue that once we look at the data we'll see it isn't
true.

Liebesman and Magidor argue against the view that `restaurant', or
`coffee shop', sometimes picks out a \emph{building}. And I agree that's
a bad view. P-shops, or P-restaurants, are not buildings. They have one
argument for not identifying P-restaurants with P-buildings; here are
four more.

\begin{itemize}
\tightlist
\item
  The storefront by gate C8 is not a building; it is a room in a
  building.
\item
  The cart by gate C20 is even less of a building.
\item
  When there's outdoor dining the restaurant extends into the street,
  but no building extends into the street.
\item
  Outdoor restaurants seem inadvisable rather than incoherent.
\end{itemize}

But p-shops might be \emph{locations} even if they aren't buildings.
Sometimes they will be campuses, as when a restaurant has multiple not
quite connected buildings. But I'll use \emph{location} as the way of
picking out p-shops.

To argue that p-shops could be locations, I'll work through a
simplified, idealised, version of O'Hare airport. Imagine a version of
O'Hare where the planes run on time, the bags are transferred, and the
food is edible, albeit barely. We'll start with a real fact about
O'Hare: there are 14 Starbucks locations there. Note that `location' is
the word that is actually used on their website talking about their
presence at O'Hare; in this respect I think Starbucks got something
right.

From here on, our imagined O'Hare will be stipulative. I'll make the
following five other assumptions, all of which I suspect are false,
though the world where they are true is closer than the one where O'Hare
has figured out bag transfer.

\begin{itemize}
\tightlist
\item
  There are three Dunkin Donuts locations at O'Hare.
\item
  There are no other coffee shops at O'Hare.
\item
  The Starbucks locations are all administratively unified. They order
  goods collectively, they have no individual managers, they share
  staff, and indeed move staff around when one is busy and another is
  quiet.
\item
  Four of the locations have an express lane out front just for simple
  orders, and a regular counter inside the store.
\item
  Starbucks O'Hare has a unified management. For management purposes,
  they obviously keep track of revenue from different parts of the
  airport. But when they are doing this, they don't count the 14
  locations; instead, they count the 18 counters. (Remember four of the
  stores have two counters.)
\end{itemize}

Now here are our two natural claims about O'Hare, as described.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{36}
\tightlist
\item
  There are two coffee shops at O'Hare: Starbucks and Dunkin.
\item
  There are seventeen coffee shops at O'Hare: 14 Starbuckses and 3
  Dunkins.
\end{enumerate}

For most travellers, (38) is the more natural, though they could make
sense of (37). Liebesman and Magidor say that both of these sentences
are about i-shops at different levels of granularity.

My objection is that the individual Starbucks locations in this story
are not \emph{institutions} in any meaningful sense. They are just
physical locations and nothing more. They don't have staff, or
management, or invoices. Management does keep track of the revenue from
most of them, but by revenue centers we'd say there are 18 Starbuckses,
not 14, since there are 18 counters.

Here's even more evidence that they are not institutions: they aren't
movable. Without anyone identified as the staff of the location at C14,
\emph{it} can't move to B9. Starbucks O'Hare could close the C14
location and open a new ;pcayopm at B9, but that would be a
close-and-open, not a relocation. This all depends on the five
assumptions I made. If, as I suspect happens in reality, there is a
staff primarily associated with the location at C14, and when that
location closes the new location at B9 is entirely staffed by those
people, that would be naturally called a relocation. Since a location
can't really relocate, that would be evidence that the store is really
an i-entity, not a location. But if there is no staffing continuity
within a location, there is nothing to move. I say that's because it is
a location, which cannot move.

Back in reality, someone who says (38) to their caffeine-deprived travel
companions need not know about, or be making a claim about, the internal
organisation of the Starbuckses at O'Hare. It could be true whether an
individual Starbucks location has the kind of staffing continuity that
would let us even make sense of it moving. And it does not seem to be a
different claim in the worlds where it does, or does not, have staffing
continuity. So, I conclude, (38) is a claim about p-shops, not about
particular kinds of i-shops.

\section{Conclusion}\label{conclusion}

This is a really fun book, and as I've been stressing, thinking through
what it says can affect how we think about things that are central to
some of our lives: schools and coffee shops. I'm sure it also has
implications for other, less important things, like municipalities or I
guess minds. So I thoroughly recommend it, and I hope it gets a wide
readership.

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\protect\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Fairchild2019}
Fairchild, Maegan. 2019. {``The Barest Flutter of the Smallest Leaf:
Understanding Material Plenitude.''} \emph{The Philosophical Review} 128
(2): 143--78. doi:
\href{https://doi.org/10.1215/00318108-7374932}{10.1215/00318108-7374932}.

\bibitem[\citeproctext]{ref-LM2025}
Liebesman, David, and Ofra Magidor. 2025. \emph{Property Versatility and
Copredication}. Oxford: Oxford University Press.

\bibitem[\citeproctext]{ref-Sider1996-SIDATW}
Sider, Theodore. 1996. {``All the World's a Stage.''} \emph{Australasian
Journal of Philosophy} 74 (3): 433--53. doi:
\href{https://doi.org/10.1080/00048409612347421}{10.1080/00048409612347421}.

\end{CSLReferences}



\noindent Draft of April 7, 2026


\end{document}
