---
title: "Persuasion in Daylight"
abstract: |
  Recent models of industry propaganda show that an interested party can lead an audience to false beliefs by sharing only true results. But the audiences in those models update on the content of what they are shown and not on the fact that they were shown it; they are, in the economists' term, cursed. I ask what survives when the audience is not. The answer divides the strategy in two. *Selection*, choosing which existing results to pass on, is neutralised by an audience that reasons about the process; its power depends on the audience's ignorance of what was generated, and transparency reforms remove that ignorance. *Design*, choosing which experiments come into existence, is not neutralised. A fully informed, fully rational audience that knows the experiment was chosen to move it is still moved: its beliefs stay calibrated while the distribution of its decisions shifts in the designer's favour. Nothing false is believed, nothing is hidden, and reason is engaged rather than bypassed; the accounts of deception and manipulation that classify design as such do so on grounds that do not track what the designer takes. I argue that the wrong is exploitation: the designer uses the audience's dependence on him for evidence, and her lack of power over the terms, to appropriate the value of information. Two institutional consequences follow. Pre-registration and disclosure, which kill selection, are the commitment device that design requires, so they relocate the problem rather than solving it. And the audience's counter-moves are authority over the design or advance commitment to a demanding standard of proof, each of which forces the designer towards the informative experiment and each of which is available only to receivers with institutional power, which is where the exploitation account says the remedy has to lie.
author:
  - name: Claude
    note: "Draft written by Claude (Fable 5.1) for Brian Weatherson's in-house blog experiment. Not for circulation."
date: 29 September 2026
categories:
  - epistemology
  - ethics
  - philosophy of science
  - claude-draft
draft: true
execute:
  echo: false
  warning: false
  message: false
bibliography:
  - ../../brian-quarto.bib
  - daylight.bib
citation: false
format:
  html:
    css: ../trad_defn.css
  pdf:
    output-file: "Persuasion in Daylight"
    include-in-header:
      - file: ../quarto2024.tex
      - text: |
         \cehead{
                 Persuasion in Daylight
                 }
    include-after-body:
        text: |
          \noindent Draft of September 2026.
---

```{r setup}
suppressMessages({library(dplyr); library(tidyr); library(purrr); library(ggplot2); library(knitr)})
mu <- 0.3; t0 <- 0.5
sens <- 0.8; fpr <- 0.3; N <- 4
```

# Introduction

In the early 1950s the American tobacco industry decided to fight science with science. Rather than deny that smoking caused cancer, it funded research, promoted the studies that happened to go its way, and let a growing body of contrary evidence be met with a manufactured sense that the question remained open [@OreskesConway2010]. Nobody had to lie. The studies that were promoted were real studies. The strategy worked for decades.

A series of recent models from philosophy of science explains why. In the models of @WeatherallOConnorBruner2020, a propagandist who forwards to policymakers only those results, produced by honest scientists, that favour the industry's position can drive the policymakers to near-certainty in the wrong theory while the scientists themselves converge on the right one. @Mohseni2022 show that a journalist who curates studies according to ordinary newsroom norms produces the same distortion without meaning to. @HolmanBruner2017 show that an industry that funds the scientists whose methods happen to yield favourable results can bias a community's consensus without corrupting any individual in it. @OConnorFreeborn2025 show that funding accurate research on *other* causes of a harm shifts blame away from the industrial cause. The common lesson, which the authors draw explicitly, is that fraud is unnecessary. True results suffice.

There is something these models share that their authors also note, but which has not received the attention it deserves. Their audiences are rational about what they are told and irrational about the fact that they are being told it. A policymaker in the Weatherall–O'Connor–Bruner model receives a study from the propagandist and conditionalises on its content exactly as she would had the study come to her at random. She does not ask what the propagandist's forwarding it tells her about the studies he did not forward. In the language of @EysterRabin2005, she is *cursed*: she correctly predicts what the propagandist does but ignores the correlation between what he does and what he knows. The authors flag as future work the question of what happens when the audience can "adjust their updating rule to accommodate the possibility that some of the evidence they receive is exaggerated, filtered, or otherwise intended to mislead" [@WeatherallOConnorBruner2020].

This paper takes up that question. The answer, I will argue, splits the tobacco strategy down the middle. One half of it, which I will call *selection*, consists in choosing which already-existing results to pass on. Against an audience that reasons about the process, selection is neutralised. This is the unravelling result of @Grossman1981 and @Milgrom1981: a sceptical audience treats silence as bad news, so the sender ends up revealing everything or being treated as if he had. Selection's power depends on the audience's ignorance of what exists to be selected from, and the transparency reforms of the last two decades, trial registries, pre-registration, mandatory disclosure, are devices for removing that ignorance. The other half, which I will call *design*, consists in choosing which experiments come into existence: what to measure, whom to enrol, what to compare against, how long to run. Against an audience that reasons about the process, design is not neutralised. This is the central result of @KamenicaGentzkow2011. A sender who commits in advance to an experiment, whose design the audience sees and understands and knows to have been chosen in the sender's interest, can still move the audience's decisions in his favour. He does this without inducing a single belief the audience should not hold. Her posterior after each result is exactly what the evidence warrants. What changes is not the accuracy of her beliefs but the frequency with which she decides as he wants.

The economics is not new, and I will present it briskly. The paper's contributions are three, and I want to be clear about which parts are mine. The first is the diagnosis: that the philosophical models of persuasion-by-true-results are models of cursed audiences, and that removing the curse divides the phenomenon into two mechanisms that behave differently under every reform that has been proposed. The second is an argument about what is wrong with the mechanism that survives. Design is not lying or deception in any sense that requires a false belief, not misleading in the sense the literature on misleading with truths has analysed, and not manipulation on accounts that require covertness, bypassing reason, or a defective mental state. Some accounts of deception and manipulation do classify it as such, and I will not pretend otherwise; but they do so on the strength of the sender's attitude or the system's payoff structure, and what those accounts are tracking, when they track anything that varies with the design, is what the sender takes rather than what he does to the receiver's mind. The right category, I will argue, is exploitation, in the form that @Wertheimer1996 calls mutually advantageous exploitation: the audience gains a little, consents to the arrangement, and is nonetheless wronged, because the sender uses her dependence on him for evidence, and her lack of power over the terms, to appropriate the value of information. The third contribution is institutional. The transparency reforms which defeat selection are the commitment device that design requires, so they relocate the problem rather than solving it, and make the residue harder to see because everything is now by the book. The counter-moves that work against design, authority over what gets studied and advance commitment to a demanding standard of proof, look from outside like obstruction or closed-mindedness, and neither is available to an individual receiver deciding case by case. That is what the exploitation account predicts: the wrong lies in an imbalance of power over the terms, and the remedy lies with receivers who have institutional power, not with the rationality of receivers who do not.

# Two ways to bias a body of evidence

Fix an audience with a question and a decision that turns on it. A regulator must decide whether a drug works well enough to approve. A judge must decide whether a defendant is guilty. A journal editor must decide whether a paper's result is real. A voter must decide whether a policy has the effects claimed for it. In each case there is a party with an interest in the decision going one way regardless of the answer to the question, and that party has some control over the evidence the audience sees.

There are two points at which that control can be exercised. The first is after results exist. The sender has a stack of studies and decides which to hand over. The file drawer, cherry-picking, "selective sharing" in the sense of @WeatherallOConnorBruner2020, the fair-minded journalist who finds one study for each side, the literature review that cites what supports its conclusion: all of these are choices about which existing results to transmit. Call this *selection*.

The second point is before results exist. The sender decides which experiments to run. He chooses the endpoint (a surrogate marker or the outcome that matters), the comparator (placebo, or the rival drug at a dose chosen to disadvantage it), the population (the patients most likely to respond), the duration (long enough to show benefit, short enough to miss harm), the sample size (large enough to reach significance if the effect is there, small enough that a null result is uninformative). Every one of these is a choice about what the world will be asked, and therefore about what it can answer. Call this *design*.

The distinction is not between honest and dishonest experiments. Everything I say about design assumes the experiments are competently run, accurately reported, and reported in full. Nor is it a distinction between weak and strong evidence in some absolute sense. It is a distinction in the timing and the object of the sender's choice: selection is a choice among realised results; design is a choice among experiments, made before any result is known.

Real cases mix the two, and some of the most striking documented findings about industry-sponsored research are design findings. @Heres2006 examined head-to-head trials of second-generation antipsychotics and found that ninety percent of them favoured the sponsor's drug, so that olanzapine beat risperidone in trials sponsored by olanzapine's maker, risperidone beat quetiapine in trials sponsored by risperidone's, and quetiapine beat olanzapine in trials sponsored by quetiapine's. The mechanism was not fabrication and only partly reporting; it was dose selection, comparator choice, and the choice of outcome measures. @Safer2002 catalogued the same devices, and @Sismondo2008 reviews the literature that finds sponsorship effects in the design of trials rather than in their conduct. The Cochrane review of industry sponsorship [@Lundh2017] finds that industry-funded studies reach favourable conclusions more often than independently funded ones, and that the difference is not explained by the standard risk-of-bias measures, which is what one would expect if the residual mechanism were design rather than conduct or reporting. The case @HolmanBruner2017 use to introduce industrial selection is a design case: trials of anti-arrhythmic drugs that measured arrhythmia suppression showed benefit, and it was only trials that measured mortality that revealed the drugs were killing people [@Echt1991; see @FlemingDeMets1996 on surrogate endpoints generally].

My question is which of these two channels survives an audience that is not cursed. To answer it I need to say what an uncursed audience is.

# Cursed audiences

Here is a case that will serve throughout. A regulator must decide whether to approve a drug. Her prior probability that the drug works is $0.3$, and she approves if and only if her posterior probability that it works is at least $0.5$: she gets one unit of value from a correct decision and nothing from an incorrect one, so this is the threshold at which approval is the better bet. The sponsor wants approval whether or not the drug works.

Suppose first that the sponsor runs four identical studies. Each study returns a positive result with probability $0.8$ if the drug works and with probability $0.3$ if it does not, and the studies are independent conditional on whether the drug works. The sponsor then reports every positive result and files away every negative one.

A regulator who sees $k$ positive reports and treats them as the whole record computes the posterior odds that the drug works as the prior odds times $(0.8/0.3)^k$. A single positive report takes her to a posterior of $0.53$, over her threshold. The chance that at least one of four studies is positive is $0.9984$ if the drug works and $0.76$ if it does not. So she approves with probability $0.83$, and her probability of making the correct decision, approving working drugs and rejecting the others, is $0.47$. That is worse than the $0.7$ she would achieve by ignoring the sponsor altogether and rejecting everything. This is the phenomenon the Weatherall–O'Connor–Bruner model exhibits at scale: a rational updater who sees a selected sample and treats it as unselected ends up with beliefs that are systematically wrong, and, in the aggregate, worse than no evidence at all.

The regulator's mistake has a precise description. @GrunwaldHalpern2003, building on @Shafer1985, distinguish conditioning in a *naive space*, whose points are the possible contents of an observation, from conditioning in a *sophisticated space*, whose points also specify the protocol by which the observation was produced. Naive conditioning gives the same answer as sophisticated conditioning only when the protocol satisfies a condition they call "coarsening at random": roughly, when the probability of being shown a given piece of evidence does not depend on the state beyond what the evidence itself says. The sponsor's protocol violates that condition as badly as a protocol can. Whether a study is shown depends on its result, and so on the state. The regulator who conditions in the naive space is not reasoning badly from her evidence; she is reasoning from the wrong evidence. Her total evidence is not "study 3 was positive" but "the sponsor showed me study 3, and it was positive, and he showed me nothing else" [see @Good1967 on the principle of total evidence, and @Sober2009; @Kotzen2012 on observation selection effects].

@EysterRabin2005 give the same mistake a game-theoretic name. A *cursed* player correctly forecasts the distribution of the other players' actions but underestimates, in the fully cursed case ignores, the extent to which those actions depend on the other players' private information. The regulator forecasts that the sponsor will forward studies; she fails to condition on the fact that which studies he forwards depends on what all the studies said. Eyster and Rabin introduced the concept to explain the winner's curse and the persistence of trade under adverse selection, both cases where people fail to ask "what does the fact that this is on offer tell me?" The audiences in the philosophy of science models fail to ask the same question.

I want to be clear that this is not a criticism of those models. Real audiences are cursed. In laboratory tests of disclosure games, receivers are systematically insufficiently sceptical about what is not disclosed [@JinLucaMartin2021; see also @Frechette2022], and the historical record that motivates the models is a record of real policymakers being moved. If the question is how the tobacco strategy worked on the audiences it actually faced, the models answer it. My question is different. It is whether rationality protects an audience from being moved by true evidence, and to answer that one has to remove the curse and see what remains.

# Selection in daylight

Uncurse the regulator. She knows that four studies were run. She knows the sponsor's reporting policy. She sees $k$ positive reports and infers that the other $4-k$ were negative. Her posterior is now the one she would have reached had all four studies been laid in front of her: the prior odds times $(0.8/0.3)^k (0.2/0.7)^{4-k}$. She approves only when at least three of the four studies are positive. The sponsor's approval rate falls from $0.83$ to $0.30$, and her accuracy rises from $0.47$ to $0.89$, which is exactly the accuracy she would achieve from four honestly reported studies. Selection has bought the sponsor nothing.

This is the unravelling argument, and it is fully general. @Grossman1981 and @Milgrom1981 showed that when a sender holds verifiable information, so that he can withhold but not fabricate, and the receiver is sceptical, so that she interprets what is not shown as the worst thing consistent with what is, the sender's best response is to show everything, because at every stage the sender with the best undisclosed news prefers to disclose it rather than be pooled with those who have worse. The equilibrium unravels to full disclosure. @MilgromRoberts1986 showed the same result obtains even with a naive receiver if there are competing senders with opposed interests, each of whom reveals what the other conceals. Against a sceptical receiver, or between adversarial senders, choosing what to reveal is not a lever.

There is one condition that matters enormously, because it is the condition the transparency reforms target. Unravelling requires that the receiver know, or be able to infer, what exists to be revealed. If she does not know whether the sender ran four studies or none, silence pools "I ran studies and they were negative" with "I ran no studies", and the sender with bad news can hide behind the second [@Dye1985; @JungKwon1988]. Selection then retains some power, and the power grows with the receiver's uncertainty about the sender's evidential endowment. @Henry2009 models a researcher who chooses how many experiments to run and which to disclose to a receiver who does not observe the count, and finds that the researcher must sometimes reveal unfavourable results to establish credibility, "the cost of proving your honesty". @ArieliStewart2025 show that if the receiver is sufficiently uncertain about the sender's capacity to experiment, selective disclosure can achieve everything that design (in the sense of the next section) achieves. So the claim that selection is neutralised needs stating carefully: selection's power is a function of the receiver's ignorance of the process, and it goes to zero as that ignorance does.

That is precisely why the reforms of the last twenty years take the form they do. Trial registration requires the sponsor to declare a study before it is run, so that the regulator knows it exists whatever its result. Pre-registration of analysis plans fixes the endpoint and the test before the data arrive, so that the sponsor cannot search the data for a favourable specification and report it as if pre-planned [@Nosek2018]. Registered reports commit a journal to publishing a study on the strength of its design, before results, so that the file drawer has nothing in it [@Chambers2013]. Every one of these is a device for making the count known, which is to say for restoring the condition under which unravelling works. @Felgenhauer2021 models pre-registration explicitly as a commitment device that deters selective reporting. The philosophy of science literature on publication bias and self-correction recommends the same instruments for the same reason [@Romero2016; @Heesen2018].

The Weatherall–O'Connor–Bruner model has a second treatment, "biased production", in which the propagandist runs his own studies and publishes only the favourable ones, and a striking finding within it: the propagandist does best by splitting his budget into the smallest possible studies, because small studies are more often spuriously favourable. This looks like a design result, since it concerns how experiments are configured. It is not. The small studies do their work only because the unfavourable ones are then withheld from a receiver who does not know how many were run. Against a receiver who knows the count and sees every result, the partition of a fixed number of draws into studies makes no difference to her total evidence, and the strategy buys the sponsor nothing at all. What I will now argue is that design in the proper sense, the choice of experiment under a regime where the receiver sees the choice and every result, has a power that no amount of scepticism removes.

# Design in daylight

Now suppose the regulator is as sophisticated as one could wish. She knows what experiment the sponsor will run before he runs it. She sees every result. She knows the sponsor chose the experiment to maximise the chance of approval. She updates by conditionalisation in the sophisticated space, on the full protocol. There is nothing hidden from her.

Suppose the sponsor may choose any experiment whose outcome depends only on whether the drug works: a test, of any design, whose statistical properties the regulator will know. In particular he may choose a test with a single pass/fail outcome, such that every working drug passes and a drug that does not work passes with probability $q$. Think of a surrogate endpoint chosen for its sensitivity: a marker that every effective drug moves, and that a certain fraction of ineffective drugs also move.

The sponsor chooses $q$. If he sets $q = 0$ the test is perfectly informative: the regulator learns exactly whether the drug works, approves with probability $0.3$, and is never wrong. If he sets $q = 1$ the test is uninformative, the regulator's posterior stays at $0.3$, and she never approves. In between, a pass takes the regulator's posterior to $0.3/(0.3 + 0.7q)$, and she approves on a pass if and only if this is at least $0.5$, which is to say if and only if $q \le 3/7$. The sponsor sets $q = 3/7$. Now every working drug passes, and $43$% of the drugs that do not work pass too. The regulator, seeing a pass, computes a posterior of exactly $0.5$, and approves. Seeing a fail, she computes a posterior of $0$ and rejects. She approves $60$% of drugs, though only $30$% work.

Nothing here is hidden, and nothing she believes is false or ill-founded. Among the drugs she approves, exactly half work, which is what she believes when she approves. Her credences are calibrated in the strict sense: conditional on each thing she does, the frequency with which she is right is the credence on which she acted. Her expected accuracy, the probability of making the correct decision, is $0.7$. That is the same accuracy she would achieve with no evidence at all, since with no evidence she rejects everything and is right $70$% of the time. (This uses the convention that she approves when exactly indifferent; if she does not, the sponsor sets $q$ just below $3/7$ and leaves her with as little as he likes. Nothing turns on the knife-edge.) The sponsor has chosen an experiment that delivers to the regulator, in expectation, as close to nothing as he pleases, while delivering to himself twice the approvals he would get from an honest and informative test.

This is the "Bayesian persuasion" result of @KamenicaGentzkow2011, with the numbers of their prosecutor example (a prosecutor who gets sixty percent convictions from a population thirty percent guilty). Their general theorem characterises exactly when a sender who commits to an experiment benefits from doing so: whenever the concave closure of the sender's payoff, taken as a function of the receiver's belief, lies strictly above that payoff at the prior. The intuition in the binary case is that the receiver's decision is a step function of her belief, so the sender benefits by pushing her belief just over the step as often as possible and letting it fall as far as it likes otherwise. The optimal experiment is the one that makes the receiver exactly indifferent whenever she takes the action the sender wants, and certain whenever she takes the action he does not. More generally, a sender who cares only about the action never induces a belief at which the receiver takes his preferred action more confidently than she must, because that confidence is wasted on him and could have been spread over more cases. The survey by @Kamenica2019 and the unification by @BergemannMorris2019 show how far this extends.

@tbl-twobytwo assembles the numbers for the four cases. The rows are the two channels; the columns are the two audiences.

```{r twobytwo}
#| label: tbl-twobytwo
#| tbl-cap: "The sponsor's approval rate and the regulator's accuracy (probability of a correct decision) under each channel and each kind of receiver. Prior that the drug works: 0.3; approval threshold: 0.5. Selection: four studies each with sensitivity 0.8 and false-positive rate 0.3, only positives reported. Design: the sponsor's optimal single-outcome test. With no evidence the regulator's accuracy is 0.7."
post_full  <- function(k) { lg <- mu * dbinom(k, N, sens); lb <- (1 - mu) * dbinom(k, N, fpr); lg / (lg + lb) }
post_naive <- function(k) { lg <- mu * sens^k; lb <- (1 - mu) * fpr^k; lg / (lg + lb) }
sel <- expand_grid(state = c("G", "B"), k = 0:N) |>
  mutate(pr = if_else(state == "G", mu, 1 - mu) * dbinom(k, N, if_else(state == "G", sens, fpr)),
         cursed = post_naive(k) >= t0, sophisticated = post_full(k) >= t0) |>
  pivot_longer(c(cursed, sophisticated), names_to = "receiver", values_to = "approve") |>
  group_by(receiver) |>
  summarise(approval = sum(pr * approve),
            accuracy = sum(pr * if_else(state == "G", approve, !approve)), .groups = "drop") |>
  mutate(channel = "Selection")
q_star <- mu * (1 - t0) / ((1 - mu) * t0)
des <- tibble(receiver = c("cursed", "sophisticated"), channel = "Design",
              approval = mu + (1 - mu) * q_star, accuracy = mu + (1 - mu) * (1 - q_star))
bind_rows(sel, des) |>
  mutate(receiver = if_else(receiver == "cursed", "Cursed receiver", "Sophisticated receiver")) |>
  pivot_wider(names_from = receiver, values_from = c(approval, accuracy)) |>
  transmute(Channel = channel,
            `Approval (cursed)` = sprintf("%.2f", `approval_Cursed receiver`),
            `Accuracy (cursed)` = sprintf("%.2f", `accuracy_Cursed receiver`),
            `Approval (sophisticated)` = sprintf("%.2f", `approval_Sophisticated receiver`),
            `Accuracy (sophisticated)` = sprintf("%.2f", `accuracy_Sophisticated receiver`)) |>
  kable(align = "lcccc")
```

Two features of the table are the point of the paper. First, the columns differ for selection and not for design. Sophistication is a complete cure for selection and no cure at all for design, and the reason is structural. At the moment the sponsor chooses which studies to forward, he knows their results and the regulator does not; his choice is a function of private information, and a receiver who ignores that is cursed. At the moment the sponsor chooses which experiment to run, in the case as I have set it up, he knows nothing the regulator does not. His choice is a function of his interests, which she knows, and of the prior, which she shares. There is no private information for the choice to leak and hence nothing for her to be cursed about. She is already conditioning on everything. That is why the sophisticated column for design equals the cursed one.

Second, compare the two sophisticated cells. Against a sophisticated receiver, a sponsor who runs four honest studies and cherry-picks gets $30$% approvals and leaves the regulator with accuracy $0.89$; a sponsor who designs one test gets $60$% approvals and leaves her with $0.7$. Design dominates selection for the sponsor, and the regulator is worse off under design than under selection-with-sophistication. The cherry-picker who is found out has given the regulator four studies' worth of information. The designer who is fully understood has given her none.

I have assumed the sponsor has no private information when he designs. That is the clean case, and it is the case that isolates the mechanism, but it is not the realistic one: a drug sponsor at the design stage of a pivotal trial has preclinical and early-phase data the regulator has not seen, and a prosecutor deciding what to investigate knows things about the case the judge does not. When the sender is privately informed, his choice of experiment is itself a signal, and the receiver must condition on it. That reintroduces a way of being cursed on the design side, and it changes the sender's problem, since a design that would be optimal for an uninformed sender may now reveal his type. The economics of this case is worked out by @PerezRichet2014, @Hedlund2017, and @KoesslerSkreta2023, and the upshot for present purposes is that the sender's gain from design survives it: there are equilibria in which the receiver correctly infers everything the choice of design reveals and is still moved by the design. The informed sender has, if anything, one more instrument than the uninformed one, since he can choose designs whose informativeness depends on what he privately knows. What the informed case does not do is restore the receiver's position by giving her something to be sceptical about. Conditioning on the choice of design, like conditioning on the choice of what to disclose, is something the sophisticated receiver already does; and unlike the disclosure case, doing it does not leave the sender with nothing to gain. I therefore treat the uninformed case as the base case and take the informed case as a complication that strengthens rather than weakens the sender's hand.

One further feature inverts a natural assumption. Design requires daylight. The persuasion result assumes the sponsor commits to the experiment and cannot hide its result, and one might think a sponsor who could instead experiment privately and disclose selectively would be better off, having more options. He is not. @FelgenhauerLoerke2017 show that private experimentation with selective disclosure yields a lower probability of persuasion, and a better-informed receiver, than public experimentation; @Frechette2022 state the general contrast, that with verifiable information commitment to an experiment *reduces* what is transmitted, because without commitment the sender unravels and with it he can garble; and @DaiFudenbergPei2025 show that adding secret follow-up experiments to a committed design never helps the sender. The sponsor should welcome the reforms. Registration, pre-specification, mandatory reporting: these take away the selection channel, which a sophisticated receiver had already neutralised, and establish the commitment that makes the design channel work. Daylight is the designer's friend.

# Is it deception? Is it manipulation?

The regulator has been moved. I want to ask what has been done to her, and the honest answer is that the existing vocabulary gives two kinds of verdict. Accounts of deception and manipulation that locate the wrong in a defect of the target, a false belief, a belief that falls short of the target's ideals, an influence she is unaware of or that bypasses her reason, exclude design, because the regulator exhibits no such defect. Accounts that locate the wrong in the influencer's attitude, or in the payoff structure of the signalling system, can include it. I will argue that the second kind of verdict, where it applies, is tracking something real but not what the designer does to the receiver's mind; it is tracking, without naming it, what he takes from her.

## Deception and misleading

Deception in the standard sense is the intentional production of a false belief [@ChisholmFeehan1977; @Carson2010]. No false belief is produced. The regulator's belief after a pass, that the drug works with probability $0.5$, is correct: half of the drugs that pass work. One might say she is kept less informed than she could have been. But keeping someone ignorant is not deceiving them, and in any case the designer does not keep her ignorant of anything that exists. He arranges for less to exist.

The literature on misleading with truths analyses a more specific failure. @Saul2012 treats misleading as conveying a falsehood without saying it; @Stokke2016 analyses it as offering a true but partial answer to the question under discussion that invites a false complete answer. Cherry-picking is misleading in exactly this sense: "study 3 was positive", offered in answer to "does the drug work?", invites the completion "and the others were too", which is false. That is why selection fails against a receiver who declines the invitation. Design is not like this. The sponsor asks the world a question, "does the drug move this marker?", reports the world's complete answer, and the regulator knows which question was asked and what its answer bears on. There is no partial answer and no false completion. What there is, is a self-serving choice of question. Stokke's apparatus lets us say exactly why that is not misleading: the receiver's posterior on *her* question, "does the drug work?", is what the evidence on the sponsor's question warrants, and she knows it. @Fallis2015 defines disinformation as information "likely to create false beliefs" that has the function of doing so, and explicitly includes true content that is selectively emphasised; on his definition the designed test is not disinformation, because it is not likely to create false beliefs. It creates calibrated ones.

There is, however, a formal tradition on which the verdict goes the other way, and I want to state it fairly rather than argue around it. @Skyrms2010 defines a signal as carrying *misinformation* when it raises the receiver's probability of a state that does not obtain, and as *deceptive* when it is misinformation that systematically benefits the sender at the receiver's expense; @FallisLewis2019 refine the definition so that the signal must move the receiver away from the truth relative to what she would otherwise have believed. The designed test passes $43$% of the drugs that do not work, each such pass raises the regulator's probability that the drug works from $0.3$ to $0.5$, and the passes systematically benefit the sponsor at her expense. On these definitions the design *system* is deceptive. I accept the verdict as a verdict about the system. What I want to notice is what it is not. It is not a verdict that any belief the regulator forms is one she ought not to form; the definitions are stated at the level of the signalling system precisely so that they do not require that. And the feature that makes the system deceptive rather than merely noisy, on Skyrms's definition, is the payoff clause: the misinformation benefits the sender at the receiver's expense. A cheap screening test with the same sensitivity and specificity, adopted by a health service for budgetary reasons, produces misinformation at the same rate and is not deceptive on Skyrms's definition, because no one profits. So the formal definition, applied here, is picking out a wrong that lies not in what the receiver comes to believe but in who gains from the arrangement. That is the wrong I will call exploitation, and the Skyrmsian definition is, I think, better read as an early formal recognition of it than as a reason to assimilate design to the deception of the philosophical literature, where a false belief is the whole point.

The value-of-information framework I invoked earlier can be pressed the same way. The regulator is denied expected accuracy she could have had; on a veritistic measure she is worse off than she might have been. That is true, and I will rely on it. But "denied accuracy relative to an available experiment" is a comparative property of the experiment, and calling it "misleading" stretches the word past the point where it does any work. Every experiment short of the most informative one available denies the receiver some accuracy she could have had. What is distinctive here is that the denial is chosen, by a party she depends on, for his gain.

## Manipulation

The literature on manipulation is less unified, and I follow the map in @NoggleSEP [see also @Noggle2025].

On the *covert influence* account of @Susser2019, manipulation is intentionally and covertly influencing someone's decision-making by exploiting their decision-making vulnerabilities. Design fails the covertness condition outright. The regulator knows everything. On *bypassing* accounts [@Wood2014], manipulation influences by means that do not engage the target's reason: playing on emotions, habits, biases. Design fails this condition as completely as an influence can. The regulator is moved by conditionalising on evidence and maximising expected value. @Levy2019 has argued that nudges are not manipulative because they present reasons to mechanisms that respond to reasons; whatever one thinks of that argument for nudges, it succeeds for design, where the mechanism is explicit Bayesian updating. On the *ideals* account [@Noggle1996; refined by @Barnhill2014], manipulation is an attempt to induce a belief, desire, or emotion that falls short of the ideals governing that state, false belief being the paradigm. The regulator's belief after a pass does not fall short of any ideal, by her lights or the sponsor's. Barnhill adds that the induced state must be against the target's interest; the regulator's *decision* is against her interest relative to a better-informed alternative, but her mental states are not defective, and the ideals account needs a defective state. @Cohen2018 argues that deception is a species of manipulation; if so, then design, which is not deception in his sense, is not thereby manipulation either.

The accounts that include design are those on which manipulation is a matter of the influencer's attitude towards the reasons he supplies. @Gorin2014b argues, with cases in which an influencer supplies entirely good reasons for entirely ulterior ends, that a manipulator need not bypass or subvert reason at all; what marks manipulation is that the influencer is indifferent to whether the reasons he gives are good ones, judging them by their efficacy rather than their quality. @Klenk2022 offers a definition in the same spirit: an influencer manipulates when he aims to get the target to do or believe something by a method and is careless about whether that method reveals to the target the reasons there are for doing or believing it. The sponsor who sets $q = 3/7$ chose that test for its efficacy in producing approvals. He would have chosen it whether or not it was informative, and he would have chosen a different test had a different one been more effective. That is Gorin's indifference and Klenk's carelessness, and I do not think it can be argued away by pointing out that the test happens to reveal every reason it generates. On these accounts, design is manipulation.

Suppose we accept that. What I want to argue is that the verdict, though correct by these accounts' lights, does not track the harm. Consider two sponsors with the same attitude. Both choose experiments purely by their efficacy in producing approvals and are indifferent to informativeness. The first faces a regulator with a threshold of $0.5$ and sets $q = 3/7$. The second faces a regulator who, for reasons of her own, has committed to a threshold of $0.95$, and finds that the most effective test he can run is one with $q = 0.023$, which is very nearly the fully informative test. On Gorin's and Klenk's accounts both sponsors manipulate, and to the same degree, because the attitude is the same. But the first regulator has been left with nothing and the second with nearly everything. Whatever is objectionable in the sponsor's attitude, it is not what makes the first regulator worse off than the second. Conversely, consider a disinterested but cost-conscious health service that adopts the $q = 3/7$ screening test because it is cheap. It has no manipulative attitude at all; and the patients screened by it are exactly as under-informed as the first regulator. What varies with the design, and what the first regulator has a complaint about that the second does not, is how much of the value of information she was left with and who took the rest. The attitude accounts of manipulation, where they apply to design, are picking out the sender's readiness to do that. They are not picking out the doing of it. To name the wrong done to the regulator we need a category that is about the taking, and that category is exploitation.

@Buss2005 argued that the wrong of an influence need not consist in what it does to the target's rational agency, and @GTsai2014 that an influence can wrong its target while working entirely through reasons. Design is a case in point, though the wrong is not the one either had in mind. It is not to be found by looking at what the sender does to the receiver's mind. It is to be found by looking at what he takes from her.

# Exploitation

Here is what the sponsor takes. With no evidence the regulator's expected accuracy is $0.7$. With a perfectly informative experiment it would be $1$. The difference, $0.3$, is the value of information to her: the surplus that experimentation makes available. The sponsor, in choosing the experiment, chooses how that surplus is divided. He can run the informative test and hand it all to her, at the cost of approvals. He can run the uninformative test and destroy it. Or he can run the test with $q = 3/7$, which leaves her with none of it and converts the rest into approvals for him. He chooses the last. In the general case the sender's optimal experiment need not leave the receiver with nothing, but it never gives her more confidence than the action he wants requires: at every result on which she acts as he wants, she is left indifferent between that action and the next one down. The sender appropriates the value of information.

This has the structure that @Wertheimer1996 calls mutually advantageous exploitation. The receiver is not made worse off than she would be by no transaction: her accuracy is $0.7$ either way, and in the general case she weakly gains from the experiment relative to none. She consents, in the sense that she relies on the sponsor's evidence voluntarily and would rather have it than not. And yet the transaction is unfair to her in the way Wertheimer's cases are unfair: the party with the power to set the terms has set them so that he captures the cooperative surplus and she captures none. Wertheimer's central puzzle is how a consensual transaction that leaves both parties no worse off can nonetheless be a serious wrong, and his answer, that consent and mutual advantage may defeat a claim to interference and a right to better terms without defeating the judgement that the terms are unfair, transfers directly.

Two more recent accounts fit the case even better. @Valdman2009 holds that wrongful exploitation is the extraction of excessive benefit from someone who cannot, or cannot reasonably, refuse one's offer, and insists that this wrong is not reducible to harm, coercion, or deception. The regulator cannot reasonably refuse. She must decide, and she must decide on the evidence that exists; she has no independent capacity to run the trial and no other party will. That is a specific instance of the general fact of epistemic dependence [@Hardwig1985]: for most of what we need to know, we depend on others to produce the evidence, and the dependence is a vulnerability. @Vrousalis2013 makes vulnerability central: exploitation is instrumentalising another's vulnerability to extract a benefit, within a systematic relationship, and its wrong is a form of domination that consent does not dissolve. The relationship between a regulator and the industry it regulates is systematic in exactly Vrousalis's sense, and the sponsor who chooses $q = 3/7$ is using the regulator's dependence on him, together with her own rationality, as the instrument by which approvals are extracted. @Wood2014 [see also @Wood1995], in the same chapter that rules design out of manipulation on the bypassing account, characterises exploitation as the use of another's weakness or need for one's own advantage, and stresses that it is compatible with the exploited party's consenting and benefiting. Design is exploitation on all three accounts.^[The phrase "epistemic exploitation" has an established use, due to @Berenstain2016, for the unpaid labour of educating the privileged that is demanded of members of marginalised groups. That is a different phenomenon, and I avoid the phrase.]

The account also says when design is *not* exploitative, and I want to spell this out, because it answers two objections that would otherwise be decisive. The first is that the account overgenerates. Job candidates choose which referees to solicit; firms choose which product demonstration to run; scientists choose the experiment most likely to yield a publishable result; a student may choose which examination to sit. All of these are self-interested choices about what evidence will exist, made for a receiver who depends on the sender for it. If all of them are exploitation, the category is too wide to be interesting. The second is that the exploitation claim and the remedy I will propose in the next section pull against each other. If the receiver can recover the value of information by committing to a demanding threshold, then she is not, after all, someone who cannot reasonably refuse; her vulnerability is her decision rule, not her dependence, and Valdman's condition fails.

Both objections have the same answer, and it is the answer exploitation theory gives generally: exploitation is a matter of *power over the terms*, and it is mitigated exactly to the extent that the vulnerable party has that power. A worker with outside options is less exploitable than one without; a worker with a union that can commit to a strike is less exploitable still. In the same way, a receiver who can dictate the design, or who can credibly commit to a standard the designer must meet, has power over the terms of the evidential exchange and is exploited only to the degree that she cannot or does not use it. Everyday evidence-gathering is arranged so that receivers have this power. The examiner sets the examination; the student does not choose which questions to be asked. The employer decides what the interview will test, asks for references of a specified kind, and imposes a probationary period. The consumer who is shown a demonstration knows it was chosen to impress and has, in a competitive market, other sellers to consult. Where design authority sits with the sender, as with references, the practice has evolved discounting conventions that everyone knows. These cases are not counter-examples to the account; they are what the account predicts a well-arranged evidential practice looks like. Where they involve residual exploitation, it is mild, because the receiver's power over the terms is large. The cases that are seriously exploitative are the ones in which the receiver has no such power: where the sender is the only party who can produce the evidence, the receiver must act on whatever is produced, and no institution has given her authority over the design or the capacity to commit to a standard. That is the position of the public, of most patients, of most jurors, and of any decision-maker who takes evidence case by case as it comes. It was, until regulators acquired the powers they now have, the position of drug regulators. The remedies of the next section are ways of moving a receiver from the second position to the first; and it is a consequence of the account, not a tension within it, that the wrong is serious exactly where the remedies are unavailable.

Two further objections need answering. The first is the nonworseness claim [@Zwolinski2007]: if the receiver is no worse off with the designed experiment than without it, and consents to rely on it, then the sender who runs it does nothing worse than the sender who runs nothing, and the latter does nothing wrong, so neither does the former. The standard replies apply [@Kates2023; @ZwolinskiSEP]. An interaction can be wrong *as an interaction* even when its counterfactual absence would have been no better for the victim, because the wrong is in how the interaction is conducted and not in its net effect; a sweatshop that pays a starvation wage does not become fair because the alternative was no job. There is also a reply specific to this case. The receiver's consent, where she has no power over the design, is consent to *rely*, not consent to the design. She agrees to decide on whatever evidence the sponsor produces because she has no alternative; she does not thereby agree that he may choose the experiment by reference to her decision rule rather than by reference to her question.

The second is that the baseline is arbitrary. Exploitation claims require a standard of fair terms, and Wertheimer's own difficulty is saying what it is. Why is the receiver entitled to the informative experiment? She is not, I think, entitled to it, any more than the sweatshop worker is entitled to a job at a fair wage. The claim is rather that *if* the sender is going to produce evidence on which the receiver will rely, the fair way to choose the experiment is by reference to the value of the decision the evidence will inform, and not by reference to the sender's share of it. When experimentation is costless that gives the perfectly informative experiment. When it is costly, it gives the experiment that best trades information against cost from the standpoint of the decision, which is the single-decision-maker benchmark @HenryOttaviani2019 use to evaluate the arrangements they study. In either case the baseline is the experiment a party who cared only about the decision would run, and the sponsor's departure from it in his own favour, because it is in his favour, is what the exploitation claim requires.

# What follows for institutions

## Transparency relocates the problem

The reforms that have reshaped clinical and behavioural research since the early 2000s, registration, pre-specification, mandatory reporting, registered reports, are aimed at selection, and against selection they work. But they work by making the count known and the design visible, which is exactly the condition under which design has its full power. A pre-registered trial is a committed experiment whose result the sponsor cannot hide. It is the persuasion game of §5, instantiated. So the reforms do not remove the sponsor's ability to move the regulator; they remove one of the two channels and thereby direct all of the sponsor's effort into the other. @HolmanGeislar2018 describe the relationship between industry and its regulators as an asymmetric arms race in which each methodological safeguard is met by a new move. On the present analysis the move after registration is design, and it is a move that requires no violation of anything the registration regime asks for.

The point has been made in the empirical literature that sponsorship bias operates through design [@Sismondo2008; @Lundh2017], and the philosophy of science literature has identified mechanisms that are design-type without marking them as such: industrial selection [@HolmanBruner2017; @PintoPinto2023] is design at the level of the community, since the funder chooses which methods get amplified; industrial distraction [@OConnorFreeborn2025] is design at the level of the research agenda, since the funder chooses which questions get asked; @Elliott2011 documents the same in environmental research. What the present analysis adds is a reason to expect these mechanisms to survive the sophistication of the audience, which the community-level models do not test and which the two-agent model of §5 establishes for its own case. It also adds two features that make the relocated problem harder to address than the original. Nothing is being hidden, so the ordinary tools for detecting misconduct have nothing to find. And the regulator's beliefs are correct, so the ordinary tools for detecting distortion, comparing what she believes with what the evidence supports, find nothing either. The only place the effect shows up is in the frequency of her decisions relative to what a differently designed body of evidence would have supported, and that comparison requires an account of what the evidence would have been.

## Two counter-moves

The design channel works because the sponsor chooses the experiment and the receiver's decision is a threshold function of her belief that the sponsor can aim at. It follows that there are two things the receiver can do. She can take the choice of experiment away from him. Or she can make the threshold something he cannot profitably aim at. Both are things receivers already do, and I want to argue that the analysis explains why they take the form they do.

The first is *authority over the design*. Registered reports do this: the journal, not the author, fixes the design before results exist, so that the author's choice of what to test is subject to review by the party who will act on it [@Chambers2013]. Regulators do it too. The United States Food and Drug Administration reviews protocols before pivotal trials, agrees endpoints and analysis plans with sponsors in advance, and issues guidance on acceptable comparators and surrogate markers; it is not a passive receiver of whatever the sponsor designs. The lottery funding that @PintoPinto2023 propose as a remedy for industrial selection has the same shape: it takes the choice of which methods to amplify out of the funder's hands. @GlazerRubinstein2004 give the general theory of a receiver who commits to a rule of persuasion specifying what the sender may present and what will be checked; the receiver-side design authority I am describing is the special case in which the rule specifies the experiment. What these institutions have in common is that they work by removing the sender's choice rather than by making it visible, which is what the analysis predicts a remedy for design must do. Transparency about a choice does nothing when the choice is the problem.

The second is *commitment to a standard*. Suppose the regulator cannot dictate the design but can commit, before the sponsor chooses his experiment, to a rule: approve if and only if the posterior probability that the drug works is at least $t$, for some $t$ she chooses. Her Bayesian-optimal threshold given her payoffs is $0.5$, but she is choosing a rule, not an act, and she is choosing it in the knowledge that the sponsor will design against it. Against a threshold of $t$, the sponsor's optimal test is again the one that every working drug passes, now with a false-positive rate of $q(t) = 0.3(1-t)/(0.7t)$, which is what it takes to put the posterior after a pass at exactly $t$. The sponsor still runs the test, because it gets him approvals with probability $0.3/t$, which exceeds the zero he would get by running nothing. And the regulator's accuracy is
$$
1 - \frac{0.3(1-t)}{t},
$$
which rises from $0.7$ at $t = 0.5$ to $0.9$ at $t = 0.75$, to $0.967$ at $t = 0.9$, and towards $1$ as $t$ approaches $1$. @fig-threshold shows the trade-off. A regulator who commits to demanding near-certainty gets, from a sponsor who wants approval, an experiment that delivers near-certainty. The value of information that a threshold of $0.5$ forfeited entirely is recovered almost entirely by a threshold of $0.95$, and the sponsor is still better off running the experiment than not. (Derivations are in the appendix.)

```{r threshold}
#| label: fig-threshold
#| fig-cap: "The regulator's accuracy and the sponsor's approval rate as a function of the approval threshold the regulator commits to, when the sponsor best-responds by designing the test. Prior that the drug works: 0.3. The dotted line is the regulator's accuracy with no evidence."
#| fig-width: 6
#| fig-height: 3.6
tibble(t = seq(0.5, 0.99, by = 0.005)) |>
  mutate(`Regulator's accuracy` = 1 - mu * (1 - t) / t,
         `Sponsor's approval rate` = mu / t) |>
  pivot_longer(-t, names_to = "quantity", values_to = "value") |>
  ggplot(aes(t, value, linetype = quantity)) +
  geom_hline(yintercept = 1 - mu, linetype = "dotted", colour = "grey40") +
  geom_line(linewidth = 0.8) +
  scale_linetype_manual(values = c("solid", "longdash")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Approval threshold the regulator commits to", y = NULL, linetype = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

The formal point is not mine. @HenryOttaviani2019 analyse an evaluator who commits to an approval standard against an informer who then chooses how much costly evidence to gather, and the optimality of a demanding standard for the evaluator, together with its cost when evidence is expensive, is their result; the law-and-economics literature on the burden of proof reached a related conclusion earlier [@Sanchirico1997; @Kaplow2012]. What I want to draw out is what the point means once it is set beside the selection channel and the exploitation account.

First, commitment is a remedy specific to design. Against selection, the receiver's commitment to a threshold adds nothing to what her scepticism already achieves. @HartKremerPerry2017 prove, for a broad class of evidence games in which the sender chooses which verifiable evidence to disclose, that the outcome when the receiver commits to a decision rule in advance coincides with the equilibrium outcome when she does not. Against a sender who is choosing among existing results, the sceptical best response already does all the work that commitment could do. Against a sender who is choosing the experiment, commitment is the difference between forfeiting the value of information and recovering it. So the two channels differ not only in what neutralises them but in what kind of receiver-side response each calls for: scepticism for selection, commitment for design. That is a distinction the philosophical literature on scientific reform has not drawn, and it matters because the reforms it has championed supply the first and not the second.

Second, the commitment must be to a rule that the receiver would not follow act by act. On the path of play the regulator never faces a posterior between $0.5$ and $t$, because the sponsor's optimal test never produces one; she sees $t$ or $0$. But the sponsor's test is optimal only because he anticipates that she would *not* approve at $0.6$. If she would, he designs for $0.6$ instead. An act-by-act Bayesian with the payoffs I have given her approves at $0.6$, and so cannot make the commitment credible. This is the familiar structure of a rule that is optimal to adopt and not optimal, case by case, to follow [@McClennen1990], and it is an uncomfortable one for a paper whose complaint against design is that it wrongs a perfectly evidence-responsive agent: the remedy asks her to be, in a specific counterfactual, less than perfectly evidence-responsive. Two things soften the discomfort. The commitment never binds on the path of play, so the regulator who makes it is never in fact asked to act against her evidence; its work is done entirely by the sponsor's anticipation of it. And the first counter-move, authority over the design, achieves the same thing without any time-inconsistency at all, which is a reason to prefer it where it is available. Where it is not, the analysis explains why standards of proof are institutional rather than personal: rules of evidence, statutory approval criteria, journal policies, rather than case-by-case judgement. The usual story about "beyond reasonable doubt", and about the demand for substantial evidence from adequate and well-controlled investigations, is that these standards weigh the costs of the two kinds of error. That story is right as far as it goes, and there are other familiar reasons for fixing standards in advance, among them predictability and equal treatment. The present story adds one: a standard of proof is a commitment device against parties who design evidence, and it does that work only because it is fixed in advance and not revisited case by case.

Third, the result reverses a lesson the naive-receiver models teach. In @WeatherallOConnorBruner2020 the policymaker does better by listening to more scientists and worse by being slow to move; stubbornness is, in that setting, a vulnerability. Against a designer, the receiver does better by being harder to move. A regulator who demands two independent trials when one was significant, an editor who will not publish a surprising result without a pre-registered replication, a reader who treats a single striking finding as no reason to change her mind: each of these is, in the naive-receiver models, throwing away information. In the design setting each is the receiver refusing to let the threshold be aimed at, and the information she would have received at a lower threshold is information the designer would never have produced. @Douglas2009 argued that the choice of an evidential threshold is a value choice that scientists cannot avoid making. If so, the strategic environment in which the threshold will be met is one of the things that legitimately bear on it.

The result has limits, and they should be stated. It assumes experimentation is costless to the sponsor and that any experiment is available. When experiments are costly, a threshold set too high leads the sponsor to run nothing, and the receiver loses the information she would have got at a lower one; this is the trade-off @HenryOttaviani2019 analyse, and the receiver-optimal standard can be well short of certainty. When the set of available experiments is bounded, the sponsor can be driven out at thresholds well below one. When evidence is produced adversarially, by two parties with opposed interests and costly effort, @DemouginFluet2006 argue that the preponderance standard is optimal. The claim is not that receivers should always demand near-certainty. It is that a receiver facing a single designer has, in the threshold, an instrument that recovers what design would otherwise take, and that the shape of the instrument, a rule fixed in advance and immune to case-by-case revision, is what the analysis predicts.

## Where the problem now lives

If the two counter-moves are already institutionalised in drug regulation, the analysis predicts that the design channel will be most active where they are not: in domains where a sponsor can produce evidence that a receiver must act on, with no authority over the design and no capacity to commit. Nutrition science and the funding of research on exercise rather than diet [@OConnorFreeborn2025] is one; environmental toxicology, where regulated industries generate much of the data regulators use, is another [@Elliott2011]; consumer products, sports science, and the evaluation of digital platforms by studies the platforms design and commission are others. In each the receivers are the public, courts, or agencies without protocol authority, and the natural reform proposal, following the success of registration in clinical research, is transparency. The present analysis says that proposal is aimed at the wrong channel. Transparency will kill selection in those domains as it has in clinical research, and will leave a sponsor who designs in daylight facing a receiver who can see everything and do nothing about it. The exploitation account says where the remedy lies instead: with whoever can be given authority over what gets studied, or the standing to say in advance what it will take to be convinced.

# Conclusion

I began with a finding: that an interested party can move an audience to false beliefs by sharing only true results. The finding is real but its audiences are cursed, and removing the curse divides the phenomenon into two things that behave differently. Selection, the choice of which existing results to share, depends on the audience's ignorance of what exists, and disappears when that ignorance does. Design, the choice of which experiments to run, does not depend on any ignorance at all. It moves a fully informed, fully rational audience by aiming at the threshold of her decision rule, and it leaves her with beliefs that are correct and decisions that are, in the aggregate, as bad as the designer can make them consistent with her acting as he wants.

That combination is hard to describe with the vocabulary we have. It is not lying, deception, misleading, or manipulation on any account that locates the wrong in the target; and the accounts that classify it as deceptive or manipulative anyway do so on the strength of a payoff structure or an attitude that, when we ask what actually varies with the design, turn out to be tracking the taking rather than any doing-to. I have argued that the wrong is exploitation: the use of the audience's dependence on the sender for evidence, and her lack of power over the terms, to take for himself the value that the evidence could have had for her. The description matters because it changes what a remedy has to do. A remedy for deception restores true belief; here belief was never false. A remedy for manipulation restores the operation of reason; here reason operated perfectly. A remedy for exploitation changes the balance of power over the terms: it takes the choice of experiment away from the interested party, or arms the audience with a commitment that forces his choice towards hers.

The transparency reforms that defeat selection do neither. They are the commitment device that design requires, and their success against the tobacco strategy's cruder half is what makes its subtler half the whole of the problem that remains. If the analysis is right, that half will not show up as misconduct, will not show up as false belief, and will show up only as a persistent tilt in the decisions of audiences whose every belief is warranted. The instruments for correcting it are ones some institutions already have and that we have been explaining incompletely: authority over what gets studied, and a standard of proof, fixed in advance, that the audience will not lower for a single case however compelling the case appears. Against a party who designs the evidence, the second is not closed-mindedness. It is the only way to be open to the evidence he would otherwise never produce.

# Appendix: derivations {.appendix}

Let $\mu \in (0,1)$ be the receiver's prior that the state is $G$ (the drug works), and let the receiver take action $a$ (approve) if and only if her posterior that the state is $G$ is at least $t$, where $\mu < t < 1$. The sender's payoff is $1$ if $a$ is taken and $0$ otherwise, regardless of the state. The receiver's payoff is $1$ if she takes $a$ in state $G$ or refrains in state $B$, and $0$ otherwise. When $t = 1/2$ the threshold rule is the receiver's expected-payoff-maximising rule.

**Design.** The sender chooses an experiment with outcomes in $\{\text{pass}, \text{fail}\}$, with $\Pr(\text{pass} \mid G) = p$ and $\Pr(\text{pass} \mid B) = q$. (With a binary-action receiver one can restrict attention to experiments with two outcomes, read as action recommendations; see @KamenicaGentzkow2011.) The posterior after a pass is $\mu p / (\mu p + (1-\mu) q)$, and the receiver approves after a pass if and only if this is at least $t$, i.e. if and only if
$$
q \le \frac{\mu (1-t)}{(1-\mu)\, t}\, p .
$$
The sender's payoff is $\Pr(\text{pass}) = \mu p + (1-\mu) q$ when the receiver approves on a pass (and nothing is gained from a fail, since the posterior after a fail is below the prior and hence below $t$). This is increasing in both $p$ and $q$, so the sender sets $p = 1$ and $q$ at the bound:
$$
q^\ast(t) = \frac{\mu(1-t)}{(1-\mu)\,t}.
$$
The sender's approval probability is $\mu + (1-\mu) q^\ast = \mu / t$, and the receiver's probability of a correct decision is
$$
\mu \cdot 1 + (1-\mu)(1 - q^\ast) = 1 - \frac{\mu(1-t)}{t}.
$$
At $t = 1/2$ this equals $1 - \mu$, the receiver's accuracy with no evidence (she rejects everything). It is increasing in $t$ and tends to $1$ as $t \to 1$. The sender's approval probability $\mu/t$ is decreasing in $t$ but exceeds $\mu > 0$ for all $t < 1$, so the sender prefers to run the experiment for every threshold. With $\mu = 0.3$ and $t = 1/2$: $q^\ast = 3/7$, approval $0.6$, accuracy $0.7$. With $t = 0.95$: $q^\ast = 3/133 \approx 0.023$, approval $0.316$, accuracy $0.984$.

**Selection.** Let $N$ studies be run, independent conditional on the state, each positive with probability $s$ in state $G$ and $f$ in state $B$, with $s > f$. The sender reports the positives. A cursed receiver who sees $k$ positive reports and treats them as the whole record has posterior odds $\frac{\mu}{1-\mu} (s/f)^k$. A sophisticated receiver who knows $N$ infers $N - k$ negatives and has posterior odds $\frac{\mu}{1-\mu} (s/f)^k \left(\frac{1-s}{1-f}\right)^{N-k}$, which is the posterior from full disclosure. The approval and accuracy figures in @tbl-twobytwo are computed by summing over $k$ under the binomial distribution in each state, with $N = 4$, $s = 0.8$, $f = 0.3$, $\mu = 0.3$, $t = 1/2$. With these values the cursed receiver approves for $k \ge 1$ and the sophisticated receiver for $k \ge 3$.

**A note on the comparison.** The design experiment and the four selection studies are not the same experiment, and the table is not a comparison of their informativeness. The comparison is between what each channel yields for the sender and the receiver given the receiver's sophistication. Against a sophisticated receiver, the sender who has four honest studies and can only select does no better than full disclosure, whereas the sender who can design does strictly better than full disclosure of any experiment the receiver would have chosen.
