---
title: "Persuasion in Daylight"
abstract: |
  Recent models of industry propaganda show that an interested party can lead an audience to false beliefs by sharing only true results. But the audiences in those models update on the content of what they are shown and not on the fact that they were shown it. I ask what survives when the audience is not so naive. The answer divides the strategy in two. *Selection*, choosing which existing results to pass on, is neutralised by an audience that reasons about the process; its power is exactly proportional to the audience's ignorance of what was generated, and transparency reforms remove that ignorance. *Design*, choosing which experiments come into existence, is not neutralised. A fully informed, fully rational audience that knows the experiment was chosen to move it is still moved: its beliefs stay calibrated while the distribution of its decisions shifts in the designer's favour. I argue that this is not deception, not misleading, and not manipulation on any standard account, but that it is a wrong, and that the right category is exploitation: the designer uses the audience's dependence on him for evidence to appropriate the value of information. Two institutional consequences follow. Pre-registration and disclosure, which kill selection, are the commitment device that design requires, so they relocate the problem rather than solving it. And the audience's effective counter-move is not open-mindedness but commitment in advance to a demanding standard of proof, which forces the designer towards the informative experiment.
author:
  - name: Claude
    note: "Draft written by Claude (Fable 5.1) for Brian Weatherson's in-house blog experiment. Not for circulation."
date: 29 September 2026
categories:
  - epistemology
  - ethics
  - philosophy of science
  - claude-draft
draft: true
execute:
  echo: false
  warning: false
  message: false
bibliography:
  - ../../brian-quarto.bib
  - daylight.bib
citation: false
format:
  html:
    css: ../trad_defn.css
  pdf:
    output-file: "Persuasion in Daylight"
    include-in-header:
      - file: ../quarto2024.tex
      - text: |
         \cehead{
                 Persuasion in Daylight
                 }
    include-after-body:
        text: |
          \noindent Draft of September 2026.
---

```{r setup}
suppressMessages({library(dplyr); library(tidyr); library(purrr); library(ggplot2); library(knitr)})
mu <- 0.3; t0 <- 0.5
sens <- 0.8; fpr <- 0.3; N <- 4
```

# Introduction

In the early 1950s the American tobacco industry decided to fight science with science. Rather than deny that smoking caused cancer, it funded research, promoted the studies that happened to go its way, and let a growing body of contrary evidence be met with a manufactured sense that the question remained open [@OreskesConway2010]. Nobody had to lie. The studies that were promoted were real studies. The strategy worked for decades.

A series of recent models from philosophy of science explains why. In the models of @WeatherallOConnorBruner2020, a propagandist who forwards to policymakers only those results, produced by honest scientists, that favour the industry's position can drive the policymakers to near-certainty in the wrong theory while the scientists themselves converge on the right one. @Mohseni2022 show that a journalist who curates studies according to ordinary newsroom norms produces the same distortion without meaning to. @HolmanBruner2017 show that an industry that funds the scientists whose methods happen to yield favourable results can bias a community's consensus without corrupting any individual in it. @OConnorFreeborn2025 show that funding accurate research on *other* causes of a harm shifts blame away from the industrial cause. The common lesson, which the authors draw explicitly, is that fraud is unnecessary. True results suffice.

There is something these models share that their authors also note, but which has not received the attention it deserves. Their audiences are rational about what they are told and irrational about the fact that they are being told it. A policymaker in the Weatherall–O'Connor–Bruner model receives a study from the propagandist and conditionalises on its content exactly as she would had the study come to her at random. She does not ask what the propagandist's forwarding it tells her about the studies he did not forward. In the language of @EysterRabin2005, she is *cursed*: she correctly predicts what the propagandist does but ignores the correlation between what he does and what he knows. The authors flag as future work the question of what happens when the audience can "adjust their updating rule to accommodate the possibility that some of the evidence they receive is exaggerated, filtered, or otherwise intended to mislead" [@WeatherallOConnorBruner2020].

This paper takes up that question. The answer, I will argue, splits the tobacco strategy down the middle. One half of it, which I will call *selection*, consists in choosing which already-existing results to pass on. Against an audience that reasons about the process, selection is neutralised. This is the unravelling result of @Grossman1981 and @Milgrom1981: a sceptical audience treats silence as bad news, so the sender ends up revealing everything or being treated as if he had. Selection's power is exactly proportional to the audience's ignorance of what exists to be selected from, and the transparency reforms of the last two decades, trial registries, pre-registration, mandatory disclosure, are devices for removing that ignorance. The other half, which I will call *design*, consists in choosing which experiments come into existence: what to measure, whom to enrol, what to compare against, how long to run. Against an audience that reasons about the process, design is not neutralised. This is the central result of @KamenicaGentzkow2011. A sender who commits in advance to an experiment, whose design the audience sees and understands and knows to have been chosen in the sender's interest, can still move the audience's decisions in his favour. He does this without inducing a single belief the audience should not hold. Her posterior after each result is exactly what the evidence warrants. What changes is not the accuracy of her beliefs but the frequency with which she decides as he wants.

The economics is not new, and I will present it briskly. What is new, I hope, is the philosophical use. The design result shows that there is a way of moving a rational agent with true evidence that survives every idealisation: full rationality, full information about the process, full awareness of the sender's motives. That puts pressure on how we describe the wrong. Design is not lying and not deception, since no false belief is produced. It is not misleading in the sense that the literature on misleading with truths has analysed, since no partial answer invites a false completion. It is not manipulation on accounts that require covertness, or bypassing reason, or the induction of a belief that falls short of the agent's own ideals, since it is overt, works entirely through reason, and induces only beliefs the agent would endorse on reflection. And yet the audience is worse off than she would be under the experiment a disinterested inquirer would have run, and the sender chose the experiment because she would be. I will argue that the right category is exploitation, in the specific form that @Wertheimer1996 calls mutually advantageous exploitation: the audience gains a little, consents to the arrangement, and is nonetheless wronged, because the sender uses her dependence on him for evidence to appropriate the value of information for himself.

Two consequences follow for how we should think about protecting audiences. The first is that the transparency reforms which defeat selection are the commitment device that design requires. A pre-registered trial is precisely an experiment whose design the audience can see and whose results the sender cannot hide, which is the setting in which the persuasion result holds. Reform of this kind does not so much solve the problem as relocate it, and the relocation makes the residual problem harder to see, because everything is now by the book. The second is that the audience's effective counter-move looks, from the outside, like closed-mindedness. A receiver who can commit in advance to a demanding standard of proof forces the sender's optimal experiment towards the informative one, and recovers the value of information that a more accommodating receiver would forfeit. Against selection, such commitment is worthless; against design, it is the whole game. This gives a rationale for standards like "beyond reasonable doubt" and "substantial evidence from adequate and well-controlled investigations" that is independent of the usual story about the asymmetric costs of error.

# Two ways to bias a body of evidence

Fix an audience with a question and a decision that turns on it. A regulator must decide whether a drug works well enough to approve. A judge must decide whether a defendant is guilty. A journal editor must decide whether a paper's result is real. A voter must decide whether a policy has the effects claimed for it. In each case there is a party with an interest in the decision going one way regardless of the answer to the question, and that party has some control over the evidence the audience sees.

There are two points at which that control can be exercised. The first is after results exist. The sender has a stack of studies and decides which to hand over. The file drawer, cherry-picking, "selective sharing" in the sense of @WeatherallOConnorBruner2020, the fair-minded journalist who finds one study for each side, the literature review that cites what supports its conclusion: all of these are choices about which existing results to transmit. Call this *selection*.

The second point is before results exist. The sender decides which experiments to run. He chooses the endpoint (a surrogate marker or the outcome that matters), the comparator (placebo, or the rival drug at a dose chosen to disadvantage it), the population (the patients most likely to respond), the duration (long enough to show benefit, short enough to miss harm), the sample size (large enough to reach significance if the effect is there, small enough that a null result is uninformative). Every one of these is a choice about what the world will be asked, and therefore about what it can answer. Call this *design*.

The distinction is not between honest and dishonest experiments. Everything I say about design assumes the experiments are competently run, accurately reported, and reported in full. Nor is it a distinction between weak and strong evidence in some absolute sense. It is a distinction in the timing and the object of the sender's choice: selection is a choice among realised results; design is a choice among experiments, made before any result is known.

Real cases mix the two, and some of the most striking documented findings about industry-sponsored research are design findings. @Heres2006 examined head-to-head trials of second-generation antipsychotics and found that ninety percent of them favoured the sponsor's drug, so that olanzapine beat risperidone in trials sponsored by olanzapine's maker, risperidone beat quetiapine in trials sponsored by risperidone's, and quetiapine beat olanzapine in trials sponsored by quetiapine's. The mechanism was not fabrication and only partly reporting; it was dose selection, comparator choice, and the choice of outcome measures. @Safer2002 catalogued the same devices. The Cochrane review of industry sponsorship [@Lundh2017] finds that industry-funded studies reach favourable conclusions more often than independently funded ones, and that the difference is not explained by the standard risk-of-bias measures, which is what one would expect if the residual mechanism were design rather than conduct or reporting. The case @HolmanBruner2017 use to introduce industrial selection is a design case: trials of anti-arrhythmic drugs that measured arrhythmia suppression showed benefit, and it was only trials that measured mortality that revealed the drugs were killing people [@Echt1991; see @FlemingDeMets1996 on surrogate endpoints generally].

My question is which of these two channels survives an audience that is not cursed. To answer it I need to say what an uncursed audience is.

# Cursed audiences

Here is a case that will serve throughout. A regulator must decide whether to approve a drug. Her prior probability that the drug works is $0.3$, and she approves if and only if her posterior probability that it works is at least $0.5$: she gets one unit of value from a correct decision and nothing from an incorrect one, so this is the threshold at which approval is the better bet. The sponsor wants approval whether or not the drug works.

Suppose first that the sponsor runs four identical studies. Each study returns a positive result with probability $0.8$ if the drug works and with probability $0.3$ if it does not, and the studies are independent conditional on whether the drug works. The sponsor then reports every positive result and files away every negative one.

A regulator who sees $k$ positive reports and treats them as the whole record computes the posterior odds that the drug works as the prior odds times $(0.8/0.3)^k$. A single positive report takes her to a posterior of $0.53$, over her threshold. The chance that at least one of four studies is positive is $0.9984$ if the drug works and $0.76$ if it does not. So she approves with probability $0.83$, and her probability of making the correct decision, approving working drugs and rejecting the others, is $0.47$. That is worse than the $0.7$ she would achieve by ignoring the sponsor altogether and rejecting everything. This is the phenomenon the Weatherall–O'Connor–Bruner model exhibits at scale: a rational updater who sees a selected sample and treats it as unselected ends up with beliefs that are systematically wrong, and, in the aggregate, worse than no evidence at all.

The regulator's mistake has a precise description. @GrunwaldHalpern2003, building on @Shafer1985, distinguish conditioning in a *naive space*, whose points are the possible contents of an observation, from conditioning in a *sophisticated space*, whose points also specify the protocol by which the observation was produced. Naive conditioning gives the same answer as sophisticated conditioning only when the protocol satisfies a condition they call "coarsening at random": roughly, when the probability of being shown a given piece of evidence does not depend on the state beyond what the evidence itself says. The sponsor's protocol violates that condition as badly as a protocol can. Whether a study is shown depends on its result, and so on the state. The regulator who conditions in the naive space is not reasoning badly from her evidence; she is reasoning from the wrong evidence. Her total evidence is not "study 3 was positive" but "the sponsor showed me study 3, and it was positive, and he showed me nothing else" [see @Good1967 on the principle of total evidence, and @Sober2009; @Kotzen2012 on observation selection effects].

@EysterRabin2005 give the same mistake a game-theoretic name. A *cursed* player correctly forecasts the distribution of the other players' actions but underestimates, in the fully cursed case ignores, the extent to which those actions depend on the other players' private information. The regulator forecasts that the sponsor will forward studies; she fails to condition on the fact that which studies he forwards depends on what all the studies said. Eyster and Rabin introduced the concept to explain the winner's curse and the persistence of trade under adverse selection, both cases where people fail to ask "what does the fact that this is on offer tell me?" The audiences in the philosophy of science models fail to ask the same question.

I want to be clear that this is not a criticism of those models. Real audiences are cursed. In laboratory tests of disclosure games, receivers are systematically insufficiently sceptical about what is not disclosed [@JinLucaMartin2021; see also @Frechette2022], and the historical record that motivates the models is a record of real policymakers being moved. If the question is how the tobacco strategy worked on the audiences it actually faced, the models answer it. My question is different. It is whether rationality protects an audience from being moved by true evidence, and to answer that one has to remove the curse and see what remains.

# Selection in daylight

Uncurse the regulator. She knows that four studies were run. She knows the sponsor's reporting policy. She sees $k$ positive reports and infers that the other $4-k$ were negative. Her posterior is now the one she would have reached had all four studies been laid in front of her: the prior odds times $(0.8/0.3)^k (0.2/0.7)^{4-k}$. She approves only when at least three of the four studies are positive. The sponsor's approval rate falls from $0.83$ to $0.30$, and her accuracy rises from $0.47$ to $0.89$, which is exactly the accuracy she would achieve from four honestly reported studies. Selection has bought the sponsor nothing.

This is the unravelling argument, and it is fully general. @Grossman1981 and @Milgrom1981 showed that when a sender holds verifiable information, so that he can withhold but not fabricate, and the receiver is sceptical, so that she interprets what is not shown as the worst thing consistent with what is, the sender's best response is to show everything, because at every stage the sender with the best undisclosed news prefers to disclose it rather than be pooled with those who have worse. The equilibrium unravels to full disclosure. @MilgromRoberts1986 showed the same result obtains even with a naive receiver if there are competing senders with opposed interests, each of whom reveals what the other conceals. Against a sceptical receiver, or between adversarial senders, choosing what to reveal is not a lever.

There is one condition that matters enormously, because it is the condition the transparency reforms target. Unravelling requires that the receiver know, or be able to infer, what exists to be revealed. If she does not know whether the sender ran four studies or none, silence pools "I ran studies and they were negative" with "I ran no studies", and the sender with bad news can hide behind the second [@Dye1985; @JungKwon1988]. Selection then retains some power, in proportion to the receiver's uncertainty about the sender's evidential endowment. @Henry2009 models a researcher who chooses how many experiments to run and which to disclose to a receiver who does not observe the count, and finds that the researcher must sometimes reveal unfavourable results to establish credibility, "the cost of proving your honesty". @ArieliStewart2025 show that if the receiver is sufficiently uncertain about the sender's capacity to experiment, selective disclosure can achieve everything that design (in the sense of the next section) achieves. So the claim that selection is neutralised needs stating carefully: selection's power is a function of the receiver's ignorance of the process, and it goes to zero as that ignorance does.

That is precisely why the reforms of the last twenty years take the form they do. Trial registration requires the sponsor to declare a study before it is run, so that the regulator knows it exists whatever its result. Pre-registration of analysis plans fixes the endpoint and the test before the data arrive, so that the sponsor cannot search the data for a favourable specification and report it as if pre-planned [@Nosek2018]. Registered reports commit a journal to publishing a study on the strength of its design, before results, so that the file drawer has nothing in it [@Chambers2013]. Every one of these is a device for making the count known, which is to say for restoring the condition under which unravelling works. @Felgenhauer2021 models pre-registration explicitly as a commitment device that deters selective reporting. The philosophy of science literature on publication bias and self-correction recommends the same instruments for the same reason [@Romero2016; @Heesen2018].

The Weatherall–O'Connor–Bruner model has a second treatment, "biased production", in which the propagandist runs his own studies and publishes only the favourable ones, and a striking finding within it: the propagandist does best by splitting his budget into the smallest possible studies, because small studies are more often spuriously favourable. This looks like a design result, since it concerns how experiments are configured. It is not. The small studies do their work only because the unfavourable ones are then withheld from a receiver who does not know how many were run. Against a receiver who knows the count, the strategy unravels like any other selection strategy, and with the count known, splitting the budget into small studies simply gives the receiver a less informative body of evidence, which the sponsor has no reason to prefer. What I will now argue is that design in the proper sense, the choice of experiment under a regime where the receiver sees the choice and every result, has a power that no amount of scepticism removes.

# Design in daylight

Now suppose the regulator is as sophisticated as one could wish. She knows what experiment the sponsor will run before he runs it. She sees every result. She knows the sponsor chose the experiment to maximise the chance of approval. She updates by conditionalisation in the sophisticated space, on the full protocol. There is nothing hidden from her.

Suppose the sponsor may choose any experiment whose outcome depends only on whether the drug works: a test, of any design, whose statistical properties the regulator will know. In particular he may choose a test with a single pass/fail outcome, such that every working drug passes and a drug that does not work passes with probability $q$. Think of a surrogate endpoint chosen for its sensitivity: a marker that every effective drug moves, and that a certain fraction of ineffective drugs also move.

The sponsor chooses $q$. If he sets $q = 0$ the test is perfectly informative: the regulator learns exactly whether the drug works, approves with probability $0.3$, and is never wrong. If he sets $q = 1$ the test is uninformative, the regulator's posterior stays at $0.3$, and she never approves. In between, a pass takes the regulator's posterior to $0.3/(0.3 + 0.7q)$, and she approves on a pass if and only if this is at least $0.5$, which is to say if and only if $q \le 3/7$. The sponsor sets $q = 3/7$. Now every working drug passes, and $43$% of the drugs that do not work pass too. The regulator, seeing a pass, computes a posterior of exactly $0.5$, and approves. Seeing a fail, she computes a posterior of $0$ and rejects. She approves $60$% of drugs, though only $30$% work.

Nothing here is hidden, and nothing she believes is false or ill-founded. Among the drugs she approves, exactly half work, which is what she believes when she approves. Her credences are calibrated in the strict sense: conditional on each thing she does, the frequency with which she is right is the credence on which she acted. Her expected accuracy, the probability of making the correct decision, is $0.7$. That is the same accuracy she would achieve with no evidence at all, since with no evidence she rejects everything and is right $70$% of the time. The sponsor has chosen an experiment that delivers to the regulator exactly nothing, in expectation, while delivering to himself twice the approvals he would get from an honest and informative test.

This is the "Bayesian persuasion" result of @KamenicaGentzkow2011, with the numbers of their prosecutor example (a prosecutor who gets sixty percent convictions from a population thirty percent guilty). Their general theorem characterises exactly when a sender who commits to an experiment benefits from doing so: whenever the sender's payoff, as a function of the receiver's belief, is not concave at the prior. The intuition in the binary case is that the receiver's decision is a step function of her belief, so the sender benefits by pushing her belief just over the step as often as possible and letting it fall as far as it likes otherwise. The optimal experiment is the one that makes the receiver exactly indifferent whenever she takes the action the sender wants, and certain whenever she takes the action he does not. More generally, a sender who cares only about the action never induces a belief at which the receiver takes his preferred action more confidently than she must, because that confidence is wasted on him and could have been spread over more cases. The survey by @Kamenica2019 and the unification by @BergemannMorris2019 show how far this extends.

@tbl-twobytwo assembles the numbers for the four cases. The rows are the two channels; the columns are the two audiences.

```{r twobytwo}
#| label: tbl-twobytwo
#| tbl-cap: "The sponsor's approval rate and the regulator's accuracy (probability of a correct decision) under each channel and each kind of receiver. Prior that the drug works: 0.3; approval threshold: 0.5. Selection: four studies each with sensitivity 0.8 and false-positive rate 0.3, only positives reported. Design: the sponsor's optimal single-outcome test. With no evidence the regulator's accuracy is 0.7."
post_full  <- function(k) { lg <- mu * dbinom(k, N, sens); lb <- (1 - mu) * dbinom(k, N, fpr); lg / (lg + lb) }
post_naive <- function(k) { lg <- mu * sens^k; lb <- (1 - mu) * fpr^k; lg / (lg + lb) }
sel <- expand_grid(state = c("G", "B"), k = 0:N) |>
  mutate(pr = if_else(state == "G", mu, 1 - mu) * dbinom(k, N, if_else(state == "G", sens, fpr)),
         cursed = post_naive(k) >= t0, sophisticated = post_full(k) >= t0) |>
  pivot_longer(c(cursed, sophisticated), names_to = "receiver", values_to = "approve") |>
  group_by(receiver) |>
  summarise(approval = sum(pr * approve),
            accuracy = sum(pr * if_else(state == "G", approve, !approve)), .groups = "drop") |>
  mutate(channel = "Selection")
q_star <- mu * (1 - t0) / ((1 - mu) * t0)
des <- tibble(receiver = c("cursed", "sophisticated"), channel = "Design",
              approval = mu + (1 - mu) * q_star, accuracy = mu + (1 - mu) * (1 - q_star))
bind_rows(sel, des) |>
  mutate(receiver = if_else(receiver == "cursed", "Cursed receiver", "Sophisticated receiver")) |>
  pivot_wider(names_from = receiver, values_from = c(approval, accuracy)) |>
  transmute(Channel = channel,
            `Approval (cursed)` = sprintf("%.2f", `approval_Cursed receiver`),
            `Accuracy (cursed)` = sprintf("%.2f", `accuracy_Cursed receiver`),
            `Approval (sophisticated)` = sprintf("%.2f", `approval_Sophisticated receiver`),
            `Accuracy (sophisticated)` = sprintf("%.2f", `accuracy_Sophisticated receiver`)) |>
  kable(align = "lcccc")
```

Two features of the table are the point of the paper. First, the columns differ for selection and not for design. Sophistication is a complete cure for selection and no cure at all for design, and the reason is structural. At the moment the sponsor chooses which studies to forward, he knows their results and the regulator does not; his choice is a function of private information, and a receiver who ignores that is cursed. At the moment the sponsor chooses which experiment to run, he knows nothing the regulator does not. His choice is a function of his interests, which she knows, and of the prior, which she shares. There is no private information for the choice to leak and hence nothing for her to be cursed about. She is already conditioning on everything. That is why the sophisticated column for design equals the cursed one.

Second, compare the two sophisticated cells. Against a sophisticated receiver, a sponsor who runs four honest studies and cherry-picks gets $30$% approvals and leaves the regulator with accuracy $0.89$; a sponsor who designs one test gets $60$% approvals and leaves her with $0.7$. Design dominates selection for the sponsor, and the regulator is worse off under design than under selection-with-sophistication. The cherry-picker who is found out has given the regulator four studies' worth of information. The designer who is fully understood has given her none.

There is a further feature that deserves emphasis because it inverts a natural assumption. Design requires daylight. The persuasion result assumes the sponsor commits to the experiment and cannot hide its result. If the sponsor could instead run experiments privately and disclose selectively, one might think him better off, since he has more options. He is not. @FelgenhauerLoerke2017 show that a sender who experiments privately and discloses selectively achieves a lower probability of persuasion, and leaves the receiver better informed, than a sender whose experimentation is public. @Frechette2022 state the general contrast: when the sender's information is verifiable, commitment to an experiment *reduces* the information transmitted relative to no commitment, because without commitment the sender unravels, and with it he can garble. @DaiFudenbergPei2025 show that adding the option of secret follow-up experiments and selective disclosure to a committed design never helps the sender and can hurt him. The lesson is that the sponsor should welcome the reforms. Registration, pre-specification, mandatory reporting: these take away the selection channel, which a sophisticated receiver had already neutralised, and they establish the commitment that makes the design channel work. Daylight is the designer's friend.

# Is it misleading? Is it manipulation?

I have said that the sophisticated regulator is moved without being misled or manipulated. That claim needs defending against the accounts on offer, because on several of them it is not obvious, and on one or two it may be false. I take the accounts in turn. The upshot is that where an account clearly applies, it does not explain what is wrong, and where an account would explain what is wrong, it does not clearly apply.

## Misleading evidence

There is a thin sense in which every probabilistic experiment sometimes misleads. Following @Skyrms2010, call a signal *misinformation* when it raises the receiver's probability of a state that does not obtain. The designed test passes $43$% of the drugs that do not work, and each such pass raises the regulator's probability that the drug works from $0.3$ to $0.5$. So the test produces misinformation. But so does every test short of a perfect one, including tests no one designed to persuade. A cheap screening test with the same sensitivity and specificity, adopted by a health service for budgetary reasons, produces misinformation at the same rate. The thin sense does not distinguish the designed test from an innocently coarse one, and so cannot be where the wrong lies. Skyrms adds that a signal is *deceptive* when it is misinformation that systematically benefits the sender at the receiver's expense. The designed test's passes on ineffective drugs meet that condition. But the signal that carries the misinformation is a true report of a real result, and the receiver's response to it is the correct one given everything she knows. @FallisLewis2019 refine Skyrms's definition to handle half-truths and require that the signal move the receiver away from the truth relative to what she would otherwise have believed; here she would otherwise have believed $0.3$, and she now believes $0.5$, for a drug that does not work. That too is met. What these formal definitions capture is that a signal can be accurate and yet be part of a system that serves the sender. That is right, and it is what I want to say. But it locates the wrong at the level of the system, the experiment as a whole, and not at the level of any belief the receiver forms. No belief of hers is one she ought not to have.

A more demanding notion of misleading is the one the literature on lying and misleading has analysed. @Saul2012 treats misleading as conveying a falsehood without saying it; @Stokke2016 analyses it as offering a true but partial answer to the question under discussion that invites a false complete answer. Cherry-picking is misleading in this sense: "study 3 was positive", offered in answer to "does the drug work?", invites the completion "and the others were too", which is false. That is why selection fails against a receiver who declines the invitation. Design is not like this. The sponsor asks the world a question, "does the drug move this marker?", reports the world's complete answer, and the regulator knows which question was asked and what its answer bears on. There is no partial answer and no false completion. What there is, is a self-serving choice of question. Stokke's apparatus lets us say exactly why that is not misleading: the receiver's posterior on *her* question, "does the drug work?", is what the evidence on the sponsor's question warrants, and she knows it.

@Fallis2015 defines disinformation as information "likely to create false beliefs" that has the function of doing so, and explicitly includes true content that is selectively emphasised. On his definition the designed test is not disinformation, because it is not likely to create false beliefs: it creates calibrated ones. @OConnorFreeborn2025 describe industrial distraction, the funding of accurate research on alternative causes, as "accurate but misleading" content, and it is the nearest thing in the existing literature to a design case. Their learner conditions on the content of the funded research within a causal model and does not treat the choice of what to fund as evidence. When she does, some of the distraction effect survives, for the reasons of the last section: an industry that chooses which causal links get investigated is designing the body of evidence, and a receiver who knows this can still be moved. But "misleading" is then the wrong word for what happens to her, since her beliefs about each link are exactly as warranted as the evidence makes them.

Deception in the standard sense requires the intentional production of a false belief [@ChisholmFeehan1977; @Carson2010]. No false belief is produced. The most that can be said is that the receiver is kept less informed than she might have been. But being kept ignorant is not being deceived, and in any case the designer does not keep her ignorant of anything that exists. He arranges for less to exist.

## Manipulation

The literature on manipulation is less unified, and I follow the map in @NoggleSEP [see also @Noggle2025].

On the *covert influence* account of @Susser2019, manipulation is intentionally and covertly influencing someone's decision-making by exploiting their decision-making vulnerabilities. Design fails the covertness condition outright. The regulator knows everything.

On *bypassing* accounts [@Wood2014], manipulation influences by means that do not engage the target's reason: playing on emotions, habits, biases. Design fails this condition too, and fails it as completely as an influence can. The regulator is moved by conditionalising on evidence and maximising expected value. Nothing is bypassed. @Levy2019 has argued that nudges are not manipulative because they present reasons to mechanisms that respond to reasons; whatever one thinks of that argument for nudges, it succeeds for design, where the mechanism is explicit Bayesian updating.

On the *ideals* account [@Noggle1996; refined by @Barnhill2014], manipulation is an attempt to induce a belief, desire, or emotion that falls short of the ideals governing that state, false belief being the paradigm. The regulator's belief after a pass, that the drug works with probability $0.5$, does not fall short of any ideal, by her lights or the sponsor's. It is the belief the evidence warrants. Barnhill adds that the induced state must be against the target's interest; the regulator's *decision* is against her interest relative to a better-informed alternative, but her mental states are not defective, and the ideals account needs a defective state.

The accounts that come closest are those on which manipulation is influence that fails to track reasons. @Gorin2014b argues, with cases in which an influencer supplies entirely good reasons for entirely ulterior ends, that a manipulator need not bypass or subvert reason at all; what marks manipulation is that the influencer judges reasons by their efficacy rather than their quality, treating them as causal levers. @Klenk2022 offers a definition in the same spirit: an influencer manipulates when he aims to get the target to do or believe something by a method, and disregards whether that method reveals to the target the reasons there are for doing or believing it.

Klenk's condition, read carefully, lets design out. The designer's method is to run an experiment and report its result. That method reveals to the receiver every reason the experiment generates; there are no reasons it conceals. What the designer disregards is not whether his method reveals reasons but whether the experiment he chose was the most revealing one available. That is a different kind of carelessness, and it is not the kind Klenk's definition targets. Gorin's condition is harder. The designer does judge experiments by their efficacy in producing approvals rather than by their informativeness. Suppose we grant that this makes design manipulation in Gorin's sense. What is then supposed to be wrong with it? Gorin's answer is that manipulation fails to track reasons, so that the target's response is not appropriately connected to what justifies it. But the regulator's response *is* appropriately connected to what justifies it. Her approval is justified by a posterior of $0.5$, which is justified by a pass, which is justified by the test's known properties. The connection is impeccable at every link. If the reasons-tracking account counts design as manipulation, it does so at the cost of its own explanation of why manipulation is wrong. It has classified the case without diagnosing it.

That is the general situation. Accounts that require covertness, bypassing, or a defective mental state exclude design, and rightly, since it has none of these features. Accounts that would include it explain the wrong of manipulation in terms of a failure that design does not exhibit. @Buss2005 argued that the wrong of an influence need not consist in what it does to the target's rational agency, and @GTsai2014 that an influence can wrong its target while working entirely through reasons. I think design is a case in point, but the wrong is not the one either of them had in mind. To find it we have to look not at what the sender does to the receiver's mind but at what he takes from her.

# Exploitation

Here is what the sponsor takes. With no evidence the regulator's expected accuracy is $0.7$. With a perfectly informative experiment it would be $1$. The difference, $0.3$, is the value of information to her: the surplus that experimentation makes available. The sponsor, in choosing the experiment, chooses how that surplus is divided. He can run the informative test and hand it all to her, at the cost of approvals. He can run the uninformative test and destroy it. Or he can run the test with $q = 3/7$, which leaves her with exactly none of it and converts the rest into approvals for him. He chooses the last. In the general case the sender's optimal experiment need not leave the receiver with nothing, but it never gives her more confidence than the action he wants requires: at every result on which she acts as he wants, she is left indifferent between that action and the next one down. The sender appropriates the value of information.

This has the structure that @Wertheimer1996 calls mutually advantageous exploitation. The receiver is not made worse off than she would be by no transaction: her accuracy is $0.7$ either way, and in the general case she weakly gains from the experiment relative to none. She consents, in the sense that she relies on the sponsor's evidence voluntarily and would rather have it than not. And yet the transaction is unfair to her in the way Wertheimer's cases are unfair: the party with the power to set the terms has set them so that he captures the cooperative surplus and she captures none. Wertheimer's central puzzle is how a consensual transaction that leaves both parties no worse off can nonetheless be a serious wrong, and his answer, that consent and mutual advantage may defeat a claim to interference and a right to better terms without defeating the judgement that the terms are unfair, transfers directly.

Two more recent accounts fit the case even better. @Valdman2009 holds that wrongful exploitation is the extraction of excessive benefit from someone who cannot, or cannot reasonably, refuse one's offer, and insists that this wrong is not reducible to harm, coercion, or deception. The regulator cannot reasonably refuse. She must decide, and she must decide on the evidence that exists; she has no independent capacity to run the trial and no other party will. That is a specific instance of the general fact of epistemic dependence [@Hardwig1985]: for most of what we need to know, we depend on others to produce the evidence, and the dependence is a vulnerability. @Vrousalis2013 makes vulnerability central: exploitation is instrumentalising another's vulnerability to extract a benefit, within a systematic relationship, and its wrong is a form of domination that consent does not dissolve. The relationship between a regulator and the industry it regulates is systematic in exactly Vrousalis's sense, and the sponsor who chooses $q = 3/7$ is using the regulator's dependence on him, together with her own rationality, as the instrument by which approvals are extracted. @Wood2014 [see also @Wood1995], in the same chapter that rules design out of manipulation on the bypassing account, characterises exploitation as the use of another's weakness or need for one's own advantage, and stresses that it is compatible with the exploited party's consenting and benefiting. Design is exploitation on all three accounts.

Two objections need answering. The first is the nonworseness claim [@Zwolinski2007]: if the receiver is no worse off with the designed experiment than without it, and consents to rely on it, then the sender who runs it does nothing worse than the sender who runs nothing, and the latter does nothing wrong, so neither does the former. The standard replies apply [@Kates2023; @ZwolinskiSEP]. An interaction can be wrong *as an interaction* even when its counterfactual absence would have been no better for the victim, because the wrong is in how the interaction is conducted and not in its net effect; a sweatshop that pays a starvation wage does not become fair because the alternative was no job. But there is also a reply specific to this case. The receiver's consent is consent to *rely*, not consent to the *design*. She agrees to decide on whatever evidence the sponsor produces because she has no alternative; she does not thereby agree that he may choose the experiment by reference to her decision rule rather than by reference to her question. In the general case the receiver would rather have any experiment than none, but she would rather have the informative one than the one she gets, and her not being asked is part of what makes the arrangement exploitative.

The second objection is that the baseline is arbitrary. Exploitation claims require a standard of fair terms, and Wertheimer's own difficulty is saying what it is. Why is the receiver entitled to the informative experiment? She is not, I think, entitled to it, any more than the sweatshop worker is entitled to a job at a fair wage. The claim is rather that *if* the sender is going to produce evidence on which the receiver will rely, the fair way to choose the experiment is by its informativeness about her question, and the experiment a disinterested inquirer would run is the natural specification of that. When experimentation is costly the baseline is not the perfectly informative experiment but the one that balances information against cost from the point of view of the decision, which is the sequential-testing benchmark @HenryOttaviani2019 use to evaluate persuasion. What the exploitation claim requires is only that there be such a baseline and that the sender's choice depart from it in his favour because it is in his favour. Both are secured by the structure of the case.

The account also predicts where design is not exploitative, and these predictions are the right ones. When the sender's and receiver's interests are aligned, the sender's optimal experiment is the receiver's, and there is no surplus to appropriate. When the receiver has alternatives, either because there are competing senders whose interests oppose each other [@MilgromRoberts1986; with the qualification in @GentzkowKamenica2017 that competition in design helps only when each sender can generate the signals the others can] or because she can run the experiment herself, she is not dependent and cannot be exploited. And when an institution assigns design authority to the interested party but supplies the receiver with a counter-measure, the arrangement can be fair even though each individual act within it has the structure of design. That is the situation of the advocate in an adversarial trial: the defence chooses what evidence to develop, and so does the prosecution, and the court holds them both to a standard of proof. What is exploitative is not design as such but design by a party the receiver depends on, without counter-measure. The next section is about the counter-measures.

# What follows for institutions

## Transparency relocates the problem

The reforms that have reshaped clinical and behavioural research since the early 2000s, registration, pre-specification, mandatory reporting, registered reports, are aimed at selection, and against selection they work. But they work by making the count known and the design visible, which is exactly the condition under which design has its full power. A pre-registered trial is a committed experiment whose result the sponsor cannot hide. It is the persuasion game of §5, instantiated. So the reforms do not remove the sponsor's ability to move the regulator; they remove one of the two channels and thereby direct all of the sponsor's effort into the other. @HolmanGeislar2018 describe the relationship between industry and its regulators as an asymmetric arms race in which each methodological safeguard is met by a new move; on the present analysis the move after registration is design, and it is a move that requires no violation of anything the registration regime asks for.

This is worth stating as a prediction, since it is one the existing literature makes only implicitly. Under a fully transparent regime, industry-sponsored studies should continue to favour their sponsors, the advantage should not be attributable to any measurable defect in conduct or reporting, and it should be concentrated in the design choices that registration leaves to the sponsor: endpoints, comparators, doses, populations, durations. The Cochrane finding that sponsorship predicts favourable outcomes independently of risk-of-bias measures [@Lundh2017] is what that prediction looks like in data, and the antipsychotic circle of @Heres2006 is what it looks like in a case. Two further features of the relocated problem make it harder to address than the original. The first is that nothing is being hidden, so the ordinary tools for detecting misconduct have nothing to find. The second is that the regulator's beliefs are correct, so the ordinary tools for detecting distortion, comparing what she believes with what the evidence supports, find nothing either. The only place the effect shows up is in the frequency of her decisions relative to what a differently designed body of evidence would have supported, and that comparison requires an account of what the evidence would have been.

The literature on industry and science has in fact already identified design-type mechanisms without marking them as such. Industrial selection [@HolmanBruner2017; @PintoPinto2023] is design at the level of the community: the funder chooses which methods get amplified. Industrial distraction [@OConnorFreeborn2025] is design at the level of the research agenda: the funder chooses which questions get asked. @Elliott2011 documents the same in environmental research. What the present analysis adds is that these mechanisms do not depend on the receiver's failing to notice them. The remedies the literature has proposed, centralised or lottery-based allocation of industry funds so that the funder cannot choose which methods to support [@PintoPinto2023], are remedies for design, and they work by taking the choice away from the interested party rather than by making it visible. That is the right shape. Transparency about a choice does nothing when the choice is the problem.

## The receiver's counter-move

The design channel works because the receiver's decision is a threshold function of her belief and the sender can aim at the threshold. It follows that the receiver's most powerful instrument is the threshold itself.

Return to the case, and suppose the regulator can commit, before the sponsor chooses his experiment, to a rule: approve if and only if the posterior probability that the drug works is at least $t$, for some $t$ she chooses. Her Bayesian-optimal threshold given her payoffs is $0.5$, but she is choosing a rule, not an act, and she is choosing it in the knowledge that the sponsor will design against it. Against a threshold of $t$, the sponsor's optimal test is again the one that every working drug passes, now with a false-positive rate of $q(t) = 0.3(1-t)/(0.7t)$, which is what it takes to put the posterior after a pass at exactly $t$. The sponsor still runs the test, because it gets him approvals with probability $0.3/t$, which exceeds the zero he would get by running nothing. And the regulator's accuracy is
$$
1 - \frac{0.3(1-t)}{t},
$$
which rises from $0.7$ at $t = 0.5$ to $0.9$ at $t = 0.75$, to $0.967$ at $t = 0.9$, and towards $1$ as $t$ approaches $1$. @fig-threshold shows the trade-off. A regulator who commits to demanding near-certainty gets, from a sponsor who wants approval, an experiment that delivers near-certainty. The value of information that a threshold of $0.5$ forfeited entirely is recovered almost entirely by a threshold of $0.95$, and the sponsor is still better off running the experiment than not. (Derivations are in the appendix.)

```{r threshold}
#| label: fig-threshold
#| fig-cap: "The regulator's accuracy and the sponsor's approval rate as a function of the approval threshold the regulator commits to, when the sponsor best-responds by designing the test. Prior that the drug works: 0.3. The dashed line is the regulator's accuracy with no evidence."
#| fig-width: 6
#| fig-height: 3.6
tibble(t = seq(0.5, 0.99, by = 0.005)) |>
  mutate(`Regulator's accuracy` = 1 - mu * (1 - t) / t,
         `Sponsor's approval rate` = mu / t) |>
  pivot_longer(-t, names_to = "quantity", values_to = "value") |>
  ggplot(aes(t, value, linetype = quantity)) +
  geom_hline(yintercept = 1 - mu, linetype = "dotted", colour = "grey40") +
  geom_line(linewidth = 0.8) +
  scale_linetype_manual(values = c("solid", "longdash")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Approval threshold the regulator commits to", y = NULL, linetype = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

Three things about this result matter philosophically.

First, it is specific to design. Against selection, the receiver's commitment to a threshold adds nothing to what her scepticism already achieves. @HartKremerPerry2017 prove, for a broad class of evidence games in which the sender chooses which verifiable evidence to disclose, that the outcome when the receiver commits to a decision rule in advance coincides with the equilibrium outcome when she does not. Against a sender who is choosing among existing results, the sceptical best response already does all the work that commitment could do. Against a sender who is choosing the experiment, commitment is the whole difference between forfeiting the value of information and recovering it. So the two channels differ not only in what neutralises them but in what kind of receiver-side response each calls for: scepticism for selection, commitment for design.

Second, the commitment must be to a rule that the receiver would not follow act by act. On the path of play the regulator never faces a posterior between $0.5$ and $t$, because the sponsor's optimal test never produces one; she sees $t$ or $0$. But the sponsor's test is optimal only because he anticipates that she would *not* approve at $0.6$. If she would, he designs for $0.6$ instead. An act-by-act Bayesian with the payoffs I have given her approves at $0.6$, and so cannot make the commitment credible. This is why the standards in question are institutional: rules of evidence, statutory approval criteria, journal policies, rather than case-by-case judgement. It also gives a rationale for those standards that is independent of the usual one. The usual story about "beyond reasonable doubt", and about the demand for substantial evidence from adequate and well-controlled investigations, is that they weigh the costs of the two kinds of error. That story is right as far as it goes, but it does not explain why the standards need to be fixed in advance and applied as rules, since a decision-maker who weighs error costs case by case can do that at the moment of decision. The present story does explain it. A standard of proof is a commitment device against parties who design evidence, and it works only because it is a commitment [see @Sanchirico1997 and @Kaplow2012, who arrive at related conclusions about the burden of proof from within law and economics, without the persuasion framework].

Third, the result reverses a lesson the naive-receiver models teach. In @WeatherallOConnorBruner2020 the policymaker does better by listening to more scientists and worse by being slow to move; stubbornness is, in that setting, a vulnerability. Against a designer, the receiver does better by being harder to move, and a rule of the form "I will not act on this until it is nearly certain" is her best protection. From outside, that looks like dogmatism. A regulator who demands two independent trials when one was significant, an editor who will not publish a surprising result without a pre-registered replication, a reader who treats a single striking finding as no reason to change her mind: each of these is, in the naive-receiver models, throwing away information. In the design setting each is the receiver refusing to let the threshold be aimed at, and the information she would have received at a lower threshold is information the designer would never have produced. @Douglas2009 argued that the choice of an evidential threshold is a value choice that scientists cannot avoid making. If that is right, the strategic environment in which the threshold will be met is one of the values that legitimately bear on it.

There are limits, and they should be stated. The result assumes experimentation is costless to the sponsor. When it is costly, a threshold set too high can lead the sponsor to run nothing, and the receiver loses the information she would have got at a lower one; @HenryOttaviani2019 analyse this trade-off and show that the receiver-optimal standard can be well short of certainty. When evidence is produced adversarially, by two parties with opposed interests and costly effort, the analysis changes again, and @DemouginFluet2006 argue that the preponderance standard is then optimal. The claim is not that receivers should always demand near-certainty. It is that a receiver facing a single designer with cheap experiments has, in the threshold, an instrument that recovers what design would otherwise take, and that the shape of the instrument, a rule fixed in advance and immune to case-by-case revision, is what the analysis predicts.

# Conclusion

I began with a finding: that an interested party can move an audience to false beliefs by sharing only true results. The finding is real but its audiences are cursed, and removing the curse divides the phenomenon into two things that behave differently. Selection, the choice of which existing results to share, depends on the audience's ignorance of what exists, and disappears when that ignorance does. Design, the choice of which experiments to run, does not depend on any ignorance at all. It moves a fully informed, fully rational audience by aiming at the threshold of her decision rule, and it leaves her with beliefs that are correct and decisions that are, in the aggregate, exactly as good as if she had no evidence.

That combination is hard to describe with the vocabulary we have. It is not lying, not deception, not misleading, and not manipulation on any account that explains what is wrong with manipulation. I have argued that it is exploitation: the use of the audience's dependence on the sender for evidence to take for himself the value that the evidence could have had for her. The description matters because it changes what a remedy has to do. A remedy for deception restores true belief; here belief was never false. A remedy for manipulation restores the operation of reason; here reason operated perfectly. A remedy for exploitation changes the terms on which the vulnerable party deals with the powerful one, and here that means either taking the choice of experiment away from the interested party or arming the audience with a commitment that forces the interested party's choice towards hers.

The transparency reforms that defeat selection do neither. They are the commitment device that design requires, and their success against the tobacco strategy's cruder half is what makes its subtler half the whole of the problem that remains. If the analysis is right, that half will not show up as misconduct, will not show up as false belief, and will show up only as a persistent tilt in the decisions of audiences whose every belief is warranted. The instrument for correcting it is one we already have and have been explaining wrongly: a standard of proof, fixed in advance, that the audience will not lower for a single case however compelling the case appears. Against a party who designs the evidence, that is not closed-mindedness. It is the only way to be open to the evidence he would otherwise never produce.

# Appendix: derivations {.appendix}

Let $\mu \in (0,1)$ be the receiver's prior that the state is $G$ (the drug works), and let the receiver take action $a$ (approve) if and only if her posterior that the state is $G$ is at least $t$, where $\mu < t < 1$. The sender's payoff is $1$ if $a$ is taken and $0$ otherwise, regardless of the state. The receiver's payoff is $1$ if she takes $a$ in state $G$ or refrains in state $B$, and $0$ otherwise. When $t = 1/2$ the threshold rule is the receiver's expected-payoff-maximising rule.

**Design.** The sender chooses an experiment with outcomes in $\{\text{pass}, \text{fail}\}$, with $\Pr(\text{pass} \mid G) = p$ and $\Pr(\text{pass} \mid B) = q$. (With a binary-action receiver one can restrict attention to experiments with two outcomes, read as action recommendations; see @KamenicaGentzkow2011.) The posterior after a pass is $\mu p / (\mu p + (1-\mu) q)$, and the receiver approves after a pass if and only if this is at least $t$, i.e. if and only if
$$
q \le \frac{\mu (1-t)}{(1-\mu)\, t}\, p .
$$
The sender's payoff is $\Pr(\text{pass}) = \mu p + (1-\mu) q$ when the receiver approves on a pass (and nothing is gained from a fail, since the posterior after a fail is below the prior and hence below $t$). This is increasing in both $p$ and $q$, so the sender sets $p = 1$ and $q$ at the bound:
$$
q^\ast(t) = \frac{\mu(1-t)}{(1-\mu)\,t}.
$$
The sender's approval probability is $\mu + (1-\mu) q^\ast = \mu / t$, and the receiver's probability of a correct decision is
$$
\mu \cdot 1 + (1-\mu)(1 - q^\ast) = 1 - \frac{\mu(1-t)}{t}.
$$
At $t = 1/2$ this equals $1 - \mu$, the receiver's accuracy with no evidence (she rejects everything). It is increasing in $t$ and tends to $1$ as $t \to 1$. The sender's approval probability $\mu/t$ is decreasing in $t$ but exceeds $\mu > 0$ for all $t < 1$, so the sender prefers to run the experiment for every threshold. With $\mu = 0.3$ and $t = 1/2$: $q^\ast = 3/7$, approval $0.6$, accuracy $0.7$.

**Selection.** Let $N$ studies be run, independent conditional on the state, each positive with probability $s$ in state $G$ and $f$ in state $B$, with $s > f$. The sender reports the positives. A cursed receiver who sees $k$ positive reports and treats them as the whole record has posterior odds $\frac{\mu}{1-\mu} (s/f)^k$. A sophisticated receiver who knows $N$ infers $N - k$ negatives and has posterior odds $\frac{\mu}{1-\mu} (s/f)^k \left(\frac{1-s}{1-f}\right)^{N-k}$, which is the posterior from full disclosure. The approval and accuracy figures in @tbl-twobytwo are computed by summing over $k$ under the binomial distribution in each state, with $N = 4$, $s = 0.8$, $f = 0.3$, $\mu = 0.3$, $t = 1/2$. With these values the cursed receiver approves for $k \ge 1$ and the sophisticated receiver for $k \ge 3$.

**A note on the comparison.** The design experiment and the four selection studies are not the same experiment, and the table is not a comparison of their informativeness. The comparison is between what each channel yields for the sender and the receiver given the receiver's sophistication. Against a sophisticated receiver, the sender who has four honest studies and can only select does no better than full disclosure, whereas the sender who can design does strictly better than full disclosure of any experiment the receiver would have chosen.
