---
title: "Changes in Citation Patters"
abstract: |
    Which journal articles are cited surprisingly often in recent times, given how often they were cited soon after publication? Conversely, which articles have a lot more citations soon after publication than you'd expect from their current prominence. This note goes over some data on these questions. NB: THIS IS INCOMPLETE BUT USEFUL TABLES HERE FOR SOMETHING THAT MIGHT BE COMPLETED.
date: today
author:
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
categories:
  - history of analytic
  - unpublished
bibliography: 
  - /Users/weath/Documents/citations-2025/cslbib.yaml
  - /Users/weath/Documents/quarto-articles/brian-quarto.bib
execute:
  echo: false
  warning: false
format:
  html:
    fig-format: svg
    fig-height: 9
    fig-width: 12
    fig-dpi: 300
    fig-responsive: true
    fontsize: 1.1rem
format-links: [html]
draft: true
---

```{r}
#| label: packages
#| cache: false

require(tidyverse)
require(knitr)
require(slider)
```

```{r}
#| label: loader
#| cache: true

load("/Users/weath/Documents/citations-2025/philo_bib.RData")
load("/Users/weath/Documents/citations-2025/philo_cite.RData")
```

```{r}
#| label: basic-setup
#| cache: true

philo_bib <- philo_bib %>%
  select(-rowid) %>%
  group_by(year) %>%
  mutate(unique_id = paste0(year, sprintf("%05d", row_number()))) %>%
  ungroup() %>%
  select(unique_id, everything()) |>
  rename(wos_id = id,
         id = unique_id)

# Add this id to citation tibble, and add years to that tibble
philo_cite <- philo_cite %>%
  left_join(philo_bib %>% select(old = id, wos_id), by = c("refs" = "wos_id")) %>%
  left_join(philo_bib %>% select(new = id, wos_id), by = c("id" = "wos_id")) %>%
  select(old, new) %>%
  mutate(old_year = as.numeric(
    str_sub(
      old,
      start = 1,
      end = 4
    )
  )
  ) %>%
  mutate(new_year = as.numeric(
    str_sub(
      new,
      start = 1,
      end = 4
    )
  )
  )

# Count citations by year
year_citations <- philo_cite |>
  group_by(new_year) |>
  tally(name = "all_citations")

# Count citations by article
citation_count <- philo_cite |>
  group_by(old) |>
  tally(name = "citations")

# Add number of citations back to philo_bib
# Remember to add extra line for 0s; they are NA after the join
philo_bib <- philo_bib |>
  left_join(
    select(
      citation_count,
      id = old,
      citations),
    by = "id"
  ) |>
  replace_na(list(citations = 0))

# This tibble does two things
# First, it counts how many articles have N cites, for each N
# Second, it counts how many articles have at least N cites
how_many_cites <- philo_bib |>
  group_by(citations) |>
  tally(name = "article_count") |>
  arrange(-citations) |>
  mutate(running_articles = cumsum(article_count))
```

```{r}
#| label: high-cites
#| cache: false

# What we'll count as a widely cited article for this study
high_cite_cutoff <- 50

# Filter philo_bib down to the widely cited
highly_cited <- philo_bib |>
  filter(citations >= high_cite_cutoff) 

# For each article in highly_cited, work out how often it is cited each year
# The complete line is to allow for 0s
# Then comapre that to how many cites there are in general that year
cites_high_with_age <- philo_cite |>
  filter(old %in% highly_cited$id) |>
  group_by(old, old_year, new_year) |>
  tally(name = "article_citations") |>
  ungroup() |>
  complete(nesting(old, old_year), new_year, fill = list(article_citations = 0)) |> # Nesting because old_year goes with old
  filter(new_year >= old_year) |>
  mutate(age = new_year - old_year) |>
  left_join(year_citations, by = "new_year" ) |>
  mutate (cite_per_k = 1000 * article_citations/all_citations) |>
  group_by(old) |>
  arrange(new_year) |>
  mutate(cites_through_year = cumsum(article_citations))

# For every cutoff between 5 years after publication and 2018, add a row for that cutoff
highly_cited <- highly_cited |>
  expand(id, crossing = 1975:2018) |>
  left_join(philo_bib, by = "id") |>
  filter(crossing >= year + 7,
         year >= 1970)

rev_cum_citations <- year_citations |>
  filter(new_year <= 2022) |>
  rename(this_year = all_citations) |>
  arrange(
    desc(
      new_year
    )) |>
  mutate(this_and_next_year = slide_int(this_year, sum, .before = 1)) |>
  mutate(citations_onward = cumsum(this_year))

prop_finder <- tibble(
  pub_year = 1970:2022,
  cite_year = 1970:2022
) |>
  expand(pub_year, cite_year) |>
  filter(cite_year >= pub_year + 7,
         cite_year <= 2018) |>
  left_join(
    select(rev_cum_citations,
           pub_year = new_year,
           avail_citations = citations_onward),
    by = "pub_year"
  ) |>
  left_join(
    select(rev_cum_citations,
           cite_year = new_year,
           cite_year_onwards = citations_onward),
    by = "cite_year"
  ) |>
  left_join(
    select(rev_cum_citations,
           cite_year = new_year,
           cite_year_itself = this_year),
    by = "cite_year"
  ) |>
  left_join(
    select(rev_cum_citations,
           pub_year = new_year,
           early_window = this_and_next_year),
    by = "pub_year"
  ) |>
  mutate(late = cite_year_onwards - cite_year_itself,
         early = avail_citations - late - early_window,
         prop_early = early/(early + late)) 
```



```{r}
#| label: bloomers
#| cache: false
highly_cited_analysis <- highly_cited |>
  left_join(
    select(prop_finder,
           year = pub_year,
           crossing = cite_year,
           prop_early),
            by = c("year", "crossing")) |>
  left_join(
    select(
      cites_high_with_age,
      id = old,
      crossing = new_year,
      early = cites_through_year
    ), by = c("id", "crossing")) |>
    mutate(early_prob = pbinom(
      q = early,
      size = citations,
      prob = prop_early,
      log.p = TRUE))

late_bloomers <- highly_cited_analysis |>
  filter(early_prob < -4) |>
  ungroup() |>
  group_by(id) |>
  slice_min(order_by = early_prob,
            n = 1) |>
  arrange(early_prob) |>
  mutate(early_prob = early_prob/log(10))

bloom_year <- late_bloomers |>
  ungroup() |>
  group_by(crossing) |>
  tally()


early_bloomers <- highly_cited |>
  left_join(
    select(prop_finder,
           year = pub_year,
           crossing = cite_year,
           prop_early),
    by = c("year", "crossing")) |>
  left_join(
    select(
      cites_high_with_age,
      id = old,
      crossing = new_year,
      early = cites_through_year
    ), by = c("id", "crossing")) |>
  mutate(late_prob = pbinom(
    q = citations - early,
    size = citations,
    prob = 1 - prop_early,
    log.p = TRUE))|>
  filter(late_prob < -4) |>
  ungroup() |>
  group_by(id) |>
  slice_min(order_by = late_prob,
            n = 1) |>
  arrange(late_prob) |>
  mutate(late_prob = late_prob/log(10))
```

The citation history of the typical philosophy paper is nasty, brutish, and short. If the paper gets cited at all, it gets most of those citations within a few years of publication, then exits, gracefully or not, into history. But a few papers buck this trend. Despite not getting a particularly large amount of attention when they are first published, they become widely discussed some time later. I'll call these papers _late bloomers_. This paper identifies some of these, and looks at what they can tell us about the history of very recent philosophy.

The opposite of a late bloomer is an early bloomer, a paper that gets most of its citations out of the way quickly. Most papers are early bloomers, but some are more extreme than others. This could be for several reasons. Historically, when academics often had better access to books than journals, a paper could cease to be cited simply because it was reprinted in an anthology. But like with the late bloomers, looking at the early bloomers collectively can tell us something about the history of philosophy.

Many of the late bloomers concern social, or at least interpersonal, issues. This reflects the rise in importance in social philosophy (which I'll hereafter understand to include interpersonal), especially since 2018. The early bloomers cover a wider range of topics, but one frequent pattern is that they reflect the presuppositions of the modal era in analytic philosophy.

_Modal era_ is Ted Sider's term for a particular era in metaphysics [@Sider2020 x]. I'm using it slightly more broadly, to pick out a trend across philosophy as a whole. But I'm mostly following Sider in taking it to pick out a period, very roughly 1970 to 2010, where issues about modality became central to philosophy.

There are two particularly striking things about the modal era. 

The slightly less striking is that it became more or less universally accepted that it was at least legimate to use modal and nomic notions to set out philosophical theories. The modal and nomic notions most commonly used were necessity, causation, and counterfactuals. The phenomena I want to stress here can be brought out by thinking about the reception to the counterfactual based theories of knowledge and mental content defended by Robert @Nozick1979 and Jerry @Fodor1987 respectively.

There are several reasons you might object to using counterfactuals here. You might say, with some positivists, that counterfactual claims are unverifiable and hence meaningless. You might say, with some post-positivists, that counterfactuals are so confused and confusing that the resulting philosophical theories will not be at all enlightening. You might say, and this is a more common complaint since the modal era, that counterfactuals are so context-sensitive, and subject to human interests, that they are too subjective to use in an account of objective things like knowledge and content. Although Nozick's and Fodor's theories were very widely discussed at the time, and very widely rejected, they were not largely rejected for any of these reasons. Even the critics, and there were many critics, typically accepted that these were reasonable tools for Nozick and Fodor to use. They just thought the theories were wrong. It's that concession that I want to highlight; it tells us something about the acceptance of modality in philosophy.

The more striking thing is how many theories were understood to simply be modal claims. Origin essentialism, as in @Kripke1972, was simply identified with a necessity of origins claim. Whether mental content was 'in the head' was simply identified with the truth or falsity of a modal supervenience claim. And, this will be the one we talk about the most, whether the world is entirely physical was also identified with some kind of supervenience claim. This last one is fascinating because there was such widespread agreement that if physicalism was anything, it was some kind of supervenience claim. This agreement persisted in the face of disagreement about (a) which supervenience claim it was, (b) whether physicalism was even true, and (c) whether physicalism was even an intelligible claim.

What we see between these two 'striking things' is that philosophers thought it was almost always permissible to give a modal answer to a philosophical question, and often enough, it was obligatory. Very few philosophers endorsed the ontology of modality Lewis put forward in _Plurality_, but they by and large agreed with him that modal space was "A Philosopher's Paradise" [@Lewis1986].

Over the last two decades, all that has changed. We'll see this in the early bloomers data, espeically with the citation history of papers particularly on physicalism and on content. In metaphysics, it has become somewhat common to use grounding notions to do the work that used to be done by modality. But this does not mean we're in a grounding era in philosophy, or even, as Sider puts it, a 'post-modal' era. Rather

<!--

```{r}
#| label: examples
#| cache: false

first_ex <- 2
second_ex <- 4

ex1_title <- late_bloomers$title[first_ex]
ex1_bib <- late_bloomers$bib[first_ex]
ex1_crossing <- late_bloomers$crossing[first_ex]
ex1_year <- late_bloomers$year[first_ex]
ex1_latecite <- late_bloomers$cites_after[first_ex]
ex1_earlycite <- late_bloomers$cites_before[first_ex]
ex1_allcite <- late_bloomers$citations[first_ex]
ex1_percentafter <- scales::percent(ex1_latecite / late_bloomers$citations[first_ex])
ex1_yearbefore <- late_bloomers$year_before[first_ex]
ex1_yearafter <- late_bloomers$year_after[first_ex]
ex1_exppercent <- scales::percent(ex1_yearbefore / (ex1_yearbefore + ex1_yearafter), accuracy = 1)
ex1_earlyprob <- late_bloomers$early_prob[first_ex]

ex2_title <- late_bloomers$title[second_ex]
ex2_bib <- late_bloomers$bib[second_ex]
ex2_crossing <- late_bloomers$crossing[second_ex]
ex2_year <- late_bloomers$year[second_ex]
ex2_latecite <- late_bloomers$cites_after[second_ex]
ex2_earlycite <- late_bloomers$cites_before[second_ex]
ex2_allcite <- late_bloomers$citations[second_ex]
ex2_percentafter <- scales::percent(ex2_latecite / late_bloomers$citations[second_ex])
ex2_yearbefore <- late_bloomers$year_before[second_ex]
ex2_yearafter <- late_bloomers$year_after[second_ex]
ex2_exppercent <- scales::percent(ex2_yearbefore / (ex2_yearbefore + ex2_yearafter), accuracy = 1)
ex2_earlyprob <- late_bloomers$early_prob[second_ex]
```

"`r ex1_title`" [`r ex1_bib`] gets talked about a lot in philosophy journals. In a study I did of one hundred prominent philosophy journals, it has been cited `r ex1_latecite` times after `r ex1_crossing`. That's a lot, and it's a lot more than you might have expected in `r ex1_crossing`, at which time it had been cited `r ex1_earlycite` times. Here's one way to get a sense of how much more.

"`r ex1_title`" was published in `r ex1_year`. Papers published in those 100 journals in `r ex1_year` were cited (in the journals I'm studying) `r ex1_yearbefore` times through `r ex1_crossing`. They have been cited `r ex1_yearafter` times since then. So about `r ex1_exppercent` of citations of articles published in `r ex1_year` were in or before `r ex1_crossing`.

Imagine a binomial process, with two options, 'early' and 'late'. We'll run the process `r ex1_allcite` times, one for each citation to "`r ex1_title`". The probability of the process saying 'early' will be `r ex1_exppercent`, since for articles in general published in `r ex1_year`, that's how often their citations are in or before `r ex1_crossing`. How likely is it that we'll end up with `r ex1_earlycite` or fewer of the results being 'early', as actually happened with cites to "`r ex1_title`"?

The answer is not very likely at all. The probability of getting a result this extreme is about 10^-`r round(ex1_earlyprob)`^. I think that meets most tests for statistical significance!

We see a similar pattern with "`r ex2_title`" [`r ex2_bib`]. Through `r ex2_crossing`, it had been cited `r ex2_earlycite` times; since then it has been cited `r ex2_latecite`. In general, articles published in `r ex2_year`, as it was, have about `r ex2_exppercent` of their citations in or before `r ex2_crossing`. The probability of a binominal process with `r ex2_earlycite` + `r ex2_latecite` = `r ex2_allcite` trials, and a probability of saying 'early' of `r ex2_exppercent`, having `r ex2_earlycite` or fewer outcomes of 'early' is about 10^-`r round(ex2_earlyprob)`^. This paper too has many more recent citations than you'd expect, though in this case we're taking 'recent' to mean after `r ex2_crossing`, not `r ex1_crossing`.

I ran this same calculation for every paper in the study with 50 or more citations in philosophy journals, and for every possible division of time into 'early' and 'late' such that the late year was no later than 2018, and there were at least five years after publication which were early.^[My citation data only runs through 2022, so when the cutoff is 2018, that did only leave four years of 'late' data. Less than that really felt like it could be noise.] @tbl-late-bloomers shows the most extreme results.

```{r}
#| label: tbl-late-bloomers
#| tbl-cap: "Papers with more recent citations than is typical."
#| column: page-right

require(knitr)
require(tidyverse)

# kable(
#   late_bloomers |>
#     mutate(
#       Article = paste0(
#         displayauth,
#         " -",
#         bib,
#         " \"",
#         title,
#         "\""
#       ),
#       Typical = scales::percent(year_before/(year_before + year_after), accuracy = 1),
#       Prob = round(early_prob, 1)
#     ) |>
#     select(Article,
#            Cutoff = crossing,
#            Early = cites_before,
#            Late = cites_after,
#            Typical,
#            Prob) |>
#     slice(1:100),
#     align = c('l', 'r', 'r', 'r', 'r', 'r')
# )
```

In @tbl-late-bloomers, 'Cutoff' is the boundary between early and late that's being used in that row. 'Early' is the number of times the paper was cited (in philosophy journals) through that cutoff year, and 'Late' is the number of times it has been cited after that. 'Typical' is the proportion of citations articles published in the year the article was cited through the cutoff year. And Prob is log~10~ of the probability of a binomial process with that probability getting a result that extreme.

I calculated this Prob value for every article with 50 or more citation, and every cutoff from five years after publication to 2018. For each article, I selected the smallest value of Prob. I then selected the 100 articles for which Prob is lowest. Note that I didn't select the 100 pairs of articles-cutoffs for which Prob is lowest. If I'd done that, I would have a list where "Famine, Affluence, and Morality" was repeated ten times at the top.^[The Prob value isn't much changed for any cutoff between 1997 and 2006.] Just including each paper once is a bit more informative.
-->

There are a few reasons why articles might turn up on a list like this.

- Some papers are in topics that are much more central to philosophy now than they were at the time of publication. This is especially true for papers concerned with social and interpersonal topics, such as @WOS000085841900002, @WOSA1977EA35800003, @WOSA1993MJ74900002, and @WOS000170434600004.
- Some papers are important instances of approaches that were not as prominent at the time they were published. This starts at the top of the list; utilitarianism wasn't nearly as prominent in the late twentieth century as in the twenty-first century.
- And, as Eric Schwitzgebel pointed out on an earlier post, in some cases what we're seeing is just the normal pattern of highly cited papers. This is, I think, what's happening with @WOS000234431300006 and @WOS000165361800002. Note that I'm comparing the trends in citations of papers like these to the citations of all papers published the same year. If it takes a while for the literature to settle on what the most important papers are, and after that time the other papers drop away, then papers like these could appear on the list as much by not having their citation rates decay as by becoming particularly more prominent.

What about the other end of the scale? To look at the other end, we create the same binomial distribution, but this time look at articles where it is surprising that there are this few or fewer citations after the cutoff. These are the articles that had a strikingly high number of early citations, given what happened later. The top of that list is shown in @tbl-early-bloomers.

<!--

```{r}
#| label: tbl-early-bloomers
#| tbl-cap: "Papers with more early citations than is typical."
#| column: page-right

require(knitr)
require(tidyverse)

# kable(
#   early_bloomers |>
#     mutate(
#       Article = paste0(
#         displayauth,
#         " -",
#         bib,
#         " \"",
#         title,
#         "\""
#       ),
#       Typical = scales::percent(year_before/(year_before + # year_after), accuracy = 1),
#       Prob = round(late_prob, 1)
#     ) |>
#     select(Article,
#            Cutoff = crossing,
#            Early = cites_before,
#            Late = cites_after,
#            Typical,
#            Prob) |>
#     slice(1:100),
#     align = c('l', 'r', 'r', 'r', 'r', 'r')
# )
```

Even though I've let the Prob values get a fair bit higher than on @tbl-late-bloomers, the list is still somewhat shorter. I think this is because of the third point above; having a later than usual distribution of citations is par for the course among widely cited articles. That said, there are several more reasons why an article's citations might be weighted towards early citations than that it might be weighted towards late citations.
-->

- The article might get superseded. This happens especially if the same author puts out a later piece that is simply better than the earlier one. I think this is what's going on with @WOSA1978EL93700009; eventually people came to think of later works, such as @WOSA1984TV24600001, as simply better. I suspect it's also true with some of the philosophy of biology papers on this list; that has been a fast moving field, and even very good papers get replaced in the canon by more up to date ones.
- The article might be incorporated into a book, and the citations move to the book. That's pretty clearly what's happened with @WOSA1985APA8500001 and @WOS000262577100002.
- There is a technical issue here with reprints in collected volumes. Web of Science _sometimes_ puts together citations to a paper in a volume with citations in the original journal, but it doesn't always. This also affects the citations to the Kim papers, and I think that's why @WOS000228214500002 is here.
- Sometimes the discipline gets into the habit of citing one paper in lieu of a family of papers that developed a point. So anyone who wants to point in the general direction of Joshua Knobe's mid-2000s work on intention cites @WOS000183806600005, while his other papers from around the same time end up on lists like this.
- And sometimes the discipline just loses interest in a topic. So we have a lot of papers here on intuitions, and on supervenience. After the boom in interest in vagueness in the 2000s, citations to @WOSA1970ZE32000003 and @10.2307_2025110 came back to earth. Even what seemed like completely central issues about modality and about mental content don't seem immune to this.

I think there is an interesting story in how many of the most influential, at least at the time, papers of the 1980s and 1990s are now not playing a major role in philosophical conversations. This did not, on the whole, happen to the other decades. There are obviously plenty of papers from the 1970s and 2000s on @tbl-early-bloomers. But they did not seem, on the whole, to be quite as central to philosophy at their time as the papers on that list from the 1980s or 1990s.^[Or if they are, as @WOS000262577100002 surely was, the reason they are here is because citations to a paper were simply replaced by citations to a book; they didn't just fall away.]

But that's for later work. For now I just wanted to post these lists of which papers were distinctively late bloomers and early bloomers, and offer some tentative suggestions for what the nature of those lists tells us about the last half-century of philosophy.