
## 1956 {#sec-s1956}

### Widely Cited Articles {-}

1. Willard van Orman Quine [-@WOSA1956CEQ2500001] "Quantifiers and Propositional Attitudes"
2. Gottlob Frege [-@WOSA1956CHJ4400001] "The Thought: A Logical Inquiry"
3. H. P. Grice and P. F. Strawson [-@WOSA1956CGZ5700001] "In Defense of a Dogma"
4. John G. Kemeny and Paul Oppenheim [-@WOSA1956CFA0700002] "On Reduction"

### Citation Count {-#sec-count-1956}

```{r}
#| label: tbl-citation-count-1956
#| tbl-cap: Citation count for widely cited articles from 1956.

year_cites <- rank_table_generator(1956)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1956}

```{r}
#| label: tbl-citation-rank-1956
#| tbl-cap: Citation rank for widely cited articles from 1956.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1956}

```{r}
#| label: fig-citation-spaghetti-1956
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1956.
#| cache: FALSE

rolling_spaghetti_graph(1956)
```

```{r}
#| label: fig-citation-facet-1956
#| fig-cap: Faceted version of @fig-citation-spaghetti-1956.
#| cache: FALSE

rolling_facet_graph(1956)
```

\newpage


## 1957 {#sec-s1957}

### Widely Cited Articles {-}

1. H. P. Grice [-@WOSA1957CGZ6000005] "Meaning"
2. Zeno Vendler [-@WOSA1957CCQ4200001] "Verbs and Times"

### Citation Count {-#sec-count-1957}

```{r}
#| label: tbl-citation-count-1957
#| tbl-cap: Citation count for widely cited articles from 1957.

year_cites <- rank_table_generator(1957)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1957}

```{r}
#| label: tbl-citation-rank-1957
#| tbl-cap: Citation rank for widely cited articles from 1957.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1957}

```{r}
#| label: fig-citation-spaghetti-1957
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1957.
#| cache: FALSE

rolling_spaghetti_graph(1957)
```

```{r}
#| label: fig-citation-facet-1957
#| fig-cap: Faceted version of @fig-citation-spaghetti-1957.
#| cache: FALSE

rolling_facet_graph(1957)
```

\newpage


## 1958 {#sec-s1958}

### Widely Cited Articles {-}

1. G. E. M. Anscombe [-@WOSA1958CDL1000001] "Modern Moral Philosophy"
2. John R. Searle [-@WOSA1958CCP4400002] "Proper Names"
3. John Rawls [-@WOSA1958CGZ6200002] "Justice as Fairness"
4. Stuart Hampshire and H. L. A. Hart [-@WOSA1958CGZ9600001] "Decision, Intention and Certainty"

### Citation Count {-#sec-count-1958}

```{r}
#| label: tbl-citation-count-1958
#| tbl-cap: Citation count for widely cited articles from 1958.

year_cites <- rank_table_generator(1958)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1958}

```{r}
#| label: tbl-citation-rank-1958
#| tbl-cap: Citation rank for widely cited articles from 1958.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1958}

```{r}
#| label: fig-citation-spaghetti-1958
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1958.
#| cache: FALSE

rolling_spaghetti_graph(1958)
```

```{r}
#| label: fig-citation-facet-1958
#| fig-cap: Faceted version of @fig-citation-spaghetti-1958.
#| cache: FALSE

rolling_facet_graph(1958)
```

\newpage


## 1959 {#sec-s1959}

### Widely Cited Articles {-}

1. J. J. C. Smart [-@WOSA1959CGZ6600001] "Sensations and Brain Processes"
2. Frank Sibley [-@WOSA1959CGZ6800001] "Aesthetic Concepts"
3. A. N. Prior [-@WOSA1959CDK2600002] "Thank Goodness That"s Over"
4. Karl R. Popper [-@WOSA1959CGZ2000003] "The Propensity Interpretation of Probability"
5. Michael Dummett [-@WOSA1959CGZ6700003] "Wittgenstein's Philosophy of Mathematics"

### Citation Count {-#sec-count-1959}

```{r}
#| label: tbl-citation-count-1959
#| tbl-cap: Citation count for widely cited articles from 1959.

year_cites <- rank_table_generator(1959)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1959}

```{r}
#| label: tbl-citation-rank-1959
#| tbl-cap: Citation rank for widely cited articles from 1959.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1959}

```{r}
#| label: fig-citation-spaghetti-1959
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1959.
#| cache: FALSE

rolling_spaghetti_graph(1959)
```

```{r}
#| label: fig-citation-facet-1959
#| fig-cap: Faceted version of @fig-citation-spaghetti-1959.
#| cache: FALSE

rolling_facet_graph(1959)
```

\newpage


## 1960 {#sec-s1960}

### Widely Cited Articles {-}

1. Peter T. Geach [-@WOSA1960CCQ4500006] "Ascriptivism"
2. Norman Malcolm [-@WOSA1960CCQ4400003] "Anselm's Ontological Arguments"

### Citation Count {-#sec-count-1960}

```{r}
#| label: tbl-citation-count-1960
#| tbl-cap: Citation count for widely cited articles from 1960.

year_cites <- rank_table_generator(1960)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1960}

```{r}
#| label: tbl-citation-rank-1960
#| tbl-cap: Citation rank for widely cited articles from 1960.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1960}

```{r}
#| label: fig-citation-spaghetti-1960
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1960.
#| cache: FALSE

rolling_spaghetti_graph(1960)
```

```{r}
#| label: fig-citation-facet-1960
#| fig-cap: Faceted version of @fig-citation-spaghetti-1960.
#| cache: FALSE

rolling_facet_graph(1960)
```

\newpage


## 1961 {#sec-s1961}

### Widely Cited Articles {-}

1. J. J. C. Smart [-@WOSA1961CCP4900001] "Free-Will, Praise and Blame"
2. J. R. Lucas [-@WOSA1961CDK3300002] "Minds, Machines and Gödel"
3. I. J. Good [-@WOSA1961CFT2300005] "A Causal Calculus (I)"

### Citation Count {-#sec-count-1961}

```{r}
#| label: tbl-citation-count-1961
#| tbl-cap: Citation count for widely cited articles from 1961.

year_cites <- rank_table_generator(1961)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1961}

```{r}
#| label: tbl-citation-rank-1961
#| tbl-cap: Citation rank for widely cited articles from 1961.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1961}

```{r}
#| label: fig-citation-spaghetti-1961
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1961.
#| cache: FALSE

rolling_spaghetti_graph(1961)
```

```{r}
#| label: fig-citation-facet-1961
#| fig-cap: Faceted version of @fig-citation-spaghetti-1961.
#| cache: FALSE

rolling_facet_graph(1961)
```

\newpage


## 1962 {#sec-s1962}

### Widely Cited Articles {-}

1. Hilary Putnam [-@WOSA1962CET8000004] "It Ain't Necessarily So"
2. E. J. Lemmon [-@WOSA1962CGX0600001] "Moral Dilemmas"
3. John R. Searle [-@WOSA1962CGX0800001] "Meaning and Speech Acts"
4. Jaako Hintikka [-@WOSA1962CGX0500001] "Cogito, Ergo Sum: Inference or Performance?"

### Citation Count {-#sec-count-1962}

```{r}
#| label: tbl-citation-count-1962
#| tbl-cap: Citation count for widely cited articles from 1962.

year_cites <- rank_table_generator(1962)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1962}

```{r}
#| label: tbl-citation-rank-1962
#| tbl-cap: Citation rank for widely cited articles from 1962.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1962}

```{r}
#| label: fig-citation-spaghetti-1962
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1962.
#| cache: FALSE

rolling_spaghetti_graph(1962)
```

```{r}
#| label: fig-citation-facet-1962
#| fig-cap: Faceted version of @fig-citation-spaghetti-1962.
#| cache: FALSE

rolling_facet_graph(1962)
```

\newpage


## 1964 {#sec-s1964}

### Widely Cited Articles {-}

1. Arthur Danto [-@WOSA1964CEU2900005] "The Artworld"
2. P. F. Strawson [-@WOSA1964CGZ7200001] "Intention and Convention in Speech Acts"
3. John R. Searle [-@WOSA1964CGZ6900003] "How To Derive Ought From Is"
4. Michael Dummett [-@WOSA1964CGZ7100003] "Bringing About the Past"
5. George Dickie [-@WOSA1964CKG3400005] "The Myth of the Aesthetic Attitude"

### Citation Count {-#sec-count-1964}

```{r}
#| label: tbl-citation-count-1964
#| tbl-cap: Citation count for widely cited articles from 1964.

year_cites <- rank_table_generator(1964)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1964}

```{r}
#| label: tbl-citation-rank-1964
#| tbl-cap: Citation rank for widely cited articles from 1964.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1964}

```{r}
#| label: fig-citation-spaghetti-1964
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1964.
#| cache: FALSE

rolling_spaghetti_graph(1964)
```

```{r}
#| label: fig-citation-facet-1964
#| fig-cap: Faceted version of @fig-citation-spaghetti-1964.
#| cache: FALSE

rolling_facet_graph(1964)
```

\newpage


## 1965 {#sec-s1965}

### Widely Cited Articles {-}

1. Paul Benacerraf [-@WOSA1965CGZ7300005] "What Numbers Could Not Be"
2. Gilbert Harman [-@WOSA1965CGZ7300007] "The Inference To the Best Explanation"
3. Peter T. Geach [-@WOSA1965CGZ7600002] "Assertion"
4. J. L. Mackie [-@WOSA1965CKS0700001] "Causes and Conditions"
5. Richard Rorty [-@WOSA1965CJV5800002] "Mind-Body Identity, Privacy, and Categories"
6. David L. Hull [-@WOSA1965CFT3500004] "The Effect of Essentialism on Taxonomy: 2000 Years of Stasis (I)"
7. Frank Sibley [-@WOSA1965CGZ7400001] "Aesthetic and Non-Aesthetic"
8. Joel Feinberg [-@WOSA1965CJR9200004] "The Expressive Function of Punishment"

### Citation Count {-#sec-count-1965}

```{r}
#| label: tbl-citation-count-1965
#| tbl-cap: Citation count for widely cited articles from 1965.

year_cites <- rank_table_generator(1965)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1965}

```{r}
#| label: tbl-citation-rank-1965
#| tbl-cap: Citation rank for widely cited articles from 1965.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1965}

```{r}
#| label: fig-citation-spaghetti-1965
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1965.
#| cache: FALSE

rolling_spaghetti_graph(1965)
```

```{r}
#| label: fig-citation-facet-1965
#| fig-cap: Faceted version of @fig-citation-spaghetti-1965.
#| cache: FALSE

rolling_facet_graph(1965)
```

\newpage


## 1966 {#sec-s1966}

### Widely Cited Articles {-}

1. Keith S. Donnellan [-@WOSA1966ZC83800001] "Reference and Definite Descriptions"
2. David Lewis [-@WOSA1966ZC30400002] "An Argument for the Identity Theory"
3. C. B. Martin and Max Deutscher [-@WOSA1966ZC83700002] "Remembering"
4. Bas C. van Fraassen [-@WOSA1966ZC32000001] "Singular Terms, Truth-Value Gaps, and Free Logic"
5. Jaegwon Kim [-@WOSA1966ZJ00300003] "On the Psycho-Physical Identity Theory"
6. Roderick M. Chisholm and Ernest Sosa [-@WOSA1966ZJ00300005] "Logic of Intrinsically Better"

### Citation Count {-#sec-count-1966}

```{r}
#| label: tbl-citation-count-1966
#| tbl-cap: Citation count for widely cited articles from 1966.

year_cites <- rank_table_generator(1966)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1966}

```{r}
#| label: tbl-citation-rank-1966
#| tbl-cap: Citation rank for widely cited articles from 1966.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1966}

```{r}
#| label: fig-citation-spaghetti-1966
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1966.
#| cache: FALSE

rolling_spaghetti_graph(1966)
```

```{r}
#| label: fig-citation-facet-1966
#| fig-cap: Faceted version of @fig-citation-spaghetti-1966.
#| cache: FALSE

rolling_facet_graph(1966)
```

\newpage


## 1967 {#sec-s1967}

### Widely Cited Articles {-}

1. Donald Davidson [-@WOSA1967ZP14500007] "Truth and Meaning"
2. Alvin I. Goldman [-@WOSA1967ZC33900001] "A Causal Theory of Knowing"
3. Donald Davidson [-@WOSA1967ZC34800001] "Causal Relations"
4. Hector-Neri Castañeda [-@WOSA1967ZH25100001] "Indicators and Quasi-Indicators"
5. Kenneth F. Schaffner [-@WOSA1967ZC89200003] "Approaches To Reduction"
6. Hilary Putnam [-@WOSA1967ZC33500002] "Time and Physical Geometry"
7. Ian Hacking [-@WOSA1967ZC89400002] "Slightly More Realistic Personal Probability"
8. Ian Hacking [-@WOSA1967ZC84100001] "Possibility"

### Citation Count {-#sec-count-1967}

```{r}
#| label: tbl-citation-count-1967
#| tbl-cap: Citation count for widely cited articles from 1967.

year_cites <- rank_table_generator(1967)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1967}

```{r}
#| label: tbl-citation-rank-1967
#| tbl-cap: Citation rank for widely cited articles from 1967.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1967}

```{r}
#| label: fig-citation-spaghetti-1967
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1967.
#| cache: FALSE

rolling_spaghetti_graph(1967)
```

```{r}
#| label: fig-citation-facet-1967
#| fig-cap: Faceted version of @fig-citation-spaghetti-1967.
#| cache: FALSE

rolling_facet_graph(1967)
```

\newpage


## 1968 {#sec-s1968}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1968ZE29500001] "Counterpart Theory and Quantified Modal Logic"
2. Sydney Shoemaker [-@WOSA1968ZE30900001] "Self-Reference and Self-Awareness"
3. Barry Stroud [-@WOSA1968ZE29900001] "Transcendental Arguments"
4. Peter Unger [-@WOSA1968ZE29600001] "An Analysis of Factual Knowledge"
5. Herbert Morris [-@WOSA1968ZL99200001] "Persons and Punishment"
6. Willard van Orman Quine [-@WOSA1968ZE29700001] "Ontological Relativity"
7. Bas C. van Fraassen [-@WOSA1968ZE29500003] "Presupposition, Implication, and Self-Reference"
8. Gilbert Harman [-@WOSA1968ZB45300003] "Knowledge, Inference, and Explanation"

### Citation Count {-#sec-count-1968}

```{r}
#| label: tbl-citation-count-1968
#| tbl-cap: Citation count for widely cited articles from 1968.

year_cites <- rank_table_generator(1968)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1968}

```{r}
#| label: tbl-citation-rank-1968
#| tbl-cap: Citation rank for widely cited articles from 1968.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1968}

```{r}
#| label: fig-citation-spaghetti-1968
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1968.
#| cache: FALSE

rolling_spaghetti_graph(1968)
```

```{r}
#| label: fig-citation-facet-1968
#| fig-cap: Faceted version of @fig-citation-spaghetti-1968.
#| cache: FALSE

rolling_facet_graph(1968)
```

\newpage


## 1969 {#sec-s1969}

### Widely Cited Articles {-}

1. Harry G. Frankfurt [-@WOSA1969Y444700002] "Alternate Possibilities and Moral Responsibility"
2. H. P. Grice [-@WOSA1969Y406100001] "Utterer's Meaning and Intentions"
3. Keith Lehrer and Thomas Paxson Jr. [-@WOSA1969Y443200001] "Knowledge: Undefeated Justified True Belief"
4. Bas C. van Fraassen [-@WOSA1969Y443900001] "Facts and Tautological Entailments"
5. J. A. Goguen [-@WOSA1969ZP70500001] "The Logic of Inexact Concepts"

### Citation Count {-#sec-count-1969}

```{r}
#| label: tbl-citation-count-1969
#| tbl-cap: Citation count for widely cited articles from 1969.

year_cites <- rank_table_generator(1969)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1969}

```{r}
#| label: tbl-citation-rank-1969
#| tbl-cap: Citation rank for widely cited articles from 1969.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1969}

```{r}
#| label: fig-citation-spaghetti-1969
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1969.
#| cache: FALSE

rolling_spaghetti_graph(1969)
```

```{r}
#| label: fig-citation-facet-1969
#| fig-cap: Faceted version of @fig-citation-spaghetti-1969.
#| cache: FALSE

rolling_facet_graph(1969)
```

\newpage


## 1970 {#sec-s1970}

### Widely Cited Articles {-}

1. Fred Dretske [-@WOSA1970ZE33800001] "Epistemic Operators"
2. David Lewis [-@WOSA1970ZE32700001] "How To Define Theoretical Terms"
3. Kendall L. Walton [-@WOSA1970Y384700002] "Categories of Art"
4. Robert C. Stalnaker [-@WOSA1970G279500005] "Probability and Conditionals"
5. Sydney Shoemaker [-@WOSA1970Y183500001] "Persons and Their Pasts"
6. Willard van Orman Quine [-@WOSA1970ZE32000003] "On the Reasons for Indeterminacy of Translation"
7. Bas C. van Fraassen [-@WOSA1970H499300001] "On Extension of Beths Semantics of Physical Theories"
8. Richard Rorty [-@WOSA1970ZE32600001] "Incorrigibility as Mark of Mental"

### Citation Count {-#sec-count-1970}

```{r}
#| label: tbl-citation-count-1970
#| tbl-cap: Citation count for widely cited articles from 1970.

year_cites <- rank_table_generator(1970)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1970}

```{r}
#| label: tbl-citation-rank-1970
#| tbl-cap: Citation rank for widely cited articles from 1970.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1970}

```{r}
#| label: fig-citation-spaghetti-1970
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1970.
#| cache: FALSE

rolling_spaghetti_graph(1970)
```

```{r}
#| label: fig-citation-facet-1970
#| fig-cap: Faceted version of @fig-citation-spaghetti-1970.
#| cache: FALSE

rolling_facet_graph(1970)
```

\newpage


## 1971 {#sec-s1971}

### Widely Cited Articles {-}

1. Harry G. Frankfurt [-@10.2307_2024717] "Freedom of the Will and the Concept of a Person"
2. Judith Jarvis Thomson [-@WOSA1971Y116900003] "A Defense of Abortion"
3. Derek Parfit [-@WOSA1971Y036400001] "Personal Identity"
4. D. C. Dennett [-@10.2307_2025382] "Intentional Systems"
5. David Lewis [-@10.2307_2024902] "Counterparts of Persons and Their Bodies"
6. George Boolos [-@10.2307_2025204] "The Iterative Conception of Set"
7. William P. Alston [-@WOSA1971Y185900002] "Varieties of Privileged Access"
8. R. Eugene Bales [-@WOSA1971Y185900004] "Act-Utilitarianism: Account of Right-Making Characteristics or Decision-Making Procedure"
9. Alvin I. Goldman [-@10.2307_2024949] "The Individuation of Action"

### Citation Count {-#sec-count-1971}

```{r}
#| label: tbl-citation-count-1971
#| tbl-cap: Citation count for widely cited articles from 1971.

year_cites <- rank_table_generator(1971)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1971}

```{r}
#| label: tbl-citation-rank-1971
#| tbl-cap: Citation rank for widely cited articles from 1971.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1971}

```{r}
#| label: fig-citation-spaghetti-1971
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1971.
#| cache: FALSE

rolling_spaghetti_graph(1971)
```

```{r}
#| label: fig-citation-facet-1971
#| fig-cap: Faceted version of @fig-citation-spaghetti-1971.
#| cache: FALSE

rolling_facet_graph(1971)
```

\newpage


## 1972 {#sec-s1972}

### Widely Cited Articles {-}

1. Peter Singer [-@WOSA1972Z066400001] "Famine, Affluence, and Morality"
2. Hartry Field [-@10.2307_2024879] "Tarski's Theory of Truth"
3. Philippa Foot [-@WOSA1972N845400002] "Morality as a System of Hypothetical Imperatives"
4. Ned Block and Jerry A. Fodor [-@WOSA1972YY85800002] "What Psychological States Are Not"
5. Fred Dretske [-@WOSA1972N864600001] "Contrastive Statements"
6. Richard Rorty [-@10.2307_2025059] "The World Well Lost"
7. Gerald Dworkin [-@WOSA1972N175300004] "Paternalism"
8. Richard Routley and Robert K. Meyer [-@WOSA1972Z110200006] "The Semantics of Entailment — II"

### Citation Count {-#sec-count-1972}

```{r}
#| label: tbl-citation-count-1972
#| tbl-cap: Citation count for widely cited articles from 1972.

year_cites <- rank_table_generator(1972)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1972}

```{r}
#| label: tbl-citation-rank-1972
#| tbl-cap: Citation rank for widely cited articles from 1972.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1972}

```{r}
#| label: fig-citation-spaghetti-1972
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1972.
#| cache: FALSE

rolling_spaghetti_graph(1972)
```

```{r}
#| label: fig-citation-facet-1972
#| fig-cap: Faceted version of @fig-citation-spaghetti-1972.
#| cache: FALSE

rolling_facet_graph(1972)
```

\newpage


## 1973 {#sec-s1973}

### Widely Cited Articles {-}

1. David Lewis [-@10.2307_2025310] "Causation"
2. Paul Benacerraf [-@10.2307_2025075] "Mathematical Truth"
3. Larry Wright [-@WOSA1973P242100001] "Functions"
4. Hilary Putnam [-@10.2307_2025079] "Meaning and Reference"
5. Hartry Field [-@10.2307_2025110] "Theory Change and the Indeterminacy of Reference"
6. Jaegwon Kim [-@10.2307_2025096] "Causation, Nomic Subsumption, and the Concept of Event"
7. Tyler Burge [-@10.2307_2025107] "Reference and Proper Names"
8. Michael Walzer [-@WOSA1973R219800003] "Political Action: The Problem of Dirty Hands"
9. Elie Zahar [-@WOSA1973Q107900001] "Why Did Einstein's Programme Supersede Lorentz's (I)"

### Citation Count {-#sec-count-1973}

```{r}
#| label: tbl-citation-count-1973
#| tbl-cap: Citation count for widely cited articles from 1973.

year_cites <- rank_table_generator(1973)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1973}

```{r}
#| label: tbl-citation-rank-1973
#| tbl-cap: Citation rank for widely cited articles from 1973.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1973}

```{r}
#| label: fig-citation-spaghetti-1973
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1973.
#| cache: FALSE

rolling_spaghetti_graph(1973)
```

```{r}
#| label: fig-citation-facet-1973
#| fig-cap: Faceted version of @fig-citation-spaghetti-1973.
#| cache: FALSE

rolling_facet_graph(1973)
```

\newpage


## 1974 {#sec-s1974}

### Widely Cited Articles {-}

1. Thomas Nagel [-@WOSA1974U469700001] "What is It Like To Be a Bat"
2. Michael Friedman [-@10.2307_2024924] "Explanation and Scientific Understanding"
3. Isaac Levi [-@10.2307_2025161] "On Indeterminate Probabilities"
4. Keith S. Donnellan [-@WOSA1974R925600001] "Speaking of Nothing"
5. Charles Parsons [-@WOSA1974U793100003] "The Liar Paradox"
6. Peter Singer [-@WOSA1974U371600008] "Sidgwick and Reflective Equilibrium"
7. Michael Devitt [-@10.2307_2025347] "Singular Terms"

### Citation Count {-#sec-count-1974}

```{r}
#| label: tbl-citation-count-1974
#| tbl-cap: Citation count for widely cited articles from 1974.

year_cites <- rank_table_generator(1974)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1974}

```{r}
#| label: tbl-citation-rank-1974
#| tbl-cap: Citation rank for widely cited articles from 1974.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1974}

```{r}
#| label: fig-citation-spaghetti-1974
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1974.
#| cache: FALSE

rolling_spaghetti_graph(1974)
```

```{r}
#| label: fig-citation-facet-1974
#| fig-cap: Faceted version of @fig-citation-spaghetti-1974.
#| cache: FALSE

rolling_facet_graph(1974)
```

\newpage


## 1975 {#sec-s1975}

### Widely Cited Articles {-}

1. Saul Kripke [-@WOSA1975BF60000005] "Outline of a Theory of Truth"
2. Robert Cummins [-@WOSA1975BF60100001] "Functional Analysis"
3. Gary Watson [-@WOSA1975W282300001] "Free Agency"
4. Allan Gibbard [-@WOSA1975AU08300005] "Contingent Identity"
5. Robert C. Stalnaker [-@WOSA1975LD17700007] "Indicative Conditionals"
6. Gilbert Harman [-@WOSA1975V416000001] "Moral Relativism Defended"
7. Dorothy L. Grover, Joseph L. Camp Jr., and Nuel D. Belnap Jr. [-@WOSA1975BC66900001] "A Pro-Sentential Theory of Truth"
8. Geoffrey Paul Hellman and Frank Wilson Thompson [-@WOSA1975AT43400003] "Physicalism: Ontology, Determination, and Reduction"
9. David Kaplan [-@WOSA1975BF60000006] "Sets, Concepts and Extensions: How To Russell a Frege-Church"

### Citation Count {-#sec-count-1975}

```{r}
#| label: tbl-citation-count-1975
#| tbl-cap: Citation count for widely cited articles from 1975.

year_cites <- rank_table_generator(1975)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1975}

```{r}
#| label: tbl-citation-rank-1975
#| tbl-cap: Citation rank for widely cited articles from 1975.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1975}

```{r}
#| label: fig-citation-spaghetti-1975
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1975.
#| cache: FALSE

rolling_spaghetti_graph(1975)
```

```{r}
#| label: fig-citation-facet-1975
#| fig-cap: Faceted version of @fig-citation-spaghetti-1975.
#| cache: FALSE

rolling_facet_graph(1975)
```

\newpage


## 1976 {#sec-s1976}

### Widely Cited Articles {-}

1. Alvin I. Goldman [-@WOSA1976CP00100001] "Discrimination and Perceptual Knowledge"
2. David Lewis [-@WOSA1976BZ95100001] "Probabilities of Conditionals and Conditional Probabilities"
3. David Lewis [-@WOSA1976BF01500006] "Paradoxes of Time Travel"
4. Michael Stocker [-@WOSA1976CB49000002] "The Schizophrenia of Modern Ethical Theories"
5. Gilbert Harman [-@WOSA1976BK58800002] "Practical Reasoning"
6. Robert C. Stalnaker [-@WOSA1976GM48400006] "Possible Worlds"
7. J. Michael Dunn [-@WOSA1976EK38200001] "Intuitive Semantics for First-Degree Entailments and Coupled Trees"
8. Robert Merrihew Adams [-@WOSA1976CB49000003] "Motive Utilitarianism"
9. Brian Loar [-@WOSA1976EK39100001] "The Semantics of Singular Terms"

### Citation Count {-#sec-count-1976}

```{r}
#| label: tbl-citation-count-1976
#| tbl-cap: Citation count for widely cited articles from 1976.

year_cites <- rank_table_generator(1976)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1976}

```{r}
#| label: tbl-citation-rank-1976
#| tbl-cap: Citation rank for widely cited articles from 1976.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1976}

```{r}
#| label: fig-citation-spaghetti-1976
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1976.
#| cache: FALSE

rolling_spaghetti_graph(1976)
```

```{r}
#| label: fig-citation-facet-1976
#| fig-cap: Faceted version of @fig-citation-spaghetti-1976.
#| cache: FALSE

rolling_facet_graph(1976)
```

\newpage


## 1977 {#sec-s1977}

### Widely Cited Articles {-}

1. John Perry [-@WOSA1977EA01800002] "Frege on Demonstratives"
2. Stephen L. Darwall [-@WOSA1977EA35800003] "Two Kinds of Respect"
3. Fred Dretske [-@WOSA1977DN52600007] "Laws of Nature"
4. Michael Tooley [-@WOSA1977EQ83600001] "Nature of Laws"
5. John M. Taurek [-@WOSA1977DX39800001] "Should the Numbers Count?"
6. Tyler Burge [-@WOSA1977DH28800002] "Belief De Re"
7. Christopher Boorse [-@WOSA1977ES93500003] "Health as a Theoretical Concept"
8. Hartry Field [-@WOSA1977DN99500001] "Logic, Meaning, and Conceptual Role"
9. Hector-Neri Castañeda [-@WOSA1977DV15800002] "Perception, Belief, and Structure of Physical Objects and Consciousness"

### Citation Count {-#sec-count-1977}

```{r}
#| label: tbl-citation-count-1977
#| tbl-cap: Citation count for widely cited articles from 1977.

year_cites <- rank_table_generator(1977)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1977}

```{r}
#| label: tbl-citation-rank-1977
#| tbl-cap: Citation rank for widely cited articles from 1977.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1977}

```{r}
#| label: fig-citation-spaghetti-1977
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1977.
#| cache: FALSE

rolling_spaghetti_graph(1977)
```

```{r}
#| label: fig-citation-facet-1977
#| fig-cap: Faceted version of @fig-citation-spaghetti-1977.
#| cache: FALSE

rolling_facet_graph(1977)
```

\newpage


## 1978 {#sec-s1978}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1978ER30500004] "Truth in Fiction"
2. David L. Hull [-@WOSA1978FR68900001] "A Matter of Individuality"
3. Kendall L. Walton [-@WOSA1978EK23200001] "Fearing Fictions"
4. Stephen P. Stich [-@WOSA1978GH93900001] "Beliefs and Subdoxastic States"
5. Harry G. Frankfurt [-@WOSA1978EL93700010] "The Problem of Action"
6. Paul R. Thagard [-@WOSA1978EP78600002] "The Best Explanation: Criteria for Theory Choice"
7. Jaegwon Kim [-@WOSA1978EL93700009] "Supervenience and Nomological Incommensurables"
8. Laurence BonJour [-@WOSA1978ER30500001] "Can Empirical Knowledge Have a Foundation?"
9. Gregory S. Kavka [-@WOSA1978FB55500001] "Some Paradoxes of Deterrence"

### Citation Count {-#sec-count-1978}

```{r}
#| label: tbl-citation-count-1978
#| tbl-cap: Citation count for widely cited articles from 1978.

year_cites <- rank_table_generator(1978)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1978}

```{r}
#| label: tbl-citation-rank-1978
#| tbl-cap: Citation rank for widely cited articles from 1978.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1978}

```{r}
#| label: fig-citation-spaghetti-1978
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1978.
#| cache: FALSE

rolling_spaghetti_graph(1978)
```

```{r}
#| label: fig-citation-facet-1978
#| fig-cap: Faceted version of @fig-citation-spaghetti-1978.
#| cache: FALSE

rolling_facet_graph(1978)
```

\newpage


## 1979 {#sec-s1979}

### Widely Cited Articles {-}

1. John Perry [-@WOSA1979HE39600001] "The Problem of the Essential Indexical"
2. David Lewis [-@WOSA1979JC64200001] "Attitudes De Dicto and De Se"
3. David Lewis [-@WOSA1979HJ57600007] "Scorekeeping in a Language Game"
4. David Lewis [-@WOSA1979JB14500003] "Counterfactual Dependence and Time's Arrow"
5. John McDowell [-@WOSA1979JT33600005] "Virtue and Reason"
6. Graham Priest [-@WOSA1979GW33200004] "The Logic of Paradox"
7. Norman Daniels [-@WOSA1979GW47300003] "Wide Reflective Equilibrium and Theory Acceptance in Ethics"
8. Nancy Cartwright [-@WOSA1979JB14500001] "Causal Laws and Effective Strategies"
9. Daniel Lascar and Bruno Poizat [-@WOSA1979HL22300006] "Introduction To Forking"

### Citation Count {-#sec-count-1979}

```{r}
#| label: tbl-citation-count-1979
#| tbl-cap: Citation count for widely cited articles from 1979.

year_cites <- rank_table_generator(1979)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1979}

```{r}
#| label: tbl-citation-rank-1979
#| tbl-cap: Citation rank for widely cited articles from 1979.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1979}

```{r}
#| label: fig-citation-spaghetti-1979
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1979.
#| cache: FALSE

rolling_spaghetti_graph(1979)
```

```{r}
#| label: fig-citation-facet-1979
#| fig-cap: Faceted version of @fig-citation-spaghetti-1979.
#| cache: FALSE

rolling_facet_graph(1979)
```

\newpage


## 1980 {#sec-s1980}

### Widely Cited Articles {-}

1. John Rawls [-@WOSA1980KH88100001] "Kantian Constructivism in Moral Theory"
2. Martin Davies and Lloyd Humberstone [-@WOSA1980KA40400001] "Two Notions of Necessity"
3. Hilary Putnam [-@WOSA1980KJ75900004] "Models and Reality"
4. Jerrold Levinson [-@WOSA1980JC98000001] "What a Musical Work Is"
5. Elliot Sober [-@WOSA1980LE33500002] "Evolution, Population Thinking, and Essentialism"
6. Ruth Barcan Marcus [-@WOSA1980JJ63300001] "Moral Dilemmas and Consistency"
7. David Lewis [-@WOSA1980KX78600003] "Veridical Hallucination and Prosthetic Vision"
8. Norman Daniels [-@WOSA1980JZ97600005] "Reflective Equilibrium and Archimedean Points"

### Citation Count {-#sec-count-1980}

```{r}
#| label: tbl-citation-count-1980
#| tbl-cap: Citation count for widely cited articles from 1980.

year_cites <- rank_table_generator(1980)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1980}

```{r}
#| label: tbl-citation-rank-1980
#| tbl-cap: Citation rank for widely cited articles from 1980.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1980}

```{r}
#| label: fig-citation-spaghetti-1980
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1980.
#| cache: FALSE

rolling_spaghetti_graph(1980)
```

```{r}
#| label: fig-citation-facet-1980
#| fig-cap: Faceted version of @fig-citation-spaghetti-1980.
#| cache: FALSE

rolling_facet_graph(1980)
```

\newpage


## 1981 {#sec-s1981}

### Widely Cited Articles {-}

1. Paul M. Churchland [-@WOSA1981LD54600001] "Eliminative Materialism and the Propositional Attitudes"
2. Larry Laudan [-@WOSA1981LY92900002] "A Confutation of Convergent Realism"
3. Philip Kitcher [-@WOSA1981NA08400001] "Explanatory Unification"
4. Jon Barwise and Robin Cooper [-@WOSA1981LH67300001] "Generalized Quantifiers and Natural-Language"
5. Ronald Dworkin [-@WOSA1981MH21100001] "What is Equality? Part 2: Equality of Resources"
6. David Lewis [-@WOSA1981LW58400001] "Causal Decision Theory"
7. Peter van Inwagen [-@WOSA1981LV91400003] "The Doctrine of Arbitrary Undetached Parts"
8. Ronald Dworkin [-@WOSA1981LU74200001] "What is Equality (I) Equality of Welfare"
9. John Dupré [-@WOSA1981KZ94600003] "Natural Kinds and Biological Taxa"

### Citation Count {-#sec-count-1981}

```{r}
#| label: tbl-citation-count-1981
#| tbl-cap: Citation count for widely cited articles from 1981.

year_cites <- rank_table_generator(1981)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1981}

```{r}
#| label: tbl-citation-rank-1981
#| tbl-cap: Citation rank for widely cited articles from 1981.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1981}

```{r}
#| label: fig-citation-spaghetti-1981
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1981.
#| cache: FALSE

rolling_spaghetti_graph(1981)
```

```{r}
#| label: fig-citation-facet-1981
#| fig-cap: Faceted version of @fig-citation-spaghetti-1981.
#| cache: FALSE

rolling_facet_graph(1981)
```

\newpage


## 1982 {#sec-s1982}

### Widely Cited Articles {-}

1. Frank Jackson [-@WOSA1982NH65300003] "Epiphenomenal Qualia"
2. Susan Wolf [-@WOSA1982PB73200001] "Moral Saints"
3. Elizabeth W. Prior, Robert Pargetter, and Frank Jackson [-@WOSA1982NS00700005] "Three Theses About Dispositions"
4. Chris Swoyer [-@WOSA1982PM91600001] "The Nature of Natural Laws"
5. Anil Gupta [-@WOSA1982NW89300001] "Truth and Paradox"
6. David Lewis [-@WOSA1982PN18900005] "Logic for Equivocators"
7. Jaegwon Kim [-@WOSA1982NC90700004] "Psychophysical Supervenience"
8. Harry G. Frankfurt [-@WOSA1982PX46500008] "The Importance of What We Care About"
9. Dudley Shapere [-@WOSA1982PW68500001] "The Concept of Observation in Science and Philosophy"

### Citation Count {-#sec-count-1982}

```{r}
#| label: tbl-citation-count-1982
#| tbl-cap: Citation count for widely cited articles from 1982.

year_cites <- rank_table_generator(1982)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1982}

```{r}
#| label: tbl-citation-rank-1982
#| tbl-cap: Citation rank for widely cited articles from 1982.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1982}

```{r}
#| label: fig-citation-spaghetti-1982
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1982.
#| cache: FALSE

rolling_spaghetti_graph(1982)
```

```{r}
#| label: fig-citation-facet-1982
#| fig-cap: Faceted version of @fig-citation-spaghetti-1982.
#| cache: FALSE

rolling_facet_graph(1982)
```

\newpage


## 1983 {#sec-s1983}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1983RR51600001] "New Work for a Theory of Universals"
2. Joseph Levine [-@WOSA1983SU49200007] "Materialism and Qualia: The Explanatory Gap"
3. Gregory S. Kavka [-@WOSA1983PX89100011] "The Toxin Puzzle"
4. Christine M. Korsgaard [-@WOSA1983QN98800001] "Two Distinctions in Goodness"
5. Robert Brandom [-@WOSA1983RV45200006] "Asserting"
6. Judith Jarvis Thomson [-@WOSA1983QK97500001] "Parthood and Identity Across Time"
7. Hilary Kornblith [-@WOSA1983PZ01000002] "Justified Belief and Epistemically Responsible Action"
8. Alvin Plantinga [-@WOSA1983QU18900001] "On Existentialism"
9. Ellery Eells and Elliot Sober [-@WOSA1983QJ85300002] "Probabilistic Causality and the Question of Transitivity"

### Citation Count {-#sec-count-1983}

```{r}
#| label: tbl-citation-count-1983
#| tbl-cap: Citation count for widely cited articles from 1983.

year_cites <- rank_table_generator(1983)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1983}

```{r}
#| label: tbl-citation-rank-1983
#| tbl-cap: Citation rank for widely cited articles from 1983.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1983}

```{r}
#| label: fig-citation-spaghetti-1983
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1983.
#| cache: FALSE

rolling_spaghetti_graph(1983)
```

```{r}
#| label: fig-citation-facet-1983
#| fig-cap: Faceted version of @fig-citation-spaghetti-1983.
#| cache: FALSE

rolling_facet_graph(1983)
```

\newpage


## 1984 {#sec-s1984}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1984TQ70900001] "Putnam's Paradox"
2. Bas C. van Fraassen [-@WOSA1984SS95000001] "Belief and the Will"
3. Peter Railton [-@WOSA1984SH40600002] "Alienation, Consequentialism, and the Demands of Morality"
4. George Boolos [-@WOSA1984TE24500002] "To Be is To Be a Value of a Variable (Or To Be Some Values of Some Variables)"
5. Jaegwon Kim [-@WOSA1984TV24600001] "Concepts of Supervenience"
6. Stewart Cohen [-@WOSA1984TN86300001] "Justification and Truth"
7. Philip Kitcher [-@WOSA1984SZ73700006] "Species"
8. Kevin Mulligan, Peter Simons, and Barry Smith [-@WOSA1984SE25700001] "Truth-Makers"
9. Jerry A. Fodor [-@WOSA1984SL56000004] "Observation Reconsidered"

### Citation Count {-#sec-count-1984}

```{r}
#| label: tbl-citation-count-1984
#| tbl-cap: Citation count for widely cited articles from 1984.

year_cites <- rank_table_generator(1984)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1984}

```{r}
#| label: tbl-citation-rank-1984
#| tbl-cap: Citation rank for widely cited articles from 1984.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1984}

```{r}
#| label: fig-citation-spaghetti-1984
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1984.
#| cache: FALSE

rolling_spaghetti_graph(1984)
```

```{r}
#| label: fig-citation-facet-1984
#| fig-cap: Faceted version of @fig-citation-spaghetti-1984.
#| cache: FALSE

rolling_facet_graph(1984)
```

\newpage


## 1985 {#sec-s1985}

### Widely Cited Articles {-}

1. Carlos E. Alchourrón, Peter Gärdenfors, and David Makinson [-@WOSA1985AKA2200025] "On the Logic of Theory Change: Partial Meet Contraction and Revision Functions"
2. Richard Feldman and Earl Conee [-@WOSA1985ANT6600002] "Evidentialism"
3. John Hardwig [-@WOSA1985ALK4200001] "Epistemic Dependence"
4. Ernan McMullin [-@WOSA1985ARQ5600003] "Galilean Idealization"
5. Vann McGee [-@WOSA1985AQZ7400002] "A Counterexample To Modus Ponens"
6. John Rawls [-@WOSA1985APA8500001] "Justice as Fairness: Political Not Metaphysical"
7. William P. Alston [-@WOSA1985AML6300004] "Concepts of Epistemic Justification"
8. Richard Feldman [-@WOSA1985APJ3700001] "Reliability and Justification"
9. Paul M. Churchland [-@WOSA1985AAC6100002] "Reduction, Qualia, and the Direct Introspection of Brain States"

### Citation Count {-#sec-count-1985}

```{r}
#| label: tbl-citation-count-1985
#| tbl-cap: Citation count for widely cited articles from 1985.

year_cites <- rank_table_generator(1985)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1985}

```{r}
#| label: tbl-citation-rank-1985
#| tbl-cap: Citation rank for widely cited articles from 1985.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1985}

```{r}
#| label: fig-citation-spaghetti-1985
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1985.
#| cache: FALSE

rolling_spaghetti_graph(1985)
```

```{r}
#| label: fig-citation-facet-1985
#| fig-cap: Faceted version of @fig-citation-spaghetti-1985.
#| cache: FALSE

rolling_facet_graph(1985)
```

\newpage


## 1986 {#sec-s1986}

### Widely Cited Articles {-}

1. Peter Railton [-@WOSA1986C044900001] "Moral Realism"
2. Tyler Burge [-@WOSA1986AYX3200001] "Individualism and Psychology"
3. Annette Baier [-@WOSA1986AYY3900001] "Trust and Antitrust"
4. Christine M. Korsgaard [-@WOSA1986AYQ1300001] "Skepticism About Practical Reason"
5. David M. Rosenthal [-@WOSA1986C316000003] "Two Concepts of Consciousness"
6. Frank Jackson and Robert Pargetter [-@WOSA1986C044900003] "Oughts, Options, and Actualism"
7. Tyler Burge [-@WOSA1986F231300001] "Intellectual Norms and Foundations of Mind"
8. Ruth Garrett Millikan [-@WOSA1986AYX3200002] "Thoughts Without Laws, Cognitive Science With Content"

### Citation Count {-#sec-count-1986}

```{r}
#| label: tbl-citation-count-1986
#| tbl-cap: Citation count for widely cited articles from 1986.

year_cites <- rank_table_generator(1986)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1986}

```{r}
#| label: tbl-citation-rank-1986
#| tbl-cap: Citation rank for widely cited articles from 1986.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1986}

```{r}
#| label: fig-citation-spaghetti-1986
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1986.
#| cache: FALSE

rolling_spaghetti_graph(1986)
```

```{r}
#| label: fig-citation-facet-1986
#| fig-cap: Faceted version of @fig-citation-spaghetti-1986.
#| cache: FALSE

rolling_facet_graph(1986)
```

\newpage


## 1987 {#sec-s1987}

### Widely Cited Articles {-}

1. Michael Smith [-@WOSA1987F993300003] "The Humean Theory of Motivation"
2. Harry G. Frankfurt [-@WOSA1987M543000002] "Equality as a Moral Ideal"
3. John Bigelow and Robert Pargetter [-@WOSA1987G947600001] "Functions"
4. John Earman and John Norton [-@WOSA1987M488500005] "What Price Spacetime Substantivalism: The Hole Story"
5. Dennis W. Stampe [-@WOSA1987J665800001] "The Authority of Desire"
6. Larry S. Temkin [-@WOSA1987H340500002] "Intransitivity and the Mere Addition Paradox"
7. Thomas Nagel [-@WOSA1987J379200001] "Moral Conflict and Political Legitimacy"
8. Margaret Gilbert [-@WOSA1987K730800008] "Modeling Collective Belief"
9. Larry Laudan [-@WOSA1987F902200002] "Progress or Rationality: The Prospects for Normative Naturalism"

### Citation Count {-#sec-count-1987}

```{r}
#| label: tbl-citation-count-1987
#| tbl-cap: Citation count for widely cited articles from 1987.

year_cites <- rank_table_generator(1987)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1987}

```{r}
#| label: tbl-citation-rank-1987
#| tbl-cap: Citation rank for widely cited articles from 1987.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1987}

```{r}
#| label: fig-citation-spaghetti-1987
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1987.
#| cache: FALSE

rolling_spaghetti_graph(1987)
```

```{r}
#| label: fig-citation-facet-1987
#| fig-cap: Faceted version of @fig-citation-spaghetti-1987.
#| cache: FALSE

rolling_facet_graph(1987)
```

\newpage


## 1988 {#sec-s1988}

### Widely Cited Articles {-}

1. Tyler Burge [-@WOSA1988R020000007] "Individualism and Self-Knowledge"
2. James Bogen and James Woodward [-@WOSA1988N938600001] "Saving the Phenomena"
3. Adam Grove [-@WOSA1988M958800004] "Two Modelings for Theory Change"
4. Kim Sterelny and Philip Kitcher [-@WOSA1988P217100001] "The Return of the Gene"
5. Shelley Kagan [-@WOSA1988Q913800001] "The Additive Fallacy"
6. William P. Alston [-@WOSA1988M863300002] "An Internalist Externalism"
7. David Lewis [-@WOSA1988P549200001] "Desire as Belief"
8. Frank Jackson and Philip Pettit [-@WOSA1988P549200004] "Functionalism and Broad Content"
9. John Rawls [-@WOSA1988Q394000001] "The Priority of Right and Ideas of the Good"

### Citation Count {-#sec-count-1988}

```{r}
#| label: tbl-citation-count-1988
#| tbl-cap: Citation count for widely cited articles from 1988.

year_cites <- rank_table_generator(1988)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1988}

```{r}
#| label: tbl-citation-rank-1988
#| tbl-cap: Citation rank for widely cited articles from 1988.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1988}

```{r}
#| label: fig-citation-spaghetti-1988
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1988.
#| cache: FALSE

rolling_spaghetti_graph(1988)
```

```{r}
#| label: fig-citation-facet-1988
#| fig-cap: Faceted version of @fig-citation-spaghetti-1988.
#| cache: FALSE

rolling_facet_graph(1988)
```

\newpage


## 1989 {#sec-s1989}

### Widely Cited Articles {-}

1. G. A. Cohen [-@WOSA1989AE70300010] "On the Currency of Egalitarian Justice"
2. Ruth Garrett Millikan [-@WOSA1989AA09400006] "In Defense of Proper Functions"
3. Ruth Garrett Millikan [-@WOSA1989U850300001] "Biosemantics"
4. Paul A. Boghossian and J. David Velleman [-@WOSA1989T231400005] "Color as a Secondary Quality"
5. Richard J. Arneson [-@WOSA1989U808000004] "Equality and Equal Opportunity for Welfare"
6. Paul A. Boghossian [-@WOSA1989CA94000002] "The Rule-Following Considerations"
7. Mark Crimmins and John Perry [-@WOSA1989CF70700001] "The Prince and the Phone Booth: Reporting Puzzling Beliefs"
8. Don Marquis [-@WOSA1989U039600002] "Why Abortion is Immoral"
9. Warren S. Quinn [-@WOSA1989AV72300002] "Actions, Intentions, and Consequences: The Doctrine of Double Effect"

### Citation Count {-#sec-count-1989}

```{r}
#| label: tbl-citation-count-1989
#| tbl-cap: Citation count for widely cited articles from 1989.

year_cites <- rank_table_generator(1989)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1989}

```{r}
#| label: tbl-citation-rank-1989
#| tbl-cap: Citation rank for widely cited articles from 1989.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1989}

```{r}
#| label: fig-citation-spaghetti-1989
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1989.
#| cache: FALSE

rolling_spaghetti_graph(1989)
```

```{r}
#| label: fig-citation-facet-1989
#| fig-cap: Faceted version of @fig-citation-spaghetti-1989.
#| cache: FALSE

rolling_facet_graph(1989)
```

\newpage


## 1990 {#sec-s1990}

### Widely Cited Articles {-}

1. Philip Kitcher [-@WOSA1990CH71200001] "The Division of Cognitive Labor"
2. Frank Jackson and Philip Pettit [-@WOSA1990CR32400008] "Program Explanation: A General Perspective"
3. Donald Davidson [-@WOSA1990EQ84600001] "The Structure and Content of Truth"
4. Gideon Rosen [-@WOSA1990DR99100001] "Modal Fictionalism"
5. Tim Crane and D. H. Mellor [-@WOSA1990DA14600002] "There is No Question of Physicalism"
6. Jamie Dreier [-@WOSA1990EK23400001] "Internalism and Speaker Relativism"
7. Jonathan Vogel [-@WOSA1990EF94500012] "Cartesian Skepticism and Inference To the Best Explanation"
8. Jaegwon Kim [-@WOSA1990FU75100001] "Supervenience as a Philosophical Concept"
9. Graeme Forbes [-@WOSA1990EB39300002] "The Indispensability of Sinn"

### Citation Count {-#sec-count-1990}

```{r}
#| label: tbl-citation-count-1990
#| tbl-cap: Citation count for widely cited articles from 1990.

year_cites <- rank_table_generator(1990)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1990}

```{r}
#| label: tbl-citation-rank-1990
#| tbl-cap: Citation rank for widely cited articles from 1990.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1990}

```{r}
#| label: fig-citation-spaghetti-1990
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1990.
#| cache: FALSE

rolling_spaghetti_graph(1990)
```

```{r}
#| label: fig-citation-facet-1990
#| fig-cap: Faceted version of @fig-citation-spaghetti-1990.
#| cache: FALSE

rolling_facet_graph(1990)
```

\newpage


## 1991 {#sec-s1991}

### Widely Cited Articles {-}

1. Daniel C. Dennett [-@WOSA1991EN62900002] "Real Patterns"
2. Karen Neander [-@WOSA1991FQ15000002] "Functions as Selected Effects: The Conceptual Analyst's Defense"
3. Richard Boyd [-@WOSA1991FC38500010] "Realism, Anti-foundationalism and the Enthusiasm for Natural Kinds"
4. Frank Jackson [-@WOSA1991FK52800001] "Decision-theoretic Consequentialism and the Nearest and Dearest Objection"
5. Judith Jarvis Thomson [-@WOSA1991GR79400001] "Self-Defense"
6. Jeroen Groenendijk and Martin Stokhof [-@WOSA1991EV09800002] "Dynamic Predicate Logic"
7. John Hardwig [-@WOSA1991GR87800001] "The Role of Trust in Knowledge"
8. Stephen Schiffer [-@WOSA1991EW92800001] "Ceteris Paribus Laws"
9. Jerry A. Fodor [-@WOSA1991EN62900001] "A Modal Argument for Narrow Content"

### Citation Count {-#sec-count-1991}

```{r}
#| label: tbl-citation-count-1991
#| tbl-cap: Citation count for widely cited articles from 1991.

year_cites <- rank_table_generator(1991)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1991}

```{r}
#| label: tbl-citation-rank-1991
#| tbl-cap: Citation rank for widely cited articles from 1991.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1991}

```{r}
#| label: fig-citation-spaghetti-1991
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1991.
#| cache: FALSE

rolling_spaghetti_graph(1991)
```

```{r}
#| label: fig-citation-facet-1991
#| fig-cap: Faceted version of @fig-citation-spaghetti-1991.
#| cache: FALSE

rolling_facet_graph(1991)
```

\newpage


## 1992 {#sec-s1992}

### Widely Cited Articles {-}

1. Stephen Yablo [-@WOSA1992JA62400001] "Mental Causation"
2. Mark Johnston [-@WOSA1992KC39800002] "How To Speak of the Colors"
3. Keith DeRose [-@WOSA1992KB29500008] "Contextualism and Knowledge Attributions"
4. Jaegwon Kim [-@WOSA1992HF90400001] "Multiple Realization and the Metaphysics of Reduction"
5. Michael E. Bratman [-@WOSA1992JA62400003] "Shared Cooperative Activity"
6. Philip Kitcher [-@WOSA1992HF90300002] "The Naturalists Return"
7. Richard Foley [-@WOSA1992JR30700002] "The Epistemology of Belief and the Epistemology of Degrees of Belief"
8. Stephen Schiffer [-@WOSA1992JQ78400001] "Belief Ascription"
9. Michael B. Burke [-@WOSA1992HC13100003] "Copper Statues and Pieces of Copper: A Challenge To the Standard Account"

### Citation Count {-#sec-count-1992}

```{r}
#| label: tbl-citation-count-1992
#| tbl-cap: Citation count for widely cited articles from 1992.

year_cites <- rank_table_generator(1992)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1992}

```{r}
#| label: tbl-citation-rank-1992
#| tbl-cap: Citation rank for widely cited articles from 1992.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1992}

```{r}
#| label: fig-citation-spaghetti-1992
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1992.
#| cache: FALSE

rolling_spaghetti_graph(1992)
```

```{r}
#| label: fig-citation-facet-1992
#| fig-cap: Faceted version of @fig-citation-spaghetti-1992.
#| cache: FALSE

rolling_facet_graph(1992)
```

\newpage


## 1993 {#sec-s1993}

### Widely Cited Articles {-}

1. Tyler Burge [-@WOSA1993ML38000001] "Content Preservation"
2. Stephen Yablo [-@WOSA1993KQ63200001] "Is Conceivability a Guide To Possibility"
3. Rae Langton [-@WOSA1993MJ74900002] "Speech Acts and Unspeakable Acts"
4. Stephen Yablo [-@WOSA1993MG45400010] "Paradox Without Self-Reference"
5. Michael E. Bratman [-@WOSA1993ME08500006] "Shared Intention"
6. Terrence Horgan [-@WOSA1993ME23100001] "From Supervenience To Superdupervenience: Meeting the Demands of a Material World"
7. David Braun [-@WOSA1993NN82400002] "Empty Names"
8. Paul E. Griffiths [-@WOSA1993MM47700002] "Functional Analysis and Proper Functions"
9. Fred Dretske [-@WOSA1993LB00700004] "Conscious Experience"

### Citation Count {-#sec-count-1993}

```{r}
#| label: tbl-citation-count-1993
#| tbl-cap: Citation count for widely cited articles from 1993.

year_cites <- rank_table_generator(1993)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1993}

```{r}
#| label: tbl-citation-rank-1993
#| tbl-cap: Citation rank for widely cited articles from 1993.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1993}

```{r}
#| label: fig-citation-spaghetti-1993
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1993.
#| cache: FALSE

rolling_spaghetti_graph(1993)
```

```{r}
#| label: fig-citation-facet-1993
#| fig-cap: Faceted version of @fig-citation-spaghetti-1993.
#| cache: FALSE

rolling_facet_graph(1993)
```

\newpage


## 1994 {#sec-s1994}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1994PM10400005] "Humean Supervenience Debugged"
2. C. B. Martin [-@WOSA1994MT56900001] "Dispositions and Conditionals"
3. Malcom Forster and Elliot Sober [-@WOSA1994NQ78600001] "How To Tell When Simpler, More Unified, or Less _Ad Hoc_ Theories Will Provide More Accurate Predictions"
4. Hartry Field [-@WOSA1994NY27600001] "Deflationist Views of Meaning and Content"
5. Peter Godfrey-Smith [-@WOSA1994PG81700003] "A Modern History Theory of Functions"
6. Richard Holton [-@WOSA1994NA94600005] "Deciding To Trust, Coming To Believe"
7. Robert Audi [-@WOSA1994PW69700001] "Dispositional Beliefs and Dispositions To Believe"
8. Galen Strawson [-@WOSA1994PB07700001] "The Impossibility of Moral Responsibility"
9. Paul E. Griffiths and R. D. Gray [-@WOSA1994NP54800001] "Developmental Systems and Evolutionary Explanation"

### Citation Count {-#sec-count-1994}

```{r}
#| label: tbl-citation-count-1994
#| tbl-cap: Citation count for widely cited articles from 1994.

year_cites <- rank_table_generator(1994)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1994}

```{r}
#| label: tbl-citation-rank-1994
#| tbl-cap: Citation rank for widely cited articles from 1994.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1994}

```{r}
#| label: fig-citation-spaghetti-1994
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1994.
#| cache: FALSE

rolling_spaghetti_graph(1994)
```

```{r}
#| label: fig-citation-facet-1994
#| fig-cap: Faceted version of @fig-citation-spaghetti-1994.
#| cache: FALSE

rolling_facet_graph(1994)
```

\newpage


## 1995 {#sec-s1995}

### Widely Cited Articles {-}

1. Keith DeRose [-@WOSA1995RC31600001] "Solving the Skeptical Problem"
2. Dorothy Edgington [-@WOSA1995QX94800001] "On Conditionals"
3. Tim van Gelder [-@WOSA1995RG53900001] "What Might Cognition Be, If Not Computation"
4. David Widerker [-@WOSA1995TB96300003] "Libertarianism and Frankfurt's Attack on the Principle of Alternative Possibilities"
5. Dean W. Zimmerman [-@WOSA1995RC31600002] "Theories of Masses and Problems of Constitution"
6. Noam Chomsky [-@WOSA1995QH55500001] "Language and Nature"
7. Karen Neander [-@WOSA1995RP14800001] "Misrepresenting and Malfunctioning"
8. John McDowell [-@WOSA1995TH53900008] "Knowledge and the Internal"
9. Kit Fine [-@WOSA1995RD61000003] "The Logic of Essence"

### Citation Count {-#sec-count-1995}

```{r}
#| label: tbl-citation-count-1995
#| tbl-cap: Citation count for widely cited articles from 1995.

year_cites <- rank_table_generator(1995)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1995}

```{r}
#| label: tbl-citation-rank-1995
#| tbl-cap: Citation rank for widely cited articles from 1995.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1995}

```{r}
#| label: fig-citation-spaghetti-1995
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1995.
#| cache: FALSE

rolling_spaghetti_graph(1995)
```

```{r}
#| label: fig-citation-facet-1995
#| fig-cap: Faceted version of @fig-citation-spaghetti-1995.
#| cache: FALSE

rolling_facet_graph(1995)
```

\newpage


## 1996 {#sec-s1996}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1996VY21200001] "Elusive Knowledge"
2. Timothy Williamson [-@WOSA1996XR76100003] "Knowing and Asserting"
3. Frank Veltman [-@WOSA1996UV93000001] "Defaults in Update Semantics"
4. Karen Jones [-@WOSA1996VL52500002] "Trust as An Affective Attitude"
5. Ronald Dworkin [-@WOSA1996UT36600001] "Objectivity and Truth: You'd Better Believe It"
6. Paul A. Boghossian [-@WOSA1996VJ65500005] "Analyticity Reconsidered"
7. Theodore Sider [-@WOSA1996VE56300003] "All the World's a Stage"
8. Alex Oliver [-@WOSA1996TT05300001] "The Metaphysics of Properties"
9. Donald Davidson [-@WOSA1996UM62300001] "The Folly of Trying To Define Truth"

### Citation Count {-#sec-count-1996}

```{r}
#| label: tbl-citation-count-1996
#| tbl-cap: Citation count for widely cited articles from 1996.

year_cites <- rank_table_generator(1996)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1996}

```{r}
#| label: tbl-citation-rank-1996
#| tbl-cap: Citation rank for widely cited articles from 1996.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1996}

```{r}
#| label: fig-citation-spaghetti-1996
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1996.
#| cache: FALSE

rolling_spaghetti_graph(1996)
```

```{r}
#| label: fig-citation-facet-1996
#| fig-cap: Faceted version of @fig-citation-spaghetti-1996.
#| cache: FALSE

rolling_facet_graph(1996)
```

\newpage


## 1997 {#sec-s1997}

### Widely Cited Articles {-}

1. David Lewis [-@WOSA1997WP33800001] "Finkish Dispositions"
2. Derek Parfit [-@WOS000070778500002] "Equality and Priority"
3. Lynne Rudder Baker [-@WOS000070661300001] "Why Constitution is Not Identity"
4. Robert Audi [-@WOS000070790100002] "The Place of Testimony in the Fabric of Knowledge and Justification"
5. Christopher S. Hill [-@WOSA1997XH01200003] "Imaginability, Conceivability, Possibility and the Mind-Body Problem"
6. Tyler Burge [-@WOSA1997WT06900002] "Interlocution, Perception, and Memory"
7. R. M. Sainsbury [-@WOS000071087200008] "Easy Possibilities"
8. Susan Wolf [-@WOSA1997WF56900009] "Happiness and Meaning: Two Aspects of the Good Life"
9. Michael J. Zimmerman [-@WOSA1997WR70900002] "Moral Responsibility and Ignorance"

### Citation Count {-#sec-count-1997}

```{r}
#| label: tbl-citation-count-1997
#| tbl-cap: Citation count for widely cited articles from 1997.

year_cites <- rank_table_generator(1997)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1997}

```{r}
#| label: tbl-citation-rank-1997
#| tbl-cap: Citation rank for widely cited articles from 1997.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1997}

```{r}
#| label: fig-citation-spaghetti-1997
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1997.
#| cache: FALSE

rolling_spaghetti_graph(1997)
```

```{r}
#| label: fig-citation-facet-1997
#| fig-cap: Faceted version of @fig-citation-spaghetti-1997.
#| cache: FALSE

rolling_facet_graph(1997)
```

\newpage


## 1998 {#sec-s1998}

### Widely Cited Articles {-}

1. Andy Clark and David J. Chalmers [-@WOS000073222300002] "The Extended Mind"
2. James M. Joyce [-@WOS000077956100002] "A Nonpragmatic Vindication of Probabilism"
3. James Ladyman [-@WOS000076086400005] "What is Structural Realism?"
4. Nathan Salmon [-@WOS000075762200001] "Nonexistence"
5. Alexander Bird [-@WOS000072823100011] "Dispositions and Antidotes"
6. Rae Langton and David Lewis [-@WOS000073836400005] "Defining 'Intrinsic'"
7. Earl Conee and Richard Feldman [-@WOS000072502200001] "The Generality Problem for Reliabilism"
8. Judith Jarvis Thomson [-@WOS000073884600001] "The Statue and the Clay"
9. John McDowell [-@WOS000075622500001] "Having the World in View: Sellars, Kant, and Intentionality: Lecture I: Sellars on Perceptual Experience"

### Citation Count {-#sec-count-1998}

```{r}
#| label: tbl-citation-count-1998
#| tbl-cap: Citation count for widely cited articles from 1998.

year_cites <- rank_table_generator(1998)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1998}

```{r}
#| label: tbl-citation-rank-1998
#| tbl-cap: Citation rank for widely cited articles from 1998.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1998}

```{r}
#| label: fig-citation-spaghetti-1998
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1998.
#| cache: FALSE

rolling_spaghetti_graph(1998)
```

```{r}
#| label: fig-citation-facet-1998
#| fig-cap: Faceted version of @fig-citation-spaghetti-1998.
#| cache: FALSE

rolling_facet_graph(1998)
```

\newpage


## 1999 {#sec-s1999}

### Widely Cited Articles {-}

1. Elizabeth S. Anderson [-@WOS000078432400003] "What is the Point of Equality?"
2. John Broome [-@WOS000084073700005] "Normative Requirements"
3. Ned Block and Robert C. Stalnaker [-@WOS000084347100001] "Conceptual Analysis, Dualism, and the Explanatory Gap"
4. Jaegwon Kim [-@WOS000082592000002] "Making Sense of Emergence"
5. William Bechtal and Jennifer Mundale [-@WOS000080550400001] "Multiple Realizability Revisited: Linking Cognitive and Neural States"
6. J. David Velleman [-@WOS000078432400004] "Love as a Moral Emotion"
7. Brandon Fitelson [-@WOS000083295800029] "The Plurality of Bayesian Measures of Confirmation and the Problem of Measure Sensitivity"
8. Tomoji Shogenji [-@WOS000085486100019] "Is Coherence Truth Conducive?"
9. John Hyman [-@WOS000082596900001] "How Knowledge Works"

### Citation Count {-#sec-count-1999}

```{r}
#| label: tbl-citation-count-1999
#| tbl-cap: Citation count for widely cited articles from 1999.

year_cites <- rank_table_generator(1999)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1999}

```{r}
#| label: tbl-citation-rank-1999
#| tbl-cap: Citation rank for widely cited articles from 1999.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1999}

```{r}
#| label: fig-citation-spaghetti-1999
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1999.
#| cache: FALSE

rolling_spaghetti_graph(1999)
```

```{r}
#| label: fig-citation-facet-1999
#| fig-cap: Faceted version of @fig-citation-spaghetti-1999.
#| cache: FALSE

rolling_facet_graph(1999)
```

\newpage


## 2000 {#sec-s2000}

### Widely Cited Articles {-}

1. Peter Machamer, Lindley Darden, and Carl F. Craver [-@WOS000087305900001] "Thinking About Mechanisms"
2. James Pryor [-@WOS000165361800002] "The Skeptic and the Dogmatist"
3. Sally Haslanger [-@WOS000085841900002] "Gender and Race: (What) Are They? (What) Do We Want Them To Be?"
4. David Lewis [-@WOS000089124200002] "Causation as Influence"
5. Justin D'Arms and Dan Jacobson [-@WOS000087998300003] "The Moralistic Fallacy: On the 'Appropriateness' of Emotions"
6. Jason Stanley and Zoltán Gendler Szabó [-@WOS000088616400001] "On Quantifier Domain Restriction"
7. Heather Douglas [-@WOS000166575500001] "Inductive Risk and Values in Science"
8. Jason Stanley [-@WOS000088534100002] "Context and Logical Form"
9. Adam Elga [-@WOS000086383700001] "Self-Locating Belief and the 'Sleeping Beauty' Problem"

### Citation Count {-#sec-count-2000}

```{r}
#| label: tbl-citation-count-2000
#| tbl-cap: Citation count for widely cited articles from 2000.

year_cites <- rank_table_generator(2000)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2000}

```{r}
#| label: tbl-citation-rank-2000
#| tbl-cap: Citation rank for widely cited articles from 2000.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2000}

```{r}
#| label: fig-citation-spaghetti-2000
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2000.
#| cache: FALSE

rolling_spaghetti_graph(2000)
```

```{r}
#| label: fig-citation-facet-2000
#| fig-cap: Faceted version of @fig-citation-spaghetti-2000.
#| cache: FALSE

rolling_facet_graph(2000)
```

\newpage


## 2001 {#sec-s2001}

### Widely Cited Articles {-}

1. Jason Stanley and Timothy Williamson [-@WOS000170277300002] "Knowing How"
2. Alex Byrne [-@WOS000171488600002] "Intentionalism Defended"
3. David J. Chalmers and Frank Jackson [-@WOS000174798400001] "Conceptual Analysis and Reductive Explanation"
4. Alvin I. Goldman [-@WOS000170434600004] "Experts: Which Ones Should You Trust?"
5. Christopher Hitchcock [-@WOS000169156400001] "The Intransitivity of Causation Revealed in Equations and Graphs"
6. Patrick Rysiew [-@WOS000172282100001] "The Context-Sensitivity of Knowledge Attributions"
7. Fred Adams and Ken Aizawa [-@WOS000167688000003] "The Bounds of Cognition"
8. Christopher Peacocke [-@WOS000168307800002] "Does Perception Have a Nonconceptual Content?"
9. Carl F. Craver [-@WOS000167722000004] "Role Functions, Mechanisms, and Hierarchy"

### Citation Count {-#sec-count-2001}

```{r}
#| label: tbl-citation-count-2001
#| tbl-cap: Citation count for widely cited articles from 2001.

year_cites <- rank_table_generator(2001)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2001}

```{r}
#| label: tbl-citation-rank-2001
#| tbl-cap: Citation rank for widely cited articles from 2001.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2001}

```{r}
#| label: fig-citation-spaghetti-2001
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2001.
#| cache: FALSE

rolling_spaghetti_graph(2001)
```

```{r}
#| label: fig-citation-facet-2001
#| fig-cap: Faceted version of @fig-citation-spaghetti-2001.
#| cache: FALSE

rolling_facet_graph(2001)
```

\newpage


## 2002 {#sec-s2002}

### Widely Cited Articles {-}

1. Michael G. F. Martin [-@WOS000177781700002] "The Transparency of Experience"
2. Jeremy Fantl and Matthew McGrath [-@WOS000181094500003] "Evidence, Pragmatics, and Justification"
3. Robert C. Stalnaker [-@WOS000179607800011] "Common Ground"
4. Stuart Glennan [-@WOS000178763700030] "Rethinking Mechanistic Explanation"
5. Stewart Cohen [-@WOS000178597300004] "Basic Knowledge and the Problem of Easy Knowledge"
6. Ruth Chang [-@WOS000177540500001] "The Possibility of Parity"
7. Crispin Wright [-@WOS000178597300005] "(Anti-)Sceptics Simple and Subtle: G.E. Moore and John McDowell"
8. Mohan Matthen and André Ariew [-@WOS000173660000001] "Two Ways of Thinking About Fitness and Natural Selection"
9. Christian List and Philip Pettit [-@WOS000175194800009] "Aggregating Sets of Judgments: An Impossibility Result"

### Citation Count {-#sec-count-2002}

```{r}
#| label: tbl-citation-count-2002
#| tbl-cap: Citation count for widely cited articles from 2002.

year_cites <- rank_table_generator(2002)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2002}

```{r}
#| label: tbl-citation-rank-2002
#| tbl-cap: Citation rank for widely cited articles from 2002.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2002}

```{r}
#| label: fig-citation-spaghetti-2002
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2002.
#| cache: FALSE

rolling_spaghetti_graph(2002)
```

```{r}
#| label: fig-citation-facet-2002
#| fig-cap: Faceted version of @fig-citation-spaghetti-2002.
#| cache: FALSE

rolling_facet_graph(2002)
```

\newpage


## 2003 {#sec-s2003}

### Widely Cited Articles {-}

1. Keith DeRose [-@WOS000184740400001] "Assertion, Knowledge, and Context"
2. Nishi Shah [-@WOS000224335200001] "How Truth Governs Belief"
3. Joshua Knobe [-@WOS000183806600005] "Intentional Action and Side Effects in Ordinary Language"
4. Alan Hájek [-@WOS000186731300001] "What Conditional Probability Could Not Be"
5. Tyler Burge [-@WOS000188410400001] "Perceptual Entitlement"
6. Thomas Kelly [-@WOS000183034300004] "Epistemic Rationality as Instrumental Rationality: A Critique"
7. Jonathan Schaffer [-@WOS000184542900005] "Is There a Fundamental Level?"
8. John MacFarlane [-@WOS000183846000001] "Future Contingents and Relative Truth"
9. Kit Fine [-@WOS000182357000001] "The Non-Identity of a Material Thing and Its Matter"

### Citation Count {-#sec-count-2003}

```{r}
#| label: tbl-citation-count-2003
#| tbl-cap: Citation count for widely cited articles from 2003.

year_cites <- rank_table_generator(2003)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2003}

```{r}
#| label: tbl-citation-rank-2003
#| tbl-cap: Citation rank for widely cited articles from 2003.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2003}

```{r}
#| label: fig-citation-spaghetti-2003
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2003.
#| cache: FALSE

rolling_spaghetti_graph(2003)
```

```{r}
#| label: fig-citation-facet-2003
#| fig-cap: Faceted version of @fig-citation-spaghetti-2003.
#| cache: FALSE

rolling_facet_graph(2003)
```

\newpage


## 2004 {#sec-s2004}

### Widely Cited Articles {-}

1. Wlodek Rabinowicz and Toni Rønnow‐Rasmussen [-@WOS000222134800001] "The Strike of the Demon: On Fitting Pro-Attitudes and Value"
2. Charles Travis [-@WOS000188660700003] "The Silence of the Senses"
3. Michael G. F. Martin [-@WOS000223334900003] "The Limits of Self-Awareness"
4. David Pitt [-@WOS000223274200001] "The Phenomenology of Cognition, Or, What is It Like To Think That P?"
5. Robert D. Rupert [-@WOS000223963700001] "Challenges To the Hypothesis of Extended Cognition"
6. Mark Johnston [-@WOS000223334900005] "The Obscure Object of Hallucination"
7. Ronald N. Giere [-@WOS000228600800009] "How Models Are Used To Represent Reality"
8. David J. Chalmers [-@WOS000220800700007] "Epistemic Two-Dimensional Semantics"
9. Jeff McMahan [-@WOS000224317900003] "The Ethics of Killing in War"

### Citation Count {-#sec-count-2004}

```{r}
#| label: tbl-citation-count-2004
#| tbl-cap: Citation count for widely cited articles from 2004.

year_cites <- rank_table_generator(2004)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2004}

```{r}
#| label: tbl-citation-rank-2004
#| tbl-cap: Citation rank for widely cited articles from 2004.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2004}

```{r}
#| label: fig-citation-spaghetti-2004
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2004.
#| cache: FALSE

rolling_spaghetti_graph(2004)
```

```{r}
#| label: fig-citation-facet-2004
#| fig-cap: Faceted version of @fig-citation-spaghetti-2004.
#| cache: FALSE

rolling_facet_graph(2004)
```

\newpage


## 2005 {#sec-s2005}

### Widely Cited Articles {-}

1. Niko Kolodny [-@WOS000231037900002] "Why Be Rational?"
2. Nishi Shah and J. David Velleman [-@WOS000240571800003] "Doxastic Deliberation"
3. Angela M. Smith [-@WOS000227058600002] "Responsibility for Attitudes: Activity and Passivity in Mental Life"
4. Peter Lasersohn [-@WOS000236414800001] "Context Dependence, Disagreement, and Predicates of Personal Taste"
5. Pamela Hieronymi [-@WOS000234618400001] "The Wrong Kind of Reason"
6. Matthew Weiner [-@WOS000240474600003] "Must We Know What We Say?"
7. Alan Baker [-@WOS000228926500001] "Are There Genuine Mathematical Explanations of Physical Phenomena?"
8. Timothy Williamson [-@WOS000228214500004] "Contextualism, Subject-Sensitive Invariantism and Knowledge of Knowledge"
9. Eddy Nahmias, Stephen Morris, Thomas Nadelhoffer, and Jason Turner [-@WOS000232807900002] "Surveying Freedom: Folk Intuitions About Free Will and Moral Responsibility"

### Citation Count {-#sec-count-2005}

```{r}
#| label: tbl-citation-count-2005
#| tbl-cap: Citation count for widely cited articles from 2005.

year_cites <- rank_table_generator(2005)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2005}

```{r}
#| label: tbl-citation-rank-2005
#| tbl-cap: Citation rank for widely cited articles from 2005.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2005}

```{r}
#| label: fig-citation-spaghetti-2005
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2005.
#| cache: FALSE

rolling_spaghetti_graph(2005)
```

```{r}
#| label: fig-citation-facet-2005
#| fig-cap: Faceted version of @fig-citation-spaghetti-2005.
#| cache: FALSE

rolling_facet_graph(2005)
```

\newpage


## 2006 {#sec-s2006}

### Widely Cited Articles {-}

1. Sharon Street [-@WOS000234431300006] "A Darwinian Dilemma for Realist Theories of Value"
2. Hilary Greaves and David Wallace [-@WOS000239761400003] "Justifying Conditionalization: Conditionalization Maximizes Expected Epistemic Utility"
3. Igor Douven [-@WOS000207419100002] "Assertion, Knowledge, and Rational Credibility"
4. Carl F. Craver [-@WOS000242288200003] "When Mechanistic Models Explain"
5. Peter Godfrey-Smith [-@WOS000244292800007] "The Strategy of Model-Based Science"
6. Roger White [-@WOS000243445600002] "Problems for Dogmatism"
7. David Enoch [-@WOS000207418900002] "Agency, Shmagency: Why Normativity Won't Come From What is Constitutive of Action"
8. Nishi Shah [-@WOS000240552100001] "A New Argument for Evidentialism"
9. Joshua Knobe [-@WOS000240410600002] "The Concept of Intentional Action: A Case Study in the Uses of Folk Psychology"

### Citation Count {-#sec-count-2006}

```{r}
#| label: tbl-citation-count-2006
#| tbl-cap: Citation count for widely cited articles from 2006.

year_cites <- rank_table_generator(2006)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2006}

```{r}
#| label: tbl-citation-rank-2006
#| tbl-cap: Citation rank for widely cited articles from 2006.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2006}

```{r}
#| label: fig-citation-spaghetti-2006
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2006.
#| cache: FALSE

rolling_spaghetti_graph(2006)
```

```{r}
#| label: fig-citation-facet-2006
#| fig-cap: Faceted version of @fig-citation-spaghetti-2006.
#| cache: FALSE

rolling_facet_graph(2006)
```

\newpage


## 2007 {#sec-s2007}

### Widely Cited Articles {-}

1. Adam Elga [-@WOS000249103800005] "Reflection and Disagreement"
2. David Christensen [-@WOS000207419300002] "Epistemology of Disagreement: The Good News"
3. Seth Yalcin [-@WOS000251545300007] "Epistemic Modals"
4. Jennifer Lackey [-@WOS000250773100002] "Norms of Assertion"
5. Michael Huemer [-@WOS000246866000002] "Compassionate Phenomenal Conservatism"
6. Michael Weisberg [-@WOS000255137700002] "Three Kinds of Idealization"
7. Andy Egan [-@WOS000245280800001] "Epistemic Modals, Relativism and Assertion"
8. John MacFarlane [-@WOS000244463400002] "Relativism and Disagreement"
9. Shaun Nichols and Joshua Knobe [-@WOS000250773100004] "Moral Responsibility and Determinism: The Cognitive Science of Folk Intuitions"

### Citation Count {-#sec-count-2007}

```{r}
#| label: tbl-citation-count-2007
#| tbl-cap: Citation count for widely cited articles from 2007.

year_cites <- rank_table_generator(2007)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2007}

```{r}
#| label: tbl-citation-rank-2007
#| tbl-cap: Citation rank for widely cited articles from 2007.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2007}

```{r}
#| label: fig-citation-spaghetti-2007
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2007.
#| cache: FALSE

rolling_spaghetti_graph(2007)
```

```{r}
#| label: fig-citation-facet-2007
#| fig-cap: Faceted version of @fig-citation-spaghetti-2007.
#| cache: FALSE

rolling_facet_graph(2007)
```

\newpage


## 2008 {#sec-s2008}

### Widely Cited Articles {-}

1. John Hawthorne and Jason Stanley [-@WOS000262624000001] "Knowledge and Action"
2. Tamar Szabò Gendler [-@WOS000262624000004] "Alief and Belief"
3. Eric Schwitzgebel [-@WOS000272164200003] "The Unreliability of Naive Introspection"
4. Stacey Swain, Joshua Alexander, and Jonathan M. Weinberg [-@WOS000252590700006] "The Instability of Philosophical Intuitions: Running Hot and Cold on Truetemp"
5. Scott Sturgeon [-@WOS000253187500006] "Reason and the Grain of Belief"
6. Jessica Brown [-@WOS000255868500001] "Subject-Sensitive Invariantism and the Knowledge Norm for Practical Reasoning"
7. Michael Fara [-@WOS000262858900004] "Masked Abilities and Compatibilism"
8. Pamela Hieronymi [-@WOS000252978200003] "Responsibility for Believing"
9. David Manley and Ryan Wasserman [-@WOS000253674800003] "On Linking Dispositions and Conditionals"

### Citation Count {-#sec-count-2008}

```{r}
#| label: tbl-citation-count-2008
#| tbl-cap: Citation count for widely cited articles from 2008.

year_cites <- rank_table_generator(2008)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2008}

```{r}
#| label: tbl-citation-rank-2008
#| tbl-cap: Citation rank for widely cited articles from 2008.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2008}

```{r}
#| label: fig-citation-spaghetti-2008
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2008.
#| cache: FALSE

rolling_spaghetti_graph(2008)
```

```{r}
#| label: fig-citation-facet-2008
#| fig-cap: Faceted version of @fig-citation-spaghetti-2008.
#| cache: FALSE

rolling_facet_graph(2008)
```

\newpage


## 2009 {#sec-s2009}

### Widely Cited Articles {-}

1. Alison Hills [-@WOS000273182700004] "Moral Testimony and Moral Epistemology"
2. John MacFarlane [-@WOS000262577100002] "Nonindexical Contextualism"
3. Alan Baker [-@WOS000269013700008] "Mathematical Explanation in Science"
4. Alex Byrne [-@WOS000268238100003] "Experience and Content"
5. Jonathan Schaffer [-@WOS000266504600006] "Spacetime the One Substance"
6. Jonathan Cohen and Craig Callender [-@WOS000266504600001] "A Better Best System Account of Lawhood"
7. Mark Schroeder [-@WOS000263525300005] "Means-End Coherence, Stringency, and Subjective Reasons"
8. Tim Bayne [-@WOS000268238100001] "Perception and the Reach of Phenomenal Content"
9. Jonathan Quong [-@WOS000266722100004] "Killing in Self-Defense"

### Citation Count {-#sec-count-2009}

```{r}
#| label: tbl-citation-count-2009
#| tbl-cap: Citation count for widely cited articles from 2009.

year_cites <- rank_table_generator(2009)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2009}

```{r}
#| label: tbl-citation-rank-2009
#| tbl-cap: Citation rank for widely cited articles from 2009.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2009}

```{r}
#| label: fig-citation-spaghetti-2009
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2009.
#| cache: FALSE

rolling_spaghetti_graph(2009)
```

```{r}
#| label: fig-citation-facet-2009
#| fig-cap: Faceted version of @fig-citation-spaghetti-2009.
#| cache: FALSE

rolling_facet_graph(2009)
```

\newpage


## 2010 {#sec-s2010}

### Widely Cited Articles {-}

1. Jonathan Schaffer [-@WOS000272855000002] "Monism: The Priority of the Whole"
2. David Christensen [-@WOS000279407600010] "Higher-Order Evidence"
3. Niko Kolodny and John MacFarlane [-@WOS000280778100001] "Ifs and Oughts"
4. James Woodward [-@WOS000278111100001] "Causation in Biology: Stability, Specificity, and the Choice of Levels of Explanation"
5. Eric Schwitzgebel [-@WOS000284854700005] "Acting Contrary To Our Professed Beliefs or the Gulf Between Occurrent Judgment and Dispositional Belief"
6. Kevin J. S. Zollman [-@WOS000272374500002] "The Epistemic Benefit of Transient Diversity"
7. Julia Markovits [-@WOS000276319000003] "Acting for the Right Reasons"
8. Jonathan Schaffer [-@WOS000275147000005] "The Least Discerning and Most Promiscuous Truthmaker"
9. Jonathan M. Weinberg, Chad Gonnerman, Cameron Buckner, and Joshua Alexander [-@WOS000279171200004] "Are Philosophers Expert Intuiters?"

### Citation Count {-#sec-count-2010}

```{r}
#| label: tbl-citation-count-2010
#| tbl-cap: Citation count for widely cited articles from 2010.

year_cites <- rank_table_generator(2010)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2010}

```{r}
#| label: tbl-citation-rank-2010
#| tbl-cap: Citation rank for widely cited articles from 2010.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2010}

```{r}
#| label: fig-citation-spaghetti-2010
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2010.
#| cache: FALSE

rolling_spaghetti_graph(2010)
```

```{r}
#| label: fig-citation-facet-2010
#| fig-cap: Faceted version of @fig-citation-spaghetti-2010.
#| cache: FALSE

rolling_facet_graph(2010)
```

\newpage


## 2011 {#sec-s2011}

### Widely Cited Articles {-}

1. Kristie Dotson [-@WOS000289948200002] "Tracking Epistemic Violence, Tracking Practices of Silencing"
2. David J. Chalmers [-@WOS000295159700002] "Verbal Disputes"
3. Karen Bennett [-@WOS000298592300002] "By Our Bootstraps"
4. David Michael Kaplan and Carl F. Craver [-@WOS000295735100004] "The Explanatory Force of Dynamical and Mathematical Models in Neuroscience: A Mechanistic Perspective"
5. C. S. Jenkins [-@WOS000209153800006] "Is Metaphysical Dependence Irreflexive?"
6. David Christensen [-@WOS000208774400001] "Disagreement, Question-Begging and Epistemic Self-Criticism"
7. Gualtiero Piccinini and Carl Craver [-@WOS000298031500001] "Integrating Psychology and Neuroscience: Functional Analyses as Mechanism Sketches"
8. Timothy Sundell [-@WOS000294571800007] "Disagreements About Taste"
9. Timothy Williamson [-@WOS000289158400004] "Philosophical Expertise and the Burden of Proof"

### Citation Count {-#sec-count-2011}

```{r}
#| label: tbl-citation-count-2011
#| tbl-cap: Citation count for widely cited articles from 2011.

year_cites <- rank_table_generator(2011)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2011}

```{r}
#| label: tbl-citation-rank-2011
#| tbl-cap: Citation rank for widely cited articles from 2011.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2011}

```{r}
#| label: fig-citation-spaghetti-2011
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2011.
#| cache: FALSE

rolling_spaghetti_graph(2011)
```

```{r}
#| label: fig-citation-facet-2011
#| fig-cap: Faceted version of @fig-citation-spaghetti-2011.
#| cache: FALSE

rolling_facet_graph(2011)
```

\newpage


## 2012 {#sec-s2012}

### Widely Cited Articles {-}

1. Duncan Pritchard [-@WOS000311002900002] "Anti-Luck Virtue Epistemology"
2. Paul Audi [-@WOS000318890500001] "Grounding: Toward a Theory of the In-Virtue-Of Relation"
3. Gaile Pohlhaus Jr. [-@WOS000309450000003] "Relational Knowing and Epistemic Injustice: Toward a Theory of Willful Hermeneutical Ignorance"
4. Fiona Macpherson [-@WOS000298593200002] "Cognitive Penetration of Colour Experience: Rethinking the Issue in Light of An Indirect Mechanism"
5. Pablo Cobreros, Paul Egre, David Ripley, and Robert Van Rooij [-@WOS000303510200003] "Tolerant, Classical, Strict"
6. Eric Schwitzgebel and Fiery Cushman [-@WOS000302010200002] "Expertise in Moral Reasoning? Order Effects on Moral Judgment in Professional Philosophers and Non-Philosophers"
7. Barry Loewer [-@WOS000307407600006] "Two Accounts of Laws and Time"
8. Susanna Siegel [-@WOS000304136000001] "Cognitive Penetrability and Perceptual Justification"
9. Elizabeth Anderson [-@WOS000209097600003] "Epistemic Justice as a Virtue of Social Institutions"

### Citation Count {-#sec-count-2012}

```{r}
#| label: tbl-citation-count-2012
#| tbl-cap: Citation count for widely cited articles from 2012.

year_cites <- rank_table_generator(2012)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2012}

```{r}
#| label: tbl-citation-rank-2012
#| tbl-cap: Citation rank for widely cited articles from 2012.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2012}

```{r}
#| label: fig-citation-spaghetti-2012
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2012.
#| cache: FALSE

rolling_spaghetti_graph(2012)
```

```{r}
#| label: fig-citation-facet-2012
#| fig-cap: Faceted version of @fig-citation-spaghetti-2012.
#| cache: FALSE

rolling_facet_graph(2012)
```

\newpage


## 2013 {#sec-s2013}

### Widely Cited Articles {-}

1. David Plunkett and Tim Sundell [-@WOS000332023600001] "Disagreement and the Semantics of Normative and Evaluative Terms"
2. Jane Friedman [-@WOS000312934500003] "Suspended Judgment"
3. Louis deRosset [-@WOS000324866000001] "Grounding Explanations"
4. Kelly Trogdon [-@WOS000326701100003] "Grounding: Necessary or Contingent?"
5. David Ripley [-@WOS000315655800008] "Paradoxes and Failures of Cut"
6. Marc Lange [-@WOS000322956100002] "What Makes a Scientific Explanation Distinctively Mathematical?"
7. Selim Berker [-@WOS000322803000001] "Epistemic Teleology and the Separateness of Propositions"
8. Pablo Cobreros, Paul Egre, David Ripley, and Robert Van Rooij [-@WOS000336209400001] "Reaching Transparent Truth"
9. Alberto Giubilini and Francesca Minerva [-@WOS000318480800009] "After-Birth Abortion: Why Should the Baby Live?"

### Citation Count {-#sec-count-2013}

```{r}
#| label: tbl-citation-count-2013
#| tbl-cap: Citation count for widely cited articles from 2013.

year_cites <- rank_table_generator(2013)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2013}

```{r}
#| label: tbl-citation-rank-2013
#| tbl-cap: Citation rank for widely cited articles from 2013.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2013}

```{r}
#| label: fig-citation-spaghetti-2013
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2013.
#| cache: FALSE

rolling_spaghetti_graph(2013)
```

```{r}
#| label: fig-citation-facet-2013
#| fig-cap: Faceted version of @fig-citation-spaghetti-2013.
#| cache: FALSE

rolling_facet_graph(2013)
```

\newpage


## 2014 {#sec-s2014}

### Widely Cited Articles {-}

1. Jessica M. Wilson [-@WOS000344393500001] "No Work for a Theory of Grounding"
2. Miriam Schoenfield [-@WOS000334424500001] "Permission To Believe: Why Permissivism is True and What It Tells Us About Irrelevant Influences on Belief"
3. Shamik Dasgupta [-@WOS000354150500006] "The Possibility of Physicalism"
4. Jacob Ross and Mark Schroeder [-@WOS000333404400001] "Belief, Credence, and Pragmatic Encroachment"
5. Paul Boghossian [-@WOS000335566200001] "What is Inference?"
6. Sophie Horowitz [-@WOS000344362900006] "Epistemic Akrasia"
7. Lara Buchak [-@WOS000336029900007] "Belief, Credence, and Norms"
8. Robert W. Batterman and Collin C. Rice [-@WOS000337746400004] "Minimal Model Explanations"
9. Stephan Leuenberger [-@WOS000330705300001] "Grounding and Necessity"

### Citation Count {-#sec-count-2014}

```{r}
#| label: tbl-citation-count-2014
#| tbl-cap: Citation count for widely cited articles from 2014.

year_cites <- rank_table_generator(2014)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2014}

```{r}
#| label: tbl-citation-rank-2014
#| tbl-cap: Citation rank for widely cited articles from 2014.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2014}

```{r}
#| label: fig-citation-spaghetti-2014
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2014.
#| cache: FALSE

rolling_spaghetti_graph(2014)
```

```{r}
#| label: fig-citation-facet-2014
#| fig-cap: Faceted version of @fig-citation-spaghetti-2014.
#| cache: FALSE

rolling_facet_graph(2014)
```

\newpage


## 2015 {#sec-s2015}

### Widely Cited Articles {-}

1. Alexander Skiles [-@WOS000360509700002] "Against Grounding Necessitarianism"
2. Michael J. Raven [-@WOS000359831800003] "Ground"
3. Collin Rice [-@WOS000358438300009] "Moving Beyond Causes: Optimality Models and Scientific Explanation"
4. David Plunkett [-@WOS000366669500008] "Which Concepts Should We Use?: Metalinguistic Negotiations and the Methodology of Philosophy"
5. James Woodward [-@WOS000360840400003] "Interventionism and Causal Exclusion"
6. Kit Fine [-@WOS000211496500002] "Unified Foundations for Essence and Ground"
7. John Bengson [-@WOS000363483500001] "The Intellectual Given"
8. Jonathan Schaffer [-@WOS000363328400002] "What Not To Multiply Without Necessity"
9. Neil Levy [-@WOS000363695100009] "Neither Fish Nor Fowl: Implicit Attitudes as Patchy Endorsements"

### Citation Count {-#sec-count-2015}

```{r}
#| label: tbl-citation-count-2015
#| tbl-cap: Citation count for widely cited articles from 2015.

year_cites <- rank_table_generator(2015)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2015}

```{r}
#| label: tbl-citation-rank-2015
#| tbl-cap: Citation rank for widely cited articles from 2015.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2015}

```{r}
#| label: fig-citation-spaghetti-2015
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2015.
#| cache: FALSE

rolling_spaghetti_graph(2015)
```

```{r}
#| label: fig-citation-facet-2015
#| fig-cap: Faceted version of @fig-citation-spaghetti-2015.
#| cache: FALSE

rolling_facet_graph(2015)
```

\newpage


## 2016 {#sec-s2016}

### Widely Cited Articles {-}

1. Jonathan Schaffer [-@WOS000368189400004] "Grounding in the Image of Causation"
2. Cian Dorr [-@WOS000397575900003] "To Be F is To Be G"
3. Alison Hills [-@WOS000387458900001] "Understanding Why"
4. Eric Mandelbaum [-@WOS000380694400009] "Attitude, Inference, Association: On the Propositional Structure of Implicit Bias"
5. Shamik Dasgupta [-@WOS000374968600007] "Metaphysical Rationalism"
6. Conor McHugh and Jonathan Way [-@WOS000373095100002] "Fittingness First"
7. Miranda Fricker [-@WOS000368807300008] "What's the Point of Blame? a Paradigm Based Explanation"
8. John Hawthorne, Daniel Rothschild, and Levi Spectre [-@WOS000373229500014] "Belief is Weak"
9. Jakob Hohwy [-@WOS000374968600002] "The Self-Evidencing Brain"

### Citation Count {-#sec-count-2016}

```{r}
#| label: tbl-citation-count-2016
#| tbl-cap: Citation count for widely cited articles from 2016.

year_cites <- rank_table_generator(2016)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2016}

```{r}
#| label: tbl-citation-rank-2016
#| tbl-cap: Citation rank for widely cited articles from 2016.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2016}

```{r}
#| label: fig-citation-spaghetti-2016
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2016.
#| cache: FALSE

rolling_spaghetti_graph(2016)
```

```{r}
#| label: fig-citation-facet-2016
#| fig-cap: Faceted version of @fig-citation-spaghetti-2016.
#| cache: FALSE

rolling_facet_graph(2016)
```

\newpage


## 2017 {#sec-s2017}

### Widely Cited Articles {-}

1. Jane Friedman [-@WOS000400022600006] "Why Suspend Judging?"
2. Jonathan Schaffer [-@WOS000404667500001] "The Ground Between the Gaps"
3. Susanna Rinard [-@WOS000394452900005] "No Exception for Belief"
4. Dennis Whitcomb, Heather Battaly, Jason Baehr, and Daniel Howard-Snyder [-@WOS000404459700001] "Intellectual Humility: Owning Our Limitations"
5. Ole Thomassen Hjortland [-@WOS000396059900005] "Anti-Exceptionalism About Logic"
6. Kit Fine [-@WOS000416231700003] "A Theory of Truthmaker Content I: Conjunction, Disjunction and Negation"
7. Jason Stanley and Timothy Williamson [-@WOS000414712900003] "Skill"

### Citation Count {-#sec-count-2017}

```{r}
#| label: tbl-citation-count-2017
#| tbl-cap: Citation count for widely cited articles from 2017.

year_cites <- rank_table_generator(2017)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2017}

```{r}
#| label: tbl-citation-rank-2017
#| tbl-cap: Citation rank for widely cited articles from 2017.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2017}

```{r}
#| label: fig-citation-spaghetti-2017
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2017.
#| cache: FALSE

rolling_spaghetti_graph(2017)
```

```{r}
#| label: fig-citation-facet-2017
#| fig-cap: Faceted version of @fig-citation-spaghetti-2017.
#| cache: FALSE

rolling_facet_graph(2017)
```

\newpage


## 2018 {#sec-s2018}

### Widely Cited Articles {-}

1. David J. Chalmers [-@WOS000445442600001] "The Meta-Problem of Consciousness"
2. Alastair Wilson [-@WOS000449886300001] "Metaphysical Causation"
3. Alex Worsnip [-@WOS000419946900001] "The Conflict of Evidence and Coherence"
4. Amia Srinivasan [-@WOS000431658000001] "The Aptness of Anger"
5. Michael Prinzing [-@WOS000443877200002] "The Revisionist's Rubric: Conceptual Engineering and the Discontinuity Objection"
6. Selim Berker [-@WOS000441806400004] "The Unity of Grounding"
7. Jelle Bruineberg, Julian Kiverstein, and Erik Rietveld [-@WOS000433358500004] "The Anticipating Brain is Not a Scientist: The Free-Energy Principle From An Ecological-Enactive Perspective"

### Citation Count {-#sec-count-2018}

```{r}
#| label: tbl-citation-count-2018
#| tbl-cap: Citation count for widely cited articles from 2018.

year_cites <- rank_table_generator(2018)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2018}

```{r}
#| label: tbl-citation-rank-2018
#| tbl-cap: Citation rank for widely cited articles from 2018.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2018}

```{r}
#| label: fig-citation-spaghetti-2018
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2018.
#| cache: FALSE

rolling_spaghetti_graph(2018)
```

```{r}
#| label: fig-citation-facet-2018
#| fig-cap: Faceted version of @fig-citation-spaghetti-2018.
#| cache: FALSE

rolling_facet_graph(2018)
```

\newpage


## 2019 {#sec-s2019}

### Widely Cited Articles {-}

1. Jane Friedman [-@WOS000465095900003] "Inquiry and Belief"
2. Rima Basu [-@WOS000477039200013] "The Wrongs of Racist Beliefs"
3. Fabrice Correia and Alexander Skiles [-@WOS000470911200007] "Grounding, Essence, and Identity"
4. Rima Basu [-@WOS000460037300004] "What We Epistemically Owe To Each Other"
5. Kevin Dorst [-@WOS000460632200006] "Lockeans Maximize Expected Accuracy"

### Citation Count {-#sec-count-2019}

```{r}
#| label: tbl-citation-count-2019
#| tbl-cap: Citation count for widely cited articles from 2019.

year_cites <- rank_table_generator(2019)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2019}

```{r}
#| label: tbl-citation-rank-2019
#| tbl-cap: Citation rank for widely cited articles from 2019.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2019}

```{r}
#| label: fig-citation-spaghetti-2019
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2019.
#| cache: FALSE

rolling_spaghetti_graph(2019)
```

```{r}
#| label: fig-citation-facet-2019
#| fig-cap: Faceted version of @fig-citation-spaghetti-2019.
#| cache: FALSE

rolling_facet_graph(2019)
```

\newpage

