% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod,
  twoside]{scrartcl}
\usepackage{xcolor}
\usepackage[left=1.1in, right=1in, top=0.8in, bottom=0.8in,
paperheight=9.5in, paperwidth=7in, includemp=TRUE, marginparwidth=0in,
marginparsep=0in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{3}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmathfont[]{Garamond-Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0ex}
\usepackage[automark]{scrlayer-scrpage}
\clearpairofpagestyles
\cehead{
  Brian Weatherson
  }
\cohead{
  Humberstone on Possibility Frames
  }
\ohead{\bfseries \pagemark}
\cfoot{}
\makeatletter
\newcommand*\NoIndentAfterEnv[1]{%
  \AfterEndEnvironment{#1}{\par\@afterindentfalse\@afterheading}}
\makeatother
\NoIndentAfterEnv{itemize}
\NoIndentAfterEnv{enumerate}
\NoIndentAfterEnv{description}
\NoIndentAfterEnv{quote}
\NoIndentAfterEnv{equation}
\NoIndentAfterEnv{longtable}
\NoIndentAfterEnv{abstract}
\renewenvironment{abstract}
 {\vspace{-1.25cm}
 \quotation\small\noindent\emph{Abstract}:}
 {\endquotation}
\newfontfamily\tfont{EB Garamond}
\addtokomafont{disposition}{\rmfamily}
\addtokomafont{title}{\normalfont\itshape}
\let\footnoterule\relax

\makeatletter
\renewcommand{\@maketitle}{%
  \newpage
  \null
  \vskip 2em%
  \begin{center}%
  \let \footnote \thanks
    {\itshape\huge\@title \par}%
    \vskip 0.5em%  % Reduced from default
    {\large
      \lineskip 0.3em%  % Reduced from default 0.5em
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%  % Reduced from default
    {\large \@date}%
  \end{center}%
  \par
  }
\makeatother
\RequirePackage{lettrine}

\renewenvironment{abstract}
 {\quotation\small\noindent\emph{Abstract}:}
 {\endquotation\vspace{-0.02cm}}

\setmainfont{EB Garamond Math}[
  BoldFont = {EB Garamond SemiBold},
  ItalicFont = {EB Garamond Italic},
  RawFeature = {+smcp},
]

\newfontfamily\scfont{EB Garamond Regular}[RawFeature=+smcp]
\renewcommand{\textsc}[1]{{\scfont #1}}

\renewcommand{\LettrineTextFont}{\scfont}
\newcommand{\nmodels}{\mathrel{\ooalign{$\models$\cr\raisebox{-0.001ex}{\hss$\mkern-1mu/\hss$}\cr}}}
\newcommand{\llbracket}{[\![}
\newcommand{\rrbracket}{]\!]}
\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0ex}
\usepackage[lines=2]{lettrine}
\cehead{Draft of February 28, 2026}
\DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
\DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Humberstone on Possibility Frames},
  pdfauthor={Brian Weatherson},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}


\title{Humberstone on Possibility Frames}
\author{Brian Weatherson}
\date{2026}
\begin{document}
\maketitle
\begin{abstract}
In his 1981 paper ``From Worlds to Possibilities'', Lloyd Humberstone
developed an approach to modal logic using \emph{possibilities} rather
than possible worlds. Possibilities, unlike worlds, may be incomplete.
This paper sets out the possibility frame approach to modal logic,
proves some results about its logic (including that some logics
definable on Humberstone frames are not definable on Kripke frames), and
surveys several applications, including to conditionals, vagueness, and
fiction.
\end{abstract}


\setstretch{1.1}
In his 1981 paper ``From Worlds to Possibilities'', Lloyd Humberstone
shows a way to do modal logic without the apparatus of possible worlds.
Instead of worlds he uses \emph{possibilities}, which may, unlike
worlds, be incomplete. The non-modal parts of the view are discussed
again in section 6.44 of \emph{The Connectives}, though the differences
between the view there and the 1981 view are largely presentational. In
this paper I'll set out this \emph{possibility frame} approach to modal
logic, make some notes about its logic, and end with a survey of its
possible applications.

Mathematically, possibilities are points in a model, like possible
worlds are points in different kinds of models. But it helps to have a
mental picture of what kind of thing they are. In ``From Worlds to
Possibilities'', Humberstone notes that one picture you could have is
that they are sets of possible worlds. This isn't a terrible picture,
but it's not perfect for a couple of reasons. For one thing, as
Humberstone notes, part of the point of developing possibilities is to
do without the machinery of possible worlds. Understanding possibilities
as sets of possible worlds wouldn't help with that project. For another,
as Wesley Holliday (\citeproc{ref-Holliday2025}{2025, 271--72}) notes,
the natural way to generate modal accessibility relations on sets of
worlds from accessibility on the worlds themselves doesn't always work
the way Humberstone wants accessibility to work. So let's start with a
different picture.

Possibilities, as I'll think of them, are \emph{stories}. To make things
concrete, I'll start with a particular story: \emph{A Study in Scarlet}
(Conan Doyle (\citeproc{ref-ConanDoyle1995}{1995})), the story in which
Sherlock Holmes was introduced. That story settles some questions, both
explicitly, e.g., that Holmes is a detective, and implicitly, e.g., that
Holmes has never set foot on the moon. But it leaves several other
questions open, e.g., how many cousins Holmes has. It's not just that
\emph{A Study in Scarlet} is a story. It has proper parts that are
stories. The first chapter is a story, one that tells of the first
meeting between Holmes and Watson. And arguably it is a proper part of a
larger story, made up of all of Conan Doyle's stories of Holmes and
Watson. When a story \(x\) is a proper part of story \(y\), what that
means is that everything settled in \(x\) is still true in \(y\), and
more things besides are settled. When this happens, we'll call \(y\) a
proper \emph{refinement} of \(x\). For most purposes it will be more
convenient to use the more general notion of \emph{refinement}, where
each story counts as an improper refinement of itself.

Following Humberstone, I'll write \(x \leqslant y\) to mean that \(y\)
is a refinement of \(x\). As he notes, this notation can be confusing if
one thinks of \(x\) and \(y\) as sets, because in that case the
refinement will typically be \emph{smaller}.\footnote{Holliday
  (\citeproc{ref-Holliday2025}{2025}) writes \(y \sqsubseteq x\) when
  \(y\) is a refinement of \(x\), mirroring this way of thinking about
  possibilities.} But if we think of possibilities as stories, the
notation becomes more intuitive. We have \(x \leqslant y\) when \(y\) is
created by adding new content to \(x\). Keeping with this theme, I'll
typically model stories not as worlds, but as finite sequences. (In the
main example in Section~\ref{sec-proof}, they will be sequences of 0s
and 1s.) In these models, \(x \leqslant y\) means that \(x\) is an
initial segment of \(y\).

\section{The Formal Structure}\label{sec-formal}

\subsection*{The Basic Language}\label{the-basic-language}
\addcontentsline{toc}{subsection}{The Basic Language}

To start with, assume we're working in a simple language that has a
countable set \(\mathcal{P}\) of propositional variables, and three
connectives: \(\neg\), \(\wedge\), and \(\vee\). We have a set of
possibilities \(W\), and a reflexive and transitive refinement relation
\(\leqslant\) on them. The following rules show how to build what I'll
call a \emph{Humberstone possibility model} on
\(\langle W, \leqslant \rangle\). (I'll call
\(\langle W, \leqslant \rangle\) a \emph{possibility frame} in most
contexts, but a \emph{Humberstone frame} when I'm comparing it to
similar structures, especially in the context of discussing Holliday
(\citeproc{ref-Holliday2025}{2025}).)

A Humberstone possibility model \(\mathcal{M}\) is a triple
\(\langle W, \leqslant, V \rangle\), where \(V\) is a function from
\(\mathcal{P}\) to \(\wp(W)\), intuitively saying where each atomic
proposition is true, satisfying these two constraints:

\begin{itemize}
\tightlist
\item
  For all \(x\), if \(x \in V(p)\) and \(y \geqslant x\), then
  \(y \in V(p)\). Intuitively, truth for atomics is \textbf{persistent}
  across refinements.
\item
  For all \(x\), if
  \(\forall y \geqslant x \exists z \geqslant y: z \in V(p)\), then
  \(x \in V(p)\). This is what Humberstone
  (\citeproc{ref-Humberstone2011}{2011, 900}) calls
  \textbf{refinability}, and it means that \(p\) only fails to be true
  at \(x\) if there is some refinement of \(x\) where it is settled as
  being untrue.
\end{itemize}

Given these constraints, Humberstone suggests the following theory of
truth at a possibility for all sentences in this language. (We'll treat
\(\rightarrow\) as a defined connective, with
\(A \rightarrow B =_{df} \neg A \vee B\).)

\begin{align*}
[\text{Vbls}] \quad & \mathcal{M} \models_x p_i \text{ iff } x \in V(p_i); \\
[\neg] \quad & \mathcal{M} \models_x \neg A \text{ iff } \forall y \geqslant x, \, \mathcal{M} \nmodels_y  A; \\
[\wedge] \quad & \mathcal{M} \models_x A \wedge B \text{ iff } \mathcal{M} \models_x A \text{ and } \mathcal{M} \models_x B; \\
[\vee] \quad & \mathcal{M} \models_x A \vee B \text{ iff } \forall y \geqslant x \, \exists z \geqslant y \, : \, \mathcal{M} \models_z A \text{ or } \mathcal{M} \models_z B.
\end{align*}

Given these definitions, it's possible to prove three things. First,
every sentence in the language is persistent. If
\(\mathcal{M} \models_x A\) and \(x \leqslant y\), then
\(\mathcal{M} \models_y A\). For any sentence, truth is always preserved
when moving to a refinement. Second, refinability holds for all
sentences in the language. This is, as Humberstone notes, easier to
state using {[}\(\neg\){]}. Once we've added negation to the language,
refinement becomes the claim that, for any \(A\), if
\(\mathcal{M} \nmodels_x A\), there is some refinement \(y\) of \(x\)
such that \(\mathcal{M} \models_y \neg A\). Third, for any set of
sentences \(\Gamma\) and sentence \(A\), the truth at a point of all
sentences in \(\Gamma\) guarantees the truth of \(A\) iff the sequent
\(\Gamma\) entails \(A\) in classical propositional logic.

In this paper, I'm going to discuss three extensions of this language.
I'll introduce them in reverse order of how much they are discussed in
Humberstone, starting with one he does not discuss at all: infinitary
disjunction.

\subsection*{Infinitary Disjunction}\label{infinitary-disjunction}
\addcontentsline{toc}{subsection}{Infinitary Disjunction}

We'll add to the language a new symbol \(\bigvee\), which forms a new
sentence out of any countable set of sentences not containing
\(\bigvee\). Intuitively, it is true when one of the sentences in the
set is true. More formally, its truth at a possibility is defined as
follows:

\begin{align*}
[\bigvee] \quad & \mathcal{M} \models_x \bigvee ({A_1, A_2, \dots})  \text{ iff } \forall y \geqslant x \, \exists z \geqslant y \, : \,\text{ for some } i \, \mathcal{M} \models_z A_i.
\end{align*}

Again, it's fairly simple to show that this addition to the language
will preserve persistence and refinability. But while this is simple, it
is significant, because things could easily have been otherwise.

\subsection*{Quantifiers}\label{quantifiers}
\addcontentsline{toc}{subsection}{Quantifiers}

The second extension will be to add quantifiers, following a suggestion
in Humberstone (\citeproc{ref-Humberstone1981a}{1981, 331}). Assume, as
usual, that the language has a stock of names \(c_1, \dots\), and for
each \(n\), a stock of \(n\)-place predicates \(F^n_1, F^n_2, \dots\). A
\emph{first-order (Humberstone) possibility model} is a structure
\(\langle W, \leqslant, D, V \rangle\), where \(D\) assigns a non-empty
domain of objects to each point, and \(V\) interprets the non-logical
vocabulary. More precisely:

\begin{itemize}
\tightlist
\item
  \(D\) is a function assigning to each \(x \in W\) a non-empty set
  \(D(x)\), the \textbf{domain} at \(x\).
\item
  \(V\) assigns to each name \(c_i\) and each \(x \in W\) either a
  designated element \(V(c_i, x) \in D(x)\), or is undefined at \(x\).
\item
  \(V\) assigns to each \(n\)-place predicate \(F^n_j\) and each
  \(x \in W\) a set \(V(F^n_j, x) \subseteq D(x)^n\), the
  \textbf{extension} of \(F^n_j\) at \(x\).
\end{itemize}

These must satisfy the following constraints:

\begin{description}
\tightlist
\item[Domain monotonicity]
If \(x \leqslant y\), then \(D(x) \subseteq D(y)\).
\item[Name coverage]
For each name \(c_i\) and each \(x \in W\), there exists some
\(y \geqslant x\) such that \(V(c_i, y)\) is defined.
\item[Persistence for names]
If \(V(c_i, x)\) is defined and \(x \leqslant y\), then \(V(c_i, y)\) is
defined and \(V(c_i, y) = V(c_i, x)\).
\item[Persistence for predicate extensions]
If \(\langle o_1, \dots, o_n \rangle \in V(F^n_j, x)\) and
\(x \leqslant y\), then
\(\langle o_1, \dots, o_n \rangle \in V(F^n_j, y)\).
\item[Refinability for predicate extensions]
If \(\langle o_1, \dots, o_n \rangle \notin V(F^n_j, x)\), then there
exists some \(y \geqslant x\) such that for all \(z \geqslant y\),
\(\langle o_1, \dots, o_n \rangle \notin V(F^n_j, z)\).
\end{description}

Given a model and a variable assignment \(g\) mapping variables to
objects, truth at a point is defined as follows. Write \(g[v/o]\) for
the assignment that maps variable \(v\) to object \(o\) and otherwise
agrees with \(g\). For a term \(t\), write
\(\llbracket t \rrbracket^{g,x}\) for the denotation of \(t\) under
\(g\) at \(x\). This will not always be defined, e.g., when the term is
a name that only gets defined at subsequent refinements.

\begin{align*}
[=] \quad & \mathcal{M}, g \models_x t_1 = t_2 \text{ iff } \forall y \geqslant x \, \exists z \geqslant y : \llbracket t_1 \rrbracket^{g,z} \text{ and } \llbracket t_2 \rrbracket^{g,z} \text{ are both defined and equal}; \\
[F^n] \quad & \mathcal{M}, g \models_x F^n_j(t_1, \dots, t_n) \text{ iff } \forall y \geqslant x \, \exists z \geqslant y : \langle \llbracket t_1 \rrbracket^{g,z}, \dots, \llbracket t_n \rrbracket^{g,z} \rangle \in V(F^n_j, z); \\
[\forall] \quad & \mathcal{M}, g \models_x \forall v \, A \text{ iff } \forall y \geqslant x \, \forall o \in D(y) : \mathcal{M}, g[v/o] \models_y A; \\
[\exists] \quad & \mathcal{M}, g \models_x \exists v \, A \text{ iff } \forall y \geqslant x \, \exists z \geqslant y \, \exists o \in D(z) : \mathcal{M}, g[v/o] \models_z A.
\end{align*}

The propositional connectives are handled exactly as before.

The surprising thing here is the \(\forall\exists\) pattern in clauses
for identity and for non-logical predicates. We need to write the clause
that way, rather than just saying for example that \(Fa\) is true at
\(x\) if
\(\llbracket a \rrbracket^{g,x} \in \llbracket F \rrbracket^{g,x}\), for
two related reasons. First, we're in classical logic, so for any name
\(c\) we want \(c=c\) to come out true, even when \(c\) lacks a
denotation at \(x\). Second, we want \(\forall y: Fy\) to entail \(Fc\).
So if \(\forall y: Fy\) is true at \(x\), we need \(Fc\) to be true at
\(x\) even when \(c\) lacks a denotation.

The underlying problem here is that it's impossible to have an
equivalent of the refinability condition for names. It seems reasonable
to have a name, say `Holmes', which picks out a particular individual,
say Holmes, at all refinements where Holmes is in the domain. But we
don't want that to imply that Holmes is already in the domain. So even
if `Holmes' will never denote something other than Holmes, it's not
already true that it denotes Holmes. The complications in the above
clauses are downstream of the fact that denotation does not satisfy
refinability in just that way.

In the special case where every name already has a denotation at \(x\),
the atomic clauses simplify in just the way you would hope. If \(t_1\)
and \(t_2\) are variables, or names that already have denotations at
\(x\), then by persistence of names and predicate extensions the
\(\forall\exists\) quantifier prefix collapses:
\(\mathcal{M}, g \models_x t_1 = t_2\) iff
\(\llbracket t_1 \rrbracket^{g,x} = \llbracket t_2 \rrbracket^{g,x}\),
and \(\mathcal{M}, g \models_x F^n_j(t_1, \dots, t_n)\) iff
\(\langle \llbracket t_1 \rrbracket^{g,x}, \dots, \llbracket t_n \rrbracket^{g,x} \rangle \in V(F^n_j, x)\).
The more complex clauses above are needed only to handle the case where
some name occurring in the formula lacks a denotation at \(x\) but is
guaranteed to acquire one.

This is a possibilist treatment of the universal quantifier, in contrast
to the actualist quantifiers discussed in Harrison-Trainor
(\citeproc{ref-HarrisonTrainor2019}{2019}). I'll return in
Section~\ref{sec-quant} to the reasons we are best off using possibilist
quantifiers, and the difficulties this raises for talking about just
what's true in a possibility.

\subsection*{Modal Operators}\label{modal-operators}
\addcontentsline{toc}{subsection}{Modal Operators}

The third extension will be the introduction of modal operators. Here
I'll follow Humberstone (\citeproc{ref-Humberstone1981a}{1981}) very
closely, save that I'll have a plurality of modal operators rather than
just one. So I'll use these structures to define (as Holliday
(\citeproc{ref-Holliday2025}{2025}) does) multi-modal logics. But I'll
follow Humberstone, and not Holliday, in defining modal operators in
terms of accessibility relations \(R_i\) satisfying these three
conditions\footnote{I'm using the names for these that Holliday uses,
  which are more evocative than Humberstone's original names.}:

\begin{description}
\tightlist
\item[\textbf{UpR}:]
If \(x \leqslant x'\) and \(x' R_i y\), then \(x R_i y\).
\item[\textbf{RDown}:]
If \(x R_i y\) and \(y \leqslant y'\), then \(x R_i y'\).
\item[\textbf{RRef++}:]
If \(x R_i y\), then there exists \(x' \geqslant x\) such that for all
\(x'' \geqslant x'\), \(x'' R_i y\).
\end{description}

\textbf{UpR} says that if a refinement of \(x\) can access \(y\), then
\(x\) itself can already access \(y\): accessibility is not something
that can be gained by adding detail to the source. \textbf{RDown} is a
converse of this; it says that accessibility cannot be lost by adding
detail to the target. \textbf{RRef++} says that if \(x\) can access
\(y\), there is some refinement \(x'\) of \(x\) where it is settled that
\(x'\) can access \emph{y}. This last access can't be overturned by
further refinement of \(x'\).

Given these constraints, the truth condition for the box operator is:

\begin{align*}
[\Box_i] \quad & \mathcal{M} \models_x \Box_i A \text{ iff } \forall y \, (x R_i y \Rightarrow \mathcal{M} \models_y A); \\
\end{align*}

This should be familiar: \(\Box_i A\) is true at \(x\) iff \(A\) is true
at every \(R_i\)-accessible possibility.

Humberstone treats \(\Diamond\) as a defined connective,
\(\Diamond_i A\) just means \(\neg \Box_i \neg A\), and I'll follow
suit. If we spell out what it means for \(\neg \Box_i \neg A\) to be
true, we get the rule {[}\(\Diamond_i\){]}\textsubscript{Official}. But
if we impose the above three constraints on \(R_i\), we can see that
this is equivalent to the more familiar
{[}\(\Diamond_i\){]}\textsubscript{Simple}.

\begin{align*}
[\Diamond_i]_{\text{Official}} \quad & \mathcal{M} \models_x \Diamond_i A \text{ iff } \forall y \geqslant x \, \exists z \geqslant y \, \exists w \, (z R_i w \text{ and } \mathcal{M} \models_w A). \\
[\Diamond_i]_{\text{Simple}} \quad & \mathcal{M} \models_x \Diamond_i A \text{ iff } \exists y \, (x R_i y \text{ and } \mathcal{M} \models_y A);
\end{align*}

If \(R_i\) obeys \textbf{UpR}, then
{[}\(\Diamond_i\){]}\textsubscript{Official} will imply
{[}\(\Diamond_i\){]}\textsubscript{Simple}. For \(\Diamond_i A\) to be
true at \(x\) according to {[}\(\Diamond_i\){]}\textsubscript{Official},
there must be some refinement which can access a point where \(A\) is
true, and so by \textbf{UpR}, \(x\) itself can access that point. If
\(R_i\) obeys \textbf{RRef++}, then
{[}\(\Diamond_i\){]}\textsubscript{Simple} will imply
{[}\(\Diamond_i\){]}\textsubscript{Official}. If there is some \(y\)
such that \(xR_iy\) and \(A\) is true at \(y\), then by \textbf{RRef++},
there is some refinement of \(x\) such that every refinement of it can
access \(y\), and hence can access a point where \(A\) is true. So these
are equivalent.

From now on, I'll use {[}\(\Diamond_i\){]}\textsubscript{Simple} when
working out what's true at points in particular models. But when we are
proving general facts about the language, it will help to remember that
\(\Diamond_i\) is a defined connective, so we don't need an extra part
of inductive arguments to cover it.

\subsection*{Modal Constraints}\label{modal-constraints}
\addcontentsline{toc}{subsection}{Modal Constraints}

Why should we impose the three constraints Humberstone proposes? It is
not hard to show that they guarantee that persistence and refinability
hold for sentences generated using these new modal connectives. At
least, it isn't hard as long as we remember that \(\Diamond\) is being
treated as defined, so the only new step in the inductive proofs
involves \(\Box\). And \textbf{UpR} guarantees persistence for \(\Box\)
sentences, while \textbf{RRef++} guarantees refinability.

But this is overkill. As Humberstone points out, we haven't used
\textbf{RDown} in the proof, so this doesn't explain why we'd impose
\textbf{RDown}. Holliday (\citeproc{ref-Holliday2025}{2025, 62}) further
points out \textbf{UpR} is stronger than we need for persistence. We
could weaken it by making greater use of the fact that \(A\) is
persistent. All we need is that if \(x \leqslant x'\) and \(xRy\) then
there is some \(z \geqslant y\) such that \(x'Rz\). That will guarantee
the key fact if \(x'\) can access a world where \(A\), then so can
\(x\).

So we need other arguments for these constraints other than their role
in ensuring persistence and refinability. Humberstone offers two other
arguments here. One anticipates the applications of possibilities to
multi-modal logics. If we want to use possibilities for tense logic,
then we want the converse of any accessibility relation to satisfy the
constraints on an accessibility relation. So if all acceptable
accessibility relations satisfy \textbf{UpR}, they should also satisfy
\textbf{RDown}. This isn't convincing on its own though. For one thing,
as already noted, we might not need \textbf{UpR}. For another, by these
lights we should worry that the system is incomplete because we haven't
put in a converse of \textbf{RRef++}.

The argument that Humberstone spends more time on, and which I think is
more compelling, comes from rethinking the relationship between \(R_i\)
and \(\Box_i\). It's very tempting to read those truth conditions as
being explanatory from right-to-left. On this way of thinking, facts
about which \(\Box_i\) sentences are true at a point are grounded in
which non-modal sentences are true and which \(R_i\) relations obtain.
But while this is tempting, it isn't compulsory.

We could instead take the modal facts as given, and ask what
accessibility relations must obtain to be consistent with them. The
process here is going to resemble the construction of canonical models.
We take the sets of consistent sentences as given, and say \(s_1R_is_2\)
iff whenever \(\Box_i A \in s_1\), then \(A \in s_2\). Humberstone's
defence of the constraints takes a similar path. Imagine that instead of
using the recursive clauses for the definition of modal truths, we
simply have a frame \(\langle W, \leqslant \rangle\) and a stipulated
assignment of truths at each point in \(W\). These assignments will be
presumed to satisfy persistence and refinability. Now say that \(xR_iy\)
iff \(\mathcal{M} \models_y A\) whenever
\(\mathcal{M} \models_x \Box_i A\). Given those assumptions, what
conditions must \(R_i\) satisfy?

The answer is that then \(R_i\) will satisfy these three constraints:
\textbf{UpR}, \textbf{RDown} and \textbf{RRef++}. If
\(\mathcal{M} \models_y A\) whenever
\(\mathcal{M} \models_x' \Box_i A\), then by the persistence of
\(\Box_i\), we know that \(\mathcal{M} \models_y A\) whenever
\(\mathcal{M} \models_x \Box_i A\), so \textbf{UpR} holds. A similar
argument, using the persistence of \(A\), justifies \textbf{RDown}.
Finally, \textbf{RRef++} follows from the fact that \(\Box_i A\) is
refinable. If \(\Box_i A\) is not true at \(x\), that means that it is
determinately not true at some refinement. So if
\(\mathcal{M} \nmodels_x A\), there must be some refinement \(x'\) such
that for all further refinements \(x''\),
\(\mathcal{M} \nmodels_x'' A\). If \(\mathcal{M} \nmodels_x \Box_i A\),
then there must be some possibility \(y\) such that \(xR_iy\) and
\(\mathcal{M} \nmodels_y A\). So as long as \(x''R_iy\), refinability
will be satisfied. I don't see how to prove there isn't a weaker
condition that would also work, it's possible we could use the
refinability of \(A\) to find some weaker condition, but I don't quite
see how that would work. So I think \textbf{RRef++} also follows from
this way of thinking about accessibility.

In the next section I'll discuss what logics can be defined using frames
that satisfy all of these conditions.

\section{Logics Determinable on Humberstone Frames}\label{sec-proof}

Holliday (\citeproc{ref-Holliday2025}{2025, sec. 8.2}) raises an
interesting question. As well as the familiar Kripke frames most
commonly used as a semantics for modal logic, and the Humberstone frames
defined above, he introduces a class of `full possibility' frames, which
weaken some of Humberstone's constraints. It won't matter here exactly
what these weakenings are, but what does matter is that using these
weakened frames, Holliday shows how to determine logics that are not
determinable on any class of Kripke frames. To state this more
precisely, for any class of frames \(\mathsf{F}\), let
\(\mathrm{L}(\mathsf{F})\) be the set of sentences true at all points in
all models definable on some member of \(\mathsf{F}\). Then let
\(\mathrm{ML}(\mathsf{F})\) be the set
\(\{\mathrm{L}(\mathsf{X}) : \mathsf{X} \subseteq \mathsf{F}\}\). That
is, \(\mathrm{ML}(\mathsf{F})\) is the class of logics that can be
determined using just \(\mathsf{F}\).

If we let \(\mathsf{K}\) denote the class of Kripke frames, and
\(\mathsf{FP}\) denote the class of full possibility frames, Holliday
(\citeproc{ref-Holliday2025}{2025, sec. 2.5}) constructs a very clever
argument to show that
\(\mathrm{ML}(\mathsf{K}) \subsetneq \mathrm{ML}(\mathsf{FP})\). If we
let \(\mathsf{H}\) denote the class of Humberstone frames, it follows
from the fact that every Kripke frame is a Humberstone frame and every
Humberstone frame is a full possibility frame that
\(\mathrm{ML}(\mathsf{K}) \subseteq \mathrm{ML}(\mathsf{H}) \subseteq \mathrm{ML}(\mathsf{FP})\).
The fact that
\(\mathrm{ML}(\mathsf{K}) \subsetneq \mathrm{ML}(\mathsf{FP})\) implies
that at least one of those inclusions is strict, it isn't clear which
one. He leaves the question of which one it is as an open question.

I don't have an answer to that question as asked, since it is asked
about languages whose sentences have finite length. I do have a proof
that if we allow infinite disjunction, as discussed above, then
\(\mathrm{ML}(\mathsf{H}) \neq \mathrm{ML}(\mathsf{K})\). If we expand
the language by allowing infinite disjunctions, at least the first
inclusion is strict. I will show this by constructing a single
Humberstone frame that, in the infinitary language, defines a logic with
no Kripke equivalent. The construction will follow Holliday's very
closely, but differ just enough to ensure compliance with Humberstone's
conditions.

\subsection*{The Frame}\label{the-frame}
\addcontentsline{toc}{subsection}{The Frame}

The frame is built from two copies of the set of finite binary sequences
--- sequences of 0s and 1s of any finite length, including the empty
sequence. Call one copy the \textbf{left-handed} sequences and the other
the \textbf{right-handed} sequences. The refinement relation is:
\(x \leqslant y\) iff \(x\) and \(y\) have the same handedness and \(x\)
is an initial segment of \(y\). So within each copy the frame is just
the binary tree ordered by extension, and no left-handed sequence
refines a right-handed sequence or vice versa. It will help to have some
notation for referring to points in this model. When \(s\) is a finite
binary sequence, I'll write \(s^L\) for the left-handed version of
\(s\), and \(s^R\) for the right-handed version.

\subsection*{The Accessibility
Relations}\label{the-accessibility-relations}
\addcontentsline{toc}{subsection}{The Accessibility Relations}

Next I'll define an accessibility relation and a separate infinite
family of accessibility relations. The single relation, which I'll write
\(R^{\rightarrow}\), is such that \(xR^{\rightarrow}y\) iff \(x\) is
left-handed and \(y\) is right-handed. The family of relations, each
written \(R^{\leftarrow}_i\) for \(i \in \mathbb{N}\), is such that
\(xR^{\leftarrow}_iy\) iff \(x\) is right-handed, \(x\) does not have a
\(0\) in its \(i\)-th position (either because \(x\) has length less
than \(i\), or because it has a \(1\) in position \(i\)), and \(y\) is
left-handed.

That \(R^{\rightarrow}\) satisfies \textbf{UpR}, \textbf{RDown}, and
\textbf{RRef++} is obvious. It is also obvious that for each \(i\),
\(R^{\leftarrow}_i\) satisfies \textbf{UpR} and \textbf{RDown}. It's
only a little harder to show that it satisfies \textbf{RRef++}. Assume
\(xR^{\leftarrow}_iy\). So \(x\) is right-handed and \(y\) is
left-handed. If \(x\) is of length at least \(i\), then \(x\) itself can
serve as the refinement such that every further refinement can access
\(y\). If \(x\)'s length is less than \(i\), extend \(x\) with enough 1s
to create a sequence of length \(i\). The result will be a refinement
such that every further refinement can access \(y\), as required.

\subsection*{The Example}\label{the-example}
\addcontentsline{toc}{subsection}{The Example}

Now consider the proposition (\textsc{Splitting}), a minor variant on
Holliday's example (\textsc{Split}). (I'm using \(\mathsf{T}\) for an
arbitrary tautology.)

\begin{equation}
\neg \Diamond^{\rightarrow} p
  \vee
\bigvee_{i \in \mathbb{N}}(
  \Diamond^{\rightarrow}
    (
      p
        \wedge
      \Diamond_i^{\leftarrow} \mathsf{T}
    )
  \wedge
  \Diamond^{\rightarrow}
    (
      p
        \wedge
      \neg \Diamond_i^{\leftarrow} \mathsf{T}
    )
  )
\tag{\textsc{Splitting}}
\end{equation}

I'm going to make three claims about (\textsc{Splitting}). First, it is
true throughout the frame I just described. Second,
\(\neg \Diamond^{\rightarrow} p\) is not true on all models on that
frame. Third, there is no class of Kripke frames throughout which
(\textsc{Splitting}) is always true and
\(\neg \Diamond^{\rightarrow} p\) is not always true. From this it
follows that \(\mathrm{ML}(\mathsf{K}) \neq \mathrm{ML}(\mathsf{H})\).

For the first claim, I'll show something slightly stronger, namely that
at each point one or other disjunct in (\textsc{Splitting}) is true. If
the point is right-handed, then the first disjunct is true, since each
right-handed point is a dead-end with respect to \(R^{\rightarrow}\). So
we just have to look at the left-handed points. Let \(x\) be an
arbitrary left-handed point. If there is no \(y\) such that
\(xR^{\rightarrow}y\) and \(p\) is true at \(y\), then again the first
disjunct is true.

Now consider the case where \(x\) is left-handed, and there are
right-handed points such that \(p\) is true at \(y\). Here it will be
helpful to denote a right-handed point \(y\) as \(s_y^R\). Among those
\(s_y^R\) at which \(p\) is true, consider the ones where \(|s_y|\), the
length of \(s_y\), is minimal. There must be some such points, since
sequence lengths are non-negative integers and \(p\) is true at some
accessible right-handed point. Let \(i = |s_y| + 1\). Let
\(s_y^R \oplus \langle 0 \rangle^R\) and
\(s_y^R \oplus \langle 1 \rangle^R\) be the right-handed sequences
generated by adding either a 0 or a 1, respectively, to \(s_y^R\). Since
\(p\) is true at \(s_y^R\) and truth is persistent, \(p\) will be true
at both \(s_y^R \oplus \langle 0 \rangle^R\) and
\(s_y^R \oplus \langle 1 \rangle^R\). Since
\(s_y^R \oplus \langle 0 \rangle^R\) has a 0 at its \(i\)th position, it
is a dead-end with respect to \(R^{\leftarrow}_i\). So
\(\neg \Diamond_i^{\leftarrow} \mathsf{T}\) is true there. So since
\(x\) is left-handed, and \(s_y^R\oplus \langle 0 \rangle^R\) is
right-handed,
\(\Diamond^{\rightarrow} p \wedge \neg \Diamond_i^{\leftarrow} \mathsf{T}\)
is true at \(x\). A similar argument shows that
\(p \wedge \Diamond_i^{\leftarrow} \mathsf{T}\) is true at
\(s_y^R\oplus \langle 1 \rangle^R\), so
\(\Diamond^{\rightarrow}(p \wedge \Diamond_i^{\leftarrow} \mathsf{T})\)
is true at \(x\). And that implies that the \(i\)th disjunct of the
right-hand disjunction of (\textsc{Splitting}) is true at \(x\), as
required.

The second claim, that \(\neg \Diamond^{\rightarrow} p\) is not true on
all models on the frame, is trivial, since it will fail at some
left-handed points whenever \(p\) is true at some right-handed point.

For the third claim, we follow Holliday's argument particularly closely.
In particular, we'll appeal to his insight that ``Worlds cannot split,
but possibilities can'' (\citeproc{ref-Holliday2025}{Holliday 2025,
95}). Consider any class of Kripke frames such that
\(\neg \Diamond^{\rightarrow} p\) is not valid on that class. Look at
the class of models on those frames where \(p\) is true at exactly one
world. For any disjunct of the right-hand disjunction of
(\textsc{Splitting}) to be true at a point, that point must access a
world where \(p\) is true that is a dead-end with respect to
\(R^{\leftarrow}_i\), and also a world where \(p\) is true that is not a
dead-end with respect to \(R^{\leftarrow}_i\). That's impossible if
\(p\) is true at just one world. So throughout this class of models, the
right-hand disjunction of (\textsc{Splitting}) will be false. But if
\(\neg \Diamond^{\rightarrow} p\) is not valid on the frame, there will
also be points in this class of models where
\(\Diamond^{\rightarrow} p\) is true. So the whole disjunction will be
false at those points, and hence (\textsc{Splitting}) is not valid on
the frame.

Putting these together, there is no class of Kripke frames that
validates exactly the sentences valid on this particular Humberstone
frame. So \(\mathrm{ML}(\mathsf{K}) \neq \mathrm{ML}(\mathsf{H})\), and
hence \(\mathrm{ML}(\mathsf{K}) \subsetneq \mathrm{ML}(\mathsf{H})\).

\section{Quantifiers and Necessitism}\label{sec-quant}

There are two distinctive features of the way that I introduced
quantifiers in Section~\ref{sec-formal}. First, I introduced the
universal quantifier as basic, and simply defined \(\exists\) as
\(\neg \forall \neg\). Second, I introduced the universal quantifier as
\emph{possibilist}, at least in the sense that it ranges over all
objects in a possibility and all its refinements. As I noted, there is a
passing remark in ``From Worlds to Possibilities'' where Humberstone
suggests that is how he would do it. It's worth going over why this ends
up being the best way to do things.

The aim here, as it was in Section~\ref{sec-formal}, was to keep
classical logic while still using things, like incomplete possibilities,
which are usually taken to be incompatible with classical logic. But in
this section the primary contrast is not with non-classical
propositional logics, but with free logics. In classical logic, this
argument looks fairly compelling, as long as the modal logic we're using
is normal.

\begin{align*}
1. && a = a && \text{=Intro} \\
2. && \exists x(x = a) && \exists\text{-Introduction} \\
3. && \Box \exists x(x = a) && \text{Necessitation} \\
4. && \forall y \Box \exists x(x = y) && \forall-\text{Introduction} \\
5. && \Box \forall y \Box \exists x(x = y) && \text{Necessitation}
\end{align*}

That is, necessarily every object is such that necessarily, something is
identical to it. If we are working in a possible worlds framework, and
assume that the modal logic we're using is at least as strong as
\textbf{KTB}, that just about implies that all worlds have the same
domain. Strictly speaking, it's consistent with there being worlds with
distinct domains which are not connected by the ancestral of \(R\), but
any world that could be relevant to the truth of any sentence at \(w\)
must have the same domain as \(w\).

In the possibilities framework, we have a bit more flexibility while
still making claims like \(\Box \forall y \Box \exists x(x = y)\) come
out true. We could go for a constant domain semantics, as in the
possible worlds picture. The upside of the constant domain semantics is
that our quantifiers could be `actualist'. We could say that
\(\forall x: \Phi x\) is true at a point, relative to an assignment
\(g\), iff \(\Phi a\) is true at \(g[x/o]\) for any \(o\) in the domain.
That is more intuitive than the possibilist clause I've endorsed for
\(\forall\).

The reason I've endorsed this less intuitive clause is that having
constant domains does not feel like it matches the spirit of the
possibilities framework. Some stories have more characters than others.
In the story that consists of one proposition, \emph{Romeo loves
Juliet}, it feels like the domain should just consist of Romeo and
Juliet. But now we face a challenge. If the quantifiers range just over
the things in that possibility, we can't have \(\exists x(x = a)\) be a
logical truth in that to be a logical truth, we can't have the domain of
the quantifier range just over Romeo and Juliet.

That doesn't quite settle things though. In the propositional case, we
made the truth value for conjunctions depend only on what was true at
that possibility, while the truth value for disjunctions depended on
later refinements. Perhaps we try a parallel move here, and have the
truth of a universally quantified statement range over only things in
that possibility, while existentially quantified statements range over
more things.

That won't work though. If the domain of
\(\langle \textit{Romeo loves Juliet}\rangle\) is just Romeo and Juliet,
and universal quantifiers only range over the domain of that
possibility, then the sentence
\(\forall x(x = \mathit{Romeo} \vee x = \mathit{Juliet})\) would come
out true. But since \(\mathit{Mercutio} = \mathit{Mercutio}\) is a
logical truth, we would then get that Mercutio is identical to Romeo or
Mercutio is identical to Juliet. We don't want that, because there are
clearly refinements of our simple story where Mercutio is neither Romeo
nor Juliet. Shakespeare's play is one such refinement.

So it looks like we are forced to say that quantifiers range over future
refinements as well as the actual possibility. Still, we want a way to
be able to say, within a possibility, that all the \(F\)'s in that
possibility are \(G\). We can't say that with
\(\forall x(Fx \rightarrow Gx)\), since there might be a counterexample
of an \(F\) in a later refinement which is not \(G\). Is there any way
to talk about what's just true in the possibility?

Harrison-Trainor (\citeproc{ref-HarrisonTrainor2019}{2019}) suggests
that we can do this by adding a special predicate \(E\) for ``exists''
which is satisfied at a world by all and only the things in the world's
domain. Then we could say what we wanted as
\(\forall x ((Fx \wedge Ex) \rightarrow Gx)\).

That's on the right track, but it can't be right as it stands. The
problem is that we want all our predicates to be persistent and
refinable, or the logic won't work. A special predicate \(E\) is
satisfied only by Romeo and Juliet in
\(\langle \textit{Romeo loves Juliet}\rangle\) would not comply with
refinability. For any object (other than Romeo and Juliet), we want them
to not be \(E\). But there is no later world where there is some name
\(c\) for them, and \(\neg Ec\) is true. So by refinability, all objects
are \(E\), defeating the point of the proposal.

I think this is just a terminological issue though. The key thing is to
not use a predicate here, but a \emph{demonstrative}. There are two ways
we could do this.

First, we might introduce a new plural referring term \(\mathbf{U}\),
short for \emph{Us}, which picks out everything in our possibility.
Imagine introducing \(\mathbf{U}\) while waving your arms around and
saying that it refers to us. The thought is that \(\mathbf{U}x\) does
not mean that \(x\) exists, but rather that \(x\) is one of us. If Romeo
and Juliet were to introduce \(\mathbf{U}\) that way in their
possibility, then the thing they say by uttering ``Mercutio is not one
of us'' would be true. Plausibly, though this depends what the ontology
of fictional characters is, we also say something true by saying
``Mercutio is not one of us.''

There is a slightly more complicated, but I suspect ultimately more
natural, way to get the same result. Let's introduce a new name @ for
the actual possibility. As with \(\mathbf{U}\), it is important that
this is a directly referring expression. It is indexical, in the way
that `actually' is in two-dimensional semantics (Davies and Humberstone
(\citeproc{ref-Davies1980}{1980})). Then we introduce a special new
two-place predicate \(I\), meaning `in'. Using those we can say that all
actual \(F\)'s are \(G\)'s by saying
\(\forall x((Fx \wedge Ix@) \rightarrow Gx)\). The move here is parallel
to what modal realists have to do to understand ordinary, world-bound,
quantification.

There is one odd thing about either of these moves. They both involve
indexicals. So one might expect that there will be a distinction between
the proposition that these utterances express, and the `diagonal'
proposition consisting of those possibilities that make true the
proposition the utterance would express there. In the possibilities
framework, there can't be these diagonal propositions. The problem is
just the one we ran into when we tried to do actualist quantification.
We can certainly find a set of possibilities where the content the
utterance would have if uttered there is true there. But that set will
typically not be a proposition because it won't satisfy persistence or
refinability. In general, one complication of the possibilities
framework is that we cannot find a proposition for arbitrary sets of
possibilities, and that is what causes the non-existence of the diagonal
proposition here.

Once we understand world-bound quantification using one or other of
these indexicals, the possibilities framework turns out to have some
interesting interactions with recent debates about necessitism.
Following Williamson (\citeproc{ref-Williamson2013book}{2013}), there
has been a resurgence of attention in the idea that everything exists
necessarily. Here is a very quick argument for necessitism.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The right logic for quantified modal logic is a normal modal logic
  with classical first-order logic.
\item
  So it is a logical truth that
  \(\Box \forall y \Box \exists x(x = y)\).
\item
  The right modal logic is not just normal, it is at least as strong as
  \textbf{KTB}.
\item
  In the possible worlds framework, the only way to have
  \(\Box \forall y \Box \exists x(x = y)\) and for the modal logic to be
  as strong as \textbf{KTB} is for the domain to be constant across all
  worlds connected by the ancestral of \(R\).
\item
  So the domain of all these \(R\)-connected worlds is constant, i.e.,
  necessitism is true.
\end{enumerate}

Here's a tempting, but I suspect ultimately mistaken, way to respond to
this argument. The possibilities framework shows that the move from step
4 to step 5 is right. In the the possible worlds framework, it's true
that we need a constant domain to validate these logical truths. But we
don't need a constant domain in the possibilities framework to make
\(\Box \forall y \Box \exists x(x = y)\) come out true. So if that's the
master argument for necessitism, the possibilities framework provides
one with tools to resist it.

This seems too quick to me for three reasons. One is that a theory which
separates domains of possibilities from the truth conditions for the
quantifiers as dramatically as this theory does is not likely to be
particularly convincing to necessitists. That's not worrying on its own;
lots of good arguments aren't convincing to theorists committed to the
other side. The other two concerns, however, are more pressing.

So the second worry is that this is far from the only argument for
necessitism. Several of the more pressing arguments involve
\emph{second-order} modal logic. I haven't even tried to formulate
second-order logic in the possibilities framework, and until that's
done, it's impossible to respond to these arguments. And the third worry
is that plenty of necessitists do not think that that necessitism has
anything to do with constant domains. Here is how Williamson introduces
the view.

\begin{quote}
Call the proposition that it is necessary what there is necessitism, and
its negation contingentism. In slightly less compressed form,
necessitism says that necessarily everything is necessarily something;
still more long-windedly: it is necessary that everything is such that
it is necessary that something is identical with it. In a slogan:
ontology is necessary. Contingentism denies that necessarily everything
is necessarily something. In a slogan: ontology is contingent.
(\citeproc{ref-Williamson2013book}{Williamson 2013, 2})
\end{quote}

On Williamson's own account, necessitism looks like what we get to in
step 2 of the little argument. The distinction between the worlds
framework and the possibilities framework only becomes relevant after
the game is already over.

A better use of the possibilities framework might not be to reject
necessitism, but to explain away some of its counterintuitive
consequences. Surely, say the contingentists, some things might not have
been, and other things that are might not have been. In the
possibilities framework, we have a way of accommodating these
intuitions.

There is some good sense in which possible beings, like Holmes, are not
actual. They are not in the actual world. At least, necessitism does not
entail that they are in the actual world. Holmes is not one of us.
Conversely, the Holmes stories may well be possible (provided we fix
where Watson's war wound is), and I'm not in them. It's true that the
sentence \(\exists x (x = \textit{Brian})\) is true in the Holmes
stories, but surprisingly that can be true without me being in the
Holmes stories.

So once we understand quantifiers and indexicals in the possibilities
framework the right way, we can say things that are very close to
contingentism without actually giving up necessitism. I suspect the best
way to interpret that is as good news for a kind of necessitism, one
that is willing to concede that there is something to contingentist
intuitions. Whether that kind of slightly qualified necessitism is
viable will depend on further questions, in particular concerning how to
do second order quantification in the possibilities framework, but it
seems worth investigating.

\section{Conditionals}\label{sec-conditionals}

The only discussion of possibilities (as opposed to worlds) in \emph{The
Connectives} is in the chapter on disjunction. But there are several
potential connections to conditionals, and in this section I'll go over
a couple of them.

One connection concerns Conditional Excluded Middle (as discussed on
pages 1008--1013 of \emph{The Connectives}), and more generally the
relationship between \(A \boxright (B \vee C)\) and
\((A \boxright B) \vee (A \boxright C)\). On a Stalnaker--Lewis style
approach to conditionals, these are equivalent iff there is a nearest
possible world in which \(A\) is true, for any possible \(A\). It is
natural to think about whether that is true in largely metaphysical
terms, asking whether there really is guaranteed to be a single nearest
world where \(A\) is true. And as Lewis
(\citeproc{ref-Lewis1973a}{1973}) argued, it is natural to answer that
question negatively.

To take one striking example of that, consider the discussion by Jeremy
Goodman (\citeproc{ref-Goodmanms}{2018}) of the example, originally due
to Max Black (\citeproc{ref-Black1952a}{1952}), of the two spheres alone
in space. Black says that the spheres are really two, so this is a
counterexample to the Principle of Identity of Indiscernibles. Let's
assume, for now, that Black is right, and we can call one sphere \(a\)
and the other sphere \(b\). Goodman asks what we should say about the
counterfactual possibility that one of the spheres is heavier. On
Lewis's picture, rejecting Conditional Excluded Middle, both (1) and (2)
are false.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  If one of the spheres were heavier, it would be \(a\).
\item
  If one of the spheres were heavier, it would be \(b\).
\end{enumerate}

A common thought at this point is that this verdict really does follow
from Lewis's `nearest possible world' semantics for conditionals, but
that data about the inferential role of conditionals shows that
Conditional Excluded Middle must be correct.\footnote{For a recent
  statement of this last view, with many more citations to similar
  statements, see Cariani and Goldstein
  (\citeproc{ref-CarianiGoldstein2020}{2020}).} This is, many think, a
problem for the Lewisian view.

One move here, discussed by Humberstone
(\citeproc{ref-Humberstone2011}{2011, 1011}), is to use supervaluations.
Perhaps it is in some sense indeterminate whether the world where \(a\)
is heavier or the world where \(b\) is heavier is more like actuality. A
related, but I think preferable, move is to analyse conditionals not in
terms of possible worlds, but in terms of possibilities.

Here is one possible way to analyse conditionals, mixing Stalnaker's
approach with Humberstone's possibilities.\footnote{The particular
  formulation I'm going to use draws heavily on the theory presented by
  Andrew Bacon (\citeproc{ref-Bacon2023}{2023, 382}). Three of the four
  conditions are directly quoted from his paper, though I mean something
  different by them since on my version the variables pick out
  possibilities, not worlds. Bacon does not endorse \textbf{AB} in the
  form shown here; he only endorses a version of it restricted to the
  case where \(f(B, x) = \emptyset\). I'll have more to say about
  Bacon's paper presently.} Extend a possibility model
\(\langle W, \leqslant, V \rangle\) to a conditional possibility model
by adding a selection function \(f\). This is a function
\(\mathcal{P}(W) \times W \rightarrow \mathcal{P}(W)\), intuitively
picking out the `nearest' possibilities to a world where a particular
proposition is true, satisfying these constraints.\footnote{Humberstone
  uses \(R\) rather than \(f\) for the same idea; I'm going to follow
  Bacon, who in turn follows Stalnaker, to highlight the connection to
  theories that validate Conditional Excluded Middle.}

\begin{description}
\tightlist
\item[\textbf{MP}]
\(x \in f(A, x)\) whenever \(x \in A\)
\item[\textbf{ID}]
\(f(A, x) \subseteq A\)
\item[\textbf{CEM}]
\(|f(A, x)| \leq 1\)
\item[\textbf{AB}]
If \(f(A, x) \subseteq B\) and \(f(B, x) \subseteq A\), then
\(f(A, x) = f(B, x)\)
\end{description}

The cardinality constraint \textbf{CEM} guarantees that Conditional
Excluded Middle will hold. But we don't have to make invidious choices
about whether the nearest possibility where one of the spheres is
heavier makes \(a\) or \(b\) heavier. Rather, we just say that the
nearest possibility is an incompletely refined possibility that makes
the disjunctive proposition \emph{One of them is heavier} true, without
making either disjunct true. It will have refinements where each is
true, but the nearest possibility will not validate either disjunct.
This seems like an intuitive treatment of the case.

Goodman uses this example to argue that Black was incorrect, and the
spheres are in fact discernible. His argument is that one but not the
other will have the property of being the one that would be heavier if
they were different. I don't think this argument goes through on the
possibilities framework, but settling that would require saying more
about how higher-order quantification works in the possibilities
framework, as noted in Section~\ref{sec-quant}, I'm leaving questions
about higher-order logic for another day. Instead I'll turn to a puzzle
that Bacon aimed to solve in the paper I just mentioned. That puzzle
starts with an example from José Bernadete
(\citeproc{ref-Bernadete1964}{1964}), and Kit Fine
(\citeproc{ref-Fine2012b}{2012a}, \citeproc{ref-Fine2012a}{2012b})
developed into a deep challenge to several theories of counterfactuals.

There is a room that is very dangerous to cross. A man is thinking of
crossing it, but he is warned off when he learns that it contains an
infinity of gods. God\textsubscript{1} will kill him if he makes it
half-way across the room. God\textsubscript{2} will kill him if he makes
it a quarter of the way across. God\textsubscript{3} will kill him if he
makes it one-eighth of the way across. More generally,
God\textsubscript{\emph{n}} will kill him if he makes it
(1/2)\textsuperscript{\emph{n}} of the way across the room. Does he
enter? Of course not; he'd be killed! But who would kill him? Presumably
not God\textsubscript{1}; how would he make it that far? This
generalises. God\textsubscript{\emph{n}} can't kill him, because
God\textsubscript{\emph{n}+1} would already have done the job. So he
would be killed by the gods, but not by any particular god. This doesn't
sound very plausible.

The case looks like the kind that motivated Lewis to reject what he
called the \emph{Limit Assumption}. This says that if \(A\) is possible,
then relative to any world \(w\) there are some closest worlds where
\(A\) is true. Humberstone (\citeproc{ref-Humberstone2011}{2011,
1014--15}) discusses Lewis's rejection of the Limit Assumption, and
adopts the position that we shouldn't impose it in general, but can
freely talk as if it is true, because it doesn't make a difference to
the logic. This is right in the context Humberstone is writing in, but
potentially misleading. The Limit Assumption does make a big difference
to the logic if we have either quantifiers or infinitary connectives in
the language. This fact is what Fine's puzzle turns on.

Stated without the Limit Assumption, Lewis's view is that
\(A \boxright B\) is true at \(w\) if there is some world where \(A\) is
true such that there is no closer world where \(A \wedge \neg B\) is
true. If we assume that for any \emph{n}, the world where the man enters
and God\textsubscript{\emph{n}+1} kills him is closer than the world
where he enters and God\textsubscript{\emph{n}} kills him, then Lewis is
committed to both (3) and (4).

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  If the man were to enter the room, he would be killed by either
  God\textsubscript{1} or God\textsubscript{2} or \(\dots\).
\item
  For each \emph{n}, it is not the case that if the man were to enter
  the room, he would be killed by God\textsubscript{\emph{n}}.
\end{enumerate}

As Fine notes, Lewis's theory of counterfactuals is committed to denying
a principle he calls \textbf{Infinite Conjunction}.

\begin{description}
\tightlist
\item[Infinite Conjunction]
If \(A \boxright C_i\) is true for each \(i\), then
\(A \boxright (C_1 \wedge C_2 \wedge \dots)\) is true.
\end{description}

With the Limit Assumption, Lewis's semantics would endorse
\textbf{Infinite Conjunction}. But it would also have a problem. Which
of the gods would kill the man? Any choice seems not only arbitrary, but
mistaken. Let's spell this out a bit more carefully. Fine's way of
spelling out the paradox makes heavy use of a principle he calls
\textbf{Disjunction}. (This is called \textbf{Subj. Dilemma} by
Humberstone (\citeproc{ref-Humberstone2011}{2011, 1015}).)

\begin{description}
\tightlist
\item[Disjunction]
If \(A \boxright C\) and \(B \boxright C\) are true, so is
\((A \vee B) \boxright C\).
\end{description}

Then both (5) and (6) seem like they should be true.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  If the man had entered the room, and been killed by one of
  God\textsubscript{1} through God\textsubscript{\emph{k}+1}, he
  wouldn't have been killed by God\textsubscript{\emph{k}} (because
  God\textsubscript{\emph{k}+1} would have killed him first).
\item
  If the man had entered the room, and not been killed by one of
  God\textsubscript{1} through God\textsubscript{\emph{k}+1}, he
  wouldn't have been killed by God\textsubscript{\emph{k}}.
\end{enumerate}

Putting these together using \textbf{Disjunction}, we get the following
sentence. It's a mouthful, but it's important to spell it out for what
comes next.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{6}
\tightlist
\item
  If either the man had entered the room, and been killed by one of
  God\textsubscript{1} through God\textsubscript{\emph{k}+1}, or he had
  entered the room, and not been killed by one of God\textsubscript{1}
  through God\textsubscript{\emph{k}+1}, he wouldn't have been killed by
  God\textsubscript{\emph{k}}.
\end{enumerate}

To finish off the paradox, let's add a new principle, \textbf{Antecedent
Substitution}.

\begin{description}
\tightlist
\item[Antecedent Substitution]
If \(A\) and \(B\) are provably equivalent in classical logic, and
\(A \boxright C\) is true, so is \(B \boxright C\).
\end{description}

Then using \textbf{Antecedent Substitution} we can get from (7) to (8).

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  If the man had entered the room, he would not have been killed by
  God\textsubscript{\emph{k}}.
\end{enumerate}

And since \emph{k} is arbitrary in (8), we can derive (4), without any
appeal to the metaphysics of counterfactuals. It looks like our only
options, short of abandoning classical logic, are to give up one of
\textbf{Infinite Conjunction}, \textbf{Disjunction}, or
\textbf{Antecedent Substitution}. In Fine's original discussion of the
paradox he introduces several more principles that could in theory be
given up, but Brian Embry (\citeproc{ref-Embry2014}{2014}) convincingly
argues that really it has to be one of these three, and I'm following
his lead.

If these are the three options, it isn't obvious which one to take. All
three paths forward have their proponents, or at least are consequences
of otherwise plausible views. I've already noted that Lewis
(\citeproc{ref-Lewis1973a}{1973}) is committed to rejecting
\textbf{Infinite Conjunction}, because he does not endorse the Limit
Assumption. This does not look great; it's crucial to reasoning with
counterfactuals that if some things would each be true were \(A\) the
case, then were \(A\) the case they would each be true.

Fine (\citeproc{ref-Fine2012a}{2012b}) recommends giving up
\textbf{Antecedent Substitution}. He develops a theory of conditionals
that doesn't use possible worlds, but instead uses incomplete states.
These are not entirely unlike Humberstone's possibilities, but the
resulting theory is quite different. I suspect the key distinction, the
one that drives all of the rest of the results, is that Fine takes
disjunctions to be true at a state only if a disjunct is true at that
state. Anyway, Fine thinks that the misstep in the trilemma above is the
derivation of (8) from (7). That step requires substituting \(A\) for
\((A \wedge B) \vee (A \wedge \neg B)\) in an antecedent, which Fine
takes to be illegitimate.

There are a couple of reasons to be unhappy with this way of getting out
of the problem. One is that this did not feel like the most
controversial step when we were developing the problem. But a bigger one
is that Fine's resolution of the trilemma ends up endorsing not just
\textbf{Disjunction}, but also its converse. This is the principle that
Humberstone (\citeproc{ref-Humberstone2011}{2011, 1016}) calls
\emph{Conv. Subj. Dilemma}, the key being that from
\((A \vee B) \boxright C\) one can infer \(A \boxright C\). The
criticisms of Fine in Embry (\citeproc{ref-Embry2014}{2014}) largely
centre on this aspect of Fine's view, and its consequences. But the key
problems with the principle are already pretty clear in Humberstone
(\citeproc{ref-Humberstone2011}{2011, 1016--22}). So I think we
shouldn't go that way.

So that leaves \textbf{Disjunction}. This is the step that Andrew Bacon
(\citeproc{ref-Bacon2023}{2023}) rejects, and it's what I'll reject as
well. I think there are two key reasons to worry about giving up
\textbf{Disjunction}, and they are pretty hard worries to address in the
possible worlds framework. But they both seem more or less manageable in
the possibilities framework.

The first worry is that without \textbf{Disjunction}, we have to give up
the idea that the selection function \(f\) is in any sense a measure of
similarity, or really any kind of nearness. Here is how Bacon puts it:

\begin{quote}
The second consideration in favour of \textbf{Disjunction} is that its
validity is predicted by the now dominant account of counterfactuals,
prominently defended by Lewis and Stalnaker, based on similarity
semantics. For roughly, if the closest \(A\) worlds are \(C\) worlds,
and the closest \(B\) worlds are \(C\) worlds, then the closest
\(A \vee B\) worlds are \(C\) worlds. (\citeproc{ref-Bacon2023}{Bacon
2023, 374})
\end{quote}

Now for Bacon, this isn't a worry, because he thinks there are
independent reasons to reject the picture of similarity or nearness as
being foundational to counterfactuals. I don't find those reasons
convincing, and basically agree with the response to them that Fine
(\citeproc{ref-Fine2023}{2023}) gives. But it's not just critics of
\textbf{Disjunction} who connect it to the similarity picture. The same
connection is drawn by Humberstone, who does endorse
\textbf{Disjunction}. He first notes that, by analogy with other maximal
relations, we should expect that the nearest \(A \vee B\)-world will be
either the nearest \(A\)-world or the nearest \(B\)-world
(\citeproc{ref-Humberstone2011}{Humberstone 2011, 1015}). He then argues
more formally that if the set of nearest \(A\)-worlds is generated by an
underlying three-place similarity relation \(S_wxy\), meaning \(x\) is
at least as similar to \(w\) as \(y\) is, and if for any \(w\), \(S_w\)
is a total preorder on worlds, then \textbf{Disjunction} is guaranteed
to hold (\citeproc{ref-Humberstone2011}{Humberstone 2011, 1025--26}).

That argument seems irrefutable if, \emph{but only if}, we're working in
a possible worlds framework. If we're in a possibilities framework, it
doesn't look right. It could be that the nearest possibility in which
\(A \vee B\) is true is not identical to either the nearest possibility
in which \(A\) is true or the nearest possibility in which \(B\) is
true, but is instead a coarsening of one of those possibilities.

How could \textbf{Disjunction} fail on the possibilities picture? We
must fail to have the nearest \(A \vee B\)-possibility be a
\(C\)-possibility. But that's impossible if the nearest
\(A\)-possibility is a \(C\)-possibility, and the nearest
\(B\)-possibility is a \(C\)-possibility, and all
\(A \vee B\)-possibilities are \(A\)-possibilities or
\(B\)-possibilities. On the possibilities picture, that last clause
fails. It might be that the nearest possibility that makes \(A \vee B\)
true does not make either \(A\) true or \(B\) true; it just guarantees
that a sequence of refinements will eventually make one or the other
true. Also note that we don't require that the nearest \(A \vee B\)
possibility makes \(\neg C\) true; it could be that \textbf{Disjunction}
fails because \(C\) is true at some refinements of the nearest
\(A \vee B\) possibility and \(\neg C\) is true at others.

That's what happens with our man who wisely doesn't enter the room.
What's the nearest possibility in which he does enter the room? It's the
incomplete possibility where he is killed by one of the gods. For each
\emph{i}, \emph{j} with \emph{i} \textgreater{} \emph{j}, the
possibility where he is killed by God\textsubscript{\emph{i}} is closer
than the one where he is killed by God\textsubscript{\emph{j}}. But the
indeterminate possibility where he is killed, without specifying which
god kills him, is closer to actuality than any complete possibility that
specifies the homicidal divinity.

So rejecting \textbf{Disjunction} is compatible with the similarity
approach to counterfactuals, as long as we use possibilities. The other
worry about rejecting \textbf{Disjunction}, one Fine
(\citeproc{ref-Fine2023}{2023}) stresses in his response to Bacon, is
that we use \textbf{Disjunction} a lot in ordinary counterfactual
reasoning. We should be cautious about giving it up. Of course, there
are plenty of rules that we use in ordinary reasoning that work in all
but a few edge cases. If we could show that \textbf{Disjunction} was
truth-preserving in all but some rare exceptional cases, we could
justify using it as a rule of inference. After all, we don't think that
the failure of Axiom V in full generality means that it's always a
mistake to infer from the existence of some things to the existence of a
set containing all and only them.

As Fine stresses, it's hard to see how on Bacon's view
\textbf{Disjunction} would even count as typically fine. The reason
Bacon says that it fails in the paradoxical case from Bernadete
generalises to more humdrum uses.

But that's not true for the possibilities model. You need to have some
very unusual relationships between Humberstone's family of similarity
relations \(S_w\) and \(\leqslant\) in order for \textbf{Disjunction} to
fail. For one thing, you need the nearest possibility \(x\) where
\(A \vee B\) holds to be an incomplete possibility where neither \(A\)
nor \(B\) holds. Clearly \(x\) has to have refinements where \(A\) is
true, and refinements where \(B\) is true. To get a \textbf{Disjunction}
failure, you need one of the refinements of \(x\) where one of the
disjuncts is true to not be (a refinement of) the closest possibility to
actuality where that disjunct obtains. I can't construct an intuitive
case where that happens that doesn't involve infinite sequences like in
Bernadete's case, though I also don't have a proof that no such case can
be constructed. This is all far from conclusive, but it seems plausible
that on the possibilities model, failures of \textbf{Disjunction} will
be rare. And that would be enough to explain the fact Fine appeals to,
that we are usually happy using it in everyday inferences.

\section{Conclusion}\label{sec-conclusion}

I've gone over two uses of the possibilities framework, but there are
many more things we could imagine using it for. I'll end by briefly
mentioning two of them.

As I alluded to in Section~\ref{sec-conditionals}, possibilities can do
a lot of work that philosophers have tried to make supervaluations do.
As well as using possibilities instead of supervaluations in preserving
Conditional Excluded Middle, it's worth exploring whether they are
useful in thinking about vagueness, or about the open future.

Humberstone (\citeproc{ref-Humberstone1981a}{1981}) mentions that
possibilities do a better job than possible worlds at making sense of
talk about `belief worlds'. We could say the same thing about the worlds
of fiction. David Lewis (\citeproc{ref-Lewis1978b}{1978}) ends up
treating the operator \emph{In this fiction} as box-like, because he
thinks otherwise we'd have to make arbitrary choices about some details
of how the story is to be filled out. Using possibilities here seems
smoother. Any coherent fiction, I conjecture, picks out a particular
possibility. That will always be a less than fully refined possibility,
but a possibility nonetheless. On this approach we don't get left with
the unfortunate triple, to which Lewis is committed, of its being true
in the story that \(A \vee B\), but false that it's true in the story
that \(A\), and false that it's true in the story that \(B\). I also
think there might be some uses of possibilities in characterising the
distinctive relationship between a story and its sequel. That a sequel
is a refinement of the original story might do a better job of capturing
some features of this relationship than anything we can do in a worlds
framework.

But I'll leave those tasks for another day. The main point of this paper
is to remind the reader how many uses Humberstone's notion of a
possibility has, and to explore what happens to the logic of
possibilities when we add quantifiers or infinitary connectives.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Bacon2023}
Bacon, Andrew. 2023. {``Counterfactuals, Infinity and Paradox.''} In
\emph{Kit Fine on Truthmakers, Relevance, and Non-Classical Logic},
edited by Federico L. G. Faroldi and Frederik Van De Putte, 349--88.
Cham: Springer International Publishing. doi:
\href{https://doi.org/10.1007/978-3-031-29415-0_17}{10.1007/978-3-031-29415-0\_17}.

\bibitem[\citeproctext]{ref-Bernadete1964}
Bernadete, Jose. 1964. \emph{Infinity: An Essay in Metaphysics}. Oxford:
Clarendon Press.

\bibitem[\citeproctext]{ref-Black1952a}
Black, Max. 1952. {``The Identity of Indiscernibles.''} \emph{Mind} 61
(242): 153--64. doi:
\href{https://doi.org/10.1093/mind/LXI.242.153}{10.1093/mind/LXI.242.153}.

\bibitem[\citeproctext]{ref-CarianiGoldstein2020}
Cariani, Fabrizio, and Simon Goldstein. 2020. {``Conditional
Heresies.''} \emph{Philosophy and Phenomenological Research} 101 (2):
251--82. doi:
\href{https://doi.org/doi.org/10.1111/phpr.12565}{doi.org/10.1111/phpr.12565}.

\bibitem[\citeproctext]{ref-ConanDoyle1995}
Conan Doyle, Arthur. 1995. \emph{A Study in Scarlet}. Urbana, Illinois:
Project Gutenberg. Accessed February 11, 2026 from
https://www.gutenberg.org/ebooks/244.

\bibitem[\citeproctext]{ref-Davies1980}
Davies, Martin, and I. L. Humberstone. 1980. {``Two Notions of
Necessity.''} \emph{Philosophical Studies} 38 (1): 1--30. doi:
\href{https://doi.org/10.1007/bf00354523}{10.1007/bf00354523}.

\bibitem[\citeproctext]{ref-Embry2014}
Embry, Brian. 2014. {``Counterfactuals Without Possible Worlds? A
Difficulty for Fine's Exact Semantics for Counterfactuals.''}
\emph{Journal of Philosophy}, no. 5: 276--87. doi:
\href{https://doi.org/10.5840/jphil2014111522}{10.5840/jphil2014111522}.

\bibitem[\citeproctext]{ref-Fine2012b}
Fine, Kit. 2012a. {``A Difficulty for the Possible Worlds Analysis of
Counterfactuals.''} \emph{Synthese} 189 (1). doi:
\href{https://doi.org/10.1007/s11229-012-0094-y}{10.1007/s11229-012-0094-y}.

\bibitem[\citeproctext]{ref-Fine2012a}
---------. 2012b. {``Counterfactuals Without Possible Worlds.''}
\emph{Journal of Philosophy} 109 (3): 221--46. doi:
\href{https://doi.org/10.5840/jphil201210938}{10.5840/jphil201210938}.

\bibitem[\citeproctext]{ref-Fine2023}
---------. 2023. {``{`Defense of a Truthmaker Approach to
Counterfactuals'}: Response to Andrew Bacon's {`Counterfactuals,
Infinity and Paradox'}.''} In \emph{Kit Fine on Truthmakers, Relevance,
and Non-Classical Logic}, edited by Federico L. G. Faroldi and Frederik
Van De Putte, 389--406. Cham: Springer International Publishing. doi:
\href{https://doi.org/10.1007/978-3-031-29415-0_18}{10.1007/978-3-031-29415-0\_18}.

\bibitem[\citeproctext]{ref-Goodmanms}
Goodman, Jeremy. 2018. {``Consequences of Conditional Excluded
Middle.''} Available at https://philarchive.org/rec/GOOCOC-6. Last
checked February 17, 2026.

\bibitem[\citeproctext]{ref-HarrisonTrainor2019}
Harrison-Trainor, Matthew. 2019. {``First-Order Possibility Models and
Finitary Completeness Proofs.''} \emph{Review of Symbolic Logic} 12 (4):
637--62. doi:
\href{https://doi.org/10.1017/S1755020319000418}{10.1017/S1755020319000418}.

\bibitem[\citeproctext]{ref-Holliday2025}
Holliday, Wesley H. 2025. {``Possibility Frames and Forcing for Modal
Logic.''} \emph{Australasian Journal of Logic} 22 (2): 44--288. doi:
\href{https://doi.org/10.26686/ajl.v22i2.5680}{10.26686/ajl.v22i2.5680}.

\bibitem[\citeproctext]{ref-Humberstone1981a}
Humberstone, Lloyd. 1981. {``From Worlds to Possibilities.''}
\emph{Journal of Philosophical Logic} 10 (3): 313--39. doi:
\href{https://doi.org/10.1007/BF00293423}{10.1007/BF00293423}.

\bibitem[\citeproctext]{ref-Humberstone2011}
---------. 2011. \emph{The Connectives}. Cambridge, MA: MIT Press.

\bibitem[\citeproctext]{ref-Lewis1973a}
Lewis, David. 1973. \emph{Counterfactuals}. Oxford: Blackwell
Publishers.

\bibitem[\citeproctext]{ref-Lewis1978b}
---------. 1978. {``Truth in Fiction.''} \emph{American Philosophical
Quarterly} 15 (1): 37--46. Reprinted in his \emph{Philosophical Papers},
Volume 1, Oxford: Oxford University Press, 1983, 261-275. References to
reprint.

\bibitem[\citeproctext]{ref-Williamson2013book}
Williamson, Timothy. 2013. \emph{Modal Logic as Metaphysics}. Oxford
University Press. doi:
\href{https://doi.org/10.1093/acprof:oso/9780199552078.001.0001}{10.1093/acprof:oso/9780199552078.001.0001}.

\end{CSLReferences}



Draft of February 28, 2026


\end{document}
