---
title: "Trends in *Philosophical Studies*"
abstract: |
  *Philosophical Studies* has become one of the most important journals for work in several large topics in philosophy. This paper uses data from the word distributions in those papers, and the citations of the papers, to look at how it has changed over time, and how it became so central.
date: today
draft: false
execute:
  echo: false
  warning: false
author:
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
categories:
  - history of analytic
  - unpublished
  - in progress
format:
    html:
       css: ../trad_defn.css
    pdf:
      fig-format: pdf
      output-file: "Trends in Philosophical Studies"
      include-in-header:
        - file: ../quarto2024.tex
        - text: |
            \setkomafont{descriptionlabel}{\normalfont\scshape\bfseries}
      include-after-body: 
        text: |
          \noindent Published online in October 2024.
format-links: [html]
bibliography: 
  - /Users/weath/Documents/citations-2025/autobib.bib
  - /Users/weath/Documents/quarto-articles/brian-quarto.bib
---

```{r}
#| label: loader
#| cache: false

for (ipkg in c("tidyverse", 
               "tidytext", 
               "tm", 
               "topicmodels", 
               "lsa",
               "slider",
               "knitr")) {
  if (!require(ipkg, character.only = TRUE)) {
    install.packages(ipkg)
    library(ipkg, character.only = TRUE)
  }
}

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = 'cairo_pdf')
}

options(knitr.kable.NA = '')

# Graph Themes
old <- theme_set(theme_minimal())
theme_set(old)
theme_update(plot.title = element_text(family = "Scala Pro", size = 24, face = "bold"),
             plot.subtitle = element_text(family = "Scala Sans Pro", size = 20),
             axis.text = element_text(family = "Scala Sans Pro", size = 18),
             axis.title = element_text(family = "Scala Sans Pro", size = 18),
             plot.background = element_rect(fill = "#F9FFFF"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "#F9FFFF"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "Scala Sans Pro", size = 20),
             strip.text = element_text(family = "Scala Sans Pro", size = 20),
             legend.key.spacing.y = unit(1, 'lines'),
             legend.key.spacing.x = unit(1, 'cm')
  )

if (knitr::is_latex_output()) {
theme_update(plot.title = element_text(family = "Europa-Bold", size = 14),
             plot.subtitle = element_text(family = "EB Garamond", size = 11),
             axis.text = element_text(family = "EB Garamond", size = 10),
             axis.title = element_text(family = "EB Garamond", size = 10),
             plot.background = element_rect(fill = "white"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "white"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "EB Garamond", size = 11),
             strip.text = element_text(family = "EB Garamond", size = 12),
             legend.key.spacing.y = unit(-0.3, 'lines'),
             legend.key.spacing.x = unit(0, 'cm')
  )

}

load("~/Documents/lda-cites-unigrams-only/ps_cites.RData")
load("~/Documents/lda-cites-unigrams-only/ps_meta.RData")
load("~/Documents/lda-cites-unigrams-only/ps_join.RData")
load("~/Documents/lda-cites-unigrams-only/common_ps_words.RData")
load("~/Documents/lda-cites-unigrams-only/ps_lda_s155376_c5_r1000.RData")
load("~/Documents/citations-2025/philo_cite.RData")
load("~/Documents/citations-2025/philo_bib.RData")
```

```{r}
#| label: commontibs
#| cache: true

philo_bib <- philo_bib |>
  mutate(year = as.numeric(year))

id_year_journal <- philo_bib |>
  select(wos_id = id, year, journal)

all_cites <- philo_cite |>
  rename(old = refs, new = id) |>
  left_join(id_year_journal, by = c("old" = "wos_id")) |>
  rename(old_year = year, old_journal = journal) |>
  left_join(id_year_journal, by = c("new" = "wos_id")) |>
  rename(new_year = year, new_journal = journal) |>
#  filter(old_year >= 1980, old_year <= 2019) |>
  mutate(decade = paste0(floor(new_year/10),"0s")) |>
  mutate(citing_journal = case_when(
    new_journal == "Philosophical Studies" ~ "PS",
    TRUE ~ "NPS")) |>
  mutate(cited_journal = case_when(
    old_journal == "Philosophical Studies" ~ "PS",
    TRUE ~ "NPS"))
  
active_cites <- all_cites |>
  filter(old_year >= 1980, old_year <= 2019)

article_count <- philo_bib |>
  ungroup() |>
  filter(year >= 1980, year <= 2019) |>
  group_by(journal, year) |>
  tally(name = "articles")

journal_citation_count <-  active_cites |>
    ungroup() |>
    group_by(old_journal) |>
    tally(name = "Citations") |>
    rename(Journal = old_journal) |>
    arrange(-Citations)

journal_article_count <-   article_count |>
    ungroup() |>
    group_by(journal) |>
    summarise(Articles = sum(articles)) |>
    rename(Journal = journal) |>
    arrange(-Articles)

journal_citation_rate <- left_join(
  journal_article_count,
  journal_citation_count,
  by = "Journal") |>
  mutate(`Citation Rate` = round(Citations/Articles, 2)) |>
  arrange(desc(`Citation Rate`))
```

```{r}
#| label: moresetup
#| cache: true

ranked_journal_citation_rate <- journal_citation_rate |>
  rowid_to_column(var = "Rank")

comp_journal_count <- 20
comp_tag <- paste0(
  "Other top ",
  comp_journal_count,
  " journals"
)

first_year <- philo_bib |>
  group_by(journal) |>
  summarise(first_year = min(year)) |>
  left_join(journal_citation_rate, by = c("journal" = "Journal")) |>
  filter(first_year <= 1980) |>
  arrange(-`Citation Rate`)

comparison_journals <- first_year$journal[1:comp_journal_count]

ps_comp_rate <- active_cites |>
  ungroup() |>
  group_by(old_year, cited_journal) |>
  filter(old_journal %in% comparison_journals) |>
  tally(name = "citations") |>
  ungroup() |>
  rename(year = old_year) |>
  left_join(
    philo_bib |>
      filter(year >= 1980, year <= 2019,
             journal %in% comparison_journals) |>
      mutate(cited_journal = case_when(
        journal == "Philosophical Studies" ~ "PS",
        TRUE ~ "NPS")) |>
      group_by(year, cited_journal) |>
      tally(name = "articles"),
    by = c("cited_journal", "year")) |>
  mutate(rate = citations/articles) |>
  ungroup() |>
  group_by(cited_journal) |>
  arrange(year) |>
  mutate(slide_arts = slide_dbl(articles, sum, .before = 4),
         slide_cites = slide_dbl(citations, sum, .before = 4),
         slide_rate = slide_cites/slide_arts) 
    

ps_comp_rate_wide <- ps_comp_rate |>
  pivot_wider(
    id_cols = year,
    names_from = cited_journal,
    values_from = slide_rate) |>
  mutate(comp = round(PS/NPS, 3))

citation_count <- active_cites |>
  group_by(old) |>
  tally(name = "cites")

short_bib <- philo_bib |>
  select(id, year, displayauth, title, journal) |>
  left_join(citation_count, by = c("id" = "old")) |>
  replace_na(list(cites = 0))

ps_top_cites <- short_bib |>
  filter(journal == "Philosophical Studies") |>
  slice_max(order_by = cites, n = 30) |>
  arrange(-cites) |>
  rowid_to_column(var = "Rank") |>
  filter(year >= 2003, year <= 2007) |>
  mutate(id = sub(":", "", id)) |>
  mutate(Article = paste0(
    "@",
    sub(":", "", id)
  )) |>
  select(Rank, Article)

ps_meta <- read_csv("~/Documents/quarto-articles/posts/phil-studies/PS-metadata.csv",
                    show_col_types = FALSE) |>
  filter(docSubType == "research-article" | docSubType == "book-review") |>
  mutate(id = paste0("PS-", str_sub(id, start = 29))) |>
  mutate(journal = "Philosophical Studies") |>
  select(id, 
         title, 
         journal, 
         year = publicationYear, 
         num = issueNumber, 
         volume = volumeNumber, 
         author = creator, 
         fpage = pageStart,
         lpage = pageEnd,
         words = wordCount) 

ps_meta_binder <- ps_meta |>
  select(id, volume, fpage) |>
  select(jstor_id = id, volume, fpage)

ps_papers <- philo_bib |>
  filter(journal == "Philosophical Studies") |>
  filter(year >= 1980) |>
  filter(year <= 2019)

ps_papers_binder <- ps_papers |>
  select(wos_id = id, volume, fpage) |>
  mutate(volume = as.numeric(volume)) |>
  mutate(fpage = as.character(fpage))

ps_join <- inner_join(
  ps_meta_binder,
  ps_papers_binder,
  by = c("volume", "fpage")
) |>
  select(wos_id, jstor_id)

ps_meta_filter <- ps_meta |>
  filter(id %in% ps_join$jstor_id)

article_count_by_year <- ps_meta_filter |>
  group_by(year) |>
  tally(name = "Articles")

word_count_by_year <- ps_meta_filter |>
  group_by(year) |>
  summarise(wordcount = sum(words))

word_max_by_year <- ps_meta_filter |>
  group_by(year) |>
  summarise(wordmax = max(words))

word_quartile_by_year <- ps_meta_filter |>
  group_by(year) |>
  summarise(Q1 = round(quantile(words, 0.25),1),
            Q2 = round(quantile(words, 0.5),1),
            Q3 = round(quantile(words, 0.75),1),
            .groups = "drop") |>
  pivot_longer(cols = starts_with("Q"),
               names_to = "statistic",
               values_to = "value") |>
  ungroup() |>
  group_by(statistic) |>
  mutate(rolling = slide_dbl(value, mean, .before = 4)) |>
  ungroup()

issue_list <- read_csv("~/Documents/quarto-articles/posts/phil-studies/PS_Special.csv",
                       show_col_types = FALSE)

issue_count_by_year_type <- ps_papers |>
  mutate(issue = case_when(
    is.na(issue) ~ "S",
    TRUE ~ issue
  )) |>
  group_by(volume, issue) |>
  slice(1) |>
  left_join(issue_list |> 
              rename(volume = Volume, issue = Issue) |>
              mutate(volume = as.character(volume)), by = c("volume", "issue")) |>
  replace_na(list(Type = "Normal", Count = 1)) |>
  ungroup() |>
  arrange(year, volume, issue) |>
  group_by(year, Type) |>
  summarise(count = sum(Count), .groups = "drop")

issue_count_by_year <- issue_count_by_year_type |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_year_normal  <- issue_count_by_year_type |>
  filter(Type == "Normal") |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_year_abnormal  <- issue_count_by_year_type |>
  filter(Type != "Normal") |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_type <- issue_count_by_year_type |>
  group_by(Type) |>
  summarise(count = sum(count), .groups = "drop")

issue_type_by_decade <- issue_count_by_year_type |>
  mutate(Type = case_when(
    Type == "Normal" ~ "Normal",
    TRUE ~ "Special"),
         Decade = paste0(floor(year/10),"0s")) |>
  group_by(Decade, Type) |>
  summarise(count = sum(count), .groups = "drop") |>
  pivot_wider(id_cols = Decade,
              names_from = Type,
              values_from = count)

issue_type_by_decade_expanded <- issue_count_by_year_type |>
  mutate(Type = case_when(
    Type == "Conference" ~ "Topic",
    TRUE ~ Type),
    Decade = paste0(floor(year/10),"0s")) |>
  group_by(Decade, Type) |>
  summarise(count = sum(count), .groups = "drop") |>
  pivot_wider(id_cols = Decade,
              names_from = Type,
              values_from = count) %>%
  replace(is.na(.), 0)
```

# Introduction {#sec-introduction}

_Philosophical Studies_ is the most cited journal in other philosophy journals in recent times, so it is worthy of study both in its own right, and as a mirror of broader trends in philosophy. This paper mixes two techniques, topic modeling and citation analysis, to look at the nature of _Philosophical Studies_, and how it has changed over time, from 1980 to 2019.

In the first half of the paper, I look at the growth the citation rate (i.e., number of citations per article) in _Philosophical Studies_. If we take its peers to be the twenty philosophy journals with the highest citation rates over the last forty years, it has gone from having a citation rate 10-20 percent below the average, to a rate 10-20 percent above the average. And it's done this despite increasing its publication volume, which one would normally expect to decrease citation rate. This is explained in part by the move to publishing more special issues, with the special issues from the Bellingham Summer Philosophy Conference being particularly important, and in part by the topic mix in _Philosophical Studies_ changing in ways that prefigured changes in the broader philosophical community.

This leads to the second half of the paper, on just how the topic mix of the journal changed over the years. The short version of those changes is shown in @fig-five-topics.

In the late twentieth century, _Philosophical Studies_ was focussed on philosophy of language, and in particular on core analytic questions about reference and description. These were central to philosophy in the 1970s after _Naming and Necessity_, and stayed central to graduate education at top schools well into the twenty-first century. But the focus of other journals moved away from these questions possibly a bit earlier than _Philosophical Studies_ did.

After the turn of the century, the journal moved into two topics that did not hurt its citation rates. First, it was part of the enormous discussion on epistemology, and in particular on contextualism in epistemology, in the 2000s. Second, in the 2010s, it, along with much of the rest of the discipline, moved more strongly into social philosophy.

One notable way in which _Philosophical Studies_ bucked a trend in philosophy is that it did not move heavily into work on grounding. As you can see in @fig-five-topics, this wasn't because it moved away from metaphysics more broadly. But is has, more than most journals, resisted the turn to what Ted @Sider2021 calls 'postmodal metaphysics'.

# Overview {#sec-overview}

## Editorial History

_Philosophical Studies_ was founded by Herbert Feigl and Wilfrid Sellars, both then at the University of Minnesota, in 1950, as the "first American journal expressly devoted to analytic philosophy" [@DeVries2005 1-2]. They stayed as editors until Feigl's retirement in 1971, though after 1954 Sellars was listed as the first editor. At Feigl's retirement the journal moved from the University of Minnesota Press to Reidel, where it has stayed ever since.^[Springer is the current continuant of Reidel after several mergers and takeovers.] Sellars edited the journal alone until Keith Lehrer was brought on as associate editor in 1974, starting an association with the journal that would last nearly half a century. 

In 1975 Lehrer, who had just moved from Rochester to Arizona, became editor. He stayed in that role until 1982, having been joined by John Pollock (also at Arizona) in 1979. From 1982, Pollock was Editor-in-Chief, and Lehrer went back to being Associate Editor. 

In 1992 the journal moved 100 miles up I-10, as Stewart Cohen, then at Arizona State, took over as Editor.^[While the journal was at Arizona, at grad student assistant was recognised on the title page as an editorial assistant. Many prominent philosophers had this role over the years, including, in 1983, Stewart Cohen.] Cohen stayed as editor through the rest of the time covered in this study, eventually being an editor of the journal for longer than even Wilfrid Sellars.

Thomas Blackson joined as book symposium editor in 2003. In 2010, Cohen moved to the University of Arizona, and so the journal was edited out of Tuscon for a second time. Jennifer Lackey and Wayne Davis, who would eventually take over from Cohen, joined as Associate Editors in 2014. In 2016 Cohen was made Editor-in-Chief, while Davis and Lackey became Editors, and that was the arrangement that persisted through 2019, the end of the focus of this paper.

There are three things about this editorial history that will become important in what follows. One is that the names here include several of the most important epistemologists of the last half century. A second is that the journal has had a very stable editorial history; a summary like this for most other peer journals would take twice as long to write. And the third is that the biggest single change, the transition from John Pollock to Stewart Cohen as Editor in 1992, does not seem to have had an immediate impact on the journal. You see dramatic changes straight away at _Mind_ when G. E. Moore takes over in 1921, and again when Gilbert Ryle takes over in 1947.^[See @Lewy1976 on Moore, and *include citation from LDA* on Ryle.] The effects of the switch from Pollock to Cohen are much more delayed.

## Articles

_Philosophical Studies_ increased its output considerably when it moved to Reidel, and then increased it again between 1980 and 2019. @fig-article-count-by-year shows how many articles _Philosophical Studies_ has published each year; @fig-word-count-by-year shows the total word count for the journal each year; @fig-word-max-by-year shows the count of the longest article each year; and @fig-word-quartiles shows the 25th, 50th, and 75th percentile article by word count for each year.

```{r}
#| label: fig-article-count-by-year
#| fig-cap: "Number of articles published each year"

ggplot(article_count_by_year,
       aes(x = year, y = Articles)) +
  geom_point() +
  labs(x = element_blank(),
       y = "Number of Articles") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, 275))

```

```{r}
#| label: fig-word-count-by-year
#| fig-cap: "Number of words published each year"

ggplot(word_count_by_year,
       aes(x = year, y = wordcount)) +
  geom_point() +
  labs(x = element_blank(),
       y = "Number of Words") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(labels = scales::scientific,
                     limits = c(0, 2500000))

```

```{r}
#| label: fig-word-max-by-year
#| fig-cap: "Longest article published each year"

ggplot(word_max_by_year,
       aes(x = year, y = wordmax)) +
  geom_point() +
  labs(x = element_blank(),
       y = "Number of Words") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, 30000))

```

```{r}
#| label: fig-word-quartiles
#| fig-cap: "25th, 50th, and 75th percentile word lengths each year."

ggplot(word_quartile_by_year,
       aes(x = year, y = value, color = statistic)) +
  geom_point() +
  theme(legend.position = "none") +
  labs(x = element_blank(),
       y = "Word Count") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, 12500)) +
  geom_line(aes(x = year, y = rolling, color = statistic))
```

Some of these changes reflect wider disciplinary changes, but others do not. Most journals have a much more stable publication rate, though there is more variation in commercially published journals. Articles have been getting longer all across philosophy. What's striking here is the 25th percentile rising to over 8000 words by the end of the 2010s.

It used to be common for philosophy colloquia to include papers that were read out by the author. This was a bad practice, and it's been mostly gone for several years. But starting in the mid-2010s it became an impractical practice. No one was writing papers that even could be read out in the length of a typical colloquium slot.

Everything I've said so far is about _articles_ in _Philosophical Studies_. As I'll go over in @sec-what-is-an-article, this is a less clear category than we might like. To get to why that's so, I'll first go over the sources I'm using.

## Special Issues

_Philosophical Studies_ has had many special issues, especially since the mid-1990s. These fall into four main categories. The first three are papers from three long-running conferences that _Philosophical Studies_ published selected papers from:

1. The APA Pacific Divsion
2. The Oberlin Colloquium
3. The Bellingham Summer Philosophy Conference (BSPC)

The fourth is a less unified set of one-off issues, either on a special topic, or, in two cases, conferences that _Philosophical Studies_ published once but did not continue with. I'll call all of these **One-off** issues.

Often these were double, or occasionally triple, issues. I'm counting these as 2, or 3, issues, because provides a better sense of what proportion of the papers in a year are from special issues. As @tbl-issues-by-decade shows, the special issues become a big part of what _Philosophical Studies_ does in the 1990s.

```{r}
#| label: issues-import
#| cache: true

issue_list <- read_csv("~/Documents/quarto-articles/posts/phil-studies/PS_Special.csv",
                       show_col_types = FALSE)

issue_count_by_year_type <- ps_papers |>
  mutate(issue = case_when(
    is.na(issue) ~ "S",
    TRUE ~ issue
  )) |>
  group_by(volume, issue) |>
  slice(1) |>
  left_join(issue_list |> 
              rename(volume = Volume, issue = Issue) |>
              mutate(volume = as.character(volume)), by = c("volume", "issue")) |>
  replace_na(list(Type = "Normal", Count = 1)) |>
  ungroup() |>
  arrange(year, volume, issue) |>
  group_by(year, Type) |>
  summarise(count = sum(Count), .groups = "drop")

issue_count_by_year <- issue_count_by_year_type |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_year_normal  <- issue_count_by_year_type |>
  filter(Type == "Normal") |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_year_abnormal  <- issue_count_by_year_type |>
  filter(Type != "Normal") |>
  group_by(year) |>
  summarise(count = sum(count), .groups = "drop")

issue_count_by_type <- issue_count_by_year_type |>
  group_by(Type) |>
  summarise(count = sum(count), .groups = "drop")

issue_type_by_decade <- issue_count_by_year_type |>
  mutate(Type = case_when(
    Type == "Normal" ~ "Normal",
    TRUE ~ "Special"),
         Decade = paste0(floor(year/10),"0s")) |>
  group_by(Decade, Type) |>
  summarise(count = sum(count), .groups = "drop") |>
  pivot_wider(id_cols = Decade,
              names_from = Type,
              values_from = count)

issue_type_by_decade_expanded <- issue_count_by_year_type |>
  mutate(Type = case_when(
    Type == "Conference" ~ "Topic",
    TRUE ~ Type),
    Decade = paste0(floor(year/10),"0s")) |>
  group_by(Decade, Type) |>
  summarise(count = sum(count), .groups = "drop") |>
  pivot_wider(id_cols = Decade,
              names_from = Type,
              values_from = count) %>%
  replace(is.na(.), 0)

citation_with_type <- ps_papers |>
  select(id, year, displayauth, title, volume, issue) |>
  left_join(issue_list |> 
              rename(volume = Volume, issue = Issue) |>
              mutate(volume = as.character(volume)) |>
              mutate(Type = case_when(
                Type == "Conference" ~ "Topic",
                TRUE ~ Type)
                     ), 
            by = c("volume", "issue")) |>
  select(-Count) |>
  left_join(citation_count, by = c("id" = "old")) |>
  replace_na(list(
    Type = "Normal",
    cites = 0))

citation_by_type <- citation_with_type |>
  ungroup() |>
  group_by(Type) |>
  summarise(cites = round(mean(cites),1))

citation_by_type_decade <- citation_with_type |>
  mutate(Decade = paste0(floor(year/10),"0s")) |>
  group_by(Type, Decade) |>
  summarise(cites = round(mean(cites),1), .groups = "drop")
```

```{r}
#| label: tbl-issues-by-decade
#| tbl-cap: "How many of each type of special issue were published each decade."

kable(issue_type_by_decade_expanded |>
  rename(
    `One-off` = Topic,
    `APA` = `APA Pacific`,
    `BSPC` = Bellingham
  ))
```

The special issues differ from the normal issues in some striking ways, so it will be helpful to keep their presence in mind.

# Methods {#sec-methods}

## Sources {#sec-sources}

The studies here are primarily based on two sources: citation data from Web of Science, and word lists from JSTOR.

Through [University X] I downloaded the Web of Science (hereafter, WoS) Core Collection in XML format. Within it, I selected 100 prominent philosophy journals that WoS indexes. The journals I selected are, like _Philosophical Studies_ primarily English-language, analytic philosophy journals. I filtered the citations for just citations from and to those 100 journals. WoS has a special way of recording citations in indexed articles to other articles that it has indexed. These records are easy to extract, and are considerably more reliable than citation records in general.^[That's not to say they are perfect. They certainly have false negatives, especially when there are any errors in the original citation. As @Petrovich2023 [77n10] notes, they are more reliable when the citations are in a bibliography than when they are in footnotes. They also do badly with supplements. So for this study I've excluded all the supplemenmts to _Noûs_, i.e., those issues of _Philosophical Perspectives_ and _Philosophical Issues_ which were listed as supplements to _Noûs_. I did include the supplemental issue _Philosophical Studies_ issued in 2013, because the data there looked reliable enough.] What follows uses just those citations. So it is citations from indexed journals to indexed journals, where WoS recognised that both the cited and citing journal were in its database.

This is obviously a small subset of all citations. It excludes citations in academic journals in other fields, in books and edited volumes, and in many other places that Google Scholar indexes, such as dissertations, lecture notes, slides, and draft manuscripts. Losing that information is a cost, but there are three large upsides. First, these citations are much more accurate. Second, we can be more confident that our data set is relatively complete; finding a full list of philosophy journals is easier than finding a full list of edited volumes in philosophy. Third, by looking at citations internal to philosophy, we can get a sense of philosophy's self-image, and how it changes over time.

The downloadable citation data is not particularly up to date. I am including citations beyond 2019, because it's helpful to get a sense of how some of these articles have been received in more recent years. But the data I have only goes through mid-2022. I'll often simply say 2022; but note that even that year is incomplete.

The other source I used is JSTOR, and in particular the Data for Research (DfR) program that they provide through their Constellate project. This lets you download lists of the words used in various journal articles, along with a count of how often each word is used.^[It also provides bigrams and trigrams, which I've occasionally used.] It also provides word counts for the articles, which I have used in @sec-overview. The words an author uses are a pretty good guide to what they are talking about; if the word 'denotation' is used frequently, it's probably a philosophy of language article.

## Articles? {#sec-what-is-an-article}

I said I'm talking about articles here, but what exactly is an _article_? A more helpful question is, which things that philosophy journals publish are not articles?

Some things are easy. The table of contents is not an article. Nor is a correction, or a report on editorial change. Book reviews are not articles. If they were, _Philosophical Review_ would have the lowest rate of citations per article, not the highest. Both WoS and JSTOR also distinguish articles from discussion notes, especially if the journal has a designated discussions section. Without this distinction, _Mind_ would have a much lower rate of citations per article.

Both of these last two categories are relevant to _Philosophical Studies_, even though it does not run book reviews or have designated discussion sections. They are relevant because it has many book symposia. The classifiers, WoS and JSTOR, struggle with how to classify articles in these symposia. They disagree with each other, and with their own past practice.

I have some sympathy for the classifiers; these are really borderline cases. Mostly what they settled on was that the précis and replies by the book author are not articles, and that the contributions by commentators are. But they did not stick precisely to this.

For the most part, I've gone with WoS's classifications. It would be practical, just barely, to go through _Philosophical Studies_ issue by issue and reclassify the book symposium entries so all and only the commentaries are articles. But it would not be practical to do this for all one hundred journals. And for this paper, we're mostly interested in comparing articles in _Philosophical Studies_ with articles in other journals, so it's best to not modify only one journal.

There is one place we're I've overridden WoS's classifications. It has categories of Discussion, Note, and Review, each of which is about 0.75% of the articles across the 100 journals. The three categories include similar enough articles that I'll treat them as a unified category. Mostly these are discussion notes, or longer book reviews, that we want to exclude. But, especially in _Philosophical Review_, they occasionally put ordinary articles here. So important articles by Stanley @WOSA1962CGX0500005, Jonathan @WOS000272855000002, and Harvey @WOS000810220800002 all got listed as not being articles.^[The Cavell article was in the discussion section of the January 1962 issue of the Review, so this classification is understandable. The other two are not.] I've counted any piece in these three categories 20 pages or longer as an article.

There is one last tricky category to flag. The special issues on the Oberlin Colloquium sometimes include commentaries on the main articles. These are mostly not counted as articles, and I think rightly so. Occasionally, as when Andy @Egan2011 was the commentator on an important paper by Tamar Szabò @WOS000295087100003, the commentary gets a reasonable number of citations. But mostly these commentaries are rarely if ever cited, and I think they aren't really what most people think of as journal articles. So I've been happy to exclude them.^[If these aren't articles, what are they? WoS calls Egan's paper 'Editorial-Matter'. That's wrong, but I'm not sure what I would say in their position.]

# Inbound Citations {#sec-overview}

## Overview of Citations {#sec-citations-overview}

Articles in _Philosophical Studies_ get cited a lot. Our first study is simply a count of citations in the 100 journals to articles published in the 100 journals between 1980 and 2019. @tbl-all-cites shows the five journals with the largest number of citations.

```{r}
#| label: tbl-all-cites
#| tbl-cap: "Leading journals by total number of citations (Articles published 1980-2019)."

kable(
  journal_citation_count |>
    slice(1:5)
)
```

_Philosophical Studies_ is in first place on that list in part, but only in part, because it publishes so much. @tbl-all-articles lists the top five journals by the number of articles they have published.

```{r}
#| label: tbl-all-articles
#| tbl-cap: "Leading journals by total number of articles (Articles published 1980-2019)."

kable(
  journal_article_count |>
    slice(1:5)
)
```

_Synthese_ has 20% more articles, but 25% fewer citations. The other three journals on that list are somewhat special cases. Two of them get a lot of citations outside of philosophy, and this is only a study of citations in philosophy journals, and _Analysis_ only publishes short papers, and so while they get a lot of citations per page, they don't get as many citations per article as other journals.

Still, we'd expect on general principles that raw volume of publication wouldn't make a big difference. Citations tend to follow something like a log-normal distribution [@Brzezinski2015]. The bulk of the citations come from a handful of highly cited articles. Publishing more articles helps, but is no guarantee. 

If we look not at total citations, but at citations per article as in @tbl-citation-rate, we get a list that looks a bit more like a familiar ranking of philosophy journals by prestige.

```{r}
#| label: tbl-citation-rate
#| tbl-cap: "Leading journals by citation rate (Articles published 1980-2019)."

this_table <- bind_rows(
  ranked_journal_citation_rate |> slice(1:5),
  tibble(
    Journal = "...",
  ),
  ranked_journal_citation_rate |> slice(13:14)
)

kable(
  this_table
)
```

I've included _Philosophy and Phenomenological Research_ there because, like _Philosophical Studies_, it publishes many book symposia. And, like _Philosophical Studies_, the articles in these symposia are typically not cited very much.

## Large Trend

Even with those possible errors in mind, it is striking to look at the step-change in citations to _Philosophical Studies_ that occurred in the mid-2000s. Cross-temporal comparisons of citations are hard because changes in the number of journals, the number of articles in those journals, and citation norms, make most comparisons tricky. To try to screen off some of that noise, I'll mostly compare citations to articles published in _Philosophical Studies_ to citations to other articles published at the same time.

In particular, in this section I'll compare _Philosophical Studies_ to a list of nineteen other prominent philosophy journals. From the one hundred journals that I'm primarily looking at, I selected the twenty that have the highest rate of citations per published article, and which Web of Science has indexed every year since 1980.^[The last constraint notably rules out _Philosophers' Imprint_ and _Mind and Language_.] That list includes _Philosophical Studies_, and the other nineteen journals are the comparison class.

@fig-compare-cites-dots shows, for each year from 1980 to 2019, the average number of citations for articles published in _Philosophical Studies_ (in blue), and in the other nineteen (in red). The figure is fairly noisy, but some trends are clear. Before 2000, the red dots, for the other journals, are mostly above the blue dots, for _Philosophical Studies_. After 2000, and especially from 2003 onwards, that is mostly reversed. Despite having less time to accrue citations, articles from the 2000s are cited more, on average, than articles published earlier. But articles published in the 2010s, especially the late 2010s, have many fewer cites largely because they haven't been around as long.

```{r}
#| label: fig-compare-cites-dots
#| fig-cap: "Average citation rates for _Philosophical Studies_ and peer journals."

ggplot(ps_comp_rate |>
         left_join(
           tribble(
             ~cited_journal, ~Journal,
             "PS", "Philosophical Studies",
             "NPS", comp_tag,
           ),
           by = "cited_journal"), 
       aes(x = year, y = rate, color = Journal)) +
       geom_point() +
       labs(x = "Publication Year",
            y = "Citations per article",
            color = element_blank())
```

@fig-compare-cites-rolling smooths out some of the noise in @fig-compare-cites-dots in two ways. First, instead of measuring average citations per year, I measure average citations over a five-year rolling window. This doesn't make a huge difference to the measure for the other nineteen, which is already fairly smooth, but it is useful for smoothing the values for just one journal. Second, instead of showing the red and blue dots separately, I've just displayed the ratio between them.

```{r}
#| label: fig-compare-cites-rolling
#| fig-cap: "Ratio of citations to Philosophical Studies to citations to other journals, for five year rolling windows"

ggplot(ps_comp_rate_wide,
       aes(x = year, y = comp)) +
  geom_point() + 
  labs(x = "Publication Year",
       y = "Ratio",
       subtitle = "Ratio of citation rate in Philosophical Studies to citation rate in other top 20 journals; five year rolling average.") +
  theme(plot.subtitle = element_text(family = "Scala Sans Pro", size = 16))
```

The difference in @fig-compare-cites-rolling between the earlier and recent years is striking. By this one measure, citations per article, _Philosophical Studies_ was doing ok before 2003, but was towards the lower end of the top 20 journals. After 2003, it is doing better than the average journal _in the top 20_.

My very anecdotal impression is that _Philosophical Studies_ is viewed as being more prestigious by younger philosophers than by older philosophers. A toy model of prestige, where it is heavily anchored to how often a journal was cited when one was in graduate school, would explain that difference. That said, I have not done (and am not going to do) a careful study of comparative prestige judgments to know if there is even an effect here to find, or whether my informal sample was not reflective of the wider population.

In some ways looking at the averages here understates the impact of _Philosophical Studies_ in the 2000s. Average numbers of citations can be very misleading. @tbl-quartiles-two-journals compares five year periods from two journals: the _Australasian Journal of Philosophy_ (AJP) from 1980-1984, and _Philosophical Studies_ (PS) from 2003-2007. Q1, Q2 and Q3 are the 25th, 50th, and 75th percentile citations, and Mean is the average number of citations.

```{r}
#| label: tbl-quartiles-two-journals
#| tbl-cap: "Statistics for  AJP 1980-1984, and PS 2003-2007."

temp_ajp <- short_bib |>
  filter(journal == "Australasian Journal Of Philosophy",
         year >= 1980,
         year <= 1984) |>
  arrange(-cites)

this_table <- short_bib |>
  filter(journal == "Australasian Journal Of Philosophy",
         year >= 1980,
         year <= 1984) |>
  summarise(Q1 = round(quantile(cites, 0.25),1),
            Q2 = round(quantile(cites, 0.5),1),
            Q3 = round(quantile(cites, 0.75),1),
            Mean = round(mean(cites),1)) |>
  pivot_longer(cols = everything(),
               names_to = "Statistic",
               values_to = "AJP 1980-1984") |>
  left_join(
    short_bib |>
  filter(journal == "Philosophical Studies",
         year >= 2003,
         year <= 2007) |>
  summarise(Q1 = round(quantile(cites, 0.25),1),
            Q2 = round(quantile(cites, 0.5),1),
            Q3 = round(quantile(cites, 0.75),1),
            Mean = round(mean(cites),1)) |>
  pivot_longer(cols = everything(),
               names_to = "Statistic",
               values_to = "PS 2003-2007"),
  by = "Statistic"
  )
```

The mean number of citations per article is higher for AJP 1980-1984 than for _Philosophical Studies_ 2003-2007. But that's because of the `r sum(temp_ajp$cites)` citations to articles from the AJP in those years, `sum(filter(temp_ajp, displayauth == "David Lewis")$cites)` of them are to five articles by David Lewis. The citations to _Philosophical Studies_ are much more widely spread around. Comparing the 75th percentiles is more indicative of what's being published in the journals.

Part of the difference between AJP 1980-1984 and _Philosophical Studies_ 2003-2007 is a general trend in the discipline to spread around the citations more. But it's not just that. _Philosophical Studies_ stands out for how widely spread around its citations are. @fig-quartiles-ps-vs-19 shows this. I've taken the same 19 journals that I used in @fig-compare-cites-rolling, and calculated the same quartile statistics for _Philosophical Studies_, and for those 19 journals collectively, each year from 1980 to 2019. The individual year numbers are rather noisy, so I've also included a five-year rolling average.

```{r}
#| label: fig-quartiles-ps-vs-19
#| fig-cap: "Quartiles of citation counts for _Philosophical Studies_ and other leading journals."

this_table <- short_bib |>
  filter(journal %in% comparison_journals,
         journal != "Philosophical Studies") |>
  mutate(cited_journal = "Other top 20") |>
  bind_rows(short_bib |>
              filter(journal == "Philosophical Studies") |>
              mutate(cited_journal = "Philosophical Studies")) |>
  group_by(cited_journal, year) |>
  filter(year >= 1980, year <= 2019) |>
  summarise(Q1 = round(quantile(cites, 0.25),1),
            Q2 = round(quantile(cites, 0.5),1),
            Q3 = round(quantile(cites, 0.75),1),
            .groups = "drop") |>
  pivot_longer(cols = starts_with("Q"),
               names_to = "statistic",
               values_to = "value") |>
  ungroup() |>
  group_by(cited_journal, statistic) |>
  mutate(rolling = slide_dbl(value, mean, .before = 4)) |>
  ungroup()

ggplot(this_table,
       aes(x = year, y = value, color = statistic)) +
  facet_wrap(vars(cited_journal),
             nrow = 1) +
  geom_point() +
  theme(legend.position = "none") +
  labs(x = "Publication Year",
       y = "Citation Count") +
  scale_x_continuous(breaks = c(1990, 2000, 2010)) +
  scale_y_continuous(limits = c(0, 20)) +
  geom_line(aes(x = year, y = rolling, color = statistic))
```

The height of the peak of the right-hand graph in @fig-quartiles-ps-vs-19 is striking. _Philosophical Studies_ was publishing a lot of articles, and at least a quarter of them are getting well into double-digit citations just in philosophy journals. This tells us that the influence _Philosophical Studies_ was having in philosophy changed, especially over the 2000s. To see how it changed, we need to look inside the journal.

# History of _Philosophical Studies_ {#sec-articles}

## Editorial History

A change like we see in the early 2000s is often a sign of editorial change in the journal. This isn't the case at _Philosophical Studies_, which has had a remarkably stable editorial history.

It was founded by Herbert Feigl and Wilfrid Sellars, both then at the University of Minnesota, in 1950, as the "first American journal expressly devoted to analytic philosophy" [@DeVries2005 1-2]. They stayed as editors until Feigl's retirement in 1971, though after 1954 Sellars was listed as the first editor. At Feigl's retirement the journal moved from the University of Minnesota Press to Reidel, where it has stayed ever since.^[Springer is the current continuant of Reidel after several mergers and takeovers.] Sellars edited the journal alone until Keith Lehrer was brought on as associate editor in 1974, starting an association with the journal that would last nearly half a century. The next year Lehrer, who had just moved from Rochester to Arizona, became editor. He stayed in that role until 1982, having been joined by John Pollock (also at Rochester) in 1979. From 1982, Pollock was Editor-in-Chief, and Lehrer went back to being Associate Editor. In 1992 the journal moved 100 miles up I-10, as Stewart Cohen, then at Arizona State, took over as Editor.^[While the journal was at Arizona, at grad student assistant was recognised on the title page as an editorial assistant. Many prominent philosophers had this role over the years, including, in 1983, Stewart Cohen.] Cohen stayed as editor through the rest of the time covered in this study, eventually being an editor of the journal for longer than even Wilfrid Sellars. Thomas Blackson joined as book symposium editor in 2003. Jennifer Lackey and Wayne Davis, who would eventually take over from Cohen, joined as Associate Editors in 2014. In 2016 Cohen was made Editor-in-Chief, while Davis and Lackey were made Editors. None of these changes seem to line up with changes in the citation rate of the journal, so we'll have to look a little deeper to see what happened.

## Publication Rate


# Studies

Number of articles
Length of articles
Number of articles over 10K, 15K, 20K
Average citations over the 100 journals - boring because can't compare
Average citations compared to top 25 - more interesting
Maybe redo that graph as a ratio

# Comparisons

Articles with highest ratio of PS cites/general cites
Articles with lowest ratio of PS cites/general cites
Previously I just did that with articles published in PS; that seems wrong

Hmm, this could be complicated. 
Study: For each decade find 20 most cited, and look at how often they are cited in PS.

For 1980s, the low is 0 for Rawls (1980) and Dennett (1971). But Rawls is cited in Post (1984), under a variant name, and Dennett is cited in Lormond (1985), but to the reprint. Maybe just live with the messiness
High five in 1980s are all language, or language-adjacent: Lewis (1979) (both de se and time's arrow), two Perry papers, and Donnellan

For 1990s, the low is 0 for McDowell's Virtue and Reason. Is in Brighouse (1990), but the citation is incomplete and uses the wrong year. Oddly the third lowest is for Discrimination and Perceptual Knowledge, only 2/38. And this looks right.
The highs in 1990s are still language based, though with metaphysics seeping in (Kim on supervenience, Lewis on Universals)

For 2000s, lows include Cummins (1975) (which is hard to track, such a common name), Anderson (1999), and Mechanisms paper (2000).
The highs are very epistemology based - Goldman is among them, and the two big contextualism papers by DeRose and Lewis. Obviously the editor at the time was also a prominent contextualist, but his papers are not cited in the journal at a particularly out of the ordinary rate. (There are many cases in history where editors are cited a lot, but this isn't one of them.)
Just outside top 20, but Jackson and Chalmers has nearly 1/3 its cites in PS. Tracing back to Davies and Humberstone's original paper.
Remarkably, Elusive Knowledge is most cited in the decade; normally this kind of calculation pushes towards less cited, high variance cases.

For 2010s, still mechanisms, Anderson (1999), also Kripke (1975) are the low ones
Top 5 is more varied, both in topic and time: Kolodny (2005), Pryor (2000), Lewis (1986), Frankfurt (1969), Jackson (1982). Could be result of publishing more papers, but striking that it's pulling these older papers in.

# The LDA

Build the model
Note the five categories
Graph the trends
Flag the methodology

# Language

Find the 40 most cited in each topic over the 40 years (i.e., most cited per year)
Look how often they are cited in PS
Look how often they are cited across the 100
See if the trends in PS track wider trends
Find other journals that have similar trends (Analysis, PQ, AJP)

# Metaphysics

Note the two Schaffer papers, and differences in citing @WOS000368189400004
Is that because little grounding
There is some - see graph of words
Maybe just count how 'modal' vs 'postmodal' the 2019 papers are
Maybe do a small LDA of the metaphysics papers

# Ethics

Is there anything to say here?
Does it go more political? Still not citing Anderson, but something?

Delicate. Even happening.
