
## 1976

### Widely Cited Articles {-}

1. AI Goldman, "Discrimination and Perceptual Knowledge" _Journal Of Philosophy_ 73 (20): 771-791.
2. D Lewis, "Probabilities of Conditionals and Conditional Probabilities" _Philosophical Review_ 85 (3): 297-315.
3. D Lewis, "Paradoxes of Time Travel" _American Philosophical Quarterly_ 13 (2): 145-152.
4. M Stocker, "Schizophrenia of Modern Ethical Theories" _Journal Of Philosophy_ 73 (14): 453-466.
5. G Harman, "Practical Reasoning" _Review Of Metaphysics_ 29 (3): 431-463.
6. RC Stalnaker, "Possible Worlds" _Noûs_ 10 (1): 65-75.
7. JM Dunn, "Intuitive Semantics for First-Degree Entailments and Coupled Trees" _Philosophical Studies_ 29 (3): 149-168.
8. WP Alston, "Two Types of Foundationalism" _Journal Of Philosophy_ 73 (7): 165-185.
9. B Loar, "Semantics of Singular Terms" _Philosophical Studies_ 30 (6): 353-377.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1976
#| tbl-cap: Citation count for widely cited articles from 1976.

year_cites <- rank_table_generator(1976)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1976
#| tbl-cap: Citation rank for widely cited articles from 1976.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1976
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1976.

rolling_spaghetti_graph(1976)
```

```{r}
#| label: fig-citation-facet-1976
#| fig-cap: Faceted version of @fig-citation-spaghetti-1976.

rolling_facet_graph(1976)
```

\newpage


## 1977

### Widely Cited Articles {-}

1. FI Dretske, "Laws of Nature" _Philosophy Of Science_ 44 (2): 248-268.
2. J Perry, "Frege on Demonstratives" _Philosophical Review_ 86 (4): 474-497.
3. SL Darwall, "Two Kinds of Respect" _Ethics_ 88 (1): 36-49.
4. M Tooley, "Nature of Laws" _Canadian Journal Of Philosophy_ 7 (4): 667-698.
5. JM Taurek, "Should Numbers Count" _Philosophy & Public Affairs_ 6 (4): 293-316.
6. T Burge, "Belief De Re" _Journal Of Philosophy_ 74 (6): 338-362.
7. C Boorse, "Health as a Theoretical Concept" _Philosophy Of Science_ 44 (4): 542-573.
8. HN Castañeda, "Perception, Belief, and Structure of Physical Objects and Consciousness" _Synthese_ 35 (3): 285-351.
9. HH Field, "Logic, Meaning, and Conceptual Role" _Journal Of Philosophy_ 74 (7): 379-409.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1977
#| tbl-cap: Citation count for widely cited articles from 1977.

year_cites <- rank_table_generator(1977)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1977
#| tbl-cap: Citation rank for widely cited articles from 1977.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1977
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1977.

rolling_spaghetti_graph(1977)
```

```{r}
#| label: fig-citation-facet-1977
#| fig-cap: Faceted version of @fig-citation-spaghetti-1977.

rolling_facet_graph(1977)
```

\newpage


## 1978

### Widely Cited Articles {-}

1. D Lewis, "Truth in Fiction" _American Philosophical Quarterly_ 15 (1): 37-46.
2. DL Hull, "A Matter of Individuality" _Philosophy Of Science_ 45 (3): 335-360.
3. KL Walton, "Fearing Fictions" _Journal Of Philosophy_ 75 (1): 5-27.
4. HG Frankfurt, "The Problem of Action" _American Philosophical Quarterly_ 15 (2): 157-162.
5. PR Thagard, "The Best Explanation: Criteria for Theory Choice" _Journal Of Philosophy_ 75 (2): 76-92.
6. M Steiner, "Mathematical Explanation" _Philosophical Studies_ 34 (2): 135-151.
7. J Kim, "Supervenience and Nomological Incommensurables" _American Philosophical Quarterly_ 15 (2): 149-156.
8. GS Kavka, "Some Paradoxes of Deterrence" _Journal Of Philosophy_ 75 (6): 285-302.
9. L BonJour, "Can Empirical Knowledge Have a Foundation?" _American Philosophical Quarterly_ 15 (1): 1-13.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1978
#| tbl-cap: Citation count for widely cited articles from 1978.

year_cites <- rank_table_generator(1978)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1978
#| tbl-cap: Citation rank for widely cited articles from 1978.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1978
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1978.

rolling_spaghetti_graph(1978)
```

```{r}
#| label: fig-citation-facet-1978
#| fig-cap: Faceted version of @fig-citation-spaghetti-1978.

rolling_facet_graph(1978)
```

\newpage


## 1979

### Widely Cited Articles {-}

1. J Perry, "The Problem of the Essential Indexical" _Noûs_ 13 (1): 3-21.
2. D Lewis, "Attitudes De Dicto and De Se" _Philosophical Review_ 88 (4): 513-543.
3. D Lewis, "Counterfactual Dependence and Time's Arrow" _Noûs_ 13 (4): 455-476.
4. D Lewis, "Scorekeeping in a Language Game" _Journal Of Philosophical Logic_ 8 (3): 339-359.
5. J McDowell, "Virtue and Reason" _Monist_ 62 (3): 331-350.
6. G Priest, "The Logic of Paradox" _Journal Of Philosophical Logic_ 8 (2): 219-241.
7. N Daniels, "Wide Reflective Equilibrium and Theory Acceptance in Ethics" _Journal Of Philosophy_ 76 (5): 256-282.
8. N Cartwright, "Causal Laws and Effective Strategies" _Noûs_ 13 (4): 419-437.
9. RM Adams, "Primitive Thisness and Primitive Identity" _Journal Of Philosophy_ 76 (1): 5-26.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1979
#| tbl-cap: Citation count for widely cited articles from 1979.

year_cites <- rank_table_generator(1979)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1979
#| tbl-cap: Citation rank for widely cited articles from 1979.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1979
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1979.

rolling_spaghetti_graph(1979)
```

```{r}
#| label: fig-citation-facet-1979
#| fig-cap: Faceted version of @fig-citation-spaghetti-1979.

rolling_facet_graph(1979)
```

\newpage


## 1980

### Widely Cited Articles {-}

1. J Rawls, "Rational and Full Autonomy" _Journal Of Philosophy_ 77 (9): 515-535.
2. M Davies and L Humberstone, "Two Notions of Necessity" _Philosophical Studies_ 38 (1): 1-30.
3. J Levinson, "What a Musical Work Is" _Journal Of Philosophy_ 77 (1): 5-28.
4. E Sober, "Evolution, Population Thinking, and Essentialism" _Philosophy Of Science_ 47 (3): 350-383.
5. D Lewis, "Veridical Hallucination and Prosthetic Vision" _Australasian Journal Of Philosophy_ 58 (3): 239-249.
6. RB Marcus, "Moral Dilemmas and Consistency" _Journal Of Philosophy_ 77 (3): 121-136.
7. N Daniels, "Reflective Equilibrium and Archimedean Points" _Canadian Journal Of Philosophy_ 10 (1): 83-103.
8. PS Churchland, "A Perspective on Mind-Brain Research" _Journal Of Philosophy_ 77 (4): 185-207.
9. N Block, "Are Absent Qualia Impossible" _Philosophical Review_ 89 (2): 257-274.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1980
#| tbl-cap: Citation count for widely cited articles from 1980.

year_cites <- rank_table_generator(1980)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1980
#| tbl-cap: Citation rank for widely cited articles from 1980.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1980
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1980.

rolling_spaghetti_graph(1980)
```

```{r}
#| label: fig-citation-facet-1980
#| fig-cap: Faceted version of @fig-citation-spaghetti-1980.

rolling_facet_graph(1980)
```

\newpage


## 1981

### Widely Cited Articles {-}

1. L Laudan, "A Confutation of Convergent Realism" _Philosophy Of Science_ 48 (1): 19-49.
2. P Kitcher, "Explanatory Unification" _Philosophy Of Science_ 48 (4): 507-531.
3. PM Churchland, "Eliminative Materialism and the Propositional Attitudes" _Journal Of Philosophy_ 78 (2): 67-90.
4. R Dworkin, "What is Equality? Part 2: Equality of Resources" _Philosophy & Public Affairs_ 10 (4): 283-345.
5. D Lewis, "Causal Decision Theory" _Australasian Journal Of Philosophy_ 59 (1): 5-30.
6. P van Inwagen, "The Doctrine of Arbitrary Undetached Parts" _Pacific Philosophical Quarterly_ 62 (2): 123-137.
7. RM Adams, "Actualism and Thisness" _Synthese_ 49 (1): 3-41.
8. J Dupre, "Natural Kinds and Biological Taxa" _Philosophical Review_ 90 (1): 66-90.
9. R Dworkin, "What is Equality? Part 1: Equality of Welfare" _Philosophy & Public Affairs_ 10 (3): 185-246.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1981
#| tbl-cap: Citation count for widely cited articles from 1981.

year_cites <- rank_table_generator(1981)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1981
#| tbl-cap: Citation rank for widely cited articles from 1981.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1981
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1981.

rolling_spaghetti_graph(1981)
```

```{r}
#| label: fig-citation-facet-1981
#| fig-cap: Faceted version of @fig-citation-spaghetti-1981.

rolling_facet_graph(1981)
```

\newpage


## 1982

### Widely Cited Articles {-}

1. F Jackson, "Epiphenomenal Qualia" _Philosophical Quarterly_ 32 (127): 127-136.
2. S Wolf, "Moral Saints" _Journal Of Philosophy_ 79 (8): 419-439.
3. EW Prior, et al, "Three Theses About Dispositions" _American Philosophical Quarterly_ 19 (3): 251-257.
4. C Swoyer, "The Nature of Natural Laws" _Australasian Journal Of Philosophy_ 60 (3): 203-223.
5. D Lewis, "Logic for Equivocators" _Noûs_ 16 (3): 431-441.
6. J Haugeland, "Weak Supervenience" _American Philosophical Quarterly_ 19 (1): 93-103.
7. J Kim, "Psychophysical Supervenience" _Philosophical Studies_ 41 (1): 51-70.
8. A Gupta, "Truth and Paradox" _Journal Of Philosophical Logic_ 11 (1): 1-60.
9. D Shapere, "The Concept of Observation in Science and Philosophy" _Philosophy Of Science_ 49 (4): 485-525.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1982
#| tbl-cap: Citation count for widely cited articles from 1982.

year_cites <- rank_table_generator(1982)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1982
#| tbl-cap: Citation rank for widely cited articles from 1982.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1982
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1982.

rolling_spaghetti_graph(1982)
```

```{r}
#| label: fig-citation-facet-1982
#| fig-cap: Faceted version of @fig-citation-spaghetti-1982.

rolling_facet_graph(1982)
```

\newpage


## 1983

### Widely Cited Articles {-}

1. D Lewis, "New Work for a Theory of Universals" _Australasian Journal Of Philosophy_ 61 (4): 343-377.
2. J Levine, "Materialism and Qualia: The Explanatory Gap" _Pacific Philosophical Quarterly_ 64 (4): 354-361.
3. GS Kavka, "The Toxin Puzzle" _Analysis_ 43 (1): 33-36.
4. CM Korsgaard, "Two Distinctions in Goodness" _Philosophical Review_ 92 (2): 169-195.
5. R Brandom, "Asserting" _Noûs_ 17 (4): 637-650.
6. H Kornblith, "Justified Belief and Epistemically Responsible Action" _Philosophical Review_ 92 (1): 33-48.
7. E Eells and E Sober, "Probabilistic Causality and the Question of Transitivity" _Philosophy Of Science_ 50 (1): 35-57.
8. PS Churchland and PM Churchland, "Stalking The Wild Epistemic Engine" _Noûs_ 17 (1): 5-18.
9. PS Churchland, "Consciousness the Transmutation of a Concept" _Pacific Philosophical Quarterly_ 64 (1): 80-95.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1983
#| tbl-cap: Citation count for widely cited articles from 1983.

year_cites <- rank_table_generator(1983)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1983
#| tbl-cap: Citation rank for widely cited articles from 1983.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1983
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1983.

rolling_spaghetti_graph(1983)
```

```{r}
#| label: fig-citation-facet-1983
#| fig-cap: Faceted version of @fig-citation-spaghetti-1983.

rolling_facet_graph(1983)
```

\newpage


## 1984

### Widely Cited Articles {-}

1. D Lewis, "Putnam's Paradox" _Australasian Journal Of Philosophy_ 62 (3): 221-236.
2. BC van Fraassen, "Belief and the Will" _Journal Of Philosophy_ 81 (5): 235-256.
3. P Railton, "Alienation, Consequentialism, and the Demands of Morality" _Philosophy & Public Affairs_ 13 (2): 134-171.
4. G Boolos, "To Be is To Be a Value of a Variable (Or To Be Some Values of Some Variables)" _Journal Of Philosophy_ 81 (8): 430-449.
5. J Kim, "Concepts of Supervenience" _Philosophy And Phenomenological Research_ 45 (2): 153-176.
6. S Cohen, "Justification and Truth" _Philosophical Studies_ 46 (3): 279-295.
7. J Fodor, "Observation Reconsidered" _Philosophy Of Science_ 51 (1): 23-43.
8. J Kim, "Epiphenomenal and Supervenient Causation" _Midwest Studies In Philosophy_ 9: 257-270.
9. P Kitcher, "Species" _Philosophy Of Science_ 51 (2): 308-333.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1984
#| tbl-cap: Citation count for widely cited articles from 1984.

year_cites <- rank_table_generator(1984)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1984
#| tbl-cap: Citation rank for widely cited articles from 1984.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1984
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1984.

rolling_spaghetti_graph(1984)
```

```{r}
#| label: fig-citation-facet-1984
#| fig-cap: Faceted version of @fig-citation-spaghetti-1984.

rolling_facet_graph(1984)
```

\newpage


## 1985

### Widely Cited Articles {-}

1. R Feldman and E Conee, "Evidentialism" _Philosophical Studies_ 48 (1): 15-34.
2. E McMullin, "Galilean Idealization" _Studies In History And Philosophy Of Science_ 16 (3): 247-273.
3. J Hardwig, "Epistemic Dependence" _Journal Of Philosophy_ 82 (7): 335-349.
4. V McGee, "A Counterexample To Modus-Ponens" _Journal Of Philosophy_ 82 (9): 462-471.
5. G Boolos, "Nominalist Platonism" _Philosophical Review_ 94 (3): 327-344.
6. RM Adams, "Involuntary Sins" _Philosophical Review_ 94 (1): 3-31.
7. J Rawls, "Justice as Fairness: Political Not Metaphysical" _Philosophy & Public Affairs_ 14 (3): 223-251.
8. PM Churchland, "Reduction, Qualia, and the Direct Introspection of Brain States" _Journal Of Philosophy_ 82 (1): 8-28.
9. R Feldman, "Reliability and Justification" _Monist_ 68 (2): 159-174.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1985
#| tbl-cap: Citation count for widely cited articles from 1985.

year_cites <- rank_table_generator(1985)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1985
#| tbl-cap: Citation rank for widely cited articles from 1985.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1985
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1985.

rolling_spaghetti_graph(1985)
```

```{r}
#| label: fig-citation-facet-1985
#| fig-cap: Faceted version of @fig-citation-spaghetti-1985.

rolling_facet_graph(1985)
```

\newpage


## 1986

### Widely Cited Articles {-}

1. P Railton, "Moral Realism" _Philosophical Review_ 95 (2): 163-207.
2. T Burge, "Individualism and Psychology" _Philosophical Review_ 95 (1): 3-45.
3. CM Korsgaard, "Skepticism About Practical Reason" _Journal Of Philosophy_ 83 (1): 5-25.
4. A Baier, "Trust and Antitrust" _Ethics_ 96 (2): 231-260.
5. DM Rosenthal, "Two Concepts of Consciousness" _Philosophical Studies_ 49 (3): 329-359.
6. F Jackson and R Pargetter, "Oughts, Options, and Actualism" _Philosophical Review_ 95 (2): 233-255.
7. N Block, "Advertisement for a Semantics for Psychology" _Midwest Studies In Philosophy_ 10: 615-678.
8. RG Millikan, "Thoughts Without Laws, Cognitive Science With Content" _Philosophical Review_ 95 (1): 47-80.
9. AL Brueckner, "Brains in a Vat" _Journal Of Philosophy_ 83 (3): 148-167.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1986
#| tbl-cap: Citation count for widely cited articles from 1986.

year_cites <- rank_table_generator(1986)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1986
#| tbl-cap: Citation rank for widely cited articles from 1986.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1986
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1986.

rolling_spaghetti_graph(1986)
```

```{r}
#| label: fig-citation-facet-1986
#| fig-cap: Faceted version of @fig-citation-spaghetti-1986.

rolling_facet_graph(1986)
```

\newpage


## 1987

### Widely Cited Articles {-}

1. M Smith, "The Humean Theory of Motivation" _Mind_ 96 (381): 36-61.
2. J Bigelow and R Pargetter, "Functions" _Journal Of Philosophy_ 84 (4): 181-196.
3. H Frankfurt, "Equality as a Moral Ideal" _Ethics_ 98 (1): 21-43.
4. J Earman and J Norton, "What Price Spacetime Substantivalism: The Hole Story" _British Journal For The Philosophy Of Science_ 38 (4): 515-525.
5. DW Stampe, "The Authority of Desire" _Philosophical Review_ 96 (3): 335-381.
6. M Gilbert, "Modeling Collective Belief" _Synthese_ 73 (1): 185-204.
7. LS Temkin, "Intransitivity and the Mere Addition Paradox" _Philosophy & Public Affairs_ 16 (2): 138-187.
8. L Laudan, "Progress or Rationality: The Prospects for Normative Naturalism" _American Philosophical Quarterly_ 24 (1): 19-31.
9. T Nagel, "Moral Conflict and Political Legitimacy" _Philosophy & Public Affairs_ 16 (3): 215-240.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1987
#| tbl-cap: Citation count for widely cited articles from 1987.

year_cites <- rank_table_generator(1987)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1987
#| tbl-cap: Citation rank for widely cited articles from 1987.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1987
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1987.

rolling_spaghetti_graph(1987)
```

```{r}
#| label: fig-citation-facet-1987
#| fig-cap: Faceted version of @fig-citation-spaghetti-1987.

rolling_facet_graph(1987)
```

\newpage


## 1988

### Widely Cited Articles {-}

1. T Burge, "Individualism and Self-Knowledge" _Journal Of Philosophy_ 85 (11): 649-663.
2. J Bogen and J Woodward, "Saving the Phenomena" _Philosophical Review_ 97 (3): 303-352.
3. A Grove, "Two Modelings for Theory Change" _Journal Of Philosophical Logic_ 17 (2): 157-170.
4. K Sterelny and P Kitcher, "The Return of the Gene" _Journal Of Philosophy_ 85 (7): 339-361.
5. S Kagan, "The Additive Fallacy" _Ethics_ 99 (1): 5-31.
6. WP Alston, "An Internalist Externalism" _Synthese_ 74 (3): 265-283.
7. DLM Baxter, "Identity in the Loose and Popular Sense" _Mind_ 97 (388): 575-582.
8. F Jackson and P Pettit, "Functionalism and Broad Content" _Mind_ 97 (387): 381-400.
9. J Rawls, "The Priority of Right and Ideas of the Good" _Philosophy & Public Affairs_ 17 (4): 251-276.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1988
#| tbl-cap: Citation count for widely cited articles from 1988.

year_cites <- rank_table_generator(1988)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1988
#| tbl-cap: Citation rank for widely cited articles from 1988.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1988
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1988.

rolling_spaghetti_graph(1988)
```

```{r}
#| label: fig-citation-facet-1988
#| fig-cap: Faceted version of @fig-citation-spaghetti-1988.

rolling_facet_graph(1988)
```

\newpage


## 1989

### Widely Cited Articles {-}

1. GA Cohen, "On the Currency of Egalitarian Justice" _Ethics_ 99 (4): 906-944.
2. RG Millikan, "In Defense of Proper Functions" _Philosophy Of Science_ 56 (2): 288-302.
3. RG Millikan, "Biosemantics" _Journal Of Philosophy_ 86 (6): 281-297.
4. PA Boghossian and JD Velleman, "Color as a Secondary Quality" _Mind_ 98 (389): 81-103.
5. RJ Arneson, "Equality and Equal-Opportunity for Welfare" _Philosophical Studies_ 56 (1): 77-93.
6. PA Boghossian, "The Rule-Following Considerations" _Mind_ 5 98 (392): 507-549.
7. WS Quinn, "Actions, Intentions, and Consequences: The Doctrine of Double Effect" _Philosophy & Public Affairs_ 18 (4): 334-351.
8. D Marquis, "Why Abortion is Immoral" _Journal Of Philosophy_ 86 (4): 183-202.
9. M Crimmins and J Perry, "The Prince and the Phone Booth: Reporting Puzzling Beliefs" _Journal Of Philosophy_ 86 (12): 685-711.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1989
#| tbl-cap: Citation count for widely cited articles from 1989.

year_cites <- rank_table_generator(1989)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1989
#| tbl-cap: Citation rank for widely cited articles from 1989.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1989
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1989.

rolling_spaghetti_graph(1989)
```

```{r}
#| label: fig-citation-facet-1989
#| fig-cap: Faceted version of @fig-citation-spaghetti-1989.

rolling_facet_graph(1989)
```

\newpage


## 1990

### Widely Cited Articles {-}

1. P Kitcher, "The Division of Cognitive Labor" _Journal Of Philosophy_ 87 (1): 5-22.
2. F Jackson and P Pettit, "Program Explanation: A General Perspective" _Analysis_ 50 (2): 107-117.
3. D Davidson, "The Structure and Content of Truth" _Journal Of Philosophy_ 87 (6): 279-328.
4. G Rosen, "Modal Fictionalism" _Mind_ 99 (395): 327-354.
5. T Crane and DH Mellor, "There is No Question of Physicalism" _Mind_ 99 (394): 185-206.
6. J Vogel, "Cartesian Skepticism and Inference To the Best Explanation" _Journal Of Philosophy_ 87 (11): 658-666.
7. J Dreier, "Internalism and Speaker Relativism" _Ethics_ 101 (1): 6-26.
8. JW Kim, "Supervenience as a Philosophical Concept" _Metaphilosophy_ 21 (1-2): 1-27.
9. M Tye, "Vague Objects" _Mind_ 99 (396): 535-557.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1990
#| tbl-cap: Citation count for widely cited articles from 1990.

year_cites <- rank_table_generator(1990)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1990
#| tbl-cap: Citation rank for widely cited articles from 1990.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1990
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1990.

rolling_spaghetti_graph(1990)
```

```{r}
#| label: fig-citation-facet-1990
#| fig-cap: Faceted version of @fig-citation-spaghetti-1990.

rolling_facet_graph(1990)
```

\newpage


## 1991

### Widely Cited Articles {-}

1. K Neander, "Functions as Selected Effects: The Conceptual Analysts Defense" _Philosophy Of Science_ 58 (2): 168-184.
2. DC Dennett, "Real Patterns" _Journal Of Philosophy_ 88 (1): 27-51.
3. R Boyd, "Realism, Antifoundationalism and the Enthusiasm for Natural Kinds" _Philosophical Studies_ 61 (1-2): 127-148.
4. F Jackson, "Decision-Theoretic Consequentialism and the Nearest and Dearest Objection" _Ethics_ 101 (3): 461-482.
5. JJ Thomson, "Self-Defense" _Philosophy & Public Affairs_ 20 (4): 283-310.
6. J Hardwig, "The Role of Trust in Knowledge" _Journal Of Philosophy_ 88 (12): 693-708.
7. M McKinsey, "Anti-Individualism and Privileged Access" _Analysis_ 51 (1): 9-16.
8. K Neander, "The Teleological Notion of Function" _Australasian Journal Of Philosophy_ 69 (4): 454-468.
9. S Schiffer, "Ceteris-Paribus Laws" _Mind_ 100 (397): 1-17.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1991
#| tbl-cap: Citation count for widely cited articles from 1991.

year_cites <- rank_table_generator(1991)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1991
#| tbl-cap: Citation rank for widely cited articles from 1991.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1991
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1991.

rolling_spaghetti_graph(1991)
```

```{r}
#| label: fig-citation-facet-1991
#| fig-cap: Faceted version of @fig-citation-spaghetti-1991.

rolling_facet_graph(1991)
```

\newpage


## 1992

### Widely Cited Articles {-}

1. S Yablo, "Mental Causation" _Philosophical Review_ 101 (2): 245-280.
2. M Johnston, "How To Speak of the Colors" _Philosophical Studies_ 68 (3): 221-263.
3. K DeRose, "Contextualism and Knowledge Attributions" _Philosophy And Phenomenological Research_ 52 (4): 913-929.
4. JW Kim, "Multiple Realization and the Metaphysics of Reduction" _Philosophy And Phenomenological Research_ 52 (1): 1-26.
5. ME Bratman, "Shared Cooperative Activity" _Philosophical Review_ 101 (2): 327-340.
6. R Foley, "The Epistemology of Belief and the Epistemology of Degrees of Belief" _American Philosophical Quarterly_ 29 (2): 111-124.
7. MB Burke, "Copper Statues and Pieces of Copper: A Challenge To the Standard Account" _Analysis_ 52 (1): 12-17.
8. P Kitcher, "The Naturalists Return" _Philosophical Review_ 101 (1): 53-114.
9. A Brueckner, "What An Antiindividualist Knows A-Priori" _Analysis_ 52 (2): 111-118.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1992
#| tbl-cap: Citation count for widely cited articles from 1992.

year_cites <- rank_table_generator(1992)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1992
#| tbl-cap: Citation rank for widely cited articles from 1992.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1992
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1992.

rolling_spaghetti_graph(1992)
```

```{r}
#| label: fig-citation-facet-1992
#| fig-cap: Faceted version of @fig-citation-spaghetti-1992.

rolling_facet_graph(1992)
```

\newpage


## 1993

### Widely Cited Articles {-}

1. T Burge, "Content Preservation" _Philosophical Review_ 102 (4): 457-488.
2. S Yablo, "Is Conceivability a Guide To Possibility" _Philosophy And Phenomenological Research_ 53 (1): 1-42.
3. R Langton, "Speech Acts and Unspeakable Acts" _Philosophy & Public Affairs_ 22 (4): 293-330.
4. S Yablo, "Paradox Without Self-Reference" _Analysis_ 53 (4): 251-252.
5. ME Bratman, "Shared Intention" _Ethics_ 104 (1): 97-113.
6. T Horgan, "From Supervenience To Superdupervenience: Meeting the Demands of a Material World" _Mind_ 102 (408): 554-586.
7. J Dreier, "Structures of Normative Theories" _Monist_ 76 (1): 22-40.
8. F Dretske, "Conscious Experience" _Mind_ 102 (406): 263-283.
9. PE Griffiths, "Functional-Analysis and Proper Functions" _British Journal For The Philosophy Of Science_ 44 (3): 409-422.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1993
#| tbl-cap: Citation count for widely cited articles from 1993.

year_cites <- rank_table_generator(1993)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1993
#| tbl-cap: Citation rank for widely cited articles from 1993.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1993
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1993.

rolling_spaghetti_graph(1993)
```

```{r}
#| label: fig-citation-facet-1993
#| fig-cap: Faceted version of @fig-citation-spaghetti-1993.

rolling_facet_graph(1993)
```

\newpage


## 1994

### Widely Cited Articles {-}

1. D Lewis, "Humean Supervenience Debugged" _Mind_ 103 (412): 473-490.
2. CB Martin, "Dispositions and Conditionals" _Philosophical Quarterly_ 44 (174): 1-8.
3. H Field, "Deflationist Views of Meaning and Content" _Mind_ 103 (411): 249-285.
4. M Forster and E Sober, "How To Tell When Simpler, More Unified, or Less Ad-Hoc Theories Will Provide More Accurate Predictions" _British Journal For The Philosophy Of Science_ 45 (1): 1-35.
5. P Godfrey-Smith, "A Modern History Theory of Functions" _Noûs_ 28 (3): 344-362.
6. G Strawson, "The Impossibility of Moral Responsibility" _Philosophical Studies_ 75 (1-2): 5-24.
7. R Audi, "Dispositional Beliefs and Dispositions To Believe" _Noûs_ 28 (4): 419-434.
8. R Holton, "Deciding To Trust, Coming To Believe" _Australasian Journal Of Philosophy_ 72 (1): 63-76.
9. H Putnam, "Sense, Nonsense, and the Senses: An Inquiry into the Powers of the Human Mind" _Journal Of Philosophy_ 91 (9): 445-465.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1994
#| tbl-cap: Citation count for widely cited articles from 1994.

year_cites <- rank_table_generator(1994)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1994
#| tbl-cap: Citation rank for widely cited articles from 1994.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1994
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1994.

rolling_spaghetti_graph(1994)
```

```{r}
#| label: fig-citation-facet-1994
#| fig-cap: Faceted version of @fig-citation-spaghetti-1994.

rolling_facet_graph(1994)
```

\newpage


## 1995

### Widely Cited Articles {-}

1. K DeRose, "Solving the Skeptical Problem" _Philosophical Review_ 104 (1): 1-52.
2. D Widerker, "Libertarianism and Frankfurt's Attack on the Principle of Alternative Possibilities" _Philosophical Review_ 104 (2): 247-261.
3. DW Zimmerman, "Theories of Masses and Problems of Constitution" _Philosophical Review_ 104 (1): 53-110.
4. T van Gelder, "What Might Cognition Be, If Not Computation" _Journal Of Philosophy_ 92 (7): 345-381.
5. K Neander, "Misrepresenting and Malfunctioning" _Philosophical Studies_ 79 (2): 109-141.
6. K Fine, "The Logic of Essence" _Journal Of Philosophical Logic_ 24 (3): 241-273.
7. J McDowell, "Knowledge and the Internal" _Philosophy And Phenomenological Research_ 55 (4): 877-893.
8. P Pietroski and G Rey, "When Other Things Arent Equal: Saving Ceteris Paribus Laws From Vacuity" _British Journal For The Philosophy Of Science_ 46 (1): 81-110.
9. J Brown, "The Incompatibility of Anti-Individualism and Privileged Access" _Analysis_ 55 (3): 149-156.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1995
#| tbl-cap: Citation count for widely cited articles from 1995.

year_cites <- rank_table_generator(1995)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1995
#| tbl-cap: Citation rank for widely cited articles from 1995.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1995
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1995.

rolling_spaghetti_graph(1995)
```

```{r}
#| label: fig-citation-facet-1995
#| fig-cap: Faceted version of @fig-citation-spaghetti-1995.

rolling_facet_graph(1995)
```

\newpage


## 1996

### Widely Cited Articles {-}

1. D Lewis, "Elusive Knowledge" _Australasian Journal Of Philosophy_ 74 (4): 549-567.
2. T Williamson, "Knowing and Asserting" _Philosophical Review_ 105 (4): 489-523.
3. F Veltman, "Defaults in Update Semantics" _Journal Of Philosophical Logic_ 25 (3): 221-261.
4. K Jones, "Trust as An Affective Attitude" _Ethics_ 107 (1): 4-25.
5. R Dworkin, "Objectivity and Truth: You'd Better Believe It" _Philosophy & Public Affairs_ 25 (2): 87-139.
6. D Davidson, "The Folly of Trying To Define Truth" _Journal Of Philosophy_ 93 (6): 263-278.
7. A Oliver, "The Metaphysics of Properties" _Mind_ 105 (417): 1-80.
8. K Sterelny, et al, "The Extended Replicator" _Biology & Philosophy_ 11 (3): 377-403.
9. T Sider, "All the World's a Stage" _Australasian Journal Of Philosophy_ 74 (3): 433-453.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1996
#| tbl-cap: Citation count for widely cited articles from 1996.

year_cites <- rank_table_generator(1996)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1996
#| tbl-cap: Citation rank for widely cited articles from 1996.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1996
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1996.

rolling_spaghetti_graph(1996)
```

```{r}
#| label: fig-citation-facet-1996
#| fig-cap: Faceted version of @fig-citation-spaghetti-1996.

rolling_facet_graph(1996)
```

\newpage


## 1997

### Widely Cited Articles {-}

1. D Lewis, "Finkish Dispositions" _Philosophical Quarterly_ 47 (187): 143-158.
2. D Parfit, "Equality and Priority" _Ratio_ 10 (3): 202-221.
3. LR Baker, "Why Constitution is Not Identity" _Journal Of Philosophy_ 94 (12): 599-621.
4. R Audi, "The Place of Testimony in the Fabric of Knowledge and Justification" _American Philosophical Quarterly_ 34 (4): 405-422.
5. CS Hill, "Imaginability, Conceivability, Possibility and the Mind-Body Problem" _Philosophical Studies_ 87 (1): 61-85.
6. MJ Zimmerman, "Moral Responsibility and Ignorance" _Ethics_ 107 (3): 410-426.
7. RM Sainsbury, "Easy Possibilities (Reliability-Conditional)" _Philosophy And Phenomenological Research_ 57 (4): 907-919.
8. T Sider, "Four-Dimensionalism" _Philosophical Review_ 106 (2): 197-231.
9. T Burge, "Interlocution, Perception, and Memory" _Philosophical Studies_ 86 (1): 21-47.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1997
#| tbl-cap: Citation count for widely cited articles from 1997.

year_cites <- rank_table_generator(1997)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1997
#| tbl-cap: Citation rank for widely cited articles from 1997.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1997
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1997.

rolling_spaghetti_graph(1997)
```

```{r}
#| label: fig-citation-facet-1997
#| fig-cap: Faceted version of @fig-citation-spaghetti-1997.

rolling_facet_graph(1997)
```

\newpage


## 1998

### Widely Cited Articles {-}

1. A Clark and D Chalmers, "The Extended Mind" _Analysis_ 58 (1): 7-19.
2. JM Joyce, "A Nonpragmatic Vindication of Probabilism" _Philosophy Of Science_ 65 (4): 575-603.
3. J Ladyman, "What is Structural Realism?" _Studies In History And Philosophy Of Science_ 29 (3): 409-424.
4. A Bird, "Dispositions and Antidotes" _Philosophical Quarterly_ 48 (191): 227-234.
5. N Salmon, "Nonexistence" _Noûs_ 32 (3): 277-319.
6. R Langton and D Lewis, "Defining 'Intrinsic'" _Philosophy And Phenomenological Research_ 58 (2): 333-345.
7. E Conee and R Feldman, "The Generality Problem for Reliabilism" _Philosophical Studies_ 89 (1): 1-29.
8. JJ Thomson, "The Statue and the Clay" _Noûs_ 32 (2): 149-173.
9. S Shoemaker, "Causal and Metaphysical Necessity" _Pacific Philosophical Quarterly_ 79 (1): 59-77.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1998
#| tbl-cap: Citation count for widely cited articles from 1998.

year_cites <- rank_table_generator(1998)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1998
#| tbl-cap: Citation rank for widely cited articles from 1998.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1998
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1998.

rolling_spaghetti_graph(1998)
```

```{r}
#| label: fig-citation-facet-1998
#| fig-cap: Faceted version of @fig-citation-spaghetti-1998.

rolling_facet_graph(1998)
```

\newpage


## 1999

### Widely Cited Articles {-}

1. ES Anderson, "What is the Point of Equality?" _Ethics_ 109 (2): 287-337.
2. J Broome, "Normative Requirements" _Ratio_ 12 (4): 398-419.
3. N Block and R Stalnaker, "Conceptual Analysis, Dualism, and the Explanatory Gap" _Philosophical Review_ 108 (1): 1-46.
4. J Kim, "Making Sense of Emergence" _Philosophical Studies_ 95 (1-2): 3-36.
5. JD Velleman, "Love as a Moral Emotion" _Ethics_ 109 (2): 338-374.
6. W Bechtel and J Mundale, "Multiple Realizability Revisited: Linking Cognitive and Neural States" _Philosophy Of Science_ 66 (2): 175-207.
7. J Hyman, "How Knowledge Works" _Philosophical Quarterly_ 49 (197): 433-451.
8. B Fitelson, "The Plurality of Bayesian Measures of Confirmation and the Problem of Measure Sensitivity" _Philosophy Of Science_ 66 (3): 362-378.
9. T Shogenji, "Is Coherence Truth Conducive?" _Analysis_ 59 (4): 338-345.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-1999
#| tbl-cap: Citation count for widely cited articles from 1999.

year_cites <- rank_table_generator(1999)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-1999
#| tbl-cap: Citation rank for widely cited articles from 1999.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-1999
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1999.

rolling_spaghetti_graph(1999)
```

```{r}
#| label: fig-citation-facet-1999
#| fig-cap: Faceted version of @fig-citation-spaghetti-1999.

rolling_facet_graph(1999)
```

\newpage


## 2000

### Widely Cited Articles {-}

1. P Machamer, et al, "Thinking About Mechanisms" _Philosophy Of Science_ 67 (1): 1-25.
2. J Pryor, "The Skeptic and the Dogmatist" _Noûs_ 34 (4): 517-549.
3. S Haslanger, "Gender and Race: (What) Are They? (What) Do We Want Them To Be?" _Noûs_ 34 (1): 31-55.
4. D Lewis, "Causation as Influence" _Journal Of Philosophy_ 97 (4): 182-197.
5. J D'Arms and D Jacobson, "The Moralistic Fallacy: On the 'Appropriateness' of Emotions" _Philosophy And Phenomenological Research_ 61 (1): 65-90.
6. H Douglas, "Inductive Risk and Values in Science" _Philosophy Of Science_ 67 (4): 559-579.
7. A Elga, "Self-Locating Belief and the 'Sleeping Beauty' Problem" _Analysis_ 60 (2): 143-147.
8. RG Heck, "Nonconceptual Content and the "Space of Reasons"" _Philosophical Review_ 109 (4): 483-523.
9. LA Shapiro, "Multiple Realizations" _Journal Of Philosophy_ 97 (12): 635-654.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2000
#| tbl-cap: Citation count for widely cited articles from 2000.

year_cites <- rank_table_generator(2000)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2000
#| tbl-cap: Citation rank for widely cited articles from 2000.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2000
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2000.

rolling_spaghetti_graph(2000)
```

```{r}
#| label: fig-citation-facet-2000
#| fig-cap: Faceted version of @fig-citation-spaghetti-2000.

rolling_facet_graph(2000)
```

\newpage


## 2001

### Widely Cited Articles {-}

1. J Stanley and T Williamson, "Knowing How" _Journal Of Philosophy_ 98 (8): 411-444.
2. DJ Chalmers and F Jackson, "Conceptual Analysis and Reductive Explanation" _Philosophical Review_ 110 (3): 315-360.
3. AI Goldman, "Experts: Which Ones Should You Trust?" _Philosophy And Phenomenological Research_ 63 (1): 85-110.
4. C Hitchcock, "The Intransitivity of Causation Revealed in Equations and Graphs" _Journal Of Philosophy_ 98 (6): 273-299.
5. P Rysiew, "The Context-Sensitivity of Knowledge Attributions" _Noûs_ 35 (4): 477-514.
6. D Lewis, "Truthmaking and Difference-Making" _Noûs_ 35 (4): 602-615.
7. C Peacocke, "Does Perception Have a Nonconceptual Content?" _Journal Of Philosophy_ 98 (5): 239-264.
8. P Hieronymi, "Articulating An Uncompromising Forgiveness" _Philosophy And Phenomenological Research_ 62 (3): 529-555.
9. CF Craver, "Role Functions, Mechanisms, and Hierarchy" _Philosophy Of Science_ 68 (1): 53-74.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2001
#| tbl-cap: Citation count for widely cited articles from 2001.

year_cites <- rank_table_generator(2001)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2001
#| tbl-cap: Citation rank for widely cited articles from 2001.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2001
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2001.

rolling_spaghetti_graph(2001)
```

```{r}
#| label: fig-citation-facet-2001
#| fig-cap: Faceted version of @fig-citation-spaghetti-2001.

rolling_facet_graph(2001)
```

\newpage


## 2002

### Widely Cited Articles {-}

1. J Fantl and M McGrath, "Evidence, Pragmatics, and Justification" _Philosophical Review_ 111 (1): 67-94.
2. S Cohen, "Basic Knowledge and the Problem of Easy Knowledge" _Philosophy And Phenomenological Research_ 65 (2): 309-329.
3. S Glennan, "Rethinking Mechanistic Explanation" _Philosophy Of Science_ 69 (3): 342-353.
4. R Chang, "The Possibility of Parity" _Ethics_ 112 (4): 659-688.
5. C Wright, "(Anti-)Sceptics Simple and Subtle: G.E. Moore and John McDowell" _Philosophy And Phenomenological Research_ 65 (2): 330-348.
6. E Schwitzgebel, "A Phenomenal, Dispositional Account of Belief" _Noûs_ 36 (2): 249-275.
7. T Kelly, "The Rationality of Belief and Some Other Propositional Attitudes" _Philosophical Studies_ 110 (2): 163-196.
8. M Matthen and A Ariew, "Two Ways of Thinking About Fitness and Natural Selection" _Journal Of Philosophy_ 99 (2): 55-83.
9. DM Walsh, et al, "The Trials of Life: Natural Selection and Random Drift" _Philosophy Of Science_ 69 (3): 452-473.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2002
#| tbl-cap: Citation count for widely cited articles from 2002.

year_cites <- rank_table_generator(2002)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2002
#| tbl-cap: Citation rank for widely cited articles from 2002.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2002
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2002.

rolling_spaghetti_graph(2002)
```

```{r}
#| label: fig-citation-facet-2002
#| fig-cap: Faceted version of @fig-citation-spaghetti-2002.

rolling_facet_graph(2002)
```

\newpage


## 2003

### Widely Cited Articles {-}

1. K DeRose, "Assertion, Knowledge, and Context" _Philosophical Review_ 111 (2): 167-203.
2. N Shah, "How Truth Governs Belief" _Philosophical Review_ 112 (4): 447-482.
3. J Knobe, "Intentional Action and Side Effects in Ordinary Language" _Analysis_ 63 (3): 190-194.
4. A Hájek, "What Conditional Probability Could Not Be" _Synthese_ 137 (3): 273-323.
5. T Burge, "Perceptual Entitlement" _Philosophy And Phenomenological Research_ 67 (3): 503-548.
6. T Kelly, "Epistemic Rationality as Instrumental Rationality: A Critique" _Philosophy And Phenomenological Research_ 66 (3): 612-640.
7. J Schaffer, "Is There a Fundamental Level?" _Noûs_ 37 (3): 498-517.
8. N Kolodny, "Love as Valuing a Relationship" _Philosophical Review_ 112 (2): 135-189.
9. J MacFarlane, "Future Contingents and Relative Truth" _Philosophical Quarterly_ 53 (212): 321-336.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2003
#| tbl-cap: Citation count for widely cited articles from 2003.

year_cites <- rank_table_generator(2003)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2003
#| tbl-cap: Citation rank for widely cited articles from 2003.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2003
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2003.

rolling_spaghetti_graph(2003)
```

```{r}
#| label: fig-citation-facet-2003
#| fig-cap: Faceted version of @fig-citation-spaghetti-2003.

rolling_facet_graph(2003)
```

\newpage


## 2004

### Widely Cited Articles {-}

1. W Rabinowicz and T Ronnow-Rasmussen, "The Strike of the Demon: On Fitting Pro-Attitudes and Value" _Ethics_ 114 (3): 391-423.
2. MGF Martin, "The Limits of Self-Awareness" _Philosophical Studies_ 120 (1-3): 37-89.
3. C Travis, "The Silence of the Senses" _Mind_ 113 (449): 57-94.
4. D Pitt, "The Phenomenology of Cognition, Or, What is It Like To Think That P?" _Philosophy And Phenomenological Research_ 69 (1): 1-36.
5. M Johnston, "The Obscure Object of Hallucination" _Philosophical Studies_ 120 (1-3): 113-183.
6. RN Giere, "How Models Are Used To Represent Reality" _Philosophy Of Science_ 71 (5): 742-752.
7. DJ Chalmers, "Epistemic Two-Dimensional Semantics" _Philosophical Studies_ 118 (1-2): 153-226.
8. J Schaffer, "From Contextualism To Contrastivism" _Philosophical Studies_ 119 (1-2): 73-103.
9. M Richard, "Contextualism and Relativism" _Philosophical Studies_ 119 (1-2): 215-242.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2004
#| tbl-cap: Citation count for widely cited articles from 2004.

year_cites <- rank_table_generator(2004)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2004
#| tbl-cap: Citation rank for widely cited articles from 2004.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2004
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2004.

rolling_spaghetti_graph(2004)
```

```{r}
#| label: fig-citation-facet-2004
#| fig-cap: Faceted version of @fig-citation-spaghetti-2004.

rolling_facet_graph(2004)
```

\newpage


## 2005

### Widely Cited Articles {-}

1. N Kolodny, "Why Be Rational?" _Mind_ 114 (455): 509-563.
2. Nishi Shah and J. David Velleman, "Doxastic Deliberation" _Philosophical Review_ 114 (4): 497-534.
3. AM Smith, "Responsibility for Attitudes: Activity and Passivity in Mental Life" _Ethics_ 115 (2): 236-271.
4. P Hieronymi, "The Wrong Kind of Reason" _Journal Of Philosophy_ 102 (9): 437-457.
5. A Baker, "Are There Genuine Mathematical Explanations of Physical Phenomena?" _Mind_ 114 (454): 223-238.
6. Matthew Weiner, "Must We Know What We Say?" _Philosophical Review_ 114 (2): 227-251.
7. T Williamson, "Contextualism, Subject-Sensitive Invariantism and Knowledge of Knowledge" _Philosophical Quarterly_ 55 (219): 213-235.
8. Jonathan Schaffer, "Contrastive Causation" _Philosophical Review_ 114 (3): 327-358.
9. E Nahmias, et al, "Surveying Freedom: Folk Intuitions About Free Will and Moral Responsibility" _Philosophical Psychology_ 18 (5): 561-584.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2005
#| tbl-cap: Citation count for widely cited articles from 2005.

year_cites <- rank_table_generator(2005)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2005
#| tbl-cap: Citation rank for widely cited articles from 2005.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2005
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2005.

rolling_spaghetti_graph(2005)
```

```{r}
#| label: fig-citation-facet-2005
#| fig-cap: Faceted version of @fig-citation-spaghetti-2005.

rolling_facet_graph(2005)
```

\newpage


## 2006

### Widely Cited Articles {-}

1. S Street, "A Darwinian Dilemma for Realist Theories of Value" _Philosophical Studies_ 27 (1): 109-166.
2. Hilary Greaves and David Wallace, "Justifying Conditionalization: Conditionalization Maximizes Expected Epistemic Utility" _Mind_ 115 (459): 607-632.
3. Igor Douven, "Assertion, Knowledge, and Rational Credibility" _Philosophical Review_ 115 (4): 449-485.
4. Roger White, "Problems for Dogmatism" _Philosophical Studies_ 131 (3): 525-557.
5. Peter Godfrey-Smith, "The Strategy of Model-Based Science" _Biology & Philosophy_ 21 (5): 725-740.
6. P Hieronymi, "Controlling Attitudes" _Pacific Philosophical Quarterly_ 87 (1): 45-74.
7. Carl F. Craver, "When Mechanistic Models Explain" _Synthese_ 153 (3): 355-376.
8. David Enoch, "Agency, Shmagency: Why Normativity Won't Come From What is Constitutive of Action" _Philosophical Review_ 115 (2): 169-198.
9. Nishi Shah, "A New Argument for Evidentialism" _Philosophical Quarterly_ 56 (225): 481-498.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2006
#| tbl-cap: Citation count for widely cited articles from 2006.

year_cites <- rank_table_generator(2006)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2006
#| tbl-cap: Citation rank for widely cited articles from 2006.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2006
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2006.

rolling_spaghetti_graph(2006)
```

```{r}
#| label: fig-citation-facet-2006
#| fig-cap: Faceted version of @fig-citation-spaghetti-2006.

rolling_facet_graph(2006)
```

\newpage


## 2007

### Widely Cited Articles {-}

1. Adam Elga, "Reflection and Disagreement" _Noûs_ 41 (3): 478-502.
2. David Christensen, "Epistemology of Disagreement: The Good News" _Philosophical Review_ 116 (2): 187-217.
3. Jennifer Lackey, "Norms of Assertion" _Noûs_ 41 (4): 594-626.
4. Seth Yalcin, "Epistemic Modals" _Mind_ 116 (464): 983-1026.
5. Michael Huemer, "Compassionate Phenomenal Conservatism" _Philosophy And Phenomenological Research_ 74 (1): 30-55.
6. Michael Weisberg, "Three Kinds of Idealization" _Journal Of Philosophy_ 104 (12): 639-659.
7. Duncan Pritchard, "Anti-Luck Epistemology" _Synthese_ 158 (3): 277-297.
8. John MacFarlane, "Relativism and Disagreement" _Philosophical Studies_ 132 (1): 17-31.
9. Andy Egan, "Epistemic Modals, Relativism and Assertion" _Philosophical Studies_ 133 (1): 1-22.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2007
#| tbl-cap: Citation count for widely cited articles from 2007.

year_cites <- rank_table_generator(2007)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2007
#| tbl-cap: Citation rank for widely cited articles from 2007.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2007
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2007.

rolling_spaghetti_graph(2007)
```

```{r}
#| label: fig-citation-facet-2007
#| fig-cap: Faceted version of @fig-citation-spaghetti-2007.

rolling_facet_graph(2007)
```

\newpage


## 2008

### Widely Cited Articles {-}

1. John Hawthorne and Jason Stanley, "Knowledge and Action" _Journal Of Philosophy_ 5 (10): 571-590.
2. Tamar Szabo Gendler, "Alief and Belief" _Journal Of Philosophy_ 5 (10): 634-663.
3. Eric Schwitzgebel, "The Unreliability of Naive Introspection" _Philosophical Review_ 117 (2): 245-273.
4. Jessica Brown, "Subject-Sensitive Invariantism and the Knowledge Norm for Practical Reasoning" _Noûs_ 42 (2): 167-189.
5. Stacey Swain, et al, "The Instability of Philosophical Intuitions: Running Hot and Cold on Truetemp" _Philosophy And Phenomenological Research_ 76 (1): 138-155.
6. Scott Sturgeon, "Reason and the Grain of Belief" _Noûs_ 42 (1): 139-165.
7. Michael Fara, "Masked Abilities and Compatibilism" _Mind_ 117 (468): 843-865.
8. Pamela Hieronymi, "Responsibility for Believing" _Synthese_ 161 (3): 357-373.
9. Ross P. Cameron, "Turtles All the Way Down: Regress, Priority and Fundamentality" _Philosophical Quarterly_ 58 (230): 1-14.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2008
#| tbl-cap: Citation count for widely cited articles from 2008.

year_cites <- rank_table_generator(2008)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2008
#| tbl-cap: Citation rank for widely cited articles from 2008.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2008
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2008.

rolling_spaghetti_graph(2008)
```

```{r}
#| label: fig-citation-facet-2008
#| fig-cap: Faceted version of @fig-citation-spaghetti-2008.

rolling_facet_graph(2008)
```

\newpage


## 2009

### Widely Cited Articles {-}

1. Alison Hills, "Moral Testimony and Moral Epistemology" _Ethics_ 120 (1): 94-127.
2. Alan Baker, "Mathematical Explanation in Science" _British Journal For The Philosophy Of Science_ 60 (3): 611-633.
3. John MacFarlane, "Nonindexical Contextualism" _Synthese_ 166 (2): 231-250.
4. Alex Byrne, "Experience and Content" _Philosophical Quarterly_ 59 (236): 429-451.
5. Jonathan Schaffer, "Spacetime the One Substance" _Philosophical Studies_ 145 (1): 131-148.
6. Jonathan Cohen and Craig Callender, "A Better Best System Account of Lawhood" _Philosophical Studies_ 145 (1): 1-34.
7. Christian List and Peter Menzies, "Nonreductive Physicalism and the Limits of the Exclusion Principle" _Journal Of Philosophy_ 106 (9): 475-502.
8. Mark Schroeder, "Means-End Coherence, Stringency, and Subjective Reasons" _Philosophical Studies_ 143 (2): 223-248.
9. Jonathan Quong, "Killing in Self-Defense" _Ethics_ 119 (3): 507-537.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2009
#| tbl-cap: Citation count for widely cited articles from 2009.

year_cites <- rank_table_generator(2009)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2009
#| tbl-cap: Citation rank for widely cited articles from 2009.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2009
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2009.

rolling_spaghetti_graph(2009)
```

```{r}
#| label: fig-citation-facet-2009
#| fig-cap: Faceted version of @fig-citation-spaghetti-2009.

rolling_facet_graph(2009)
```

\newpage


## 2010

### Widely Cited Articles {-}

1. David Christensen, "Higher-Order Evidence" _Philosophy And Phenomenological Research_ 81 (1): 185-215.
2. Niko Kolodny and John MacFarlane, "Ifs and Oughts" _Journal Of Philosophy_ 107 (3): 115-143.
3. James Woodward, "Causation in Biology: Stability, Specificity, and the Choice of Levels of Explanation" _Biology & Philosophy_ 25 (3): 287-318.
4. Maria Lasonen Aarnio, "Unreasonable Knowledge" _Philosophical Perspectives_ 24 (1): 1-21.
5. Eric Schwitzgebel, "Acting Contrary To Our Professed Beliefs or the Gulf Between Occurrent Judgment and Dispositional Belief" _Pacific Philosophical Quarterly_ 91 (4): 531-553.
6. Julia Markovits, "Acting for the Right Reasons" _Philosophical Review_ 119 (2): 201-242.
7. Jonathan Schaffer, "The Least Discerning and Most Promiscuous Truthmaker" _Philosophical Quarterly_ 60 (239): 307-324.
8. Kevin J. S. Zollman, "The Epistemic Benefit of Transient Diversity" _Erkenntnis_ 72 (1): 17-35.
9. John Turri, "On the Relationship Between Propositional and Doxastic Justification" _Philosophy And Phenomenological Research_ 80 (2): 312-326.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2010
#| tbl-cap: Citation count for widely cited articles from 2010.

year_cites <- rank_table_generator(2010)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2010
#| tbl-cap: Citation rank for widely cited articles from 2010.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2010
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2010.

rolling_spaghetti_graph(2010)
```

```{r}
#| label: fig-citation-facet-2010
#| fig-cap: Faceted version of @fig-citation-spaghetti-2010.

rolling_facet_graph(2010)
```

\newpage


## 2011

### Widely Cited Articles {-}

1. Kristie Dotson, "Tracking Epistemic Violence, Tracking Practices of Silencing" _Hypatia_ 26 (2): 236-257.
2. Karen Bennett, "By Our Bootstraps" _Philosophical Perspectives_ 25 (1): 27-41.
3. David J. Chalmers, "Verbal Disputes" _Philosophical Review_ 120 (4): 515-566.
4. David Michael Kaplan and Carl F. Craver, "The Explanatory Force of Dynamical and Mathematical Models in Neuroscience: A Mechanistic Perspective" _Philosophy Of Science_ 78 (4): 601-627.
5. C. S. Jenkins, "Is Metaphysical Dependence Irreflexive?" _Monist_ 94 (2): 267-276.
6. David Christensen, "Disagreement, Question-Begging and Epistemic Self-Criticism" _Philosophers Imprint_ 11 (6):.
7. Guy Kahane, "Evolutionary Debunking Arguments" _Noûs_ 45 (1): 103-125.
8. Alisa Bokulich, "How Scientific Models Can Explain" _Synthese_ 180 (1): 33-45.
9. Gualtiero Piccinini and Carl Craver, "Integrating Psychology and Neuroscience: Functional Analyses as Mechanism Sketches" _Synthese_ 183 (3): 283-311.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2011
#| tbl-cap: Citation count for widely cited articles from 2011.

year_cites <- rank_table_generator(2011)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2011
#| tbl-cap: Citation rank for widely cited articles from 2011.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2011
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2011.

rolling_spaghetti_graph(2011)
```

```{r}
#| label: fig-citation-facet-2011
#| fig-cap: Faceted version of @fig-citation-spaghetti-2011.

rolling_facet_graph(2011)
```

\newpage


## 2012

### Widely Cited Articles {-}

1. Duncan Pritchard, "Anti-Luck Virtue Epistemology" _Journal Of Philosophy_ 109 (3): 247-279.
2. Paul Audi, "Grounding: Toward a Theory of the In-Virtue-Of Relation" _Journal Of Philosophy_ 109 (12): 685-711.
3. Fiona Macpherson, "Cognitive Penetration of Colour Experience: Rethinking the Issue in Light of An Indirect Mechanism" _Philosophy And Phenomenological Research_ 84 (1): 24-62.
4. Pablo Cobreros, et al, "Tolerant, Classical, Strict" _Journal Of Philosophical Logic_ 41 (2): 347-385.
5. Barry Loewer, "Two Accounts of Laws and Time" _Philosophical Studies_ 60 (1): 115-137.
6. Gaile Pohlhaus Jr., "Relational Knowing and Epistemic Injustice: Toward a Theory of Willful Hermeneutical Ignorance" _Hypatia_ 27 (4): 715-735.
7. Declan Smithies, "Moore's Paradox and the Accessibility of Justification" _Philosophy And Phenomenological Research_ 85 (2): 273-300.
8. Kit Fine, "The Pure Logic of Ground" _Review Of Symbolic Logic_ 5 (1): 1-25.
9. Eric Schwitzgebel and Fiery Cushman, "Expertise in Moral Reasoning? Order Effects on Moral Judgment in Professional Philosophers and Non-Philosophers" _Mind & Language_ 27 (2): 135-153.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2012
#| tbl-cap: Citation count for widely cited articles from 2012.

year_cites <- rank_table_generator(2012)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2012
#| tbl-cap: Citation rank for widely cited articles from 2012.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2012
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2012.

rolling_spaghetti_graph(2012)
```

```{r}
#| label: fig-citation-facet-2012
#| fig-cap: Faceted version of @fig-citation-spaghetti-2012.

rolling_facet_graph(2012)
```

\newpage


## 2013

### Widely Cited Articles {-}

1. David Plunkett and Tim Sundell, "Disagreement and the Semantics of Normative and Evaluative Terms" _Philosophers Imprint_ 13 (23): 1-37.
2. Louis deRosset, "Grounding Explanations" _Philosophers Imprint_ 13 (7):.
3. Jane Friedman, "Suspended Judgment" _Philosophical Studies_ 162 (2): 165-181.
4. Kelly Trogdon, "Grounding: Necessary or Contingent?" _Pacific Philosophical Quarterly_ 94 (4): 465-485.
5. David Ripley, "Paradoxes and Failures of Cut" _Australasian Journal Of Philosophy_ 91 (1): 139-164.
6. Marc Lange, "What Makes a Scientific Explanation Distinctively Mathematical?" _British Journal For The Philosophy Of Science_ 64 (3): 485-511.
7. Pablo Cobreros, et al, "Reaching Transparent Truth" _Mind_ 122 (488): 841-866.
8. Selim Berker, "Epistemic Teleology and the Separateness of Propositions" _Philosophical Review_ 122 (3): 337-393.
9. Berit Brogaard and Joe Salerno, "Remarks on Counterpossibles" _Synthese_ 190 (4): 639-660.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2013
#| tbl-cap: Citation count for widely cited articles from 2013.

year_cites <- rank_table_generator(2013)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2013
#| tbl-cap: Citation rank for widely cited articles from 2013.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2013
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2013.

rolling_spaghetti_graph(2013)
```

```{r}
#| label: fig-citation-facet-2013
#| fig-cap: Faceted version of @fig-citation-spaghetti-2013.

rolling_facet_graph(2013)
```

\newpage


## 2014

### Widely Cited Articles {-}

1. Jessica M. Wilson, "No Work for a Theory of Grounding" _Inquiry_ 57 (5-6): 535-579.
2. Shamik Dasgupta, "The Possibility of Physicalism" _Journal Of Philosophy_ 0): 557-592.
3. Miriam Schoenfield, "Permission To Believe: Why Permissivism is True and What It Tells Us About Irrelevant Influences on Belief" _Noûs_ 48 (2): 193-218.
4. Jacob Ross and Mark Schroeder, "Belief, Credence, and Pragmatic Encroachment" _Philosophy And Phenomenological Research_ 88 (2): 259-288.
5. Sophie Horowitz, "Epistemic Akrasia" _Noûs_ 48 (4): 718-744.
6. Maria Lasonen-Aarnio, "Higher-Order Evidence and the Limits of Defeat" _Philosophy And Phenomenological Research_ 88 (2): 314-345.
7. Paul Boghossian, "What is Inference?" _Philosophical Studies_ 169 (1): 1-18.
8. Lara Buchak, "Belief, Credence, and Norms" _Philosophical Studies_ 169 (2): 285-311.
9. Robert W. Batterman and Collin C. Rice, "Minimal Model Explanations" _Philosophy Of Science_ 81 (3): 349-376.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2014
#| tbl-cap: Citation count for widely cited articles from 2014.

year_cites <- rank_table_generator(2014)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2014
#| tbl-cap: Citation rank for widely cited articles from 2014.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2014
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2014.

rolling_spaghetti_graph(2014)
```

```{r}
#| label: fig-citation-facet-2014
#| fig-cap: Faceted version of @fig-citation-spaghetti-2014.

rolling_facet_graph(2014)
```

\newpage


## 2015

### Widely Cited Articles {-}

1. Alexander Skiles, "Against Grounding Necessitarianism" _Erkenntnis_ 80 (4): 717-751.
2. Michael J. Raven, "Ground" _Philosophy Compass_ 10 (5): 322-333.
3. Collin Rice, "Moving Beyond Causes: Optimality Models and Scientific Explanation" _Noûs_ 49 (3): 589-615.
4. David Plunkett, "Which Concepts Should We Use?: Metalinguistic Negotiations and the Methodology of Philosophy" _Inquiry_ -8): 828-874.
5. Kit Fine, "Unified Foundations for Essence and Ground" _Journal Of The American Philosophical Association_ 1 (2):.
6. James Woodward, "Interventionism and Causal Exclusion" _Philosophy And Phenomenological Research_ 91 (2): 303-347.
7. John Bengson, "The Intellectual Given" _Mind_ 124 (495): 707-760.
8. Gonzalo Rodriguez-Pereyra, "Grounding is Not a Strict Order" _Journal Of The American Philosophical Association_ 1 (3): 517-534.
9. Matthew H. Slater, "Natural Kindness" _British Journal For The Philosophy Of Science_ 66 (2): 375-411.

### Citation Count {-}

```{r}
#| label: tbl-citation-count-2015
#| tbl-cap: Citation count for widely cited articles from 2015.

year_cites <- rank_table_generator(2015)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-}

```{r}
#| label: tbl-citation-rank-2015
#| tbl-cap: Citation rank for widely cited articles from 2015.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-}

```{r}
#| label: fig-citation-spaghetti-2015
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2015.

rolling_spaghetti_graph(2015)
```

```{r}
#| label: fig-citation-facet-2015
#| fig-cap: Faceted version of @fig-citation-spaghetti-2015.

rolling_facet_graph(2015)
```

\newpage

