
## 1956 {#sec-s1956}

### Widely Cited Articles {-}

1. W. V. Quine (1956) "Quantifiers and Propositional Attitudes," _Journal Of Philosophy_ 53 (5): 177-187 1956.
2. G Frege (1956) "The Thought: A Logical Inquiry," _Mind_ 65 (259): 289-311 1956.
3. HP Grice and PF Strawson (1956) "In Defense of a Dogma," _Philosophical Review_ 65 (2): 141-158 1956.
4. JG Kemeny and P Oppenheim (1956) "On Reduction," _Philosophical Studies_ 7 (1-2): 6-19 1956.

### Citation Count {-#sec-count-1956}

```{r}
#| label: tbl-citation-count-1956
#| tbl-cap: Citation count for widely cited articles from 1956.

year_cites <- rank_table_generator(1956)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1956}

```{r}
#| label: tbl-citation-rank-1956
#| tbl-cap: Citation rank for widely cited articles from 1956.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1956}

```{r}
#| label: fig-citation-spaghetti-1956
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1956.
#| cache: TRUE

rolling_spaghetti_graph(1956)
```

```{r}
#| label: fig-citation-facet-1956
#| fig-cap: Faceted version of @fig-citation-spaghetti-1956.
#| cache: TRUE

rolling_facet_graph(1956)
```

\newpage


## 1957 {#sec-s1957}

### Widely Cited Articles {-}

1. HP Grice (1957) "Meaning," _Philosophical Review_ 66 (3): 377-388 1957.
2. Z Vendler (1957) "Verbs and Times," _Philosophical Review_ 66 (2): 143-160 1957.

### Citation Count {-#sec-count-1957}

```{r}
#| label: tbl-citation-count-1957
#| tbl-cap: Citation count for widely cited articles from 1957.

year_cites <- rank_table_generator(1957)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1957}

```{r}
#| label: tbl-citation-rank-1957
#| tbl-cap: Citation rank for widely cited articles from 1957.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1957}

```{r}
#| label: fig-citation-spaghetti-1957
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1957.
#| cache: TRUE

rolling_spaghetti_graph(1957)
```

```{r}
#| label: fig-citation-facet-1957
#| fig-cap: Faceted version of @fig-citation-spaghetti-1957.
#| cache: TRUE

rolling_facet_graph(1957)
```

\newpage


## 1958 {#sec-s1958}

### Widely Cited Articles {-}

1. GEM Anscombe (1958) "Modern Moral Philosophy," _Philosophy_ 33 (124): 1-19 1958.
2. JR Searle (1958) "Proper Names," _Mind_ 67 (266): 166-173 1958.
3. John Rawls (1958) "Justice as Fairness," _Philosophical Review_ 67 (2): 164-194 1958.
4. S Hampshire and HLA Hart (1958) "Decision, Intention and Certainty," _Mind_ 67 (265): 1-12 1958.

### Citation Count {-#sec-count-1958}

```{r}
#| label: tbl-citation-count-1958
#| tbl-cap: Citation count for widely cited articles from 1958.

year_cites <- rank_table_generator(1958)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1958}

```{r}
#| label: tbl-citation-rank-1958
#| tbl-cap: Citation rank for widely cited articles from 1958.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1958}

```{r}
#| label: fig-citation-spaghetti-1958
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1958.
#| cache: TRUE

rolling_spaghetti_graph(1958)
```

```{r}
#| label: fig-citation-facet-1958
#| fig-cap: Faceted version of @fig-citation-spaghetti-1958.
#| cache: TRUE

rolling_facet_graph(1958)
```

\newpage


## 1959 {#sec-s1959}

### Widely Cited Articles {-}

1. JJC Smart (1959) "Sensations and Brain Processes," _Philosophical Review_ 68 (2): 141-156 1959.
2. F Sibley (1959) "Aesthetic Concepts," _Philosophical Review_ 68 (4): 421-450 1959.
3. AN Prior (1959) "Thank Goodness That's Over," _Philosophy_ 34 (128): 12-17 1959.
4. KR Popper (1959) "The Propensity Interpretation of Probability," _British Journal For The Philosophy Of Science_ 10 (37): 25-42 1959.
5. M Dummett (1959) "Wittgenstein's Philosophy of Mathematics," _Philosophical Review_ 68 (3): 324-348 1959.

### Citation Count {-#sec-count-1959}

```{r}
#| label: tbl-citation-count-1959
#| tbl-cap: Citation count for widely cited articles from 1959.

year_cites <- rank_table_generator(1959)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1959}

```{r}
#| label: tbl-citation-rank-1959
#| tbl-cap: Citation rank for widely cited articles from 1959.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1959}

```{r}
#| label: fig-citation-spaghetti-1959
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1959.
#| cache: TRUE

rolling_spaghetti_graph(1959)
```

```{r}
#| label: fig-citation-facet-1959
#| fig-cap: Faceted version of @fig-citation-spaghetti-1959.
#| cache: TRUE

rolling_facet_graph(1959)
```

\newpage


## 1960 {#sec-s1960}

### Widely Cited Articles {-}

1. Peter T. Geach (1960) "Ascriptivism," _Philosophical Review_ 69 (2): 221-225 1960.
2. N Malcolm (1960) "Anselm's Ontological Arguments," _Philosophical Review_ 69 (1): 41-62 1960.

### Citation Count {-#sec-count-1960}

```{r}
#| label: tbl-citation-count-1960
#| tbl-cap: Citation count for widely cited articles from 1960.

year_cites <- rank_table_generator(1960)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1960}

```{r}
#| label: tbl-citation-rank-1960
#| tbl-cap: Citation rank for widely cited articles from 1960.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1960}

```{r}
#| label: fig-citation-spaghetti-1960
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1960.
#| cache: TRUE

rolling_spaghetti_graph(1960)
```

```{r}
#| label: fig-citation-facet-1960
#| fig-cap: Faceted version of @fig-citation-spaghetti-1960.
#| cache: TRUE

rolling_facet_graph(1960)
```

\newpage


## 1961 {#sec-s1961}

### Widely Cited Articles {-}

1. JJC Smart (1961) "Free-Will, Praise and Blame," _Mind_ 70 (279): 291-306 1961.
2. JR Lucas (1961) "Minds, Machines and Gödel," _Philosophy_ 36 (137): 112-127 1961.
3. IJ Good (1961) "A Causal Calculus (I)," _British Journal For The Philosophy Of Science_ 11 (44): 305-318 1961.

### Citation Count {-#sec-count-1961}

```{r}
#| label: tbl-citation-count-1961
#| tbl-cap: Citation count for widely cited articles from 1961.

year_cites <- rank_table_generator(1961)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1961}

```{r}
#| label: tbl-citation-rank-1961
#| tbl-cap: Citation rank for widely cited articles from 1961.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1961}

```{r}
#| label: fig-citation-spaghetti-1961
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1961.
#| cache: TRUE

rolling_spaghetti_graph(1961)
```

```{r}
#| label: fig-citation-facet-1961
#| fig-cap: Faceted version of @fig-citation-spaghetti-1961.
#| cache: TRUE

rolling_facet_graph(1961)
```

\newpage


## 1962 {#sec-s1962}

### Widely Cited Articles {-}

1. Hilary Putnam (1962) "It Ain't Necessarily So," _Journal Of Philosophy_ 59 (22): 658-671 1962.
2. EJ Lemmon (1962) "Moral Dilemmas," _Philosophical Review_ 71 (2): 139-158 1962.
3. JR Searle (1962) "Meaning and Speech Acts," _Philosophical Review_ 71 (4): 423-432 1962.
4. J Hintikka (1962) "Cogito, Ergo Sum: Inference or Performance?," _Philosophical Review_ 71 (1): 3-32 1962.

### Citation Count {-#sec-count-1962}

```{r}
#| label: tbl-citation-count-1962
#| tbl-cap: Citation count for widely cited articles from 1962.

year_cites <- rank_table_generator(1962)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1962}

```{r}
#| label: tbl-citation-rank-1962
#| tbl-cap: Citation rank for widely cited articles from 1962.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1962}

```{r}
#| label: fig-citation-spaghetti-1962
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1962.
#| cache: TRUE

rolling_spaghetti_graph(1962)
```

```{r}
#| label: fig-citation-facet-1962
#| fig-cap: Faceted version of @fig-citation-spaghetti-1962.
#| cache: TRUE

rolling_facet_graph(1962)
```

\newpage


## 1964 {#sec-s1964}

### Widely Cited Articles {-}

1. A Danto (1964) "The Artworld," _Journal Of Philosophy_ 61 (19): 571-584 1964.
2. PF Strawson (1964) "Intention and Convention in Speech Acts," _Philosophical Review_ 73 (4): 439-460 1964.
3. JR Searle (1964) "How To Derive Ought From Is," _Philosophical Review_ 73 (1): 43-58 1964.
4. M Dummett (1964) "Bringing About the Past," _Philosophical Review_ 73 (3): 338-359 1964.
5. G Dickie (1964) "The Myth of the Aesthetic Attitude," _American Philosophical Quarterly_ 1 (1): 56-65 1964.

### Citation Count {-#sec-count-1964}

```{r}
#| label: tbl-citation-count-1964
#| tbl-cap: Citation count for widely cited articles from 1964.

year_cites <- rank_table_generator(1964)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1964}

```{r}
#| label: tbl-citation-rank-1964
#| tbl-cap: Citation rank for widely cited articles from 1964.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1964}

```{r}
#| label: fig-citation-spaghetti-1964
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1964.
#| cache: TRUE

rolling_spaghetti_graph(1964)
```

```{r}
#| label: fig-citation-facet-1964
#| fig-cap: Faceted version of @fig-citation-spaghetti-1964.
#| cache: TRUE

rolling_facet_graph(1964)
```

\newpage


## 1965 {#sec-s1965}

### Widely Cited Articles {-}

1. Paul Benacerraf (1965) "What Numbers Could Not Be," _Philosophical Review_ 74 (1): 47-73 1965.
2. Gilbert Harman (1965) "The Inference To the Best Explanation," _Philosophical Review_ 74 (1): 88-95 1965.
3. Peter T. Geach (1965) "Assertion," _Philosophical Review_ 74 (4): 449-465 1965.
4. J. L. Mackie (1965) "Causes and Conditions," _American Philosophical Quarterly_ 2 (4): 245-264 1965.
5. Richard Rorty (1965) "Mind-Body Identity, Privacy, and Categories," _Review Of Metaphysics_ 19 (1): 24-54 1965.
6. DL Hull (1965) "The Effect of Essentialism on Taxonomy: 2000 Years of Stasis (I)," _British Journal For The Philosophy Of Science_ 15 (60): 314-326 1965.
7. F Sibley (1965) "Aesthetic and Non-Aesthetic," _Philosophical Review_ 74 (2): 135-159 1965.
8. J Feinberg (1965) "The Expressive Function of Punishment," _Monist_ 49 (3): 397-423 1965.

### Citation Count {-#sec-count-1965}

```{r}
#| label: tbl-citation-count-1965
#| tbl-cap: Citation count for widely cited articles from 1965.

year_cites <- rank_table_generator(1965)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1965}

```{r}
#| label: tbl-citation-rank-1965
#| tbl-cap: Citation rank for widely cited articles from 1965.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1965}

```{r}
#| label: fig-citation-spaghetti-1965
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1965.
#| cache: TRUE

rolling_spaghetti_graph(1965)
```

```{r}
#| label: fig-citation-facet-1965
#| fig-cap: Faceted version of @fig-citation-spaghetti-1965.
#| cache: TRUE

rolling_facet_graph(1965)
```

\newpage


## 1966 {#sec-s1966}

### Widely Cited Articles {-}

1. Keith S. Donnellan (1966) "Reference and Definite Descriptions," _Philosophical Review_ 75 (3): 281-304 1966.
2. David Lewis (1966) "An Argument for the Identity Theory," _Journal Of Philosophy_ 63 (1): 17-25 1966.
3. C. B. Martin and M Deutscher (1966) "Remembering," _Philosophical Review_ 75 (2): 161-196 1966.
4. Bas C. van Fraassen (1966) "Singular Terms, Truth-Value Gaps, and Free Logic," _Journal Of Philosophy_ 63 (17): 481-495 1966.
5. Jaegwon Kim (1966) "On the Psycho-Physical Identity Theory," _American Philosophical Quarterly_ 3 (3): 227-235 1966.
6. Roderick M. Chisholm and Ernest Sosa (1966) "Logic of Intrinsically Better," _American Philosophical Quarterly_ 3 (3): 244-249 1966.

### Citation Count {-#sec-count-1966}

```{r}
#| label: tbl-citation-count-1966
#| tbl-cap: Citation count for widely cited articles from 1966.

year_cites <- rank_table_generator(1966)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1966}

```{r}
#| label: tbl-citation-rank-1966
#| tbl-cap: Citation rank for widely cited articles from 1966.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1966}

```{r}
#| label: fig-citation-spaghetti-1966
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1966.
#| cache: TRUE

rolling_spaghetti_graph(1966)
```

```{r}
#| label: fig-citation-facet-1966
#| fig-cap: Faceted version of @fig-citation-spaghetti-1966.
#| cache: TRUE

rolling_facet_graph(1966)
```

\newpage


## 1967 {#sec-s1967}

### Widely Cited Articles {-}

1. Donald Davidson (1967) "Truth and Meaning," _Synthese_ 17 (3): 304-323 1967.
2. Alvin I. Goldman (1967) "A Causal Theory of Knowing," _Journal Of Philosophy_ 64 (12): 357-372 1967.
3. Donald Davidson (1967) "Causal Relations," _Journal Of Philosophy_ 64 (21): 691-703 1967.
4. Hector-Neri Castañeda (1967) "Indicators and Quasi-Indicators," _American Philosophical Quarterly_ 4 (2): 85-100 1967.
5. Kenneth F. Schaffner (1967) "Approaches To Reduction," _Philosophy Of Science_ 34 (2): 137-147 1967.
6. Hilary Putnam (1967) "Time and Physical Geometry," _Journal Of Philosophy_ 64 (8): 240-247 1967.
7. I Hacking (1967) "Slightly More Realistic Personal Probability," _Philosophy Of Science_ 34 (4): 311-325 1967.
8. I Hacking (1967) "Possibility," _Philosophical Review_ 76 (2): 143-168 1967.

### Citation Count {-#sec-count-1967}

```{r}
#| label: tbl-citation-count-1967
#| tbl-cap: Citation count for widely cited articles from 1967.

year_cites <- rank_table_generator(1967)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1967}

```{r}
#| label: tbl-citation-rank-1967
#| tbl-cap: Citation rank for widely cited articles from 1967.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1967}

```{r}
#| label: fig-citation-spaghetti-1967
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1967.
#| cache: TRUE

rolling_spaghetti_graph(1967)
```

```{r}
#| label: fig-citation-facet-1967
#| fig-cap: Faceted version of @fig-citation-spaghetti-1967.
#| cache: TRUE

rolling_facet_graph(1967)
```

\newpage


## 1968 {#sec-s1968}

### Widely Cited Articles {-}

1. David Lewis (1968) "Counterpart Theory and Quantified Modal Logic," _Journal Of Philosophy_ 65 (5): 113-126 1968.
2. SSydney Shoemaker (1968) "Self-Reference and Self-Awareness," _Journal Of Philosophy_ 65 (19): 555-567 1968.
3. Barry Stroud (1968) "Transcendental Arguments," _Journal Of Philosophy_ 65 (9): 241-256 1968.
4. P Unger (1968) "An Analysis of Factual Knowledge," _Journal Of Philosophy_ 65 (6): 157-170 1968.
5. H Morris (1968) "Persons and Punishment," _Monist_ 52 (4): 475-501 1968.
6. W. V. Quine (1968) "Ontological Relativity," _Journal Of Philosophy_ 65 (7): 185-212 1968.
7. Bas C. van Fraassen (1968) "Presupposition, Implication, and Self-Reference," _Journal Of Philosophy_ 65 (5): 136-151 1968.
8. Gilbert Harman (1968) "Knowledge, Inference, and Explanation," _American Philosophical Quarterly_ 5 (3): 164-173 1968.

### Citation Count {-#sec-count-1968}

```{r}
#| label: tbl-citation-count-1968
#| tbl-cap: Citation count for widely cited articles from 1968.

year_cites <- rank_table_generator(1968)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1968}

```{r}
#| label: tbl-citation-rank-1968
#| tbl-cap: Citation rank for widely cited articles from 1968.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1968}

```{r}
#| label: fig-citation-spaghetti-1968
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1968.
#| cache: TRUE

rolling_spaghetti_graph(1968)
```

```{r}
#| label: fig-citation-facet-1968
#| fig-cap: Faceted version of @fig-citation-spaghetti-1968.
#| cache: TRUE

rolling_facet_graph(1968)
```

\newpage


## 1969 {#sec-s1969}

### Widely Cited Articles {-}

1. Harry G. Frankfurt (1969) "Alternate Possibilities and Moral Responsibility," _Journal Of Philosophy_ 66 (23): 829-839 1969.
2. HP Grice (1969) "Utterer's Meaning and Intentions," _Philosophical Review_ 78 (2): 147-177 1969.
3. Keith Lehrer and Thomas Paxson Jr. (1969) "Knowledge: Undefeated Justified True Belief," _Journal Of Philosophy_ 66 (8): 225-237 1969.
4. Bas C. van Fraassen (1969) "Facts and Tautological Entailments," _Journal Of Philosophy_ 66 (15): 477-487 1969.
5. JA Goguen (1969) "The Logic of Inexact Concepts," _Synthese_ 19 (3-4): 325-373 1969.

### Citation Count {-#sec-count-1969}

```{r}
#| label: tbl-citation-count-1969
#| tbl-cap: Citation count for widely cited articles from 1969.

year_cites <- rank_table_generator(1969)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1969}

```{r}
#| label: tbl-citation-rank-1969
#| tbl-cap: Citation rank for widely cited articles from 1969.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1969}

```{r}
#| label: fig-citation-spaghetti-1969
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1969.
#| cache: TRUE

rolling_spaghetti_graph(1969)
```

```{r}
#| label: fig-citation-facet-1969
#| fig-cap: Faceted version of @fig-citation-spaghetti-1969.
#| cache: TRUE

rolling_facet_graph(1969)
```

\newpage


## 1970 {#sec-s1970}

### Widely Cited Articles {-}

1. Fred Dretske (1970) "Epistemic Operators," _Journal Of Philosophy_ 67 (24): 1007-1023 1970.
2. David Lewis (1970) "How To Define Theoretical Terms," _Journal Of Philosophy_ 67 (13): 427-446 1970.
3. KL Walton (1970) "Categories of Art," _Philosophical Review_ 79 (3): 334-367 1970.
4. Robert Stalnaker (1970) "Probability and Conditionals," _Philosophy Of Science_ 37 (1): 64-& 1970.
5. Sydney Shoemaker (1970) "Persons and Their Pasts," _American Philosophical Quarterly_ 7 (4): 269-285 1970.
6. W. V. Quine (1970) "On the Reasons for Indeterminacy of Translation," _Journal Of Philosophy_ 67 (6): 178-183 1970.
7. VANFRAAS.BC NA (1970) "On Extension of Beths Semantics of Physical Theories," _Philosophy Of Science_ 37 (3): 325-& 1970.
8. Richard Rorty (1970) "Incorrigibility as Mark of Mental," _Journal Of Philosophy_ 67 (12): 399-424 1970.

### Citation Count {-#sec-count-1970}

```{r}
#| label: tbl-citation-count-1970
#| tbl-cap: Citation count for widely cited articles from 1970.

year_cites <- rank_table_generator(1970)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1970}

```{r}
#| label: tbl-citation-rank-1970
#| tbl-cap: Citation rank for widely cited articles from 1970.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1970}

```{r}
#| label: fig-citation-spaghetti-1970
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1970.
#| cache: TRUE

rolling_spaghetti_graph(1970)
```

```{r}
#| label: fig-citation-facet-1970
#| fig-cap: Faceted version of @fig-citation-spaghetti-1970.
#| cache: TRUE

rolling_facet_graph(1970)
```

\newpage


## 1971 {#sec-s1971}

### Widely Cited Articles {-}

1. Harry G. Frankfurt (1971) "Freedom of the Will and the Concept of a Person," _Journal Of Philosophy_ 68 (1): 5-20 1971.
2. Judith Jarvis Thomson (1971) "A Defense of Abortion," _Philosophy & Public Affairs_ 1 (1): 47-66 1971.
3. Derek Parfit (1971) "Personal Identity," _Philosophical Review_ 80 (1): 3-27 1971.
4. D. C. Dennett (1971) "Intentional Systems," _Journal Of Philosophy_ 68 (4): 87-106 1971.
5. David Lewis (1971) "Counterparts of Persons and Their Bodies," _Journal Of Philosophy_ 68 (7): 203-211 1971.
6. George Boolos (1971) "The Iterative Conception of Set," _Journal Of Philosophy_ 68 (8): 215-231 1971.
7. W Alston (1971) "Varieties of Privileged Access," _American Philosophical Quarterly_ 8 (3): 223-241 1971.
8. RE Bales (1971) "Act-Utilitarianism: Account of Right-Making Characteristics or Decision-Making Procedure," _American Philosophical Quarterly_ 8 (3): 257-265 1971.
9. Alvin I. Goldman (1971) "The Individuation of Action," _Journal Of Philosophy_ 68 (21): 761-774 1971.

### Citation Count {-#sec-count-1971}

```{r}
#| label: tbl-citation-count-1971
#| tbl-cap: Citation count for widely cited articles from 1971.

year_cites <- rank_table_generator(1971)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1971}

```{r}
#| label: tbl-citation-rank-1971
#| tbl-cap: Citation rank for widely cited articles from 1971.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1971}

```{r}
#| label: fig-citation-spaghetti-1971
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1971.
#| cache: TRUE

rolling_spaghetti_graph(1971)
```

```{r}
#| label: fig-citation-facet-1971
#| fig-cap: Faceted version of @fig-citation-spaghetti-1971.
#| cache: TRUE

rolling_facet_graph(1971)
```

\newpage


## 1972 {#sec-s1972}

### Widely Cited Articles {-}

1. Peter Singer (1972) "Famine, Affluence, and Morality," _Philosophy & Public Affairs_ 1 (3): 229-243 1972.
2. Hartry Field (1972) "Tarski's Theory of Truth," _Journal Of Philosophy_ 69 (13): 347-375 1972.
3. P Foot (1972) "Morality as a System of Hypothetical Imperatives," _Philosophical Review_ 81 (3): 305-316 1972.
4. NJ Block and Jerry A. Fodor (1972) "What Psychological States Are Not," _Philosophical Review_ 81 (2): 159-181 1972.
5. Fred Dretske (1972) "Contrastive Statements," _Philosophical Review_ 81 (4): 411-437 1972.
6. Richard Rorty (1972) "The World Well Lost," _Journal Of Philosophy_ 69 (19): 649-665 1972.
7. G Dworkin (1972) "Paternalism," _Monist_ 56 (1): 64-84 1972.
8. R Routley and RK Meyer (1972) "The Semantics of Entailment — II," _Journal Of Philosophical Logic_ 1 (1): 53-73 1972.

### Citation Count {-#sec-count-1972}

```{r}
#| label: tbl-citation-count-1972
#| tbl-cap: Citation count for widely cited articles from 1972.

year_cites <- rank_table_generator(1972)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1972}

```{r}
#| label: tbl-citation-rank-1972
#| tbl-cap: Citation rank for widely cited articles from 1972.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1972}

```{r}
#| label: fig-citation-spaghetti-1972
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1972.
#| cache: TRUE

rolling_spaghetti_graph(1972)
```

```{r}
#| label: fig-citation-facet-1972
#| fig-cap: Faceted version of @fig-citation-spaghetti-1972.
#| cache: TRUE

rolling_facet_graph(1972)
```

\newpage


## 1973 {#sec-s1973}

### Widely Cited Articles {-}

1. David Lewis (1973) "Causation," _Journal Of Philosophy_ 70 (17): 556-567 1973.
2. Paul Benacerraf (1973) "Mathematical Truth," _Journal Of Philosophy_ 70 (19): 661-679 1973.
3. L Wright (1973) "Functions," _Philosophical Review_ 82 (2): 139-168 1973.
4. Hilary Putnam (1973) "Meaning and Reference," _Journal Of Philosophy_ 70 (19): 699-711 1973.
5. Hartry Field (1973) "Theory Change and the Indeterminacy of Reference," _Journal Of Philosophy_ 70 (14): 462-481 1973.
6. Jaegwon Kim (1973) "Causation, Nomic Subsumption, and the Concept of Event," _Journal Of Philosophy_ 70 (8): 217-236 1973.
7. Tyler Burge (1973) "Reference and Proper Names," _Journal Of Philosophy_ 70 (14): 425-439 1973.
8. M Walzer (1973) "Political Action: The Problem of Dirty Hands," _Philosophy & Public Affairs_ 2 (2): 160-180 1973.
9. Elie Zahar (1973) "Why Did Einsteins Programme Supersede Lorentzs (I)," _British Journal For The Philosophy Of Science_ 24 (2): 95-123 1973.

### Citation Count {-#sec-count-1973}

```{r}
#| label: tbl-citation-count-1973
#| tbl-cap: Citation count for widely cited articles from 1973.

year_cites <- rank_table_generator(1973)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1973}

```{r}
#| label: tbl-citation-rank-1973
#| tbl-cap: Citation rank for widely cited articles from 1973.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1973}

```{r}
#| label: fig-citation-spaghetti-1973
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1973.
#| cache: TRUE

rolling_spaghetti_graph(1973)
```

```{r}
#| label: fig-citation-facet-1973
#| fig-cap: Faceted version of @fig-citation-spaghetti-1973.
#| cache: TRUE

rolling_facet_graph(1973)
```

\newpage


## 1974 {#sec-s1974}

### Widely Cited Articles {-}

1. Thomas Nagel (1974) "What is It Like To Be a Bat," _Philosophical Review_ 83 (4): 435-450 1974.
2. Michael Friedman (1974) "Explanation and Scientific Understanding," _Journal Of Philosophy_ 71 (1): 5-19 1974.
3. Isaac Levi (1974) "On Indeterminate Probabilities," _Journal Of Philosophy_ 71 (13): 391-418 1974.
4. Keith S. Donnellan (1974) "Speaking of Nothing," _Philosophical Review_ 83 (1): 3-31 1974.
5. C Parsons (1974) "The Liar Paradox," _Journal Of Philosophical Logic_ 3 (4): 381-412 1974.
6. Peter Singer (1974) "Sidgwick and Reflective Equilibrium," _Monist_ 58 (3): 490-517 1974.
7. Michael Devitt (1974) "Singular Terms," _Journal Of Philosophy_ 71 (7): 183-205 1974.

### Citation Count {-#sec-count-1974}

```{r}
#| label: tbl-citation-count-1974
#| tbl-cap: Citation count for widely cited articles from 1974.

year_cites <- rank_table_generator(1974)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1974}

```{r}
#| label: tbl-citation-rank-1974
#| tbl-cap: Citation rank for widely cited articles from 1974.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1974}

```{r}
#| label: fig-citation-spaghetti-1974
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1974.
#| cache: TRUE

rolling_spaghetti_graph(1974)
```

```{r}
#| label: fig-citation-facet-1974
#| fig-cap: Faceted version of @fig-citation-spaghetti-1974.
#| cache: TRUE

rolling_facet_graph(1974)
```

\newpage


## 1975 {#sec-s1975}

### Widely Cited Articles {-}

1. Saul Kripke (1975) "Outline of a Theory of Truth," _Journal Of Philosophy_ 72 (19): 690-716 1975.
2. Robert Cummins (1975) "Functional Analysis," _Journal Of Philosophy_ 72 (20): 741-765 1975.
3. Gary Watson (1975) "Free Agency," _Journal Of Philosophy_ 72 (8): 205-220 1975.
4. A Gibbard (1975) "Contingent Identity," _Journal Of Philosophical Logic_ 4 (2): 187-221 1975.
5. R Stalnaker (1975) "Indicative Conditionals," _Philosophia_ 5 (3): 269-286 1975.
6. Gilbert Harman (1975) "Moral Relativism Defended," _Philosophical Review_ 84 (1): 3-22 1975.
7. DL Grover, JL Camp, and ND Belnap (1975) "A Pro-Sentential Theory of Truth," _Philosophical Studies_ 27 (2): 73-125 1975.
8. GP Hellman and FW Thompson (1975) "Physicalism: Ontology, Determination, and Reduction," _Journal Of Philosophy_ 72 (17): 551-564 1975.
9. D Kaplan (1975) "Sets, Concepts and Extensions: How To Russell a Frege-Church," _Journal Of Philosophy_ 72 (19): 716-729 1975.

### Citation Count {-#sec-count-1975}

```{r}
#| label: tbl-citation-count-1975
#| tbl-cap: Citation count for widely cited articles from 1975.

year_cites <- rank_table_generator(1975)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1975}

```{r}
#| label: tbl-citation-rank-1975
#| tbl-cap: Citation rank for widely cited articles from 1975.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1975}

```{r}
#| label: fig-citation-spaghetti-1975
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1975.
#| cache: TRUE

rolling_spaghetti_graph(1975)
```

```{r}
#| label: fig-citation-facet-1975
#| fig-cap: Faceted version of @fig-citation-spaghetti-1975.
#| cache: TRUE

rolling_facet_graph(1975)
```

\newpage


## 1976 {#sec-s1976}

### Widely Cited Articles {-}

1. Alvin I. Goldman (1976) "Discrimination and Perceptual Knowledge," _Journal Of Philosophy_ 73 (20): 771-791 1976.
2. David Lewis (1976) "Probabilities of Conditionals and Conditional Probabilities," _Philosophical Review_ 85 (3): 297-315 1976.
3. David Lewis (1976) "Paradoxes of Time Travel," _American Philosophical Quarterly_ 13 (2): 145-152 1976.
4. M Stocker (1976) "The Schizophrenia of Modern Ethical Theories," _Journal Of Philosophy_ 73 (14): 453-466 1976.
5. Gilbert Harman (1976) "Practical Reasoning," _Review Of Metaphysics_ 29 (3): 431-463 1976.
6. RC Stalnaker (1976) "Possible Worlds," _Noûs_ 10 (1): 65-75 1976.
7. JM Dunn (1976) "Intuitive Semantics for First-Degree Entailments and Coupled Trees," _Philosophical Studies_ 29 (3): 149-168 1976.
8. Robert Merrihew Adams (1976) "Motive Utilitarianism," _Journal Of Philosophy_ 73 (14): 467-481 1976.
9. B Loar (1976) "The Semantics of Singular Terms," _Philosophical Studies_ 30 (6): 353-377 1976.

### Citation Count {-#sec-count-1976}

```{r}
#| label: tbl-citation-count-1976
#| tbl-cap: Citation count for widely cited articles from 1976.

year_cites <- rank_table_generator(1976)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1976}

```{r}
#| label: tbl-citation-rank-1976
#| tbl-cap: Citation rank for widely cited articles from 1976.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1976}

```{r}
#| label: fig-citation-spaghetti-1976
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1976.
#| cache: TRUE

rolling_spaghetti_graph(1976)
```

```{r}
#| label: fig-citation-facet-1976
#| fig-cap: Faceted version of @fig-citation-spaghetti-1976.
#| cache: TRUE

rolling_facet_graph(1976)
```

\newpage


## 1977 {#sec-s1977}

### Widely Cited Articles {-}

1. John Perry (1977) "Frege on Demonstratives," _Philosophical Review_ 86 (4): 474-497 1977.
2. Stephen L. Darwall (1977) "Two Kinds of Respect," _Ethics_ 88 (1): 36-49 1977.
3. Fred Dretske (1977) "Laws of Nature," _Philosophy Of Science_ 44 (2): 248-268 1977.
4. Michael Tooley (1977) "Nature of Laws," _Canadian Journal Of Philosophy_ 7 (4): 667-698 1977.
5. JM Taurek (1977) "Should the Numbers Count?," _Philosophy & Public Affairs_ 6 (4): 293-316 1977.
6. Tyler Burge (1977) "Belief De Re," _Journal Of Philosophy_ 74 (6): 338-362 1977.
7. C Boorse (1977) "Health as a Theoretical Concept," _Philosophy Of Science_ 44 (4): 542-573 1977.
8. HHartry Field (1977) "Logic, Meaning, and Conceptual Role," _Journal Of Philosophy_ 74 (7): 379-409 1977.
9. Hector-Neri Castañeda (1977) "Perception, Belief, and Structure of Physical Objects and Consciousness," _Synthese_ 35 (3): 285-351 1977.

### Citation Count {-#sec-count-1977}

```{r}
#| label: tbl-citation-count-1977
#| tbl-cap: Citation count for widely cited articles from 1977.

year_cites <- rank_table_generator(1977)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1977}

```{r}
#| label: tbl-citation-rank-1977
#| tbl-cap: Citation rank for widely cited articles from 1977.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1977}

```{r}
#| label: fig-citation-spaghetti-1977
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1977.
#| cache: TRUE

rolling_spaghetti_graph(1977)
```

```{r}
#| label: fig-citation-facet-1977
#| fig-cap: Faceted version of @fig-citation-spaghetti-1977.
#| cache: TRUE

rolling_facet_graph(1977)
```

\newpage


## 1978 {#sec-s1978}

### Widely Cited Articles {-}

1. David Lewis (1978) "Truth in Fiction," _American Philosophical Quarterly_ 15 (1): 37-46 1978.
2. DL Hull (1978) "A Matter of Individuality," _Philosophy Of Science_ 45 (3): 335-360 1978.
3. KL Walton (1978) "Fearing Fictions," _Journal Of Philosophy_ 75 (1): 5-27 1978.
4. SP Stich (1978) "Beliefs and Subdoxastic States," _Philosophy Of Science_ 45 (4): 499-518 1978.
5. Harry G. Frankfurt (1978) "The Problem of Action," _American Philosophical Quarterly_ 15 (2): 157-162 1978.
6. PR Thagard (1978) "The Best Explanation: Criteria for Theory Choice," _Journal Of Philosophy_ 75 (2): 76-92 1978.
7. Jaegwon Kim (1978) "Supervenience and Nomological Incommensurables," _American Philosophical Quarterly_ 15 (2): 149-156 1978.
8. L BonJour (1978) "Can Empirical Knowledge Have a Foundation?," _American Philosophical Quarterly_ 15 (1): 1-13 1978.
9. GS Kavka (1978) "Some Paradoxes of Deterrence," _Journal Of Philosophy_ 75 (6): 285-302 1978.

### Citation Count {-#sec-count-1978}

```{r}
#| label: tbl-citation-count-1978
#| tbl-cap: Citation count for widely cited articles from 1978.

year_cites <- rank_table_generator(1978)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1978}

```{r}
#| label: tbl-citation-rank-1978
#| tbl-cap: Citation rank for widely cited articles from 1978.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1978}

```{r}
#| label: fig-citation-spaghetti-1978
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1978.
#| cache: TRUE

rolling_spaghetti_graph(1978)
```

```{r}
#| label: fig-citation-facet-1978
#| fig-cap: Faceted version of @fig-citation-spaghetti-1978.
#| cache: TRUE

rolling_facet_graph(1978)
```

\newpage


## 1979 {#sec-s1979}

### Widely Cited Articles {-}

1. John Perry (1979) "The Problem of the Essential Indexical," _Noûs_ 13 (1): 3-21 1979.
2. David Lewis (1979) "Attitudes De Dicto and De Se," _Philosophical Review_ 88 (4): 513-543 1979.
3. David Lewis (1979) "Scorekeeping in a Language Game," _Journal Of Philosophical Logic_ 8 (3): 339-359 1979.
4. David Lewis (1979) "Counterfactual Dependence and Time's Arrow," _Noûs_ 13 (4): 455-476 1979.
5. John McDowell (1979) "Virtue and Reason," _Monist_ 62 (3): 331-350 1979.
6. Graham Priest (1979) "The Logic of Paradox," _Journal Of Philosophical Logic_ 8 (2): 219-241 1979.
7. Norman Daniels (1979) "Wide Reflective Equilibrium and Theory Acceptance in Ethics," _Journal Of Philosophy_ 76 (5): 256-282 1979.
8. Nancy Cartwright (1979) "Causal Laws and Effective Strategies," _Noûs_ 13 (4): 419-437 1979.
9. D Lascar and B Poizat (1979) "Introduction To Forking," _Journal Of Symbolic Logic_ 44 (3): 330-350 1979.

### Citation Count {-#sec-count-1979}

```{r}
#| label: tbl-citation-count-1979
#| tbl-cap: Citation count for widely cited articles from 1979.

year_cites <- rank_table_generator(1979)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1979}

```{r}
#| label: tbl-citation-rank-1979
#| tbl-cap: Citation rank for widely cited articles from 1979.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1979}

```{r}
#| label: fig-citation-spaghetti-1979
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1979.
#| cache: TRUE

rolling_spaghetti_graph(1979)
```

```{r}
#| label: fig-citation-facet-1979
#| fig-cap: Faceted version of @fig-citation-spaghetti-1979.
#| cache: TRUE

rolling_facet_graph(1979)
```

\newpage


## 1980 {#sec-s1980}

### Widely Cited Articles {-}

1. John Rawls (1980) "Kantian Constructivism in Moral Theory," _Journal Of Philosophy_ 77 (9): 515-535 1980.
2. M Davies and L Humberstone (1980) "Two Notions of Necessity," _Philosophical Studies_ 38 (1): 1-30 1980.
3. Hilary Putnam (1980) "Models and Reality," _Journal Of Symbolic Logic_ 45 (3): 464-482 1980.
4. J Levinson (1980) "What a Musical Work Is," _Journal Of Philosophy_ 77 (1): 5-28 1980.
5. Elliot Sober (1980) "Evolution, Population Thinking, and Essentialism," _Philosophy Of Science_ 47 (3): 350-383 1980.
6. Ruth Barcan Marcus (1980) "Moral Dilemmas and Consistency," _Journal Of Philosophy_ 77 (3): 121-136 1980.
7. David Lewis (1980) "Veridical Hallucination and Prosthetic Vision," _Australasian Journal Of Philosophy_ 58 (3): 239-249 1980.
8. Norman Daniels (1980) "Reflective Equilibrium and Archimedean Points," _Canadian Journal Of Philosophy_ 10 (1): 83-103 1980.

### Citation Count {-#sec-count-1980}

```{r}
#| label: tbl-citation-count-1980
#| tbl-cap: Citation count for widely cited articles from 1980.

year_cites <- rank_table_generator(1980)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1980}

```{r}
#| label: tbl-citation-rank-1980
#| tbl-cap: Citation rank for widely cited articles from 1980.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1980}

```{r}
#| label: fig-citation-spaghetti-1980
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1980.
#| cache: TRUE

rolling_spaghetti_graph(1980)
```

```{r}
#| label: fig-citation-facet-1980
#| fig-cap: Faceted version of @fig-citation-spaghetti-1980.
#| cache: TRUE

rolling_facet_graph(1980)
```

\newpage


## 1981 {#sec-s1981}

### Widely Cited Articles {-}

1. Paul M. Churchland (1981) "Eliminative Materialism and the Propositional Attitudes," _Journal Of Philosophy_ 78 (2): 67-90 1981.
2. Larry Laudan (1981) "A Confutation of Convergent Realism," _Philosophy Of Science_ 48 (1): 19-49 1981.
3. Philip Kitcher (1981) "Explanatory Unification," _Philosophy Of Science_ 48 (4): 507-531 1981.
4. J Barwise and R Cooper (1981) "Generalized Quantifiers and Natural-Language," _Linguistics And Philosophy_ 4 (2): 159-219 1981.
5. Ronald Dworkin (1981) "What is Equality? Part 2: Equality of Resources," _Philosophy & Public Affairs_ 10 (4): 283-345 1981.
6. David Lewis (1981) "Causal Decision Theory," _Australasian Journal Of Philosophy_ 59 (1): 5-30 1981.
7. P van Inwagen (1981) "The Doctrine of Arbitrary Undetached Parts," _Pacific Philosophical Quarterly_ 62 (2): 123-137 1981.
8. Ronald Dworkin (1981) "What is Equality (I) Equality of Welfare," _Philosophy & Public Affairs_ 10 (3): 185-246 1981.
9. J Dupre (1981) "Natural Kinds and Biological Taxa," _Philosophical Review_ 90 (1): 66-90 1981.

### Citation Count {-#sec-count-1981}

```{r}
#| label: tbl-citation-count-1981
#| tbl-cap: Citation count for widely cited articles from 1981.

year_cites <- rank_table_generator(1981)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1981}

```{r}
#| label: tbl-citation-rank-1981
#| tbl-cap: Citation rank for widely cited articles from 1981.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1981}

```{r}
#| label: fig-citation-spaghetti-1981
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1981.
#| cache: TRUE

rolling_spaghetti_graph(1981)
```

```{r}
#| label: fig-citation-facet-1981
#| fig-cap: Faceted version of @fig-citation-spaghetti-1981.
#| cache: TRUE

rolling_facet_graph(1981)
```

\newpage


## 1982 {#sec-s1982}

### Widely Cited Articles {-}

1. Frank Jackson (1982) "Epiphenomenal Qualia," _Philosophical Quarterly_ 32 (127): 127-136 1982.
2. S Wolf (1982) "Moral Saints," _Journal Of Philosophy_ 79 (8): 419-439 1982.
3. EW Prior, Robert Pargetter, and Frank Jackson (1982) "Three Theses About Dispositions," _American Philosophical Quarterly_ 19 (3): 251-257 1982.
4. C Swoyer (1982) "The Nature of Natural Laws," _Australasian Journal Of Philosophy_ 60 (3): 203-223 1982.
5. Anil Gupta (1982) "Truth and Paradox," _Journal Of Philosophical Logic_ 11 (1): 1-60 1982.
6. David Lewis (1982) "Logic for Equivocators," _Noûs_ 16 (3): 431-441 1982.
7. Jaegwon Kim (1982) "Psychophysical Supervenience," _Philosophical Studies_ 41 (1): 51-70 1982.
8. H Frankfurt (1982) "The Importance of What We Care About," _Synthese_ 53 (2): 257-272 1982.
9. Dudley Shapere (1982) "The Concept of Observation in Science and Philosophy," _Philosophy Of Science_ 49 (4): 485-525 1982.

### Citation Count {-#sec-count-1982}

```{r}
#| label: tbl-citation-count-1982
#| tbl-cap: Citation count for widely cited articles from 1982.

year_cites <- rank_table_generator(1982)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1982}

```{r}
#| label: tbl-citation-rank-1982
#| tbl-cap: Citation rank for widely cited articles from 1982.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1982}

```{r}
#| label: fig-citation-spaghetti-1982
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1982.
#| cache: TRUE

rolling_spaghetti_graph(1982)
```

```{r}
#| label: fig-citation-facet-1982
#| fig-cap: Faceted version of @fig-citation-spaghetti-1982.
#| cache: TRUE

rolling_facet_graph(1982)
```

\newpage


## 1983 {#sec-s1983}

### Widely Cited Articles {-}

1. David Lewis (1983) "New Work for a Theory of Universals," _Australasian Journal Of Philosophy_ 61 (4): 343-377 1983.
2. Joseph Levine (1983) "Materialism and Qualia: The Explanatory Gap," _Pacific Philosophical Quarterly_ 64 (4): 354-361 1983.
3. GS Kavka (1983) "The Toxin Puzzle," _Analysis_ 43 (1): 33-36 1983.
4. Christine M. Korsgaard (1983) "Two Distinctions in Goodness," _Philosophical Review_ 92 (2): 169-195 1983.
5. R Brandom (1983) "Asserting," _Noûs_ 17 (4): 637-650 1983.
6. Judith Jarvis Thomson (1983) "Parthood and Identity Across Time," _Journal Of Philosophy_ 80 (4): 201-220 1983.
7. Hilary Kornblith (1983) "Justified Belief and Epistemically Responsible Action," _Philosophical Review_ 92 (1): 33-48 1983.
8. A Plantinga (1983) "On Existentialism," _Philosophical Studies_ 44 (1): 1-20 1983.
9. Ellery Eells and Elliot Sober (1983) "Probabilistic Causality and the Question of Transitivity," _Philosophy Of Science_ 50 (1): 35-57 1983.

### Citation Count {-#sec-count-1983}

```{r}
#| label: tbl-citation-count-1983
#| tbl-cap: Citation count for widely cited articles from 1983.

year_cites <- rank_table_generator(1983)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1983}

```{r}
#| label: tbl-citation-rank-1983
#| tbl-cap: Citation rank for widely cited articles from 1983.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1983}

```{r}
#| label: fig-citation-spaghetti-1983
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1983.
#| cache: TRUE

rolling_spaghetti_graph(1983)
```

```{r}
#| label: fig-citation-facet-1983
#| fig-cap: Faceted version of @fig-citation-spaghetti-1983.
#| cache: TRUE

rolling_facet_graph(1983)
```

\newpage


## 1984 {#sec-s1984}

### Widely Cited Articles {-}

1. David Lewis (1984) "Putnam's Paradox," _Australasian Journal Of Philosophy_ 62 (3): 221-236 1984.
2. Bas C. van Fraassen (1984) "Belief and the Will," _Journal Of Philosophy_ 81 (5): 235-256 1984.
3. Peter Railton (1984) "Alienation, Consequentialism, and the Demands of Morality," _Philosophy & Public Affairs_ 13 (2): 134-171 1984.
4. George Boolos (1984) "To Be is To Be a Value of a Variable (Or To Be Some Values of Some Variables)," _Journal Of Philosophy_ 81 (8): 430-449 1984.
5. Jaegwon Kim (1984) "Concepts of Supervenience," _Philosophy And Phenomenological Research_ 45 (2): 153-176 1984.
6. Stewart Cohen (1984) "Justification and Truth," _Philosophical Studies_ 46 (3): 279-295 1984.
7. Philip Kitcher (1984) "Species," _Philosophy Of Science_ 51 (2): 308-333 1984.
8. K Mulligan, P Simons, and B Smith (1984) "Truth-Makers + Moments and the 'Tractatus'," _Philosophy And Phenomenological Research_ 44 (3): 287-321 1984.
9. Jerry Fodor (1984) "Observation Reconsidered," _Philosophy Of Science_ 51 (1): 23-43 1984.

### Citation Count {-#sec-count-1984}

```{r}
#| label: tbl-citation-count-1984
#| tbl-cap: Citation count for widely cited articles from 1984.

year_cites <- rank_table_generator(1984)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1984}

```{r}
#| label: tbl-citation-rank-1984
#| tbl-cap: Citation rank for widely cited articles from 1984.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1984}

```{r}
#| label: fig-citation-spaghetti-1984
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1984.
#| cache: TRUE

rolling_spaghetti_graph(1984)
```

```{r}
#| label: fig-citation-facet-1984
#| fig-cap: Faceted version of @fig-citation-spaghetti-1984.
#| cache: TRUE

rolling_facet_graph(1984)
```

\newpage


## 1985 {#sec-s1985}

### Widely Cited Articles {-}

1. Carlos E. Alchourrón, Peter Gärdenfors, and David Makinson (1985) "On the Logic of Theory Change: Partial Meet Contraction and Revision Functions," _Journal Of Symbolic Logic_ 50 (2): 510-530 1985.
2. Richard Feldman and Earl Conee (1985) "Evidentialism," _Philosophical Studies_ 48 (1): 15-34 1985.
3. J Hardwig (1985) "Epistemic Dependence," _Journal Of Philosophy_ 82 (7): 335-349 1985.
4. E McMullin (1985) "Galilean Idealization," _Studies In History And Philosophy Of Science_ 16 (3): 247-273 1985.
5. V McGee (1985) "A Counterexample To Modus Ponens," _Journal Of Philosophy_ 82 (9): 462-471 1985.
6. John Rawls (1985) "Justice as Fairness: Political Not Metaphysical," _Philosophy & Public Affairs_ 14 (3): 223-251 1985.
7. William P. Alston (1985) "Concepts of Epistemic Justification," _Monist_ 68 (1): 57-89 1985.
8. Richard Feldman (1985) "Reliability and Justification," _Monist_ 68 (2): 159-174 1985.
9. Paul M. Churchland (1985) "Reduction, Qualia, and the Direct Introspection of Brain States," _Journal Of Philosophy_ 82 (1): 8-28 1985.

### Citation Count {-#sec-count-1985}

```{r}
#| label: tbl-citation-count-1985
#| tbl-cap: Citation count for widely cited articles from 1985.

year_cites <- rank_table_generator(1985)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1985}

```{r}
#| label: tbl-citation-rank-1985
#| tbl-cap: Citation rank for widely cited articles from 1985.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1985}

```{r}
#| label: fig-citation-spaghetti-1985
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1985.
#| cache: TRUE

rolling_spaghetti_graph(1985)
```

```{r}
#| label: fig-citation-facet-1985
#| fig-cap: Faceted version of @fig-citation-spaghetti-1985.
#| cache: TRUE

rolling_facet_graph(1985)
```

\newpage


## 1986 {#sec-s1986}

### Widely Cited Articles {-}

1. Peter Railton (1986) "Moral Realism," _Philosophical Review_ 95 (2): 163-207 APR 1986.
2. Tyler Burge (1986) "Individualism and Psychology," _Philosophical Review_ 95 (1): 3-45 JAN 1986.
3. Annette Baier (1986) "Trust and Antitrust," _Ethics_ 96 (2): 231-260 JAN 1986.
4. Christine M. Korsgaard (1986) "Skepticism About Practical Reason," _Journal Of Philosophy_ 83 (1): 5-25 JAN 1986.
5. DM Rosenthal (1986) "Two Concepts of Consciousness," _Philosophical Studies_ 49 (3): 329-359 MAY 1986.
6. Frank Jackson and Robert Pargetter (1986) "Oughts, Options, and Actualism," _Philosophical Review_ 95 (2): 233-255 APR 1986.
7. Tyler Burge (1986) "Intellectual Norms and Foundations of Mind," _Journal Of Philosophy_ 83 (12): 697-720 DEC 1986.
8. Ruth Garrett Millikan (1986) "Thoughts Without Laws, Cognitive Science With Content," _Philosophical Review_ 95 (1): 47-80 JAN 1986.

### Citation Count {-#sec-count-1986}

```{r}
#| label: tbl-citation-count-1986
#| tbl-cap: Citation count for widely cited articles from 1986.

year_cites <- rank_table_generator(1986)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1986}

```{r}
#| label: tbl-citation-rank-1986
#| tbl-cap: Citation rank for widely cited articles from 1986.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1986}

```{r}
#| label: fig-citation-spaghetti-1986
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1986.
#| cache: TRUE

rolling_spaghetti_graph(1986)
```

```{r}
#| label: fig-citation-facet-1986
#| fig-cap: Faceted version of @fig-citation-spaghetti-1986.
#| cache: TRUE

rolling_facet_graph(1986)
```

\newpage


## 1987 {#sec-s1987}

### Widely Cited Articles {-}

1. M Smith (1987) "The Humean Theory of Motivation," _Mind_ 96 (381): 36-61 JAN 1987.
2. H Frankfurt (1987) "Equality as a Moral Ideal," _Ethics_ 98 (1): 21-43 OCT 1987.
3. John Bigelow and Robert Pargetter (1987) "Functions," _Journal Of Philosophy_ 84 (4): 181-196 APR 1987.
4. John Earman and John Norton (1987) "What Price Spacetime Substantivalism: The Hole Story," _British Journal For The Philosophy Of Science_ 38 (4): 515-525 DEC 1987.
5. DW Stampe (1987) "The Authority of Desire," _Philosophical Review_ 96 (3): 335-381 JUL 1987.
6. LS Temkin (1987) "Intransitivity and the Mere Addition Paradox," _Philosophy & Public Affairs_ 16 (2): 138-187 SPR 1987.
7. Thomas Nagel (1987) "Moral Conflict and Political Legitimacy," _Philosophy & Public Affairs_ 16 (3): 215-240 SUM 1987.
8. M Gilbert (1987) "Modeling Collective Belief," _Synthese_ 73 (1): 185-204 OCT 1987.
9. Larry Laudan (1987) "Progress or Rationality: The Prospects for Normative Naturalism," _American Philosophical Quarterly_ 24 (1): 19-31 JAN 1987.

### Citation Count {-#sec-count-1987}

```{r}
#| label: tbl-citation-count-1987
#| tbl-cap: Citation count for widely cited articles from 1987.

year_cites <- rank_table_generator(1987)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1987}

```{r}
#| label: tbl-citation-rank-1987
#| tbl-cap: Citation rank for widely cited articles from 1987.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1987}

```{r}
#| label: fig-citation-spaghetti-1987
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1987.
#| cache: TRUE

rolling_spaghetti_graph(1987)
```

```{r}
#| label: fig-citation-facet-1987
#| fig-cap: Faceted version of @fig-citation-spaghetti-1987.
#| cache: TRUE

rolling_facet_graph(1987)
```

\newpage


## 1988 {#sec-s1988}

### Widely Cited Articles {-}

1. Tyler Burge (1988) "Individualism and Self-Knowledge," _Journal Of Philosophy_ 85 (11): 649-663 NOV 1988.
2. James Bogen and James Woodward (1988) "Saving the Phenomena," _Philosophical Review_ 97 (3): 303-352 JUL 1988.
3. A Grove (1988) "Two Modelings for Theory Change," _Journal Of Philosophical Logic_ 17 (2): 157-170 MAY 1988.
4. K Sterelny and Philip Kitcher (1988) "The Return of the Gene," _Journal Of Philosophy_ 85 (7): 339-361 JUL 1988.
5. S Kagan (1988) "The Additive Fallacy," _Ethics_ 99 (1): 5-31 OCT 1988.
6. William P. Alston (1988) "An Internalist Externalism," _Synthese_ 74 (3): 265-283 MAR 1988.
7. David Lewis (1988) "Desire as Belief," _Mind_ 97 (387): 323-332 JUL 1988.
8. Frank Jackson and Philip Pettit (1988) "Functionalism and Broad Content," _Mind_ 97 (387): 381-400 JUL 1988.
9. John Rawls (1988) "The Priority of Right and Ideas of the Good," _Philosophy & Public Affairs_ 17 (4): 251-276 FAL 1988.

### Citation Count {-#sec-count-1988}

```{r}
#| label: tbl-citation-count-1988
#| tbl-cap: Citation count for widely cited articles from 1988.

year_cites <- rank_table_generator(1988)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1988}

```{r}
#| label: tbl-citation-rank-1988
#| tbl-cap: Citation rank for widely cited articles from 1988.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1988}

```{r}
#| label: fig-citation-spaghetti-1988
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1988.
#| cache: TRUE

rolling_spaghetti_graph(1988)
```

```{r}
#| label: fig-citation-facet-1988
#| fig-cap: Faceted version of @fig-citation-spaghetti-1988.
#| cache: TRUE

rolling_facet_graph(1988)
```

\newpage


## 1989 {#sec-s1989}

### Widely Cited Articles {-}

1. G. A. Cohen (1989) "On the Currency of Egalitarian Justice," _Ethics_ 99 (4): 906-944 JUL 1989.
2. Ruth Garrett Millikan (1989) "In Defense of Proper Functions," _Philosophy Of Science_ 56 (2): 288-302 JUN 1989.
3. Ruth Garrett Millikan (1989) "Biosemantics," _Journal Of Philosophy_ 86 (6): 281-297 JUN 1989.
4. Paul A. Boghossian and J. David Velleman (1989) "Color as a Secondary Quality," _Mind_ 98 (389): 81-103 JAN 1989.
5. RJ Arneson (1989) "Equality and Equal Opportunity for Welfare," _Philosophical Studies_ 56 (1): 77-93 MAY 1989.
6. Paul A. Boghossian (1989) "The Rule-Following Considerations," _Mind_ 98 (392): 507-549 OCT 1989.
7. M Crimmins and John Perry (1989) "The Prince and the Phone Booth: Reporting Puzzling Beliefs," _Journal Of Philosophy_ 86 (12): 685-711 DEC 1989.
8. D Marquis (1989) "Why Abortion is Immoral," _Journal Of Philosophy_ 86 (4): 183-202 APR 1989.
9. WS Quinn (1989) "Actions, Intentions, and Consequences: The Doctrine of Double Effect," _Philosophy & Public Affairs_ 18 (4): 334-351 FAL 1989.

### Citation Count {-#sec-count-1989}

```{r}
#| label: tbl-citation-count-1989
#| tbl-cap: Citation count for widely cited articles from 1989.

year_cites <- rank_table_generator(1989)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1989}

```{r}
#| label: tbl-citation-rank-1989
#| tbl-cap: Citation rank for widely cited articles from 1989.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1989}

```{r}
#| label: fig-citation-spaghetti-1989
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1989.
#| cache: TRUE

rolling_spaghetti_graph(1989)
```

```{r}
#| label: fig-citation-facet-1989
#| fig-cap: Faceted version of @fig-citation-spaghetti-1989.
#| cache: TRUE

rolling_facet_graph(1989)
```

\newpage


## 1990 {#sec-s1990}

### Widely Cited Articles {-}

1. Philip Kitcher (1990) "The Division of Cognitive Labor," _Journal Of Philosophy_ 87 (1): 5-22 JAN 1990.
2. Frank Jackson and Philip Pettit (1990) "Program Explanation: A General Perspective," _Analysis_ 50 (2): 107-117 MAR 1990.
3. Donald Davidson (1990) "The Structure and Content of Truth," _Journal Of Philosophy_ 87 (6): 279-328 JUN 1990.
4. Gideon Rosen (1990) "Modal Fictionalism," _Mind_ 99 (395): 327-354 JUL 1990.
5. Tim Crane and D. H. Mellor (1990) "There is No Question of Physicalism," _Mind_ 99 (394): 185-206 APR 1990.
6. J Dreier (1990) "Internalism and Speaker Relativism," _Ethics_ 101 (1): 6-26 OCT 1990.
7. J Vogel (1990) "Cartesian Skepticism and Inference To the Best Explanation," _Journal Of Philosophy_ 87 (11): 658-666 NOV 1990.
8. Jaegwon Kim (1990) "Supervenience as a Philosophical Concept," _Metaphilosophy_ 21 (1-2): 1-27 JAN-APR 1990.
9. Graeme Forbes (1990) "The Indispensability of Sinn," _Philosophical Review_ 99 (4): 535-563 OCT 1990.

### Citation Count {-#sec-count-1990}

```{r}
#| label: tbl-citation-count-1990
#| tbl-cap: Citation count for widely cited articles from 1990.

year_cites <- rank_table_generator(1990)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1990}

```{r}
#| label: tbl-citation-rank-1990
#| tbl-cap: Citation rank for widely cited articles from 1990.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1990}

```{r}
#| label: fig-citation-spaghetti-1990
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1990.
#| cache: TRUE

rolling_spaghetti_graph(1990)
```

```{r}
#| label: fig-citation-facet-1990
#| fig-cap: Faceted version of @fig-citation-spaghetti-1990.
#| cache: TRUE

rolling_facet_graph(1990)
```

\newpage


## 1991 {#sec-s1991}

### Widely Cited Articles {-}

1. Daniel C. Dennett (1991) "Real Patterns," _Journal Of Philosophy_ 88 (1): 27-51 JAN 1991.
2. Karen Neander (1991) "Functions as Selected Effects: The Conceptual Analyst's Defense," _Philosophy Of Science_ 58 (2): 168-184 JUN 1991.
3. Richard Boyd (1991) "Realism, Anti-foundationalism and the Enthusiasm for Natural Kinds," _Philosophical Studies_ 61 (1-2): 127-148 FEB 1991.
4. Frank Jackson (1991) "Decision-theoretic Consequentialism and the Nearest and Dearest Objection," _Ethics_ 101 (3): 461-482 APR 1991.
5. Judith Jarvis Thomson (1991) "Self-Defense," _Philosophy & Public Affairs_ 20 (4): 283-310 FAL 1991.
6. J Groenendijk and M Stokhof (1991) "Dynamic Predicate Logic," _Linguistics And Philosophy_ 14 (1): 39-100 FEB 1991.
7. J Hardwig (1991) "The Role of Trust in Knowledge," _Journal Of Philosophy_ 88 (12): 693-708 DEC 1991.
8. Stephen Schiffer (1991) "Ceteris Paribus Laws," _Mind_ 100 (397): 1-17 JAN 1991.
9. Jerry A. Fodor (1991) "A Modal Argument for Narrow Content," _Journal Of Philosophy_ 88 (1): 5-26 JAN 1991.

### Citation Count {-#sec-count-1991}

```{r}
#| label: tbl-citation-count-1991
#| tbl-cap: Citation count for widely cited articles from 1991.

year_cites <- rank_table_generator(1991)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1991}

```{r}
#| label: tbl-citation-rank-1991
#| tbl-cap: Citation rank for widely cited articles from 1991.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1991}

```{r}
#| label: fig-citation-spaghetti-1991
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1991.
#| cache: TRUE

rolling_spaghetti_graph(1991)
```

```{r}
#| label: fig-citation-facet-1991
#| fig-cap: Faceted version of @fig-citation-spaghetti-1991.
#| cache: TRUE

rolling_facet_graph(1991)
```

\newpage


## 1992 {#sec-s1992}

### Widely Cited Articles {-}

1. Stephen Yablo (1992) "Mental Causation," _Philosophical Review_ 101 (2): 245-280 APR 1992.
2. Mark Johnston (1992) "How To Speak of the Colors," _Philosophical Studies_ 68 (3): 221-263 DEC 1992.
3. Keith DeRose (1992) "Contextualism and Knowledge Attributions," _Philosophy And Phenomenological Research_ 52 (4): 913-929 DEC 1992.
4. Jaegwon Kim (1992) "Multiple Realization and the Metaphysics of Reduction," _Philosophy And Phenomenological Research_ 52 (1): 1-26 MAR 1992.
5. ME Bratman (1992) "Shared Cooperative Activity," _Philosophical Review_ 101 (2): 327-340 APR 1992.
6. Philip Kitcher (1992) "The Naturalists Return," _Philosophical Review_ 101 (1): 53-114 JAN 1992.
7. R Foley (1992) "The Epistemology of Belief and the Epistemology of Degrees of Belief," _American Philosophical Quarterly_ 29 (2): 111-124 APR 1992.
8. Stephen Schiffer (1992) "Belief Ascription," _Journal Of Philosophy_ 89 (10): 499-521 OCT 1992.
9. Michael B. Burke (1992) "Copper Statues and Pieces of Copper: A Challenge To the Standard Account," _Analysis_ 52 (1): 12-17 JAN 1992.

### Citation Count {-#sec-count-1992}

```{r}
#| label: tbl-citation-count-1992
#| tbl-cap: Citation count for widely cited articles from 1992.

year_cites <- rank_table_generator(1992)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1992}

```{r}
#| label: tbl-citation-rank-1992
#| tbl-cap: Citation rank for widely cited articles from 1992.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1992}

```{r}
#| label: fig-citation-spaghetti-1992
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1992.
#| cache: TRUE

rolling_spaghetti_graph(1992)
```

```{r}
#| label: fig-citation-facet-1992
#| fig-cap: Faceted version of @fig-citation-spaghetti-1992.
#| cache: TRUE

rolling_facet_graph(1992)
```

\newpage


## 1993 {#sec-s1993}

### Widely Cited Articles {-}

1. Tyler Burge (1993) "Content Preservation," _Philosophical Review_ 102 (4): 457-488 OCT 1993.
2. Stephen Yablo (1993) "Is Conceivability a Guide To Possibility," _Philosophy And Phenomenological Research_ 53 (1): 1-42 MAR 1993.
3. Rae Langton (1993) "Speech Acts and Unspeakable Acts," _Philosophy & Public Affairs_ 22 (4): 293-330 FAL 1993.
4. Stephen Yablo (1993) "Paradox Without Self-Reference," _Analysis_ 53 (4): 251-252 OCT 1993.
5. ME Bratman (1993) "Shared Intention," _Ethics_ 104 (1): 97-113 OCT 1993.
6. T Horgan (1993) "From Supervenience To Superdupervenience: Meeting the Demands of a Material World," _Mind_ 102 (408): 554-586 OCT 1993.
7. D Braun (1993) "Empty Names," _Noûs_ 27 (4): 449-469 DEC 1993.
8. P. E. Griffiths (1993) "Functional Analysis and Proper Functions," _British Journal For The Philosophy Of Science_ 44 (3): 409-422 SEP 1993.
9. F Dretske (1993) "Conscious Experience," _Mind_ 102 (406): 263-283 APR 1993.

### Citation Count {-#sec-count-1993}

```{r}
#| label: tbl-citation-count-1993
#| tbl-cap: Citation count for widely cited articles from 1993.

year_cites <- rank_table_generator(1993)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1993}

```{r}
#| label: tbl-citation-rank-1993
#| tbl-cap: Citation rank for widely cited articles from 1993.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1993}

```{r}
#| label: fig-citation-spaghetti-1993
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1993.
#| cache: TRUE

rolling_spaghetti_graph(1993)
```

```{r}
#| label: fig-citation-facet-1993
#| fig-cap: Faceted version of @fig-citation-spaghetti-1993.
#| cache: TRUE

rolling_facet_graph(1993)
```

\newpage


## 1994 {#sec-s1994}

### Widely Cited Articles {-}

1. David Lewis (1994) "Humean Supervenience Debugged," _Mind_ 103 (412): 473-490 OCT 1994.
2. C. B. Martin (1994) "Dispositions and Conditionals," _Philosophical Quarterly_ 44 (174): 1-8 JAN 1994.
3. Malcom Forster and Elliot Sober (1994) "How To Tell When Simpler, More Unified, or Less _Ad Hoc_ Theories Will Provide More Accurate Predictions," _British Journal For The Philosophy Of Science_ 45 (1): 1-35 MAR 1994.
4. Hartry Field (1994) "Deflationist Views of Meaning and Content," _Mind_ 103 (411): 249-285 JUL 1994.
5. P Godfrey-Smith (1994) "A Modern History Theory of Functions," _Noûs_ 28 (3): 344-362 SEP 1994.
6. R Holton (1994) "Deciding To Trust, Coming To Believe," _Australasian Journal Of Philosophy_ 72 (1): 63-76 MAR 1994.
7. R Audi (1994) "Dispositional Beliefs and Dispositions To Believe," _Noûs_ 28 (4): 419-434 DEC 1994.
8. G Strawson (1994) "The Impossibility of Moral Responsibility," _Philosophical Studies_ 75 (1-2): 5-24 AUG 1994.
9. P. E. Griffiths and R. D. Gray (1994) "Developmental Systems and Evolutionary Explanation," _Journal Of Philosophy_ 91 (6): 277-304 JUN 1994.

### Citation Count {-#sec-count-1994}

```{r}
#| label: tbl-citation-count-1994
#| tbl-cap: Citation count for widely cited articles from 1994.

year_cites <- rank_table_generator(1994)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1994}

```{r}
#| label: tbl-citation-rank-1994
#| tbl-cap: Citation rank for widely cited articles from 1994.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1994}

```{r}
#| label: fig-citation-spaghetti-1994
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1994.
#| cache: TRUE

rolling_spaghetti_graph(1994)
```

```{r}
#| label: fig-citation-facet-1994
#| fig-cap: Faceted version of @fig-citation-spaghetti-1994.
#| cache: TRUE

rolling_facet_graph(1994)
```

\newpage


## 1995 {#sec-s1995}

### Widely Cited Articles {-}

1. Keith DeRose (1995) "Solving the Skeptical Problem," _Philosophical Review_ 104 (1): 1-52 JAN 1995.
2. Dorothy Edgington (1995) "On Conditionals," _Mind_ 104 (414): 235-329 APR 1995.
3. T van Gelder (1995) "What Might Cognition Be, If Not Computation," _Journal Of Philosophy_ 92 (7): 345-381 JUL 1995.
4. D Widerker (1995) "Libertarianism and Frankfurt's Attack on the Principle of Alternative Possibilities," _Philosophical Review_ 104 (2): 247-261 APR 1995.
5. Dean W. Zimmerman (1995) "Theories of Masses and Problems of Constitution," _Philosophical Review_ 104 (1): 53-110 JAN 1995.
6. N Chomsky (1995) "Language and Nature," _Mind_ 104 (413): 1-61 JAN 1995.
7. Karen Neander (1995) "Misrepresenting and Malfunctioning," _Philosophical Studies_ 79 (2): 109-141 AUG 1995.
8. John McDowell (1995) "Knowledge and the Internal," _Philosophy And Phenomenological Research_ 55 (4): 877-893 DEC 1995.
9. Kit Fine (1995) "The Logic of Essence," _Journal Of Philosophical Logic_ 24 (3): 241-273 JUN 1995.

### Citation Count {-#sec-count-1995}

```{r}
#| label: tbl-citation-count-1995
#| tbl-cap: Citation count for widely cited articles from 1995.

year_cites <- rank_table_generator(1995)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1995}

```{r}
#| label: tbl-citation-rank-1995
#| tbl-cap: Citation rank for widely cited articles from 1995.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1995}

```{r}
#| label: fig-citation-spaghetti-1995
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1995.
#| cache: TRUE

rolling_spaghetti_graph(1995)
```

```{r}
#| label: fig-citation-facet-1995
#| fig-cap: Faceted version of @fig-citation-spaghetti-1995.
#| cache: TRUE

rolling_facet_graph(1995)
```

\newpage


## 1996 {#sec-s1996}

### Widely Cited Articles {-}

1. David Lewis (1996) "Elusive Knowledge," _Australasian Journal Of Philosophy_ 74 (4): 549-567 DEC 1996.
2. Timothy Williamson (1996) "Knowing and Asserting," _Philosophical Review_ 105 (4): 489-523 OCT 1996.
3. F Veltman (1996) "Defaults in Update Semantics," _Journal Of Philosophical Logic_ 25 (3): 221-261 JUN 1996.
4. Karen Jones (1996) "Trust as An Affective Attitude," _Ethics_ 107 (1): 4-25 OCT 1996.
5. Ronald Dworkin (1996) "Objectivity and Truth: You'd Better Believe It," _Philosophy & Public Affairs_ 25 (2): 87-139 SPR 1996.
6. Paul A. Boghossian (1996) "Analyticity Reconsidered," _Noûs_ 30 (3): 360-391 SEP 1996.
7. Theodore Sider (1996) "All the World's a Stage," _Australasian Journal Of Philosophy_ 74 (3): 433-453 SEP 1996.
8. A Oliver (1996) "The Metaphysics of Properties," _Mind_ 105 (417): 1-80 JAN 1996.
9. Donald Davidson (1996) "The Folly of Trying To Define Truth," _Journal Of Philosophy_ 93 (6): 263-278 JUN 1996.

### Citation Count {-#sec-count-1996}

```{r}
#| label: tbl-citation-count-1996
#| tbl-cap: Citation count for widely cited articles from 1996.

year_cites <- rank_table_generator(1996)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1996}

```{r}
#| label: tbl-citation-rank-1996
#| tbl-cap: Citation rank for widely cited articles from 1996.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1996}

```{r}
#| label: fig-citation-spaghetti-1996
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1996.
#| cache: TRUE

rolling_spaghetti_graph(1996)
```

```{r}
#| label: fig-citation-facet-1996
#| fig-cap: Faceted version of @fig-citation-spaghetti-1996.
#| cache: TRUE

rolling_facet_graph(1996)
```

\newpage


## 1997 {#sec-s1997}

### Widely Cited Articles {-}

1. David Lewis (1997) "Finkish Dispositions," _Philosophical Quarterly_ 47 (187): 143-158 APR 1997.
2. Derek Parfit (1997) "Equality and Priority," _Ratio_ 10 (3): 202-221 DEC 1997.
3. LR Baker (1997) "Why Constitution is Not Identity," _Journal Of Philosophy_ 94 (12): 599-621 DEC 1997.
4. R Audi (1997) "The Place of Testimony in the Fabric of Knowledge and Justification," _American Philosophical Quarterly_ 34 (4): 405-422 OCT 1997.
5. CS Hill (1997) "Imaginability, Conceivability, Possibility and the Mind-Body Problem," _Philosophical Studies_ 87 (1): 61-85 JUL 1997.
6. Tyler Burge (1997) "Interlocution, Perception, and Memory," _Philosophical Studies_ 86 (1): 21-47 APR 1997.
7. RM Sainsbury (1997) "Easy Possibilities," _Philosophy And Phenomenological Research_ 57 (4): 907-919 DEC 1997.
8. S Wolf (1997) "Happiness and Meaning: Two Aspects of the Good Life," _Social Philosophy & Policy_ 14 (1): 207-225 WIN 1997.
9. MJ Zimmerman (1997) "Moral Responsibility and Ignorance," _Ethics_ 107 (3): 410-426 APR 1997.

### Citation Count {-#sec-count-1997}

```{r}
#| label: tbl-citation-count-1997
#| tbl-cap: Citation count for widely cited articles from 1997.

year_cites <- rank_table_generator(1997)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1997}

```{r}
#| label: tbl-citation-rank-1997
#| tbl-cap: Citation rank for widely cited articles from 1997.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1997}

```{r}
#| label: fig-citation-spaghetti-1997
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1997.
#| cache: TRUE

rolling_spaghetti_graph(1997)
```

```{r}
#| label: fig-citation-facet-1997
#| fig-cap: Faceted version of @fig-citation-spaghetti-1997.
#| cache: TRUE

rolling_facet_graph(1997)
```

\newpage


## 1998 {#sec-s1998}

### Widely Cited Articles {-}

1. Andy Clark and David J. Chalmers (1998) "The Extended Mind," _Analysis_ 58 (1): 7-19 JAN 1998.
2. James M. Joyce (1998) "A Nonpragmatic Vindication of Probabilism," _Philosophy Of Science_ 65 (4): 575-603 DEC 1998.
3. J Ladyman (1998) "What is Structural Realism?," _Studies In History And Philosophy Of Science_ 29A (3): 409-424 SEP 1998.
4. Nathan Salmon (1998) "Nonexistence," _Noûs_ 32 (3): 277-319 SEP 1998.
5. Alexander Bird (1998) "Dispositions and Antidotes," _Philosophical Quarterly_ 48 (191): 227-234 APR 1998.
6. Rae Langton and David Lewis (1998) "Defining 'Intrinsic'," _Philosophy And Phenomenological Research_ 58 (2): 333-345 JUN 1998.
7. Earl Conee and Richard Feldman (1998) "The Generality Problem for Reliabilism," _Philosophical Studies_ 89 (1): 1-29 JAN 1998.
8. Judith Jarvis Thomson (1998) "The Statue and the Clay," _Noûs_ 32 (2): 149-173 JUN 1998.
9. John McDowell (1998) "Having the World in View: Sellars, Kant, and Intentionality: Lecture I: Sellars on Perceptual Experience," _Journal Of Philosophy_ 95 (9): 431-450 SEP 1998.

### Citation Count {-#sec-count-1998}

```{r}
#| label: tbl-citation-count-1998
#| tbl-cap: Citation count for widely cited articles from 1998.

year_cites <- rank_table_generator(1998)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1998}

```{r}
#| label: tbl-citation-rank-1998
#| tbl-cap: Citation rank for widely cited articles from 1998.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1998}

```{r}
#| label: fig-citation-spaghetti-1998
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1998.
#| cache: TRUE

rolling_spaghetti_graph(1998)
```

```{r}
#| label: fig-citation-facet-1998
#| fig-cap: Faceted version of @fig-citation-spaghetti-1998.
#| cache: TRUE

rolling_facet_graph(1998)
```

\newpage


## 1999 {#sec-s1999}

### Widely Cited Articles {-}

1. Elizabeth S. Anderson (1999) "What is the Point of Equality?," _Ethics_ 109 (2): 287-337 JAN 1999.
2. John Broome (1999) "Normative Requirements," _Ratio_ 12 (4): 398-419 DEC 1999.
3. Ned Block and Robert Stalnaker (1999) "Conceptual Analysis, Dualism, and the Explanatory Gap," _Philosophical Review_ 108 (1): 1-46 JAN 1999.
4. Jaegwon Kim (1999) "Making Sense of Emergence," _Philosophical Studies_ 95 (1-2): 3-36 AUG 1999.
5. W Bechtel and J Mundale (1999) "Multiple Realizability Revisited: Linking Cognitive and Neural States," _Philosophy Of Science_ 66 (2): 175-207 JUN 1999.
6. J. David Velleman (1999) "Love as a Moral Emotion," _Ethics_ 109 (2): 338-374 JAN 1999.
7. Brandon Fitelson (1999) "The Plurality of Bayesian Measures of Confirmation and the Problem of Measure Sensitivity," _Philosophy Of Science_ 66 (3): S362-S378 Suppl. S SEP 1999.
8. Tomoji Shogenji (1999) "Is Coherence Truth Conducive?," _Analysis_ 59 (4): 338-345 OCT 1999.
9. J Hyman (1999) "How Knowledge Works," _Philosophical Quarterly_ 49 (197): 433-451 OCT 1999.

### Citation Count {-#sec-count-1999}

```{r}
#| label: tbl-citation-count-1999
#| tbl-cap: Citation count for widely cited articles from 1999.

year_cites <- rank_table_generator(1999)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-1999}

```{r}
#| label: tbl-citation-rank-1999
#| tbl-cap: Citation rank for widely cited articles from 1999.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-1999}

```{r}
#| label: fig-citation-spaghetti-1999
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 1999.
#| cache: TRUE

rolling_spaghetti_graph(1999)
```

```{r}
#| label: fig-citation-facet-1999
#| fig-cap: Faceted version of @fig-citation-spaghetti-1999.
#| cache: TRUE

rolling_facet_graph(1999)
```

\newpage


## 2000 {#sec-s2000}

### Widely Cited Articles {-}

1. Peter Machamer, Lindley Darden, and Carl F. Craver (2000) "Thinking About Mechanisms," _Philosophy Of Science_ 67 (1): 1-25 MAR 2000.
2. James Pryor (2000) "The Skeptic and the Dogmatist," _Noûs_ 34 (4): 517-549 DEC 2000.
3. Sally Haslanger (2000) "Gender and Race: (What) Are They? (What) Do We Want Them To Be?," _Noûs_ 34 (1): 31-55 MAR 2000.
4. David Lewis (2000) "Causation as Influence," _Journal Of Philosophy_ 97 (4): 182-197 Sp. Iss. SI APR 2000.
5. Justin D'Arms and Dan Jacobson (2000) "The Moralistic Fallacy: On the 'Appropriateness' of Emotions," _Philosophy And Phenomenological Research_ 61 (1): 65-90 JUL 2000.
6. Jason Stanley and Zoltán Gendler Szabó (2000) "On Quantifier Domain Restriction," _Mind & Language_ 15 (2-3): 219-261 APR-JUN 2000.
7. Heather Douglas (2000) "Inductive Risk and Values in Science," _Philosophy Of Science_ 67 (4): 559-579 DEC 2000.
8. Jason Stanley (2000) "Context and Logical Form," _Linguistics And Philosophy_ 23 (4): 391-434 AUG 2000.
9. Adam Elga (2000) "Self-Locating Belief and the 'Sleeping Beauty' Problem," _Analysis_ 60 (2): 143-147 APR 2000.

### Citation Count {-#sec-count-2000}

```{r}
#| label: tbl-citation-count-2000
#| tbl-cap: Citation count for widely cited articles from 2000.

year_cites <- rank_table_generator(2000)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2000}

```{r}
#| label: tbl-citation-rank-2000
#| tbl-cap: Citation rank for widely cited articles from 2000.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2000}

```{r}
#| label: fig-citation-spaghetti-2000
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2000.
#| cache: TRUE

rolling_spaghetti_graph(2000)
```

```{r}
#| label: fig-citation-facet-2000
#| fig-cap: Faceted version of @fig-citation-spaghetti-2000.
#| cache: TRUE

rolling_facet_graph(2000)
```

\newpage


## 2001 {#sec-s2001}

### Widely Cited Articles {-}

1. Jason Stanley and Timothy Williamson (2001) "Knowing How," _Journal Of Philosophy_ 98 (8): 411-444 AUG 2001.
2. Alex Byrne (2001) "Intentionalism Defended," _Philosophical Review_ 110 (2): 199-240 APR 2001.
3. David J. Chalmers and Frank Jackson (2001) "Conceptual Analysis and Reductive Explanation," _Philosophical Review_ 110 (3): 315-360 JUL 2001.
4. Alvin I. Goldman (2001) "Experts: Which Ones Should You Trust?," _Philosophy And Phenomenological Research_ 63 (1): 85-110 JUL 2001.
5. C Hitchcock (2001) "The Intransitivity of Causation Revealed in Equations and Graphs," _Journal Of Philosophy_ 98 (6): 273-299 JUN 2001.
6. Patrick Rysiew (2001) "The Context-Sensitivity of Knowledge Attributions," _Noûs_ 35 (4): 477-514 DEC 2001.
7. F Adams and K Aizawa (2001) "The Bounds of Cognition," _Philosophical Psychology_ 14 (1): 43-64 MAR 2001.
8. Christopher Peacocke (2001) "Does Perception Have a Nonconceptual Content?," _Journal Of Philosophy_ 98 (5): 239-264 MAY 2001.
9. Carl F. Craver (2001) "Role Functions, Mechanisms, and Hierarchy," _Philosophy Of Science_ 68 (1): 53-74 MAR 2001.

### Citation Count {-#sec-count-2001}

```{r}
#| label: tbl-citation-count-2001
#| tbl-cap: Citation count for widely cited articles from 2001.

year_cites <- rank_table_generator(2001)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2001}

```{r}
#| label: tbl-citation-rank-2001
#| tbl-cap: Citation rank for widely cited articles from 2001.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2001}

```{r}
#| label: fig-citation-spaghetti-2001
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2001.
#| cache: TRUE

rolling_spaghetti_graph(2001)
```

```{r}
#| label: fig-citation-facet-2001
#| fig-cap: Faceted version of @fig-citation-spaghetti-2001.
#| cache: TRUE

rolling_facet_graph(2001)
```

\newpage


## 2002 {#sec-s2002}

### Widely Cited Articles {-}

1. Michael G. F. Martin (2002) "The Transparency of Experience," _Mind & Language_ 17 (4): 376-425 SEP 2002.
2. Jeremy Fantl and Matthew McGrath (2002) "Evidence, Pragmatics, and Justification," _Philosophical Review_ 111 (1): 67-94 JAN 2002.
3. R Stalnaker (2002) "Common Ground (Speaker Presupposition)," _Linguistics And Philosophy_ 25 (5-6): 701-721 DEC 2002.
4. Stuart Glennan (2002) "Rethinking Mechanistic Explanation," _Philosophy Of Science_ 69 (3): S342-S353 Suppl. S SEP 2002.
5. Stewart Cohen (2002) "Basic Knowledge and the Problem of Easy Knowledge," _Philosophy And Phenomenological Research_ 65 (2): 309-329 SEP 2002.
6. Ruth Chang (2002) "The Possibility of Parity," _Ethics_ 112 (4): 659-688 JUL 2002.
7. C Wright (2002) "(Anti-)Sceptics Simple and Subtle: G.E. Moore and John McDowell," _Philosophy And Phenomenological Research_ 65 (2): 330-348 SEP 2002.
8. Mohan Matthen and André Ariew (2002) "Two Ways of Thinking About Fitness and Natural Selection," _Journal Of Philosophy_ 99 (2): 55-83 FEB 2002.
9. C List and Philip Pettit (2002) "Aggregating Sets of Judgments: An Impossibility Result," _Economics And Philosophy_ 18 (1): 89-110 APR 2002.

### Citation Count {-#sec-count-2002}

```{r}
#| label: tbl-citation-count-2002
#| tbl-cap: Citation count for widely cited articles from 2002.

year_cites <- rank_table_generator(2002)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2002}

```{r}
#| label: tbl-citation-rank-2002
#| tbl-cap: Citation rank for widely cited articles from 2002.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2002}

```{r}
#| label: fig-citation-spaghetti-2002
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2002.
#| cache: TRUE

rolling_spaghetti_graph(2002)
```

```{r}
#| label: fig-citation-facet-2002
#| fig-cap: Faceted version of @fig-citation-spaghetti-2002.
#| cache: TRUE

rolling_facet_graph(2002)
```

\newpage


## 2003 {#sec-s2003}

### Widely Cited Articles {-}

1. Keith DeRose (2003) "Assertion, Knowledge, and Context," _Philosophical Review_ 111 (2): 167-203 APR 2003.
2. Nishi Shah (2003) "How Truth Governs Belief," _Philosophical Review_ 112 (4): 447-482 OCT 2003.
3. Joshua Knobe (2003) "Intentional Action and Side Effects in Ordinary Language," _Analysis_ 63 (3): 190-194 JUL 2003.
4. A Hájek (2003) "What Conditional Probability Could Not Be," _Synthese_ 137 (3): 273-323 DEC 2003.
5. Tyler Burge (2003) "Perceptual Entitlement," _Philosophy And Phenomenological Research_ 67 (3): 503-548 NOV 2003.
6. Thomas Kelly (2003) "Epistemic Rationality as Instrumental Rationality: A Critique," _Philosophy And Phenomenological Research_ 66 (3): 612-640 MAY 2003.
7. Jonathan Schaffer (2003) "Is There a Fundamental Level?," _Noûs_ 37 (3): 498-517 SEP 2003.
8. John MacFarlane (2003) "Future Contingents and Relative Truth," _Philosophical Quarterly_ 53 (212): 321-336 JUL 2003.
9. Kit Fine (2003) "The Non-Identity of a Material Thing and Its Matter," _Mind_ 112 (446): 195-234 APR 2003.

### Citation Count {-#sec-count-2003}

```{r}
#| label: tbl-citation-count-2003
#| tbl-cap: Citation count for widely cited articles from 2003.

year_cites <- rank_table_generator(2003)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2003}

```{r}
#| label: tbl-citation-rank-2003
#| tbl-cap: Citation rank for widely cited articles from 2003.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2003}

```{r}
#| label: fig-citation-spaghetti-2003
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2003.
#| cache: TRUE

rolling_spaghetti_graph(2003)
```

```{r}
#| label: fig-citation-facet-2003
#| fig-cap: Faceted version of @fig-citation-spaghetti-2003.
#| cache: TRUE

rolling_facet_graph(2003)
```

\newpage


## 2004 {#sec-s2004}

### Widely Cited Articles {-}

1. Wlodek Rabinowicz and Toni Rønnow‐Rasmussen (2004) "The Strike of the Demon: On Fitting Pro-Attitudes and Value," _Ethics_ 114 (3): 391-423 APR 2004.
2. Charles Travis (2004) "The Silence of the Senses," _Mind_ 113 (449): 57-94 JAN 2004.
3. Michael G. F. Martin (2004) "The Limits of Self-Awareness," _Philosophical Studies_ 120 (1-3): 37-89 JUL-SEP 2004.
4. David Pitt (2004) "The Phenomenology of Cognition, Or, What is It Like To Think That P?," _Philosophy And Phenomenological Research_ 69 (1): 1-36 JUL 2004.
5. RD Rupert (2004) "Challenges To the Hypothesis of Extended Cognition," _Journal Of Philosophy_ 101 (8): 389-428 AUG 2004.
6. Mark Johnston (2004) "The Obscure Object of Hallucination," _Philosophical Studies_ 120 (1-3): 113-183 JUL-SEP 2004.
7. RN Giere (2004) "How Models Are Used To Represent Reality," _Philosophy Of Science_ 71 (5): 742-752 DEC 2004.
8. David J. Chalmers (2004) "Epistemic Two-Dimensional Semantics," _Philosophical Studies_ 118 (1-2): 153-226 MAR 2004.
9. J Mcmahan (2004) "The Ethics of Killing in War," _Ethics_ 114 (4): 693-733 JUL 2004.

### Citation Count {-#sec-count-2004}

```{r}
#| label: tbl-citation-count-2004
#| tbl-cap: Citation count for widely cited articles from 2004.

year_cites <- rank_table_generator(2004)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2004}

```{r}
#| label: tbl-citation-rank-2004
#| tbl-cap: Citation rank for widely cited articles from 2004.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2004}

```{r}
#| label: fig-citation-spaghetti-2004
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2004.
#| cache: TRUE

rolling_spaghetti_graph(2004)
```

```{r}
#| label: fig-citation-facet-2004
#| fig-cap: Faceted version of @fig-citation-spaghetti-2004.
#| cache: TRUE

rolling_facet_graph(2004)
```

\newpage


## 2005 {#sec-s2005}

### Widely Cited Articles {-}

1. Nico Kolodny (2005) "Why Be Rational?," _Mind_ 114 (455): 509-563 JUL 2005.
2. Nishi Shah and J. David Velleman (2005) "Doxastic Deliberation," _Philosophical Review_ 114 (4): 497-534 OCT 2005.
3. Angela M. Smith (2005) "Responsibility for Attitudes: Activity and Passivity in Mental Life," _Ethics_ 115 (2): 236-271 JAN 2005.
4. P Lasersohn (2005) "Context Dependence, Disagreement, and Predicates of Personal Taste," _Linguistics And Philosophy_ 28 (6): 643-686 DEC 2005.
5. Pamela Hieronymi (2005) "The Wrong Kind of Reason," _Journal Of Philosophy_ 102 (9): 437-457 SEP 2005.
6. Matthew Weiner (2005) "Must We Know What We Say?," _Philosophical Review_ 114 (2): 227-251 APR 2005.
7. Alan Baker (2005) "Are There Genuine Mathematical Explanations of Physical Phenomena?," _Mind_ 114 (454): 223-238 APR 2005.
8. Timothy Williamson (2005) "Contextualism, Subject-Sensitive Invariantism and Knowledge of Knowledge," _Philosophical Quarterly_ 55 (219): 213-235 APR 2005.
9. E Nahmias, S Morris, T Nadelhoffer, and J Turner (2005) "Surveying Freedom: Folk Intuitions About Free Will and Moral Responsibility," _Philosophical Psychology_ 18 (5): 561-584 OCT 2005.

### Citation Count {-#sec-count-2005}

```{r}
#| label: tbl-citation-count-2005
#| tbl-cap: Citation count for widely cited articles from 2005.

year_cites <- rank_table_generator(2005)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2005}

```{r}
#| label: tbl-citation-rank-2005
#| tbl-cap: Citation rank for widely cited articles from 2005.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2005}

```{r}
#| label: fig-citation-spaghetti-2005
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2005.
#| cache: TRUE

rolling_spaghetti_graph(2005)
```

```{r}
#| label: fig-citation-facet-2005
#| fig-cap: Faceted version of @fig-citation-spaghetti-2005.
#| cache: TRUE

rolling_facet_graph(2005)
```

\newpage


## 2006 {#sec-s2006}

### Widely Cited Articles {-}

1. Sharon Street (2006) "A Darwinian Dilemma for Realist Theories of Value," _Philosophical Studies_ 127 (1): 109-166 Sp. Iss. SI JAN 2006.
2. Hilary Greaves and David Wallace (2006) "Justifying Conditionalization: Conditionalization Maximizes Expected Epistemic Utility," _Mind_ 115 (459): 607-632 JUL 2006.
3. Igor Douven (2006) "Assertion, Knowledge, and Rational Credibility," _Philosophical Review_ 115 (4): 449-485 OCT 2006.
4. Carl F. Craver (2006) "When Mechanistic Models Explain," _Synthese_ 153 (3): 355-376 DEC 2006.
5. Peter Godfrey-Smith (2006) "The Strategy of Model-Based Science," _Biology & Philosophy_ 21 (5): 725-740 NOV 2006.
6. Roger White (2006) "Problems for Dogmatism," _Philosophical Studies_ 131 (3): 525-557 DEC 2006.
7. David Enoch (2006) "Agency, Shmagency: Why Normativity Won't Come From What is Constitutive of Action," _Philosophical Review_ 115 (2): 169-198 APR 2006.
8. Nishi Shah (2006) "A New Argument for Evidentialism," _Philosophical Quarterly_ 56 (225): 481-498 OCT 2006.
9. Joshua Knobe (2006) "The Concept of Intentional Action: A Case Study in the Uses of Folk Psychology," _Philosophical Studies_ 130 (2): 203-231 AUG 2006.

### Citation Count {-#sec-count-2006}

```{r}
#| label: tbl-citation-count-2006
#| tbl-cap: Citation count for widely cited articles from 2006.

year_cites <- rank_table_generator(2006)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2006}

```{r}
#| label: tbl-citation-rank-2006
#| tbl-cap: Citation rank for widely cited articles from 2006.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2006}

```{r}
#| label: fig-citation-spaghetti-2006
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2006.
#| cache: TRUE

rolling_spaghetti_graph(2006)
```

```{r}
#| label: fig-citation-facet-2006
#| fig-cap: Faceted version of @fig-citation-spaghetti-2006.
#| cache: TRUE

rolling_facet_graph(2006)
```

\newpage


## 2007 {#sec-s2007}

### Widely Cited Articles {-}

1. Adam Elga (2007) "Reflection and Disagreement," _Noûs_ 41 (3): 478-502 SEP 2007.
2. David Christensen (2007) "Epistemology of Disagreement: The Good News," _Philosophical Review_ 116 (2): 187-217 APR 2007.
3. Seth Yalcin (2007) "Epistemic Modals," _Mind_ 116 (464): 983-1026 OCT 2007.
4. Jennifer Lackey (2007) "Norms of Assertion," _Noûs_ 41 (4): 594-626 DEC 2007.
5. Michael Huemer (2007) "Compassionate Phenomenal Conservatism," _Philosophy And Phenomenological Research_ 74 (1): 30-55 JAN 2007.
6. Michael Weisberg (2007) "Three Kinds of Idealization," _Journal Of Philosophy_ 104 (12): 639-659 DEC 2007.
7. Andy Egan (2007) "Epistemic Modals, Relativism and Assertion," _Philosophical Studies_ 133 (1): 1-22 MAR 2007.
8. John MacFarlane (2007) "Relativism and Disagreement," _Philosophical Studies_ 132 (1): 17-31 JAN 2007.
9. Shaun Nichols and Joshua Knobe (2007) "Moral Responsibility and Determinism: The Cognitive Science of Folk Intuitions," _Noûs_ 41 (4): 663-685 DEC 2007.

### Citation Count {-#sec-count-2007}

```{r}
#| label: tbl-citation-count-2007
#| tbl-cap: Citation count for widely cited articles from 2007.

year_cites <- rank_table_generator(2007)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2007}

```{r}
#| label: tbl-citation-rank-2007
#| tbl-cap: Citation rank for widely cited articles from 2007.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2007}

```{r}
#| label: fig-citation-spaghetti-2007
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2007.
#| cache: TRUE

rolling_spaghetti_graph(2007)
```

```{r}
#| label: fig-citation-facet-2007
#| fig-cap: Faceted version of @fig-citation-spaghetti-2007.
#| cache: TRUE

rolling_facet_graph(2007)
```

\newpage


## 2008 {#sec-s2008}

### Widely Cited Articles {-}

1. John Hawthorne and Jason Stanley (2008) "Knowledge and Action," _Journal Of Philosophy_ 105 (10): 571-590 Sp. Iss. SI OCT 2008.
2. Tamar Szabò Gendler (2008) "Alief and Belief," _Journal Of Philosophy_ 105 (10): 634-663 Sp. Iss. SI OCT 2008.
3. Eric Schwitzgebel (2008) "The Unreliability of Naive Introspection," _Philosophical Review_ 117 (2): 245-273 APR 2008.
4. Stacey Swain, Joshua Alexander, and Jonathan M. Weinberg (2008) "The Instability of Philosophical Intuitions: Running Hot and Cold on Truetemp," _Philosophy And Phenomenological Research_ 76 (1): 138-155 JAN 2008.
5. Scott Sturgeon (2008) "Reason and the Grain of Belief," _Noûs_ 42 (1): 139-165 MAR 2008.
6. Jessica Brown (2008) "Subject-Sensitive Invariantism and the Knowledge Norm for Practical Reasoning," _Noûs_ 42 (2): 167-189 JUN 2008.
7. Michael Fara (2008) "Masked Abilities and Compatibilism," _Mind_ 117 (468): 843-865 OCT 2008.
8. Pamela Hieronymi (2008) "Responsibility for Believing," _Synthese_ 161 (3): 357-373 APR 2008.
9. David Manley and Ryan Wasserman (2008) "On Linking Dispositions and Conditionals," _Mind_ 117 (465): 59-84 JAN 2008.

### Citation Count {-#sec-count-2008}

```{r}
#| label: tbl-citation-count-2008
#| tbl-cap: Citation count for widely cited articles from 2008.

year_cites <- rank_table_generator(2008)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2008}

```{r}
#| label: tbl-citation-rank-2008
#| tbl-cap: Citation rank for widely cited articles from 2008.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2008}

```{r}
#| label: fig-citation-spaghetti-2008
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2008.
#| cache: TRUE

rolling_spaghetti_graph(2008)
```

```{r}
#| label: fig-citation-facet-2008
#| fig-cap: Faceted version of @fig-citation-spaghetti-2008.
#| cache: TRUE

rolling_facet_graph(2008)
```

\newpage


## 2009 {#sec-s2009}

### Widely Cited Articles {-}

1. Alison Hills (2009) "Moral Testimony and Moral Epistemology," _Ethics_ 120 (1): 94-127 OCT 2009.
2. John MacFarlane (2009) "Nonindexical Contextualism," _Synthese_ 166 (2): 231-250 JAN 2009.
3. Alan Baker (2009) "Mathematical Explanation in Science," _British Journal For The Philosophy Of Science_ 60 (3): 611-633 SEP 2009.
4. Alex Byrne (2009) "Experience and Content," _Philosophical Quarterly_ 59 (236): 429-451 JUL 2009.
5. Jonathan Schaffer (2009) "Spacetime the One Substance," _Philosophical Studies_ 145 (1): 131-148 JUL 2009.
6. Jonathan Cohen and Craig Callender (2009) "A Better Best System Account of Lawhood," _Philosophical Studies_ 145 (1): 1-34 JUL 2009.
7. Mark Schroeder (2009) "Means-End Coherence, Stringency, and Subjective Reasons," _Philosophical Studies_ 143 (2): 223-248 MAR 2009.
8. Tim Bayne (2009) "Perception and the Reach of Phenomenal Content," _Philosophical Quarterly_ 59 (236): 385-404 JUL 2009.
9. Jonathan Quong (2009) "Killing in Self-Defense," _Ethics_ 119 (3): 507-537 APR 2009.

### Citation Count {-#sec-count-2009}

```{r}
#| label: tbl-citation-count-2009
#| tbl-cap: Citation count for widely cited articles from 2009.

year_cites <- rank_table_generator(2009)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2009}

```{r}
#| label: tbl-citation-rank-2009
#| tbl-cap: Citation rank for widely cited articles from 2009.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2009}

```{r}
#| label: fig-citation-spaghetti-2009
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2009.
#| cache: TRUE

rolling_spaghetti_graph(2009)
```

```{r}
#| label: fig-citation-facet-2009
#| fig-cap: Faceted version of @fig-citation-spaghetti-2009.
#| cache: TRUE

rolling_facet_graph(2009)
```

\newpage


## 2010 {#sec-s2010}

### Widely Cited Articles {-}

1. Jonathan Schaffer (2010) "Monism: The Priority of the Whole," _Philosophical Review_ 119 (1): 31-76 JAN 2010.
2. David Christensen (2010) "Higher-Order Evidence," _Philosophy And Phenomenological Research_ 81 (1): 185-215 JUL 2010.
3. Niko Kolodny and John MacFarlane (2010) "Ifs and Oughts," _Journal Of Philosophy_ 107 (3): 115-143 MAR 2010.
4. James Woodward (2010) "Causation in Biology: Stability, Specificity, and the Choice of Levels of Explanation," _Biology & Philosophy_ 25 (3): 287-318 JUN 2010.
5. Eric Schwitzgebel (2010) "Acting Contrary To Our Professed Beliefs or the Gulf Between Occurrent Judgment and Dispositional Belief," _Pacific Philosophical Quarterly_ 91 (4): 531-553 DEC 2010.
6. Kevin J. S. Zollman (2010) "The Epistemic Benefit of Transient Diversity," _Erkenntnis_ 72 (1): 17-35 JAN 2010.
7. Julia Markovits (2010) "Acting for the Right Reasons," _Philosophical Review_ 119 (2): 201-242 APR 2010.
8. Jonathan Schaffer (2010) "The Least Discerning and Most Promiscuous Truthmaker," _Philosophical Quarterly_ 60 (239): 307-324 APR 2010.
9. Jonathan M. Weinberg, Chad Gonnerman, Cameron Buckner, and Joshua Alexander (2010) "Are Philosophers Expert Intuiters?," _Philosophical Psychology_ 23 (3): 331-355 Part 1 Sp. Iss. SI 2010.

### Citation Count {-#sec-count-2010}

```{r}
#| label: tbl-citation-count-2010
#| tbl-cap: Citation count for widely cited articles from 2010.

year_cites <- rank_table_generator(2010)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2010}

```{r}
#| label: tbl-citation-rank-2010
#| tbl-cap: Citation rank for widely cited articles from 2010.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2010}

```{r}
#| label: fig-citation-spaghetti-2010
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2010.
#| cache: TRUE

rolling_spaghetti_graph(2010)
```

```{r}
#| label: fig-citation-facet-2010
#| fig-cap: Faceted version of @fig-citation-spaghetti-2010.
#| cache: TRUE

rolling_facet_graph(2010)
```

\newpage


## 2011 {#sec-s2011}

### Widely Cited Articles {-}

1. Kristie Dotson (2011) "Tracking Epistemic Violence, Tracking Practices of Silencing," _Hypatia_ 26 (2): 236-257 SPR 2011.
2. David J. Chalmers (2011) "Verbal Disputes," _Philosophical Review_ 120 (4): 515-566 OCT 2011.
3. Karen Bennett (2011) "By Our Bootstraps," _Philosophical Perspectives_ 25 (1): 27-41 DEC 2011.
4. David Michael Kaplan and Carl F. Craver (2011) "The Explanatory Force of Dynamical and Mathematical Models in Neuroscience: A Mechanistic Perspective," _Philosophy Of Science_ 78 (4): 601-627 OCT 2011.
5. C. S. Jenkins (2011) "Is Metaphysical Dependence Irreflexive?," _Monist_ 94 (2): 267-276 APR 2011.
6. David Christensen (2011) "Disagreement, Question-Begging and Epistemic Self-Criticism," _Philosophers Imprint_ 11 (6): - MAR 2011.
7. Gualtiero Piccinini and Carl Craver (2011) "Integrating Psychology and Neuroscience: Functional Analyses as Mechanism Sketches," _Synthese_ 183 (3): 283-311 DEC 2011.
8. Timothy Sundell (2011) "Disagreements About Taste," _Philosophical Studies_ 155 (2): 267-288 SEP 2011.
9. Timothy Williamson (2011) "Philosophical Expertise and the Burden of Proof," _Metaphilosophy_ 42 (3): 215-229 Sp. Iss. SI APR 2011.

### Citation Count {-#sec-count-2011}

```{r}
#| label: tbl-citation-count-2011
#| tbl-cap: Citation count for widely cited articles from 2011.

year_cites <- rank_table_generator(2011)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2011}

```{r}
#| label: tbl-citation-rank-2011
#| tbl-cap: Citation rank for widely cited articles from 2011.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2011}

```{r}
#| label: fig-citation-spaghetti-2011
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2011.
#| cache: TRUE

rolling_spaghetti_graph(2011)
```

```{r}
#| label: fig-citation-facet-2011
#| fig-cap: Faceted version of @fig-citation-spaghetti-2011.
#| cache: TRUE

rolling_facet_graph(2011)
```

\newpage


## 2012 {#sec-s2012}

### Widely Cited Articles {-}

1. Duncan Pritchard (2012) "Anti-Luck Virtue Epistemology," _Journal Of Philosophy_ 109 (3): 247-279 MAR 2012.
2. Paul Audi (2012) "Grounding: Toward a Theory of the In-Virtue-Of Relation," _Journal Of Philosophy_ 109 (12): 685-711 DEC 2012.
3. Gaile Pohlhaus Jr. (2012) "Relational Knowing and Epistemic Injustice: Toward a Theory of Willful Hermeneutical Ignorance," _Hypatia_ 27 (4): 715-735 NOV 2012.
4. Fiona Macpherson (2012) "Cognitive Penetration of Colour Experience: Rethinking the Issue in Light of An Indirect Mechanism," _Philosophy And Phenomenological Research_ 84 (1): 24-62 JAN 2012.
5. Pablo Cobreros, Paul Egre, David Ripley, and Robert Van Rooij (2012) "Tolerant, Classical, Strict," _Journal Of Philosophical Logic_ 41 (2): 347-385 APR 2012.
6. Eric Schwitzgebel and Fiery Cushman (2012) "Expertise in Moral Reasoning? Order Effects on Moral Judgment in Professional Philosophers and Non-Philosophers," _Mind & Language_ 27 (2): 135-153 APR 2012.
7. Barry Loewer (2012) "Two Accounts of Laws and Time," _Philosophical Studies_ 160 (1): 115-137 Sp. Iss. SI AUG 2012.
8. Susanna Siegel (2012) "Cognitive Penetrability and Perceptual Justification," _Noûs_ 46 (2): 201-222 JUN 2012.
9. Elizabeth Anderson (2012) "Epistemic Justice as a Virtue of Social Institutions," _Social Epistemology_ 26 (2): 163-173 Sp. Iss. SI 2012.

### Citation Count {-#sec-count-2012}

```{r}
#| label: tbl-citation-count-2012
#| tbl-cap: Citation count for widely cited articles from 2012.

year_cites <- rank_table_generator(2012)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2012}

```{r}
#| label: tbl-citation-rank-2012
#| tbl-cap: Citation rank for widely cited articles from 2012.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2012}

```{r}
#| label: fig-citation-spaghetti-2012
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2012.
#| cache: TRUE

rolling_spaghetti_graph(2012)
```

```{r}
#| label: fig-citation-facet-2012
#| fig-cap: Faceted version of @fig-citation-spaghetti-2012.
#| cache: TRUE

rolling_facet_graph(2012)
```

\newpage


## 2013 {#sec-s2013}

### Widely Cited Articles {-}

1. David Plunkett and Tim Sundell (2013) "Disagreement and the Semantics of Normative and Evaluative Terms," _Philosophers Imprint_ 13 (23): 1-37 DEC 2013.
2. Jane Friedman (2013) "Suspended Judgment," _Philosophical Studies_ 162 (2): 165-181 JAN 2013.
3. Louis deRosset (2013) "Grounding Explanations," _Philosophers Imprint_ 13 (7): - APR 2013.
4. Kelly Trogdon (2013) "Grounding: Necessary or Contingent?," _Pacific Philosophical Quarterly_ 94 (4): 465-485 DEC 2013.
5. David Ripley (2013) "Paradoxes and Failures of Cut," _Australasian Journal Of Philosophy_ 91 (1): 139-164 MAR 1 2013.
6. Marc Lange (2013) "What Makes a Scientific Explanation Distinctively Mathematical?," _British Journal For The Philosophy Of Science_ 64 (3): 485-511 SEP 2013.
7. Selim Berker (2013) "Epistemic Teleology and the Separateness of Propositions," _Philosophical Review_ 122 (3): 337-393 JUL 2013.
8. Pablo Cobreros, Paul Egre, David Ripley, and Robert Van Rooij (2013) "Reaching Transparent Truth," _Mind_ 122 (488): 841-866 OCT 2013.
9. Alberto Giubilini and Francesca Minerva (2013) "After-Birth Abortion: Why Should the Baby Live?," _Journal Of Medical Ethics_ 39 (5): 261-263 MAY 2013.

### Citation Count {-#sec-count-2013}

```{r}
#| label: tbl-citation-count-2013
#| tbl-cap: Citation count for widely cited articles from 2013.

year_cites <- rank_table_generator(2013)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2013}

```{r}
#| label: tbl-citation-rank-2013
#| tbl-cap: Citation rank for widely cited articles from 2013.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2013}

```{r}
#| label: fig-citation-spaghetti-2013
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2013.
#| cache: TRUE

rolling_spaghetti_graph(2013)
```

```{r}
#| label: fig-citation-facet-2013
#| fig-cap: Faceted version of @fig-citation-spaghetti-2013.
#| cache: TRUE

rolling_facet_graph(2013)
```

\newpage


## 2014 {#sec-s2014}

### Widely Cited Articles {-}

1. Jessica M. Wilson (2014) "No Work for a Theory of Grounding," _Inquiry_ 57 (5-6): 535-579 NOV 2 2014.
2. Miriam Schoenfield (2014) "Permission To Believe: Why Permissivism is True and What It Tells Us About Irrelevant Influences on Belief," _Noûs_ 48 (2): 193-218 JUN 2014.
3. Shamik Dasgupta (2014) "The Possibility of Physicalism," _Journal Of Philosophy_ 111 (9-10): 557-592 Sp. Iss. SI SEP-OCT 2014.
4. Jacob Ross and Mark Schroeder (2014) "Belief, Credence, and Pragmatic Encroachment," _Philosophy And Phenomenological Research_ 88 (2): 259-288 MAR 2014.
5. Paul Boghossian (2014) "What is Inference?," _Philosophical Studies_ 169 (1): 1-18 Sp. Iss. SI MAY 2014.
6. Sophie Horowitz (2014) "Epistemic Akrasia," _Noûs_ 48 (4): 718-744 DEC 2014.
7. Lara Buchak (2014) "Belief, Credence, and Norms," _Philosophical Studies_ 169 (2): 285-311 JUN 2014.
8. Robert W. Batterman and Collin C. Rice (2014) "Minimal Model Explanations," _Philosophy Of Science_ 81 (3): 349-376 JUL 2014.
9. Stephan Leuenberger (2014) "Grounding and Necessity," _Inquiry_ 57 (2): 151-174 Sp. Iss. SI MAR 4 2014.

### Citation Count {-#sec-count-2014}

```{r}
#| label: tbl-citation-count-2014
#| tbl-cap: Citation count for widely cited articles from 2014.

year_cites <- rank_table_generator(2014)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2014}

```{r}
#| label: tbl-citation-rank-2014
#| tbl-cap: Citation rank for widely cited articles from 2014.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2014}

```{r}
#| label: fig-citation-spaghetti-2014
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2014.
#| cache: TRUE

rolling_spaghetti_graph(2014)
```

```{r}
#| label: fig-citation-facet-2014
#| fig-cap: Faceted version of @fig-citation-spaghetti-2014.
#| cache: TRUE

rolling_facet_graph(2014)
```

\newpage


## 2015 {#sec-s2015}

### Widely Cited Articles {-}

1. Alexander Skiles (2015) "Against Grounding Necessitarianism," _Erkenntnis_ 80 (4): 717-751 AUG 2015.
2. Michael J. Raven (2015) "Ground," _Philosophy Compass_ 10 (5): 322-333 MAY 2015.
3. Collin Rice (2015) "Moving Beyond Causes: Optimality Models and Scientific Explanation," _Noûs_ 49 (3): 589-615 SEP 2015.
4. David Plunkett (2015) "Which Concepts Should We Use?: Metalinguistic Negotiations and the Methodology of Philosophy," _Inquiry_ 58 (7-8): 828-874 Sp. Iss. SI NOV 17 2015.
5. James Woodward (2015) "Interventionism and Causal Exclusion," _Philosophy And Phenomenological Research_ 91 (2): 303-347 SEP 2015.
6. Kit Fine (2015) "Unified Foundations for Essence and Ground," _Journal Of The American Philosophical Association_ 1 (2): - SUM 2015.
7. John Bengson (2015) "The Intellectual Given," _Mind_ 124 (495): 707-760 JUL 2015.
8. Jonathan Schaffer (2015) "What Not To Multiply Without Necessity," _Australasian Journal Of Philosophy_ 93 (4): 644-664 OCT 2 2015.
9. Neil Levy (2015) "Neither Fish Nor Fowl: Implicit Attitudes as Patchy Endorsements," _Noûs_ 49 (4): 800-823 DEC 2015.

### Citation Count {-#sec-count-2015}

```{r}
#| label: tbl-citation-count-2015
#| tbl-cap: Citation count for widely cited articles from 2015.

year_cites <- rank_table_generator(2015)
kable(select(year_cites, Article, All = Citations, Early = `Early Citations`, Late = `Late Citations`))
```


### Citation Rank {-#sec-rank-2015}

```{r}
#| label: tbl-citation-rank-2015
#| tbl-cap: Citation rank for widely cited articles from 2015.

kable(select(year_cites, Article, Overall = `Citation Rank`, Early = `Early Rank`, Late = `Late Rank`))
```


### Citation Trends {-#sec-trends-2015}

```{r}
#| label: fig-citation-spaghetti-2015
#| fig-cap: Rolling five year average of citation frequency for widely cited articles from 2015.
#| cache: TRUE

rolling_spaghetti_graph(2015)
```

```{r}
#| label: fig-citation-facet-2015
#| fig-cap: Faceted version of @fig-citation-spaghetti-2015.
#| cache: TRUE

rolling_facet_graph(2015)
```

\newpage

