% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  10pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod,
  twoside]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[ItalicFont=EB Garamond Italic,BoldFont=EB Garamond
Bold]{EB Garamond Math}
    \setsansfont[]{Europa-Bold}
  \setmathfont[]{Garamond-Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\usepackage[left=1in, right=1in, top=0.8in, bottom=0.8in,
paperheight=9.5in, paperwidth=6.5in, includemp=TRUE, marginparwidth=0in,
marginparsep=0in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{3}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0ex}
\usepackage[automark]{scrlayer-scrpage}
\clearpairofpagestyles
\cehead{
  Brian Weatherson
  }
\cohead{
  Questioning Contextualism
  }
\ohead{\bfseries \pagemark}
\cfoot{}
\makeatletter
\newcommand*\NoIndentAfterEnv[1]{%
  \AfterEndEnvironment{#1}{\par\@afterindentfalse\@afterheading}}
\makeatother
\NoIndentAfterEnv{itemize}
\NoIndentAfterEnv{enumerate}
\NoIndentAfterEnv{description}
\NoIndentAfterEnv{quote}
\NoIndentAfterEnv{equation}
\NoIndentAfterEnv{longtable}
\NoIndentAfterEnv{abstract}
\renewenvironment{abstract}
 {\vspace{-1.25cm}
 \quotation\small\noindent\rule{\linewidth}{.5pt}\par\smallskip
 \noindent }
 {\par\noindent\rule{\linewidth}{.5pt}\endquotation}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Questioning Contextualism},
  pdfauthor={Brian Weatherson},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}


\title{Questioning Contextualism}
\author{Brian Weatherson}
\date{2006}

\begin{document}
\maketitle
\begin{abstract}
This chapter argues against the pragmatism that shows that there is a
striking disanalogy between the behavior of ``knows'' in questions and
the behavior of ``knows'' in terms. The chapter discusses that different
people may have different standards for knowledge, so perhaps they may
mean different things by a statement, because they communicate to meet
their preferred standards for knowledge. Standards for knowledge are not
the kind of thing that people can differ on without making a mistake, in
the way one would say that different people can have different immediate
goals (about what to have for dinner) without making a mistake. This
explains that one does not just adopt questioners' standards for
knowledge while answering their knowledge questions. So, it is argued
that questions involving ``knows'' should have the three
properties---speaker, clarification, and different answers. However, the
counter argument is that the proposition can be true relative to some
contexts and false relative to other contexts, just as temporality about
propositions that a proposition can be true at some times and false at
other times, and the utterance is true if the proposition is true only
in the context of the utterance.
\end{abstract}


\setstretch{1.1}
There are currently a dizzying variety of theories on the market holding
that whether an utterance of the form \emph{A knows that p} is true
depends on pragmatic or contextual factors. Even if we allow that
pragmatics matters, there are three questions to be answered. First,
\emph{whose} interests matter? Here there are three options: the
interests of \emph{A} matter, the interests of the person making the
knowledge ascription matter, or the interests of the person evaluating
the ascription matter. Second, \emph{which} kind of pragmatic factors
matter? Broadly speaking, the debate here is about whether practical
interests (the stakes involved) or intellectual interests (which
propositions are being considered) are most important. Third, \emph{how}
do pragmatic factors matter? Here there is not even a consensus about
what the options are.

This paper is about the first question. I'm going to present some data
from the behaviour of questions about who knows what that show it is not
the interests of the person making the knowledge ascription that matter.
This means the view normally known as \emph{contextualism} about
knowledge-ascriptions is false. Since that term is a little contested,
and for some suggests merely the view that someone's context matters,
I'll introduce three different terms for the three answers to the first
question.

Consider a token utterance by B of \emph{A knows that p}. This utterance
is being evaluated by C. A \emph{semantic pragmatist} about knowledge
ascriptions says that whether C can correctly evaluate that utterance as
true or false depends on some salient party's context or
interests.\footnote{Note that the focus here is on the truth or falsity
  of the utterance, and not on the truth or falsity of the proposition
  the utterance expresses. I'm indebted to John MacFarlane for stressing
  to me the importance of this distinction.} We can produce a quick
taxonomy of semantic pragmatist positions by looking at which of the
three parties is the salient one.

\begin{description}
\tightlist
\item[Type A pragmatism]
A's context or interests matter.
\item[Type B pragmatism]
B's context or interests matter.
\item[Type C pragmatism]
C's context or interests matter.
\end{description}

Type A pragmatism is defended by Hawthorne
(\citeproc{ref-Hawthorne2004}{2004}) under the name `subject-sensitive
invariantism' and Stanley (\citeproc{ref-Stanley2005-STAKAP}{2005})
under the name `interest-relative invariantism'. The theory commonly
known as \emph{contextualism}, defended by Cohen
(\citeproc{ref-Cohen1986}{1986}), DeRose
(\citeproc{ref-DeRose1995}{1995}) and Lewis
(\citeproc{ref-Lewis1996b}{1996}), is a form of \emph{Type B}
pragmatism. On their theory, the semantic value of `knows' depends on
the context in which it is uttered, i.e.~B's context. (And the salient
feature of B's context is, broadly speaking, B's interests.) Recently
MacFarlane (\citeproc{ref-MacFarlane2009-MACNC}{2009}) has outlined a
very different variant of Type B pragmatism that we will discuss below.
Type C pragmatism is the radical view that the token utterance does not
have a context-invariant truth value, so one and the same utterance can
be properly evaluated as true by one evaluator and false by another.
This position is outlined, and defended, by MacFarlane
(\citeproc{ref-MacFarlane2005-Knowledge}{2005}).

The purpose of this paper is to argue \emph{against} Type B pragmatism.
I'll show that there is a striking disanalogy between the behaviour of
`knows' in questions and the behaviour of terms for which a Type B-type
theory is true. The best explanation for this disanalogy is that Type B
theories, contextualism included, are false.\footnote{My own view is
  that if any pragmatic theory is true, it is Type A pragmatism. In
  Weatherson (\citeproc{ref-Weatherson2005-WEACWD}{2005}) I defend the
  view that whether an agent is sufficiently confident in \emph{p} to
  count as believing that \emph{p} depends on features of her context.
  In contexts where it is very important for practical deliberation
  whether \emph{p} is true, a degree of confidence that might ordinarily
  count as belief that \emph{p} might no longer so count. This is an odd
  kind of doxastic externalism, namely the view that whether a state
  amounts to a \emph{belief} is environment-dependent. Now to know that
  \emph{p} also requires having a certain level of confidence that
  \emph{p} is true, and it is arguable (though I haven't argued it) that
  this level is also dependent on the would be knowers environment. It
  is also arguable that the best theory of epistemic \emph{defeaters}
  will contain pragmatic features.

  Though I describe Type C pragmatism as radical, I've been convinced by
  John MacFarlane's work that it is a perfectly coherent doctrine. In
  Egan, Hawthorne, and Weatherson (\citeproc{ref-Egan2005-EGAEMI}{2005})
  we defend a version of Type C pragmatism for sentences of the form
  \emph{A might be F}, where \emph{might} is understood epistemically.}

I won't be addressing the second or third questions here, but I'll
assume (basically for ease of exposition) that the right answer to the
second has more to do with \emph{practical} than \emph{intellectual}
interests. So a sceptical possibility becomes relevant not because
anyone is actively considering it, but because it makes a difference to
someone's actions. Everything I say here should be restatable given any
answer to that question, so little beyond exposition turns on this.

\section{Basic Indexicals in
Questions}\label{basic-indexicals-in-questions}

As well as considering these three pragmatic theories about `know', we
can consider similar theories about other words. We'll start with words
that are universally considered to be indexicals. Consider the following
three theories about `here'.

\begin{description}
\tightlist
\item[Type A pragmatism]
A token of `here' denotes the location of the subject of the sentence in
which it appears.
\item[Type B pragmatism]
A token of `here' denotes the location of the speaker.
\item[Type C pragmatism]
A token of `here' denotes the location of the person evaluating the
sentence.
\end{description}

So when C evaluates B's utterance \emph{A is here}, the Type A
pragmatist says that it gets evaluated as true iff A is where A is, the
Type B pragmatist says that it gets evaluated as true iff A is where B
is, and the Type C pragmatist says that it gets evaluated as true iff A
is where C is. Obviously Type B pragmatism is true in general about
`here', as it is for all obvious indexicals.\footnote{Whether the `in
  general' is strictly necessary turns on tricky considerations about
  non-standard usages, such as answering machines. I'm generally
  favourable to the view that if any qualification is needed it is a
  very small one. See Weatherson
  (\citeproc{ref-Weatherson2002-WEAMI}{2002}) for more discussion of
  this point.} What we're interested in for now, however, is not its
truth but the kind of evidence that can be adduced for it. One very
simple way of separating out these three theories involves questions, as
in the following example.

Watson is at a party in Liverpool, and he is worried that Moriarty is
there as well. He calls Holmes, who is tracking Moriarty's movements by
satellite, and asks (1).

This question has three properties that are distinctive of questions
involving indexicals.

\begin{description}
\tightlist
\item[SPEAKER]
How Holmes should answer the question depends on the speaker's
(i.e.~Watson's) environment, not his own and not Moriarty's. It would be
wrong to say ``Yes'' because Moriarty is where he is, or ``No'' because
Moriarty is not in the lab with Holmes following the satellite movement.
\item[CLARIFICATION]
It is permissible in certain contexts to ask the speaker for more
information about their context before answering. If Holmes's is unsure
of Watson's location, he can reply with ``Where are you?'' rather than
answering directly.\footnote{It is important here that we restrict
  attention to clarificatory questions about the context, and in
  particular to features of the context that (allegedly) affect the
  truth value of utterances involving the indexical. Speakers can always
  ask for clarification of all sorts of features of a question, but a
  question only has CLARIFICATION if it is appropriate to ask for
  clarifying information about the nature of the questioner's context.}
\item[DIFFERENT ANSWERS]
If two different people, who are in different locations, ask Holmes (1),
he can answer differently. Assume that Moriarty is at the party, so
Holmes says ``Yes'' in reply to Watson. Lestrade then calls from
Scotland Yard, because he is worried that Moriarty has broken in and
asks Holmes (1). Holmes says ``No'', and this is consistent with his
previous answer.
\end{description}

Questions involving indexicals have a fourth property that we'll return
to from time to time in what follows.

\begin{description}
\tightlist
\item[NEGATIVE AGREEMENT]
It is coherent to answer the question by saying ``No'', then basically
repeating the question, inverting the verb-subject order so you have an
indicative sentence. So Holmes could consistently (if falsely in this
story) say, ``No, Moriarty is here.''
\end{description}

The truth of Type B Pragmatism about `here' explains, indeed predicts,
that (1) has these properties. If a correct answer is a true answer,
then Type B Pragmatism directly entails that (1) has SPEAKER. That
assumption (that correctness is truth) plus the fact that you can speak
to someone without knowing their location implies that (1) has
CLARIFICATION, and adding the fact that different people can be in
different locations implies that (1) has DIFFERENT ANSWERS. Whether
Holmes can say \emph{Moriarty is here} depends whether he can truthfully
answer his own question \emph{Is Moriarty here?} so NEGATIVE AGREEMENT
is related to DIFFERENT ANSWERS. For these reasons it isn't surprising
that other terms that are agreed on all sides to be indexicals generate
questions that have all four properties. For instance, because `me' is
an indexical, (2) has all four properties.

This suggests a hypothesis, that all terms for which Type B pragmatism
is true generate questions with those four properties. This hypothesis
seems to be false; some terms for which Type B pragmatism is true do not
generate questions that have NEGATIVE AGREEMENT. But a weaker claim,
that all terms for which Type B pragmatism is true generate questions
with the first three properties, does seem to be true.\footnote{The
  failure of NEGATIVE AGREEMENT for questions involving quantifiers,
  comparative adjectives and similar terms is interesting is
  interesting, and is something that a full semantic theory should
  account for. My feeling is that the best explanation will draw on the
  resources of a theory like that defended by
  (\citeproc{ref-Stanley2000-STACAL}{Stanley 2000},
  \citeproc{ref-Stanley2002-STANR}{2002}) but it would take us far away
  from our primary purpose to explore this here. It is certainly an
  argument in favour of the `semantic minimalism' defended by Cappelen
  and Lepore (\citeproc{ref-Cappelen2005}{2005}) that all and only the
  terms in their `basic set' (apart from tense markers), i.e.~the
  obvious indexicals, generate questions with NEGATIVE AGREEMENT. I
  think the fact that many terms generate questions with the SPEAKER,
  CLARIFICATION and DIFFERENT ANSWERS property tells more strongly
  against their view.} Or so I will argue in the next section.

\section{Other Type B terms in
Questions}\label{other-type-b-terms-in-questions}

Various philosophers have argued that a version of Type B pragmatism is
true for each of the following four terms: `tall', `empty', `ready' and
`everyone'. Various defenders of Type B pragmatism about `knows' have
argued that `knows' is analogous to terms on this list. In this section
I'll argue that questions involving those four terms have the first
three properties of questions listed above, though they don't seem to
have NEGATIVE AGREEMENT. In the next section I'll argue that questions
involving `know' do not have those three properties. These facts combine
to form an argument against the hypothesis that Type B pragmatism is
true of `knows'. (The argument here does not turn on supposing that Type
B pragmatism is true of these four terms. All I want to argue for is the
claim that any term for which Type B pragmatism is true generates
questions with the first three properties. It is possible that other
terms also generate these kinds of questions, but this possibility
doesn't threaten the argument.) The examples involving these four terms
will be a little complicated, but the intuitions about them are clear.

Moriarty has hired a new lackey, a twelve year old jockey. She is tall
for a twelve year old girl, and tall for a jockey, but not tall for a
person. Moriarty is most interested in her abilities as a jockey, so he
worries that she's tall. Holmes is also most interested in her
\emph{qua} jockey. Watson has noted that Moriarty never hires people who
are tall for adults (he thinks this is because Moriarty likes lording
over his lackeys) and is wondering whether the new hire fits this
property. He asks Holmes (3).

(3) Is Moriarty's new lackey tall?

Holmes should say ``No''. What matters is whether she is tall \emph{by
the standards Watson cares about}, not whether she is tall by the
standards Holmes cares about (i.e.~jockeys) or the standards Moriarty
cares about (i.e.~also jockeys). So (3) has SPEAKER. Lestrade wants
information from Holmes about the lackey so his men can pick her up.
They have this conversation.

\begin{quote}
Lestrade: Is Moriarty's new lackey tall? My men are looking for her.

Holmes: Where are they looking?

Lestrade: At her school.

Holmes: Yes, she looks like she could be fourteen or fifteen.
\end{quote}

Holmes quite properly asks for a clarification of the question so as to
work out what standards for tallness are in play, so (3) has
CLARIFICATION. And he properly gives different answers to Watson and
Lestrade, so it has DIFFERENT ANSWERS. But note that `tall' doesn't have
NEGATIVE AGREEMENT. Holmes can't answer (3) with ``No, she's tall.'' I
won't repeat this observation for the other terms discussed in this
section, but the point generalises.

Next we'll consider `empty'. Holmes and Watson are stalking Moriarty at
a party. Watson is mixing poisons, and Holmes is trying to slip the
poison into Moriarty's glass. Unfortunately Moriarty has just about
finished his drink, and might be about to abandon it. Watson is
absent-mindedly trying to concoct the next poison, but he seems to have
run out of mixing dishes.

\begin{quote}
Watson: Is Moriarty's glass empty?

Holmes: What do you want it for?

Watson: I need something dry to mix this poison in.

Holmes: No, it's got a small bit of ice left in it.

(Lestrade arrives, and sees Holmes holding a vial.)

Lestrade: Why haven't you moved in? Is Moriarty's glass empty?

Holmes: Yes. He should get another soon.
\end{quote}

Holmes behaves entirely appropriately here, and his three responses show
that the question \emph{Is Moriarty's glass empty?} has the
CLARIFICATION, SPEAKER and DIFFERENT ANSWERS properties respectively.
Note in particular that the glass is empty by the standards that matter
to Moriarty and Holmes (i.e.~it's got not much more than ice left in it)
doesn't matter to how Holmes should answer until someone with the same
interests, Lestrade, asks about the glass.

Third, we'll look at `ready'. Moriarty is planning four things: to rob
the Bank of England, to invade Baker St and kill Holmes, to invade
Scotland Yard to free his friends, and to leave for a meeting of
criminals where they will plan for the three missions. Moriarty cares
most about the first plan, Holmes about the second, and Lestrade about
the third, but right now Watson cares most about the fourth because it's
his job to track Moriarty to the meeting. Holmes is tracking Moriarty
through an installed spycam.

\begin{quote}
Watson: Is Moriarty ready?

Holmes: Yes. You should go now.

(Watson departs and Lestrade arrives)

Lestrade: Is Moriarty ready?

Holmes: Who's that? Oh, hello Inspector. No, he still has to plan the
attack out.
\end{quote}

Again, Holmes's answers show that the question \emph{Is Moriarty ready?}
has the CLARIFICATION, SPEAKER and DIFFERENT ANSWERS properties. Note
that in this case the issue of whether Moriarty is ready for the thing
he cares most about, and the issue of whether he is ready for the thing
Holmes cares most about, are not relevant to Holmes's answers. It is the
interests of the different speakers that matter, which suggests that if
one of the three types of pragmatism is true about `ready', it is Type B
pragmatism.

Finally we'll look at `everyone'. Lewis
(\citeproc{ref-Lewis1996b}{1996}) suggests that `know' is directly
analogous to `every', so the two words should behave the same way in
questions. Moriarty's gang just robbed a department store while the
royal family, along with many police, were there. Holmes is most
interested in how this affected the royals, Watson in how the public
reacted, Lestrade in how his police reacted, and Moriarty merely in his
men and his gold. The public, and the royals, were terrified by the raid
on the store, but the police reacted bravely.

\begin{quote}
Watson: Did Moriarty's men terrify everyone?

Holmes: Her majesty and her party were quite shocked. Oh, you mean
\emph{everyone}. Yes, the masses there were completely stunned.

(Lestrade enters.)

Lestrade: I just heard about the raid. How did they get through
security? Did Moriarty's men terrify everyone?

Holmes: No, your men did their job, but they were outnumbered.
\end{quote}

Again, Holmes's answers show that the question \emph{Did Moriarty's men
terrify everyone?} has the CLARIFICATION, SPEAKER and DIFFERENT ANSWERS
properties. And again, what the quantifier domain would be if Holmes
were to use the word `everyone', namely all the royal family, is
irrelevant to how he should answer a question involving `everyone'.
That's the distinctive feature of expressions for which Type B
pragmatism is true, and it suggests that in this respect at least
`everyone' behaves as if Type B pragmatism is true of it.

\section{Questions about Knowledge}\label{questions-about-knowledge}

We have two reasons for thinking that if Type B pragmatism is true about
`knows', then questions about knowledge should have all the SPEAKER,
CLARIFICATION and DIFFERENT ANSWERS properties. First, the assumption
that correct answers are true answers plus trivial facts about the
environment (namely that environments are not always fully known and
differ between speakers) implies that the questions have these
properties. Second, many words that are either uncontroversial or
controversial instances where Type B pragmatism is true generate
questions with these properties. So if `knows' is meant to be analogous
to these controversial examples, questions about knowledge should have
these properties. I'll argue in this section that knowledge questions do
not have these properties. Again we'll work through a long example to
show this.

Last week Watson discovered where Moriarty was storing a large amount of
gold, and retrieved it. Moriarty is now coming to Baker St to try to get
the gold back, and Holmes is planning a trap for him. Moriarty has made
educated guesses that it was Watson (rather than Holmes) who retrieved
the gold, and that Holmes is planning a trap at Baker St Station. But he
doesn't have a lot of evidence for either proposition. Holmes has been
spying on Moriarty, so he knows that Moriarty is in just this position.
Neither Moriarty nor Holmes care much about who it was who retrieved the
gold from Moriarty's vault, but this is very important to Watson, who
plans to write a book about it. On the other hand, that Holmes is
planning a trap at Baker St Station is very important to both Holmes and
Moriarty, but surprisingly unimportant to Watson. He would prefer that
he was the hero of the week for recovering the gold, not Holmes for
capturing Moriarty. They have this conversation.

\begin{quote}
Watson: Does Moriarty know that you've got a trap set up at Baker St
Station?

Holmes: No, he's just guessing. If I set up a diversion I'm sure I can
get him to change his mind.

Watson: Does he know it was me who recovered the gold?

Holmes: Yes, dear Watson, he figured that out.
\end{quote}

These answers sound to me like the answers Holmes \emph{should} give.
Because the trap is practically important to both him and Moriarty, it
seems he should say no to the first question unless Moriarty has very
strong evidence.\footnote{The Type A pragmatist says that it is the
  importance of the trap to Moriarty that makes this a high-stakes
  question, and the Type C pragmatist (at least as I understand that
  view) says that it is the importance of the trap to Holmes that
  matters. Since Moriarty and Holmes agree about what is important here,
  the Type A and Type C pragmatists can agree with each other and
  disagree with the Type B pragmatist.} But because it is unimportant to
Holmes and Moriarty just what \emph{Watson} did, the fact that Moriarty
has a true belief that's based on the right evidence that Watson
recovered the gold is sufficient for Holmes to answer the second
question ``Yes''. This shows that questions involving `knows' do not
have the SPEAKER property.

Some might dispute the intuitions involved here, but note that on a
simple Type B pragmatist theory, one that sets the context just by the
\emph{speaker's} interests (as opposed to the speaker \emph{and} her
interlocutors) Holmes should assent to (4) and (5).

And it is \emph{very} intuitive that if he should assent to (4) and (5),
then he should answer ``No'' to Watson's first question, and ``Yes'' to
the second.

Some adherents of a more sophisticated Type B pragmatist theory will not
say that Holmes should assent to these two, because they think he should
take Watson's interests on board in his use of `knows'. This is the
`single scoreboard view' of Keith DeRose
(\citeproc{ref-DeRose2004}{2004}).\footnote{The failure of NEGATIVE
  AGREEMENT for knowledge questions suggests that if any contextualist
  theory is true, it had better be a single scoreboard view.} But we
can, with a small addition of complexity rearrange the case so as to
avoid this complication. Imagine that Watson is not talking to Holmes,
but to Lestrade, and that Lestrade (surprisingly) shares Watson's
interests. Unbeknownst to the two of them, Holmes is listening in to
their conversation via a bug. When listening in to conversations, Holmes
has the habit of answering any questions that are asked, even if they
obviously aren't addressed to him. (I do the same thing when watching
sports broadcasts, though the questions are often mind-numbingly bland.
Listening to the intuitive answers one gives is a good guide to the
content of the question.) So the conversation now goes as follows.

\begin{quote}
Watson: Does Moriarty know that Holmes has got a trap set up at Baker St
Station?

Holmes (eavesdropping): No, he's just guessing. If I set up a diversion
I'm sure I can get him to change his mind.

Lestrade: I'm not sure. My Moriarty spies aren't doing that well.

Watson: Does he know it was me who recovered the gold?

Holmes (eavesdropping): Yes, dear Watson, he figured that out.
\end{quote}

It is important here that Holmes is talking \emph{to himself}, even
though he is using Watson's questions to guide what he says. So it will
be a \emph{very} extended sense of context if somehow Watson's interests
guide Holmes's context. Some speakers may be moved by empathy to align
their interests with the people they are speaking about, but
\emph{Holmes} is not such a speaker. So Type B pragmatic theories should
say that Holmes should endorse (4) and (5) in this context, and
intuitively if this is true he should speak in the above interaction
just as I have recorded. But this is just to say that questions about
knowledge do not have SPEAKER.\footnote{As noted above, the Type A and
  Type C pragmatists agree with this intuition, though for very
  different reasons.}

One might worry that we're changing the rules, since we did not use
eavesdropping situations above in arguing that if Type B pragmatism is
true of `knows', then questions about knowledge should have SPEAKER. But
it is a simple exercise to check that even if Holmes is eavesdropping,
his answers to questions including `tall', `empty', `ready' and
`everyone' should still have the three properties. So this change of
scenery does not tilt the deck against the Type B pragmatist.

Cases like this one also suggest that questions involving `knows' also
lack the CLARIFICATION and DIFFERENT ANSWERS property. It would be odd
of Holmes to reply to one of Watson's questions with ``How much does it
matter to you?'', as it would be in any case where a questioner who
knows that \emph{p} asks whether \emph{S} also knows that \emph{p}.
Intuitions about cases where the questioner does not know that \emph{p}
are a little trickier, because then the respondent can only answer `yes'
if she has sufficient evidence to assure the speaker that \emph{p}, and
it is quite plausible that the amount of evidence needed to assure
someone that \emph{p} varies with the interests of the person being
assured.\footnote{With the right supplementary assumptions, I believe
  this claim can be argued to be a consequence of any of our three types
  of pragmatism.} But if Type B pragmatism were true, we'd expect to
find cases of CLARIFICATION where it is common ground that the speaker
knows \emph{p}, and yet a request for standards is in order, and no such
cases seem to exist. Similarly, it's hard to imagine circumstances where
Holmes would offer a different answer if Lestrade rather than Watson
asked the questions. And more generally, if two questioners who each
know that \emph{p} ask whether S knows that \emph{p}, it is hard to see
how it could be apt to answer them differently.\footnote{The above
  remarks about cases where the speakers don't know that \emph{p} also
  apply. I think that without a very careful story about how the norms
  governing assertion relate to the interests of the speaker and the
  audience, such cases will not tell us much about the semantics of
  `knows'. Best then to stick with cases where it is common ground that
  everyone, except the subject, knows that \emph{p}.} But if Type B
pragmatism about `knows' were true, knowledge questions would have these
three properties, so it follows that Type B pragmatism about `knows' is
false.

\section{Objections and Replies}\label{objections-and-replies}

\emph{Objection}: The argument that Type B pragmatism implies that
questions involving `knows' should have the three properties assumes
that correct answers are true answers. But there are good Gricean
reasons to think that there are other standards for correctness.

\emph{Reply}: It is true that one of the arguments for thinking that
Type B pragmatism has this implication uses this assumption. But the
other argument, the argument from analogy with indexicals and other
terms for which Type B pragmatism is true, does not. Whatever one thinks
of the theory, there is data here showing that `knows' does not behave
in questions like other context-sensitive terms for which Type B
pragmatism is the most plausible view.

Moreover, Type B pragmatists have to be very careful wielding this
objection. If there is a substantial gap between correct answers to
knowledge questions and true answers, then it is likely that there is a
substantial gap between correct knowledge ascriptions and true knowledge
ascriptions. As a general (though not universal) rule, truth and
correctness are more tightly connected for questions than for simple
statements. For example, some utterances do not generate all the scalar
implicatures as answers to questions that they typically generate when
asserted unprompted.\footnote{Here are a couple of illustrations of this
  point. Yao Ming is seven feet six inches tall. It would be odd (at
  best) to use (6) to describe him, but it is clearly improper to answer
  (7) with `No'.

  For a second case, consider an example of Hart's that Grice
  (\citeproc{ref-Grice1989}{1989}) uses to motivate his distinction
  between semantics and pragmatics. A motorist drives slowly down the
  street, pausing at every driveway to see if anyone or anything is
  rushing out. It seems extremely odd to use (8) to describe him.

  Is this oddity due to (8) being false, or it being otherwise
  infelicitous? Part of the argument that (8) is true, but infelicitous,
  is that intuitively it is correct to say `Yes' in response to (9), and
  incorrect to say `No'.

  The implicatures associated with (8) are largely absent from
  affirmative answers to (9), though such an answer presumably has the
  same truth-conditional content as (8).} But the primary `ordinary
language' argument for Type B pragmatism about knowledge ascriptions
assumes that correct knowledge ascriptions are, by and large, true.

We can put this in more theoretical terms. If we are to use these
considerations to generate a \emph{rebutting} defeater for Type B
pragmatism, we would need an argument that Holmes's answers are correct
iff they are true. And while that step of the argument is plausible, it
is not beyond contention. But that isn't the only use of the examples.
We can also use them to \emph{undercut} the argument from ordinary
language to Type B pragmatism. We have a wide range of cases where
ordinary usage is as if Type B pragmatism is false. And these cases are
not peripheral or obscure features of ordinary usage. Answering
questions is one of the most common things we do with language. So
ordinary usage doesn't provide an all things considered reason to
believe that Type B pragmatism is true. If ordinary usage is (or at
least was) the best reason to believe Type B pragmatism, it follows that
there is no good reason to believe Type B pragmatism.

\emph{Objection}: Sometimes when we ask \emph{Does S know that p?} all
we want to know is whether \emph{S} has the information that \emph{p}.
In this mood, questions of justification are not relevant. But Type B
pragmatism is a theory about the interaction between the subject's
\emph{justification} and knowledge ascriptions. So these questions are
irrelevant to evaluating indexicalism.\footnote{A similar view is
  defended by Alvin Goldman (\citeproc{ref-Goldman2002}{2002}).}

\emph{Reply}: It is plausible that there is this use of knowledge
questions. It seems to me that this is a usage that needs to be
explained, and isn't easily explained on current theories of
knowledge.\footnote{One explanation, due to Stephen Hetherington
  (\citeproc{ref-Hetherington2001}{2001}), is that all that is ever
  required for a \emph{true} ascription of knowledge that \emph{p} to S
  is that \emph{p} is true and S believe it. This leaves open the
  question, as discussed below, of why we sometimes deny that true
  believers are knowers, but we can bring out familiar Gricean
  explanations about why we might usefully deny something that is
  strictly speaking true, or we could follow Hetherington and offer an
  explanation in terms of the gradability of knowledge claims. Another
  possible explanation is that `know' univocally means something like
  what most epistemologists say that it means, but there is a good
  pragmatic story about why speakers sometimes attribute knowledge to
  those with merely true belief. (I don't know how such an explanation
  would go, especially if Type B pragmatism is not true.) Finally, we
  might follow Goldman and say the English word `know' is ambiguous
  between a weak and strong reading, and the strong reading has been
  what has concerned epistemologists, and the weak reading just requires
  true belief. Such an ambiguity would be a small concession to Type B
  pragmatism (since it is the interests of the speaker that resolve
  ambiguities) but we could still sensibly ask whether Type B pragmatism
  is true of the strong reading.} But I'll leave discussion of that use
of knowledge questions for another day. For now I'll just note that even
if this can be an explanation of why we sometimes \emph{assent} to
knowledge questions, it can't be an explanation of why Holmes
\emph{denies} that Moriarty knows about the planned trap at Baker St
Station. Holmes agrees that Moriarty \emph{believes} there is a trap
planned, but insists that because Moriarty is `just guessing' that this
belief does not amount to knowledge. What really needs explaining is the
difference between Holmes's two answers, and this other use of knowledge
questions doesn't seem sufficient to generate that explanation.

\emph{Objection}: There is no explanation offered here for the data, and
we shouldn't give up an explanatory theory without an explanation of why
it fails.

\emph{Reply}: The best way to explain the data is to look at some
differences in our attitudes towards questions containing `knows' and
questions containing other terms for which Type B pragmatism is
plausibly true. I'll just go over the difference between `knows' and
`ready', the point I'm making easily generalises to the other cases.

Different people may be concerned with different bits of preparation, so
they may (speaker) mean different things by \emph{X is ready}. But
neither will regard the other as making a \emph{mistake} when they focus
on a particular bit of preparing to talk about by saying \emph{X is
ready}. And this is true even if they think that the person
\emph{should} be thinking about something else that X is preparing.

Knowledge cases are not like that. Different people may have different
standards for knowledge, so perhaps they may (speaker) mean different
things by \emph{A knows that p}, because they will communicate that
\emph{A} has met their preferred standards for knowledge. But in these
cases, each will regard the other as making a \emph{mistake}. Standards
for knowledge aren't the kind of thing we say people can differ on
without making a mistake, in the way we do (within reason) say that
different people can have different immediate goals (e.g.~about what to
have for dinner) without making a mistake. That explains why we don't
just adopt our questioners standards for knowledge when answering their
knowledge questions.

\emph{Objection}: In section 2 it was argued that questions involving
`knows' should have the three properties because questions involving
other terms for which Type B pragmatism is true have the properties. But
this argument by analogy may be flawed. All those terms are `indexical'
in John MacFarlane's sense
(\citeproc{ref-MacFarlane2009-MACNC}{MacFarlane 2009}). That is, the
\emph{content} of any utterance of them varies with the context. But not
all Type B pragmatist theories are indexical, and this argument does not
tell against a non-indexical Type B pragmatism.

\emph{Reply}: The view under consideration says that all utterances of
`\emph{S} knows that \emph{p}' express the same proposition, namely that
\emph{S} knows that \emph{p}. But the view is Type B because it says
that proposition can be true relative to some contexts and false
relative to other contexts, just as temporalists about propositions say
that a proposition can be true at some times and false at other times,
and the utterance is true iff the proposition is true in the context of
the utterance. This \emph{is} a Type B view, and I agree that the
argument by analogy in section 2 is powerless against it.

But that argument was not the only argument that Type B views are
committed to questions involving `knows' having the three properties.
There was also an argument, at the end of section 1, from purely
theoretical considerations. It turns out this argument is also
complicated to apply here, but it does tell against this type of Type B
pragmatist as well.

Here are two hypotheses about how one should answer a question
\emph{Does NP VP?} where NP is a noun phrase and VP a verb phrase.
Consider the proposition expressed by the sentence \emph{NP VP} in the
speaker's context. First hypothesis: the correct answer is `Yes' iff
that proposition is true in the speaker's context. Second hypothesis:
the correct answer is `Yes' iff that proposition is true in the
respondent's context. If propositions do not change their truth value
between contexts, these two hypotheses are equivalent, but on this
version of Type B pragmatism that is not so, so we have to decide
between them. The best way to do this is by thinking about cases where
it is common ground that propositions change their truth value between
contexts, namely cases where the contexts are possible worlds. Let's
consider the scenario I briefly discussed above of the television
watcher answering whatever question gets asked. Above I put the
questioners in the same possible world as me, but we can imagine they
are fictional characters in a different possible world. Imagine a show
where it has just been revealed to the audience, but not all the
characters, that the Prime Minister is a space alien. The following
happens.

\begin{quote}
Character (on screen): Is the Prime Minister a space alien?

Me (in real world): Yes!
\end{quote}

Since the proposition that the Prime Minister is a space alien is true
in their world, but not in our world, the propriety of this response
tells in favour of the first hypothesis above. Now this is not a
conclusive argument, because it might be that there is some distinctive
feature of fiction that is causing this answer, even though the second
hypothesis is in general correct. But it seems we have reason to think
that \emph{if} this kind of Type B pragmatism were true, respondents
would use the speaker's context to work out what kind of answer to give.
And as we saw above, this is not what respondents \emph{actually} do,
they either use their own context or (more likely) the subject's.

\emph{Objection}: At most this shows that Type B pragmatism about
`knows' is not actually true of English. But there might still be good
epistemological reasons to adopt it as a philosophically motivated
revision, even if the data from questions shows it isn't true. So even
if hermeneutic Type B pragmatism is false, revolutionary Type B
pragmatism might be well motivated.

\emph{Reply}: It's true that the philosophically most interesting
concepts may not map exactly on to the meanings of words in natural
language. (Though I think we should be careful before abandoning the
concepts that have proven useful enough to get simple representation in
the language.) And it's true that there are reasons for having
epistemological concepts that are sensitive to pragmatic factors. But
what is hard to see is what interest we could have in having
epistemological terms whose application is sensitive to the interests of
the person using them. Hawthorne (\citeproc{ref-Hawthorne2004}{2004})
provides many reasons for thinking that terms whose applications are
sensitive to the interests of the person to whom they are being applied
are philosophically and epistemologically valuable. Such terms provide
ways of expressing unified judgements about the person's intellectual
and practical reasoning. On the other hand, there is little to be gained
by \emph{adopting} Type B pragmatism. If there needs to be a revision
around here, and my guess is that there does not, it should be towards
Type A, not Type B, pragmatism.

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Cappelen2005}
Cappelen, Herman, and Ernest Lepore. 2005. \emph{Insensitive Semantics:
A Defence of Semantic Minimalism and Speech Act Pluralism}. Oxford:
Blackwell.

\bibitem[\citeproctext]{ref-Cohen1986}
Cohen, Stewart. 1986. {``Knowledge and Context.''} \emph{The Journal of
Philosophy} 83 (10): 574--83. doi:
\href{https://doi.org/10.2307/2026434}{10.2307/2026434}.

\bibitem[\citeproctext]{ref-DeRose1995}
DeRose, Keith. 1995. {``Solving the Skeptical Problem.''}
\emph{Philosophical Review} 104 (1): 1--52. doi:
\href{https://doi.org/10.2307/2186011}{10.2307/2186011}.

\bibitem[\citeproctext]{ref-DeRose2004}
---------. 2004. {``Single Scoreboard Semantics.''} \emph{Philosophical
Studies} 119 (1/2): 1--21. doi:
\href{https://doi.org/10.1023/b:phil.0000029347.01790.f2}{10.1023/b:phil.0000029347.01790.f2}.

\bibitem[\citeproctext]{ref-Egan2005-EGAEMI}
Egan, Andy, John Hawthorne, and Brian Weatherson. 2005. {``{Epistemic
Modals in Context}.''} In \emph{Contextualism in Philosophy: Knowledge,
Meaning, and Truth}, edited by Gerhard Preyer and Georg Peter, 131--70.
Oxford: Oxford University Press.

\bibitem[\citeproctext]{ref-Goldman2002}
Goldman, Alvin. 2002. {``What Is Social Epistemology? A Smorgasbord of
Projects.''} In \emph{Pathways to Knowledge: Private and Public}, by
Alvin Goldman, 182--204. Oxford: Oxford University Press.

\bibitem[\citeproctext]{ref-Grice1989}
Grice, H. Paul. 1989. \emph{Studies in the Way of Words}. Cambridge,
MA.: Harvard University Press.

\bibitem[\citeproctext]{ref-Hawthorne2004}
Hawthorne, John. 2004. \emph{Knowledge and Lotteries}. Oxford: Oxford
University Press.

\bibitem[\citeproctext]{ref-Hetherington2001}
Hetherington, Stephen. 2001. \emph{Good Knowledge, Bad Knowledge: On Two
Dogmas of Epistemology}. Oxford: Oxford University Press.

\bibitem[\citeproctext]{ref-Lewis1996b}
Lewis, David. 1996. {``Elusive Knowledge.''} \emph{Australasian Journal
of Philosophy} 74 (4): 549--67. doi:
\href{https://doi.org/10.1080/00048409612347521}{10.1080/00048409612347521}.
Reprinted in his \emph{Papers in Metaphysics and Epistemology},
Cambridge: Cambridge University Press, 1999, 418-446. References to
reprint.

\bibitem[\citeproctext]{ref-MacFarlane2005-Knowledge}
MacFarlane, John. 2005. {``The Assessment Sensitivity of Knowledge
Attributions.''} \emph{Oxford Studies in Epistemology} 1: 197--233.

\bibitem[\citeproctext]{ref-MacFarlane2009-MACNC}
---------. 2009. {``{Nonindexical Contextualism}.''} \emph{Synthese} 166
(2): 231--50. doi:
\href{https://doi.org/10.1007/s11229-007-9286-2}{10.1007/s11229-007-9286-2}.

\bibitem[\citeproctext]{ref-Stanley2000-STACAL}
Stanley, Jason. 2000. {``{Context and Logical Form}.''}
\emph{Linguistics and Philosophy} 23 (4): 391--434. doi:
\href{https://doi.org/10.1023/A:1005599312747}{10.1023/A:1005599312747}.

\bibitem[\citeproctext]{ref-Stanley2002-STANR}
---------. 2002. {``Nominal Restriction.''} In \emph{Logical Form and
Language}, edited by Georg Peter and Gerhard Preyer, 365--88. Oxford:
Oxford University Press.

\bibitem[\citeproctext]{ref-Stanley2005-STAKAP}
---------. 2005. \emph{{Knowledge and Practical Interests}}. Oxford
University Press.

\bibitem[\citeproctext]{ref-Weatherson2002-WEAMI}
Weatherson, Brian. 2002. {``Misleading Indexicals.''} \emph{Analysis} 62
(4): 308--10. doi:
\href{https://doi.org/10.1093/analys/62.4.308}{10.1093/analys/62.4.308}.

\bibitem[\citeproctext]{ref-Weatherson2005-WEACWD}
---------. 2005. {``{Can We Do Without Pragmatic Encroachment?}''}
\emph{Philosophical Perspectives} 19 (1): 417--43. doi:
\href{https://doi.org/10.1111/j.1520-8583.2005.00068.x}{10.1111/j.1520-8583.2005.00068.x}.

\end{CSLReferences}



\noindent Published in\emph{
Aspects of Knowing: Epistemological Essays}, 2006, pp. 133-147.


\end{document}
