---
title: "Changes in Citation Patterns"
abstract: |
  By looking at changes in citation patterns, we can tell something about the way in which academic philosophy has changed over the last few decades. One thing that stands out is the reduction in armchair approaches to non-fundamental questions. Another is that topics no longer disappear from philosophy. Since around 2002, every topic that has reached a certain level of prominence in the literature has retained its prominence. This is notably not the case before the late 1990s.
date: today
author:
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
categories:
  - history of analytic
  - in progress
  - unpublished
pdf-engine: xelatex
bibliography: /Users/weath/Documents/citations-2024/autobib.bib
csl: ../../../chicago-with-note.csl
draft: true
execute:
  echo: false
  warning: false
format:
  html:
    fig-format: svg
    fig-height: 9
    fig-width: 12
    fig-dpi: 300
    fig-responsive: true
    fontsize: 1.1rem
  pdf:
    fig-format: pdf
    include-after-body: 
        text: |
          \noindent Published online in September 2024.
  docx:
    reference-doc: ../../../quarto-articles-template.docx
---

```{r}
#| label: loader
#| cache: false

require(tidyverse)
require(slider)
require(stringr)
require(knitr)
require(toOrdinal)
require(kableExtra)

if(knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = 'cairo_pdf')
}

# Graph Themes
old <- theme_set(theme_minimal())
theme_set(old)
theme_update(plot.title = element_text(family = "Scala Pro", size = 24, face = "bold"),
             plot.subtitle = element_text(family = "Scala Sans Pro", size = 20),
             axis.text = element_text(family = "Scala Sans Pro", size = 18),
             plot.background = element_rect(fill = "#F9FFFF"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "#F9FFFF"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "Scala Sans Pro", size = 20),
             strip.text = element_text(family = "Scala Sans Pro", size = 20),
             legend.key.spacing.y = unit(0.5, 'lines'),
             legend.key.spacing.x = unit(1, 'cm')
  )

if(knitr::is_latex_output()) {
theme_update(plot.title = element_text(family = "Europa-Bold", size = 14),
             plot.subtitle = element_text(family = "EB Garamond", size = 11),
             axis.text = element_text(family = "EB Garamond", size = 10),
             plot.background = element_rect(fill = "white"),
             panel.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "white"),
             panel.grid = element_line(color = "grey92"),
             legend.text = element_text(family = "EB Garamond", size = 11),
             strip.text = element_text(family = "EB Garamond", size = 12),
             legend.key.spacing.y = unit(-0.3, 'lines'),
             legend.key.spacing.x = unit(0, 'cm')
  )

}
```

```{r}
#| lable: mainscripts
#| cache: false

require(tidyverse)
require(slider)
require(stringr)
require(lsa)

load("/Users/weath/Documents/citations-2024/philo_bib_fix.RData")
load("/Users/weath/Documents/citations-2024/philo_cite_with_jp.RData")

start_year <- 1965
end_year <- 2022
window <- 0
min_data <- 5

active_philo_bib <- philo_bib_fix |>
  filter(year >= start_year, year <= end_year) |>
  mutate(tbl_cite = paste0(display_author, " [-@",str_replace(id,":",""),"] \"", art_title, "\""))

authadjust <- function(x){
  paste0(str_extract(x, '\\b[^,]+$'), " ", str_to_title(str_extract(x,".+(?=,)")))
}

authadjust_short <- function(x){
  str_to_title(str_extract(x,".+(?=,)"))
}

article_years <- active_philo_bib |>
  as_tibble() |>
  select(id, year)

citation_tibble <- philo_cite_with_jp |>
  as_tibble() |>
  rename(new = id, old = refs) |>
  left_join(article_years, by = c("old" = "id")) |>
  rename(old_year = year)  |>
  left_join(article_years, by = c("new" = "id")) |>
  rename(new_year = year) |> # The next lines are new - restricting attention to 1966-end_year
  filter(new_year <= end_year, new_year >= start_year, old_year >= start_year, old_year <= end_year) 
```

```{r}
#| label: looper
#| cache: true

all_still_standing <- c()
all_median <- c()

for (i in 4:0){
  new_citation_tibble <- citation_tibble |>
    mutate(range_year = floor((old_year-i)/5)*5+i)
  all_early_cites <- new_citation_tibble |>
    filter(new_year - range_year <= 9)
  
  all_late_cites <- new_citation_tibble |>
    filter(new_year >= 2020)
  
  tally_late_cites <- all_late_cites |>
    ungroup() |>
    group_by(old) |>
    tally() |>
    arrange(desc(n))
  
  summ_early_cites <- all_early_cites |>
    ungroup() |>
    group_by(old, old_year, range_year) |>
    summarise(e_cites = n(), .groups = "drop")
  
  summ_late_cites <- all_late_cites |>
    ungroup() |>
    group_by(old, old_year, range_year) |>
    summarise(l_cites = n(), .groups = "drop")
  
  combined_cites <- summ_early_cites |>
    full_join(summ_late_cites, by = c("old", "old_year", "range_year")) |>
    mutate(
      across(everything(), ~replace_na(.x, 0))
    ) |>
    mutate(
      e_score = e_cites + l_cites/1000,
      l_score = l_cites + e_cites/1000
    ) |>
    group_by(range_year) |>
    mutate(
      e_rank = min_rank(-e_score),
      l_rank = min_rank(-l_score),
      o_rank = pmin(e_rank, l_rank)
    ) |>
    ungroup() |>
    arrange(o_rank, -e_score, -l_score) |>
    group_by(range_year) |>
    mutate(f_rank = row_number()) |>
    filter(f_rank <= 100) |>
    ungroup() |>
    left_join(active_philo_bib, by = c("old" = "id", "old_year" = "year"))
  
  still_standing <- combined_cites |>
    filter(e_rank <= 20) |>
    select(e_cites, l_cites, display_author, old_year, range_year, art_title, journal, everything()) |>
    arrange(range_year, desc(e_cites))
  
  still_standing_by_range <- still_standing |>
    filter(l_cites >= 16) |>
    ungroup() |>
    group_by(range_year) |>
    tally()
  
  median_new_cites_of_classics <- combined_cites |>
    ungroup() |>
    group_by(range_year) |>
    filter(e_rank <= 20) |>
    summarise(cites = median(l_cites))
  
  all_still_standing <- bind_rows(all_still_standing, still_standing_by_range)
  all_median <- bind_rows(all_median, median_new_cites_of_classics)
}

article_count <- active_philo_bib |>
  group_by(year) |>
  tally() |>
  mutate(five_year = slide_int(n, sum, .before = 4))

how_many_recent_cites <- philo_cite_with_jp |>
  as_tibble() |>
  rename(new = id, old = refs) |>
  left_join(article_years, by = c("old" = "id")) |>
  rename(old_year = year)  |>
  left_join(article_years, by = c("new" = "id")) |>
  rename(new_year = year) |> # The next lines are new - restricting attention to 1966-end_year
  filter(new_year <= end_year, new_year >= start_year, old_year >= start_year, old_year <= end_year) |>
  filter(new_year >= 2020) |>
  ungroup() |>
  group_by(old) |>
  tally() |>
  left_join(active_philo_bib, by = c("old" = "id")) |>
  arrange(-n)

top_20_recent <- how_many_recent_cites |>
  select(`Recent Citations` = n, Article = tbl_cite) |>
  slice(1:20)

top_20_last_quartile <- how_many_recent_cites |>
  filter(year >= 1976, year <= 1997) |>
  select(`Recent Citations` = n, Article = tbl_cite) |>
  slice(1:20)

top_20_last_five <- how_many_recent_cites |>
  filter(year >= 2015) |>
  select(`Recent Citations` = n, Article = tbl_cite) |>
  slice(1:20)

most_cited_years_recently <- philo_cite_with_jp |>
  as_tibble() |>
  rename(new = id, old = refs) |>
  left_join(article_years, by = c("old" = "id")) |>
  rename(old_year = year)  |>
  left_join(article_years, by = c("new" = "id")) |>
  rename(new_year = year) |> # The next lines are new - restricting attention to 1966-end_year
  filter(new_year <= end_year, new_year >= start_year, old_year >= start_year, old_year <= end_year) |>
  filter(new_year >= 2020) |>
  group_by(old_year) |>
  tally(name = "cites") |>
  left_join(article_count, by = c("old_year" = "year")) |>
  select(year = old_year, cites, articles = n) |>
  mutate(rate = cites / articles)

recent_cite_frequency <- how_many_recent_cites |>
  group_by(n) |>
  tally(name = "art_num") |>
  arrange(-n) |>
  mutate(at_least = cumsum(art_num)) |>
  arrange(n) |>
  slice(1:10, 3:10*5)

median_cites_unqualified <- tribble(~year, ~median)

for (y in 1965:2010){
  temp <- citation_tibble |>
    filter(old_year >= y, old_year <= y + 4, new_year >= 2020) |>
    group_by(old) |>
    tally() |>
    arrange(-n) |>
    slice(1:20)
  median_cites_unqualified <- median_cites_unqualified |>
    add_row(year = y, median = median(temp$n))
}

the_top_few <- c()

for (y in 1965:2010){
  target_articles <- floor(
    filter(
      article_count, year == y + 4
      )$five_year[1] * 0.003
  )
#  target_articles <- 20
  yearly_additions <- citation_tibble |>
    ungroup() |>
#    select(-range_year) |>
    filter(old_year >= y, old_year <= y + 4) |>
    filter(new_year <= y + 9 | new_year >= 2020) |>
    mutate(cite_age = case_when(
      new_year <= y + 9 ~ "e_cites",
      new_year >= 2020 ~ "l_cites"
    )) |>
    group_by(old, old_year, cite_age) |>
    summarise(cites = n(), .groups = "drop") |>
    pivot_wider(id_cols = c(old), names_from = cite_age, values_from = cites) |>
    replace_na(list(e_cites = 0, l_cites = 0)) |>
    mutate(score = e_cites + l_cites/1000) |>
    mutate(the_rank = rank(-score)) |>
    arrange(the_rank) |>
    slice(1:target_articles) |>
    select(-score, -the_rank) |>
    mutate(range_year = y) |>
    left_join(philo_bib_fix, by = c("old" = "id")) |>
    select(e_cites, l_cites, display_author, year, range_year, art_title, journal, everything()) 
  
  the_top_few <- bind_rows(the_top_few, yearly_additions)
}

the_top_few <- the_top_few |>
  ungroup() |>
  group_by(old) |>
  mutate(appear = n()) |>
  select(appear, everything()) |>
  arrange(-appear, l_cites, old)

proportion_recent <- the_top_few |>
  group_by(range_year) |>
  summarise(med_cites = median(l_cites))

the_920 <- c()

for (y in 1965:2010){
  the_20 <- citation_tibble |>
    ungroup() |>
#    select(-range_year) |>
    filter(old_year >= y, old_year <= y + 4) |>
    filter(new_year <= y + 9 | new_year >= 2020) |>
    mutate(cite_age = case_when(
      new_year <= y + 9 ~ "e_cites",
      new_year >= 2020 ~ "l_cites"
    )) |>
    group_by(old, old_year, cite_age) |>
    summarise(cites = n(), .groups = "drop") |>
    pivot_wider(id_cols = c(old), names_from = cite_age, values_from = cites) |>
    replace_na(list(e_cites = 0, l_cites = 0)) |>
    mutate(score = e_cites + l_cites/1000) |>
    mutate(the_rank = rank(-score)) |>
    arrange(the_rank) |>
    slice(1:20) |>
    select(-score, -the_rank) |>
    mutate(range_year = y) |>
    left_join(active_philo_bib, by = c("old" = "id")) |>
    select(e_cites, l_cites, display_author, year, range_year, art_title, journal, everything()) 
  
  the_920 <- bind_rows(the_920, the_20)
}

the_920 <- the_920 |>
  ungroup() |>
  group_by(old) |>
  mutate(appear = n()) |>
  select(appear, everything()) |>
  arrange(-appear, l_cites, old) |>
  ungroup()

the_4600 <- c()

for (y in 1965:2010){
  the_100 <- citation_tibble |>
    ungroup() |>
#    select(-range_year) |>
    filter(old_year >= y, old_year <= y + 4) |>
    filter(new_year <= y + 9 | new_year >= 2020) |>
    mutate(cite_age = case_when(
      new_year <= y + 9 ~ "e_cites",
      new_year >= 2020 ~ "l_cites"
    )) |>
    group_by(old, old_year, cite_age) |>
    summarise(cites = n(), .groups = "drop") |>
    pivot_wider(id_cols = c(old), names_from = cite_age, values_from = cites) |>
    replace_na(list(e_cites = 0, l_cites = 0)) |>
    mutate(score = e_cites + l_cites/1000) |>
    mutate(the_rank = rank(-score)) |>
    arrange(the_rank) |>
    slice(1:100) |>
    select(-score, -the_rank) |>
    mutate(range_year = y) |>
    left_join(active_philo_bib, by = c("old" = "id")) |>
    select(e_cites, l_cites, display_author, year, range_year, art_title, journal, everything()) |>
    arrange(-e_cites, -l_cites) |>
    ungroup() |>
    mutate(rank = row_number())
  
  the_4600 <- bind_rows(the_4600, the_100)
}

the_4600 <- the_4600 |>
  ungroup() |>
  group_by(old) |>
  mutate(appear = n()) |>
  select(appear, everything()) |>
  arrange(-appear, l_cites, old) |>
  ungroup()

appear_median <- the_920 |>
  ungroup() |>
  group_by(appear) |>
  summarise(l_cites = median(l_cites))

# the_920 |> 
#     filter(appear == 3) |>
#     ungroup() |>
#     mutate(l_cites = replace(l_cites, l_cites == 0, 0.5)) |>
#     ungroup() |>
#     distinct(old, .keep_all = TRUE) |>
#     select(year, l_cites) |>
#     ggplot(aes(x = year, y = l_cites)) + 
#       geom_point() + 
#       scale_y_log10() +
#       ggrepel::geom_label_repel(data = filter(the_920, appear == 3, (l_cites <= 1 | (year >= 2000 & l_cites <= 10))), aes(label = shortcite))

the_920_graph <- the_920 |>
  filter(appear == 3, year >= 1979) |>
  ungroup() |>
  mutate(l_cites = replace(l_cites, l_cites == 0, 0.5)) |>
  distinct(old, .keep_all = TRUE) |>
  mutate(outlier = case_when(
    l_cites <= 5 ~ TRUE,
    year >= 2000 & l_cites <= 9 ~ TRUE,
    TRUE ~ FALSE))

#ggplot(the_920_graph, aes(x = year, y = l_cites))  + 
#  geom_point() + 
#  scale_y_log10(limits = c(0.5, 250)) 

widely_cited <- citation_tibble |>
  filter(old_year >= 1974, old_year <= 2010) |>
  filter(new_year <= old_year + 9 | new_year >= 2020) |>
  mutate(cite_age = case_when(
    new_year <= old_year + 9 ~ "e_cites",
    new_year >= 2020 ~ "l_cites"
  )) |>
  group_by(old, old_year, cite_age) |>
  summarise(cites = n(), .groups = "drop") |>
  pivot_wider(id_cols = c(old, old_year), names_from = cite_age, values_from = cites) |>
  replace_na(list(e_cites = 0, l_cites = 0)) |>
  left_join(active_philo_bib, by = c("old" = "id", "old_year" = "year")) |>
  select(e_cites, l_cites, display_author, old_year, art_title, journal, everything()) |>
  filter(l_cites >= 16)

widely_cited_years <- widely_cited |>
  filter(l_cites >= 16) |>
  group_by(old_year) |>
  tally()

very_late_bloomers <- widely_cited |>
  anti_join(the_920, by = "old") |>
  filter(old_year <= 2005) |>
  arrange(-l_cites)
```

By looking at changes in citation patterns, we can tell something about the way in which academic philosophy has changed over the last few decades. One thing that stands out is the reduction in armchair approaches to non-fundamental questions. Another is that topics no longer disappear from philosophy. Since around 2002, every topic that has reached a certain level of prominence in the literature has retained its prominence. This is notably not the case before the late 1990s.

# Introduction {#sec-introduction}

This paper is about citations of philosophy journal articles in philosophy journal articles. The data comes from Web of Science. I'm focussing on citations between philosophy journals for two reasons. One is that the data is much cleaner. Citations to books, chapters, theses, and other sources, requires a lot of work to be even approximately correct, while citations of journals in journals are reasonably reliable. (This is especially true for journals that use end of article bibliographies; there the reliability is very high.) The second is that the data is complete. It's very hard to get a complete list of all the philosophy books published in a year, or even conceptually to think about what that would mean. It's much easier to find some journals, and get a complete list of their articles.

I'm focusing on journals published since 1965. So the citations are of articles published since 1965, in articles published since 1965. That means that at the start there are very few citations, since most citations are to things a few years earlier.

One problem with using Web of Science is that it is very slow to update. I'm using the XML files that are provided to subscribing institutions. The most recent such files that are provided only go through mid-2022. Much of the focus here is on citations since 2020. Crucially, this does not mean 2020-2024; it just means 2020-to-mid-2022. This still turns out to be a lot of citations.

Web of Science is also slow to add journals to its index. As @tbl-list-of-journals shows, several journals are only added to the index well after 1965, or (in the case of some recently founded journals) well after their founding. The biggest impact this has on this paper is that we don't have the citation data for _Analysis_ before 1975, and that probably affects some of the results.

I'm also focusing on one hundred journals. I downloaded the citation data for every journal in the categories Philosophy, and History and Philosophy of Science, and picked out the hundred journals with the most articles, which seemed to be primarily English language, analytic, and philosophy as opposed to history of science journals. The journals that I picked are listed in @tbl-list-of-journals.

```{r}
#| label: tbl-list-of-journals
#| tbl-cap: "The journals included in this study."

require(knitr)
temp <- philo_bib_fix |>
  filter(year >= 1956, year <= 2022) |>
  filter(id != "gettier1963") |>
  group_by(journal) |> 
  summarise(Articles = n(), `First Year` = min(year), `Most Recent Year` = max(year)) |>
  rename(Journal = journal)
kable(temp)
```

Of course the first year isn't the first year the journal started publishing; it's when Web of Science started indexing them. And the last year isn't when they ceased publishing; it's the most recent year indexed. Web of Science is very slow at adding journals, and at adding volumes. But it is, as far as I've found, pretty accurate within what it adds.

One big exception to this is that it's never really understood how to handle the 'supplements' to _Noûs_, i.e., _Philosophical Perspectives_ and _Philosophical Issues_. Some of these are recorded as being their own thing, some of them are recorded as special issues of _Noûs_. In the latter case, the citations often only start being tracked several years after publication, and the bibliographic information is spotty. I've manually removed the ones that were listed as being published in _Noûs_ but actually in one of the supplements, because the data didn't seem sufficiently reliable. The major cost of this is that Kit Fine's paper "Essence and Modality" isn't part of the study; this is something that I might need to correct.

I've also manually added citations to articles published in _Journal of Philosophy_ between 1971 and 1974. I don't have good data for what was cited in those articles. I don't know why Web of Science indexes the Journal before and after that period, but it's an important gap. Several of the most important articles of the journals era are published in the Journal in those years, so I felt it was important to include them. I hope that the manual adding I did led to values on the same scale as what I got from everything else, but this is a possible source of noise in the data.

Because Web of Science keeps adding journals, and journals keep getting larger, the number of articles in this study keeps going up. The only downward pressure comes from the fact that some journals haven't been indexed for 2022 or even, in some cases, 2021. @fig-number-of-articles-by-year shows how many articles each year are in the study.

```{r}
#| label: fig-number-of-articles-by-year
#| fig-cap: "Number of articles in the study each year" 

philo_bib_fix |>
  group_by(year) |>
  filter(year >= 1965, year <= 2022) |>
  tally() |>
  ggplot(aes(x = year, y = n)) +
    geom_line() +

    labs(x = element_blank(),
         y = element_blank(),
         title = "Number of Articles in Database Each Year") +
  scale_x_continuous(breaks = 195:202 * 10, minor_breaks = 390:404*5) 
```

On top of that, citation practices have changed and people now cite much more widely than they used to. So the number of citations recorded each year (to articles since 1965 indexed in these hundred journals), has risen rather dramatically, as shown in @fig-number-of-citations-by-year.

```{r}
#| label: fig-number-of-citations-by-year
#| fig-cap: "Number of citations to articles in the study each year" 

citation_tibble |>
  group_by(new_year) |>
  filter(new_year >= 1965, new_year <= 2022) |>
  tally() |>
  ggplot(aes(x = new_year, y = n)) +
  geom_line() +
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.direction = "vertical") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Number of Citations in Database Each Year") +
  scale_x_continuous(breaks = 195:202 * 10, minor_breaks = 390:404*5) 
```

On the other hand, since the overwhelming majority of citations are to articles published earlier than the citing article, a larger number of citations in total might be consistent with fewer citations per article available to be cited. If we somewhat arbitrarily set the universe of available to be cited papers as the set of papers with the same publication date as the citing article or earlier, @fig-average-of-citations-by-year shows how often the average paper was cited each year (in these 100 journals).

```{r}
#| label: fig-average-of-citations-by-year
#| fig-cap: "Average number of citations per available article in each year" 

article_years_summary <- article_years |>
  ungroup() |>
  group_by(year) |>
  tally(name = "yearly_articles") |>
  mutate(cumulative_articles = cumsum(yearly_articles))

mean_citations <- citation_tibble |>
  group_by(new_year) |>
  tally(name = "yearly_citations") |>
  left_join(article_years_summary, by = c("new_year" = "year")) |>
  mutate(mean_citations = yearly_citations/cumulative_articles) |>
  filter(new_year <= 2022)

ggplot(mean_citations, aes(x = new_year, y = mean_citations)) +
  geom_line() +
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.direction = "vertical") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Average number of citations articles get each year",
       subtitle = "Number of citations in a year divided by articles published up to that year") +
  scale_x_continuous(breaks = 195:202 * 10, minor_breaks = 390:404*5) 
```

Between about 1978 and 2004, the different forces are roughly balanced. There are more papers, and each paper cites more often, but there are more papers available to be cited, and the mean stays at about 0.1. But then the forces pushing this number up take over.

# Recent Citations {#sec-recent-citations}

The focus here is going to be on articles whose recent citation patterns are markedly different to their citation pattern since 2020. To understand these, it helps to have a sense of what the citations since 2020 are like.

The first thing to know about the 2020s is that the number of outbound citations per article shot up, starting in 2021. This is shown in @fig-outbound-citation-rate.

```{r}
#| label: fig-outbound-citation-rate
#| fig-cap: "Average number of outbound citations in each year" 

article_years_summary <- article_years |>
  ungroup() |>
  group_by(year) |>
  tally(name = "yearly_articles") |>
  mutate(cumulative_articles = cumsum(yearly_articles))

mean_outbound_citations <- citation_tibble |>
  group_by(new_year) |>
  tally(name = "yearly_citations") |>
  left_join(article_years_summary, by = c("new_year" = "year")) |>
  mutate(mean_citations = yearly_citations/yearly_articles) |>
  filter(new_year <= 2022)

ggplot(mean_outbound_citations, aes(x = new_year, y = mean_citations)) +
  geom_line() +
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.direction = "vertical") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Average number of outbound citations in each year",
       subtitle = "Number of citations in a year divided by articles published in that year") +
  scale_x_continuous(breaks = 195:202 * 10, minor_breaks = 390:404*5) 
```

Remember these are outbound citations to philosophy journal articles published since 1965. At the left hand edge of @fig-outbound-citation-rate, the 'since 1965' constraint probably makes a big difference to the graph. It shouldn't really make a difference towards the right of the graph, and yet the line keeps going up.

Between the number of articles published since 2020, and the high rate of outbound citations in those articles, there are a lot of citations since 2020. The whole study, from 1965 to 2022, includes `r nrow(citation_tibble)` citations. The part since 2020 alone includes `r nrow(filter(citation_tibble, new_year >= 2020))` of those citations.

The study contains `r nrow(active_philo_bib)` papers. So the average paper was cited about 1.2 times since 2020. Citations are not distributed at all evenly. @tbl-count-of-recent-citations shows how many articles have at least *n* citations since 2020 for various values of *n*.

```{r}
#| label: tbl-count-of-recent-citations
#| tbl-cap: "Frequency of articles with at least n citations, for various values of n"
#| html-table-processing: none
#| warning: false

select(
  recent_cite_frequency, n, `Number of articles` = at_least
) |>
  kable() |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

Just over 1% of articles have at least fifteen citations since 2020. Just under 0.1% have at least fifty citations. I'll sometimes talk below about articles that were once the center of attention having 'only' five citations since 2020. It's worth remembering that this still means they are in the top 7% or so for citations over that time. Most things don't get cited, at least in other philosophy journals in this time period.

The very top of the citation list, since 2020, is shown in @tbl-recent-high-cite.

```{r}
#| label: tbl-recent-high-cite
#| tbl-cap: "Twenty most cited articles since 2020"
#| column: page-right
#| tbl-colwidths: [15,85]

kable(top_20_recent, align = 'll')
```

The most recent article in that list is from 2016. That might lead you to think that philosophy citations are typically to rather old articles. This isn't true. @fig-recent-cite-rate shows how often, on average, papers with different publication years are cited since 2020.

```{r}
#| label: fig-recent-cite-rate
#| fig-cap: "Average number of cites since 2020 by year of original publication"

ggplot(most_cited_years_recently, aes(x = year, y = rate)) +
  geom_line() +
  labs(x = element_blank(), 
       y = element_blank(),
       title = "Average number of recent citations",
       subtitle = "Number of citations since 2020 to a year, divided by number of articles published that year")  +
  scale_x_continuous(breaks = 195:202 * 10, minor_breaks = 390:404*5)

```

The peak is actually in 2018. Recently published articles are, on average, cited more than articles from longer ago. It's just that the citations are more widely spread out. @tbl-recent-from-last-five shows which articles since 2016 have the most citations since 2020.

```{r}
#| label: tbl-recent-from-last-five
#| tbl-cap: "Twenty most cited articles since 2020, first published since 2016."
#| column: page-right
#| tbl-colwidths: [15,85]

kable(top_20_last_five, align = 'll')
```

The list of authors there is a little less white, and a little less male, than most of the lists we'll see below. As we'll see, that's not saying much.

Many of the articles that were recently widely cited have been cited a lot almost as soon as they were published. But not all of them were. @tbl-very-late-bloomers lists the articles with the most cites since 2020 that were, in a sense I'll get to below, not widely cited when they were first published.

```{r}
#| label: tbl-very-late-bloomers
#| tbl-cap: "Twenty most cited articles since 2020 that were not (as) widely cited when they were published."
#| column: page-right
#| tbl-colwidths: [15,85]

kable(
  select(
    very_late_bloomers,
    `Recent Citations` = l_cites,
    Article = tbl_cite
  ) |> slice(1:20), align = 'll'
)
```

The variety of subjects there is interesting, and this will become important later. Several of these papers can be now seen as foundational papers in thriving topics within philosophy.^[Citation counts are usually not a particularly reliable guide to philosophical quality, but this table might be an exception. A pro-seminar based around the fin de siècle papers from the top of this list would give students a very good guide to both what has been happening in philosophy, and how to do it well. You could, for instance, do the articles by Haslanger, Joyce, D'Arms and Jacobson, Douglas, Goldman, Smith, and Hieronymi, perhaps pairing each with a recent article building on that foundational work.]

The last thing to note, and something that will be central to what I'm discussing the rest of the paper, is that there is a 'missing middle' in @tbl-recent-high-cite. The only articles on that list between 1976 and 1997 are by David Lewis. @tbl-last-quartile shows the ten most cited articles, since 2020, published from 1976 to 1997.

```{r}
#| label: tbl-last-quartile
#| tbl-cap: "The most cited articles since 2020 first published between 1976 and 1997."

kable(top_20_last_quartile |> slice(1:10), align = 'll')
```

If we extended that list, the 15th, 16th, and 17th entries would also be by David Lewis.

One thing I'm investigating here is how relatively little influence journal articles from the 1980s and (much of) the 1990s have on the recent literature, compared to the decades either side of that. The focus here will be on the change in citation rates, how things that were the center of attention in the 1980s and 1990s are not so important now. But in the background will be the broader topic of how much the recent literature is shaped by the 1970s, 2000s, and 2010s, but not the decades in between.

# Where Are They Now? {#sec-where-are}

Focus for now on the period from 1965 to 2014. That fifty year period naturally divides into ten half-decades. 

For each half-decade, find the articles first published in that half-decade that are most cited by the end of the subsequent half-decade. For example, for the early 1990s (1990-1994), find the articles that are most cited by the end of the 1990s. These are shown in @tbl-20-from-early-90s.

```{r}
#| label: tbl-20-from-early-90s
#| tbl-cap: "The twenty articles from the early 1990s most cited by the end of the 1990s."
#| column: page-right
#| tbl-colwidths: [15,85]

kable(
  the_920 |>
    filter(range_year == 1990) |>
    arrange(-l_cites) |>
    ungroup() |>
    select('Recent Citations' = l_cites, Article = tbl_cite), align = 'll'
)
```

A few notes about this table.

On the left are the number of citations each article has in the dataset since 2020; i.e., between 2020 and mid-2022 in the hundred journals I'm focusing on.

Citations come in whole numbers and they aren't large, so ties are common. For finding the twenty most cited articles by the end of the 1990s, I used the number of citations since 2020 as a tie-breaker. In this case there were two papers, "What An Anti-Individualist Knows A Priori" [@WOSA1992HT19500013], and "Must Psychology Be Individualistic" [@WOSA1991FF02900001], which had 16 citations in the 1990s, the same as many other papers in @tbl-20-from-early-90s. But they only had two cites each since 2020, and they were not included on the list on this tie-breaker rule.

The effect of using this as a tie-breaker is to somewhat increase the numbers in the left-hand column. Despite this, the numbers there are surprisingly low. The median number of citations is just 8.5. This doesn't feel like a lot for the twenty papers that, at the time, most dominated discussion in the journals. If we do the same calculation for each of the other ten half-decades, and graph the results, we get @fig-median-by-half-decades. 

```{r}
#| label: fig-median-by-half-decades
#| fig-cap: "Median citations since 2020 for the 20 articles most cited at the time in different half-decades."

ggplot(filter(
        all_median, range_year %% 5 == 0, range_year <= 2010
        ),
       aes(x = range_year, y = cites)) +
  geom_point(size = 2) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites")
```

The value for 1990 is rather low, in fact the second-lowest of all the half-decades. But all the values in the 1980s and 1990s are surprisingly low. In none of those four periods does the median top-20 article, in terms of citations at the time, land in the top 1% of articles in terms in recent citations.

@fig-median-by-half-decades is a bit misleading though, because it gives too much weight to articles published at the start of half-decades. It is much easier to get articles published in 1990 or 1991 onto lists like @tbl-20-from-early-90s than articles published in 1993 or 1994; they simply have more time to accure citations before the somewhat arbitrary 'end of the 90s' cutoff.

The way to fix that problem is to think more abstractly about what @tbl-20-from-early-90s represents. For some year *y* (in this case 1990), we find the twenty articles published between *y* and *y*+4 with the most citations by *y*+9. When *y* is a multiple of 10 there are relatively natural ways to state what we're doing: articles from the early 90s with the most citations in the 90s. But we could do exactly the same thing for years that are not multiples of 5. If *y* is 1988, we could find the twenty articles published between 1988 and 1992 with the most citations by 1997; that's the same idea as @tbl-20-from-early-90s, just using years that aren't as natural to represent in base 10.

If find that list of twenty articles for every value of *y* from 1965 to 2010, we can fill in the gaps between the dots in @fig-median-by-half-decades. The result is @fig-all-median. (I'll come back to what the colors represent.)

```{r}
#| label: fig-all-median
#| fig-cap: "Median citations since 2020 for the 20 articles most cited at the time in different 5 year periods."

ggplot(all_median |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = cites)
         ) +
  geom_point(aes(x = range_year, y = cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")
```

@fig-all-median is a measure of how often articles that were widely cited at the time they were published are cited in the recent literature.

Each dot represents twenty articles published in the five years starting with the year on the x-axis. Those five year periods overlap, and so the twenty articles each dot represents can overlap too. @tbl-the-fives lists the articles that appear in five different 'top-twenty' lists, alongside how often they have been cited since 2020.

```{r}
#| label: tbl-the-fives
#| tbl-cap: "Articles appearing in five of the top twenty lists."
#| column: page-right
#| tbl-colwidths: [15,85]

kable(
  the_920 |>
    ungroup() |>
    filter(appear == 5) |>
    distinct(old, .keep_all = TRUE) |>
    arrange(year, -l_cites) |>
    select(`Recent Citations` = l_cites, Article = tbl_cite), align = 'll'
)
```

The existence of papers like this tells us something about the kind of thing that @fig-all-median is measuring. Ultimately we're trying to look at this question:

- In the recent literature, how widely cited are articles which were widely cited when they were first published?

One immediate challenge is that the last clause in that, 'when they were first published' is rather vague. Philosophy moves slowly, so citations within five years of publication definitely count for judging whether a paper was widely cited when it was first published. But citations ten years later do not seem to count. Between five and ten though, where is the boundary?

One option would be to pick an arbitrary boundary, perhaps seven years, and work with that. But it would be better if we could have a measure that respected the vagueness in the original question. There are a lot of ways to do that, and the measure I'm using is one of them. To see how that's true, it helps to use some extreme (and fictional) cases. Consider two papers, which I'll simply call A and B. Both of them, we'll imagine, were published in 1990.

- Paper A was cited 10 times every year from 1991-1996, and never cited again.
- Paper B was not cited at all until 1999, then cited twenty times a year every year since.

Both Paper A and Paper B will show up in @fig-all-median. But Paper A will make a much bigger impact on the graph. 

Paper A will be part of the 'top twenty' for the ranges 1990-1994, 1991-1995, 1992-1996, 1993-1997, and 1994-1998. In every one of those years, it will pull down the median value as shown on @fig-all-median, since it is not cited at all since 2020.

Paper B will only be part of the 'top twenty' for the range 1990-1999. It will the median for that range, since it was cited 60 times since 2020.

The general pattern is that because I'm using overlapping ranges, and not using a simple on-off criteria for whether a citation is soon after publication, papers which get cited even earlier can make more impact on this graph. That's not to say this is the only measure that one could use to answer the question, but it's one reason that this is a particularly helpful measure to use.

# The Missing Middle {#sec-missing-middle}

Here's a very striking thing about @fig-all-median. All the blue dots, representing the ranges from 1980-1984 to 1995-1999, are below all the purple dots, representing later ranges, and, more strikingly, all the green dots, representing ranges from 1974-1978 to 1979-1983. There are a few reasons that you might expect the graph to trend upwards. But the uniformity here, every blue dot being below the all the greens and purples, and the two notable falls, in the early 1980s and again in the early 1990s, are striking.

What could explain this pattern?

Before I get to that, I want to run over some data that suggests this is really a pattern, and not just an artifact of the way I'm measuring things. So this section will go over a few other ways of representing the data that mostly show a similar pattern.

In @fig-all-median, I'm looking at the median citations for twenty articles from each five year period. You might worry that this is a bad way to look at things. As @fig-number-of-articles-by-year shows, there are more articles published in later years. Being in the top twenty gets harder and harder as the competition expands. Perhaps all that @fig-all-median shows is that some articles which aren't really _widely cited at the time_ in a natural sense are nevertheless ending up in top twenties.

There is a grain of truth to this worry. One reason I'm using ranges, rather than focussing on the most cited articles in individual years, is that there are some years where very few articles at all are widely cited at the time. This was particularly true in 1980, 1985, and 1990. (I think it's just a coincidence that they are all multiples of 5.) Using ranges moderated that a little.

Still, the cut off of top _twenty_ might seem inappropriate given the changing size of the population of articles. So I reran the analysis instead looking at articles that were in the top 0.3% of articles cited from the five year range. I picked that percentage because for the 1980s and 1990s that gives us approximately twenty articles per range. But it means fewer articles before 1980, and considerably more articles after 2000. The results are shown in @fig-proportion-median.

```{r}
#| label: fig-proportion-median
#| fig-cap: "Median citations since 2020 for the 0.3% most cited at the time in different 5 year periods."

ggplot(proportion_recent |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = med_cites)
         ) +
  geom_point(aes(x = range_year, y = med_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")
```

Not a lot changes from @fig-all-median to @fig-proportion-median. Some of the red dots move up, the last of the red dots and first of the green dots switch values, and the gap between the blue and purple dots decreases. But the shape is the same. Since it easier to talk about twenty articles per range than 0.3%, and the shape is roughly the same, I'll stick to looking at top twenties.

It's usually a mistake to look at arithmetic means of citations, since they are so affected by outliers. But we can rerun the calculation behind @fig-all-median using means. The results, as shown in @fig-all-mean, are a little different since every range that includes "New Work for a Theory of Universals" [@WOSA1983RR51600001] gets raised a lot. But the shape is still fairly similar.

```{r}
#| label: fig-all-mean
#| fig-cap: "Mean citations since 2020 for the top twenty most cited at the time in different 5 year periods."

all_mean <- the_920 |>
  ungroup() |>
  group_by(range_year) |>
  summarise(mean_cites = mean(l_cites))

ggplot(all_mean |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = mean_cites)
         ) +
  geom_point(aes(x = range_year, y = mean_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Mean cites") +
  theme(legend.position = "none")
```

One natural way to mitigate the impact of these outliers is to take the geometric mean of the values rather than the arithmetic mean. The problem here is that some of the articles have zero citations, and the geometric mean of any set of (non-negative) integers including a zero is zero. Rather than having that value swamp, I've taken the geometric means of the number of recent citations of the twenty articles after replacing all zero values with 0.5. So for the purposes of @fig-all-geometric-mean, articles with no citations since 2020 are recorded as having half a citation. The shape is back to something similar to @fig-all-median.

```{r}
#| label: fig-all-geometric-mean
#| fig-cap: "Geometric mean citations since 2020 for the top twenty most cited at the time in different 5 year periods."

all_geom_mean <- the_920 |>
  ungroup() |>
  mutate(l_cites = case_when(
    l_cites == 0 ~ 0.5,
    TRUE ~ l_cites
  )) |>
  group_by(range_year) |>
  summarise(mean_cites = exp(mean(log(l_cites))))

ggplot(all_geom_mean |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = mean_cites)
         ) +
  geom_point(aes(x = range_year, y = mean_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Geometric mean cites") +
  theme(legend.position = "none")
```

The value for 1978-1982 is pulled down, and the values for the ranges after 1990 are a bit higher, but the shape is still pretty similar to @fig-all-median.

Maybe this is an artifact of looking at the top twenty rather than some different number. We could be more restrictive, or more expansive, with the number of articles from each range we regard as widely cited. In @fig-diff-top-median, I show what happens if we recreate @fig-all-median using top tens and top forties.

::::{.column-page}

::: {#fig-diff-top-median layout-ncol=2 fig-cap="Recreation of @fig-all-median using different numbers of articles per five year range."}

```{r}
#| label: fig-diff-top-median-10
#| fig-cap: "Top ten."

top_10_median <- the_4600 |>
  ungroup() |>
  filter(rank <= 10) |>
  group_by(range_year) |>
  summarise(median_cites = median(l_cites))

top_40_median <- the_4600 |>
  ungroup() |>
  filter(rank <= 40) |>
  group_by(range_year) |>
  summarise(median_cites = median(l_cites))

ggplot(top_10_median |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = median_cites)
         ) +
  geom_point(aes(x = range_year, y = median_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")
```

```{r}
#| label: fig-diff-top-median-40
#| fig-cap: "Top forty."

ggplot(top_40_median |>
         filter(range_year >= 1965,
                range_year <= 2010) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = median_cites)
         ) +
  geom_point(aes(x = range_year, y = median_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")
```
:::
::::

On the top tens graph, the pattern is the same as @fig-all-median, and perhaps a little more pronounces. The blue dots are also below the last three red dots; we could have started that period with the 1971-1975 range and seen the same pattern. On the top forties graph, the numbers are compressed. There is one relatively high blue dot (for 1991-1995), the first purple dot is still rather low, and some of the green dots are not that high. But I think the shape, of a rise in the 1970s followed by a fall and not much movement until the late 1990s, is still there.

Finally, we might worry that @fig-all-median simply shows that philosophers have a disposition to note cite things more than twenty-five years old. If that were right, we'd expect to see the graphs look rather different if we imagined doing the same study with different stopping points. In @fig-different-ends I reran the study using first 2015-2017, and then 2010-2012, as the values for 'recent' cites. In both cases I stopped doing calculations just before the point where the ranges for _citations at the time_ and _recent citations_ would overlap.

::::{.column-page}
::: {#fig-different-ends layout-ncol=2 fig-cap="Recreation of @fig-all-median using different years as the range for later citations."}

```{r}
#| label: fig-different-ends-2015
#| fig-cap: "Recent = 2015-2017"

middle_cites <- citation_tibble |>
  filter(new_year >= 2015, new_year <= 2017) |>
  group_by(old, old_year) |>
  tally(name = "m_cites") |>
  ungroup() |>
  select(old, m_cites)

the_920_middle <- the_920 |>
  left_join(middle_cites, by = "old") |>
  mutate(m_cites = replace_na(m_cites, 0)) |>
  ungroup() |>
  group_by(range_year) |>
  summarise(median_cites = median(m_cites))

ggplot(the_920_middle |>
         filter(range_year >= 1965,
                range_year <= 2005) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = median_cites)
         ) +
  geom_point(aes(x = range_year, y = median_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")
```

```{r}
#| label: fig-different-ends-2010
#| fig-cap: "Recent = 2010-2012"

middle_cites <- citation_tibble |>
  filter(new_year >= 2010, new_year <= 2012) |>
  group_by(old, old_year) |>
  tally(name = "m_cites") |>
  ungroup() |>
  select(old, m_cites)

the_920_middle <- the_920 |>
  left_join(middle_cites, by = "old") |>
  mutate(m_cites = replace_na(m_cites, 0)) |>
  ungroup() |>
  group_by(range_year) |>
  summarise(median_cites = median(m_cites))

ggplot(the_920_middle |>
         filter(range_year >= 1965,
                range_year <= 2000) |>
         mutate(colortype = case_when(
           range_year <= 1973 ~ 1,
           range_year <= 1979 ~ 2,
           range_year <= 1995 ~ 3,
           TRUE ~ 4)),
       aes(x = range_year, y = median_cites)
         ) +
  geom_point(aes(x = range_year, y = median_cites, size = 2, color = as.factor(colortype))) +
  geom_line() +
  labs(x = "First year of range",
       y = "Median cites") +
  theme(legend.position = "none")

```
:::
::::

It's not quite true that in both graphs every blue dot is below every green dot and every purple dot, but it's pretty close. What's clearly true is that it's not just a disposition among philosophers to stop citing articles once they reach a certain age. 

There is something about the 1980s and (most of) the 1990s that is doing this. The articles that were widely cited then stop being widely cited at least as early as 2010. This is true across a number of ways of counting what is widely cited at the time. The next task is to look at what changed in philosophy that brought this about.

# Looking at Papers {#sec-looking-papers}

One possible thought of what explains @fig-all-median is that the influential articles from the 1980s and 1990s aren't impacting that graph because they weren't cited enough at the time to be in the top twenties. For example, "Speech Acts and Unspeakable Acts" [@citeLangton] is widely cited since 2020, but was not much cited at the time.

This can't be the whole story though. There are always papers that get more citations long after publication than they had at the time. Indeed, if you look back to @tbl-very-late-bloomers, you see that there are more of these articles after 2000 than before.

Had every article from the 1980s and 1990s that's now widely cited been widely cited at the time, the dip in @fig-all-median wouldn't be there. But that's an implausible counterfactual; it's never true that _all_ the articles with the most long-term influence are widely cited straight away.

A better explanation goes in the other direction. During the 1980s and 1990s, there was a particularly high frequency of articles which were widely cited at the time, but which have relatively few citations in recent years. 'Relatively' is an important word there. The articles I'm about to focus on typically have 5-9 citations in philosophy journals since 2020. As @tbl-count-of-recent-citations shows, that means they are still cited more often than the overwhelming majority of articles in philosophy journals. But they are cited much less often than you'd expect given their prominence at the time. Or, if you prefer, they were much more cited at the time than you'd expect knowing just the recent literature.

Anyway, @fig-jitter-citations is a scatterplot of how often various articles have been cited. Each dot represents an article that appears in three or more of the top twenty lists, for articles widely cited at the time.

```{r}
#| label: fig-jitter-citations
#| fig-cap: "Number of recent citations for articles appearing in three or more top twenty lists."

ggplot(the_920 |>
         distinct(old, .keep_all = TRUE) |>
         filter(appear >= 3) |>
         mutate(l_cites = case_when(
           l_cites == 0 ~ 0.5,
           TRUE ~ l_cites
         )),
       aes(x = year, y = l_cites)) +
  geom_jitter(size = 2) +
  scale_y_log10(limits = c(0.4, 250)) +
  labs(x = "Publication Year",
       y = "Recent Citations")
```

The y-axis is the number of citations since 2020. Since these numbers can get very large, this is put on a log scale. Since log scales create problems with zero values, I've replaced all zero citation values with 0.5. The x-axis is no longer a range, it's simply the first year of publication. Since there are often pairs of articles with the same publication year and the same number of citations since 2020, I've added some 'jitter' to the graph.

The striking thing is that the bottom right part of the graph is empty. Focus on the part of the graph below the *y*=10 line, representing ten citations since 2020. After 2000, there are hardly any dots there. @tbl-below-ten lists all the papers since 1974 which appear on three top twenty lists with fewer than ten citations since 2020, i.e., all the dots below the *y*=10 line since 1974. (The points before 1974 are interesting, but I think that's ultimately a different category.)

```{r}
#| label: tbl-below-ten
#| tbl-cap: "Articles which appear on three or more top twenty lists, with fewer than ten recent citations."

kable(
  the_920 |>
    distinct(old, .keep_all = TRUE) |>
    filter(appear >= 3) |>
    filter(l_cites < 10, year >=1974) |>
    arrange(year) |>
    select(`Recent Citations` = l_cites, Article = tbl_cite)
)
```

There are two questions we might be interested in here. Why are there so many such articles before the late 1990s, and why are there so few after? It's a bit easier to start with the first, because we can see the particular articles.

The list on @tbl-below-ten seems to have a few natural categories.

Some papers have relatively few citations because they **became books**, or parts of books, and most citations these days are to the book. The most obvious of these are the papers by Rawls [-@WOSA1985APA8500001, -@WOSA1988Q394000001] and @WOS000073301000002. It's possible the papers by Kim should be included in that category too, though in that case the book (_Supervenience and Mind_) reprinted the papers rather than incorporated them. And, as can be seen by the number of citations to Lewis articles, the existence of collections of papers doesn't have the same systematic effect on citations.

There are several papers on **laws**, especially ceteris paribus laws, i.e., (include list). These actually rather surprise me; it's not like these topics are not discussed in the recent literature. "Causation as Influence" [@citeCaI] has many citations since 2020. My best guess, and this will come up a bit in what follows, is that there is much less interest these days in papers that take relatively armchair approaches to these topics. Of course, one could say the same thing about "Causation as Influence", so this isn't the whole story. Still, I think it's part of the story.

There are three papers on **mental content**: (include list). If we look beyond the top twenties, and at other papers that are somewhat widely cited at the time, we see many more papers on mental content. Mental content is still a huge topic in contemporary philosophy, but these big picture, largely armchair, debates about externalism and internalism have largely receded. Contemporary work tends to be more focused on questions of detail, or more sensitive to recent empirical work, or both.

```{r}
#| label: scripts-for-wide-tables

the_4600_simplified <- the_4600 |>
  distinct(old, .keep_all = TRUE) |>
  select(old, `Recent Citations` = l_cites, `Article` = tbl_cite)

the_4600_wide <- the_4600 |>
  select(old, year, range_year, rank) |>
  mutate(range_age = toOrdinal::toOrdinal(range_year - year + 5)) |>
  mutate(rank = as.character(rank)) |>
  select(-range_year) |>
  complete(nesting(old, year), range_age, fill = list(rank = "--")) |>
  pivot_wider(names_from = range_age, values_from = rank) |>
  left_join(the_4600_simplified, by = "old") |>
  select(`Recent Citations`, Article, everything()) |>
  arrange(year)
  
table_of_perform <- function(refs){
    the_4600_wide |>
      filter(old %in% refs) |>
      arrange(year) |>
      select(-old, -year)
  }
```

In @tbl-mental-content, the column on the left shows how often the article was cited since 2020, and the five columns on the right show how the article ranked at the time among different ranges. So for (include citation), the table says:

-  among articles published between (first range), it had the (n'th) most citations by (year for first range)
- (include other four)

The dashes in the table mean that the article was not in the top hundred for that range; I didn't measure beyond that.

Now many of these articles are still widely cited: (include citation) still has (include cites) since 2020, which is more than 99% of all published articles. 
