---
title: "New Work for Dempster-Shafer Functions"
abstract: |
 TBD
date: today
author:
  - name: Brian Weatherson 
    url: http://brian.weatherson.org
    affiliation: University of Michigan
    affiliation_url: https://umich.edu
    orcid_id: 0000-0002-0830-141X
categories:
  - epistemology
  - games and decisions
  - logic
  - language
  - vagueness
engine: knitr
bibliography: ../../brian-quarto.bib
execute:
  echo: false
  warning: false
citation: false
format:
  html:
    css: ../trad_defn.css
    include-in-header:
      - text: |
          <script>
          MathJax = {
            tex: {
              macros: {
                llbracket: "⟦",
                rrbracket: "⟧",
                nmodels: "\\not\\models",
                boxright: "\\mathrel{\\Box\\!\\!\\to}"
              }
            }
          };
          </script>
  pdf:
    output-file: "New Work for Dempster-Shafer"
    keep-tex: true
    geometry: "left=1.8in,
                 right=1.8in,
                 top=1.5in,
                 bottom=1.5in,
                 includemp=TRUE,
                 marginparwidth=0in,
                 marginparsep=0in"
    include-in-header:
      - text: |
          \newcommand{\nmodels}{\mathrel{\ooalign{$\models$\cr\raisebox{-0.001ex}{\hss$\mkern-1mu/\hss$}}}}
          \newcommand{\llbracket}{[\![}
          \newcommand{\rrbracket}{]\!]}
          \setlength\heavyrulewidth{0ex}
          \setlength\lightrulewidth{0ex}
          \usepackage[lines=2]{lettrine}
          \cehead{Draft of February 28, 2026}
          \DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
          \DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}
          \cehead{
                 Brian Weatherson
                 }
    include-after-body: 
        text: |
          \noindent Draft for discussion.
draft: true
---

Eleanor Rigby, we are told, picked up the rice in a church where a wedding had been. Have you ever thought about that wedding? Who were the happy couple? What were their names? Did they stay together for years, eventually bounce grandchildren on their knees? The song says enough to make it possible to raise these questions, but not to answer them.

_Eleanor Rigby_, the song, is special in many respects, but this is not one of them. Works of fiction typically raise questions they do not answer. Mostly these questions are not worth even trying to answer, though in some cases at least trying to answer them feels important to engaging with the fiction. (_Blade Runner_ is a famous example of this.) Still, even the silly questions can be philosophically interesting. For while it's not important what the answers to those questions are, it is somewhat important what an answer to the questions looks like.

What's true in a fiction is sometimes settled by the words of the song. In realistic fictions, others are settled by what would have to be true for the text to make sense. For instance, the married couple in _Eleanor Rigby_ (hereafter, The Couple) must have names. How else would Father McKenzie marry them? Some are settled by the context the fiction was produced in. _Eleanor Rigby_ was released in 1966, and it feels like it's set in the reasonably recent past, so the wedding takes place probably in the 1960s, or perhaps the late 1950s. It's not meant to take place too far away, so it's certainly set in the UK, and probably in England. Others are settled by facts about the world which are imported in. For instance, we know Rocky Raccoon lives in _South_ Dakota (at least while he lives) because he lives in the Black Hills, and these are actually in South Dakota. Relatedly, because all church marriages in the UK in the 1960s were heterosexual, The Couple must consist of The Husband and The Wife. Perhaps the intent of the author also affects what's true in the story, beyond the factors already mentioned; we'll leave that question to one side.

What we will focus on is whether these questions must have answers. Is there a fact about what The Husband's name is? A fairly orthodox theory, developed in most detail by David @Lewis1978b, says that there is not. Lewis's theory has three parts. First, sentences like (@HusbandVincent) and (@HusbandHasName), have an implicit operator in them.

(@HusbandVincent) The Husband's name is Vincent.
(@HusbandHasName) The Husband's has a name.

We should understand these as saying

(@HusbandVincentOp) In the fiction, The Husband's name is Vincent.
(@HusbandHasNameOp) In the fiction, The Husband's has a name.

Second, the logic of this operator is that of a box in a normal modal logic which is not _functional_ in the sense described by @Standefer2018. In particular, it does not include (@FunctAxiom) as an axiom.^[Standefer is interested primarily in the logic which also has $\Diamond \top$ as an axiom. The designation of these logics as 'functional' makes sense in a possible worlds framework, but is somewhat misleading in the possibility frame setting of this paper.]

(@FunctAxiom) $\Box \Phi \vee \Box \neg \Phi$

For Lewis, there are many worlds which have an equally good claim to be the world of the fiction, and something is only true in the fiction if it is true at all of them. So the English sentence (@HusbandNotVincent) is ambiguous between (@HusbandOpNotVincent) and (@HusbandNotOpVincent), with (@HusbandOpNotVincent) false and (@HusbandNotOpVincent) true. Because (@HusbandVincentOp) and (@HusbandOpNotVincent) are both false, (@FunctAxiom) fails.

(@HusbandNotVincent) The Husband's name is not Vincent.
(@HusbandOpNotVincent) In the fiction, The Husband's name is not Vincent.
(@HusbandNotOpVincent) It is not the case that in the fiction, The Husband's name is Vincent.

Third, Lewis thinks that this 'in the fiction' operator can be understood in terms of counterfactuals. Roughly, what's true in the fiction is what would be true were the text of the story told as known truth.

In this paper, I'll accept the first of Lewis's claims (that there is an operator), reject the second (that it has a non-functional logic), and mostly set aside the third. In 'Fictional Reality', [@BlumbergHolguin2025], Kyle Blumberg and Ben Holguín run a series of arguments against this second assumption of Lewis's. I'll briefly mention a handful that I find most compelling.

For many questions that seem to be left open by a fiction, it makes sense to wonder about them. This can range from questions that are central to how one understands a fiction, like _Is Decker a replicant?_, to trivial questions like _Do The Couple have grandchildren?_. But on Lewis's picture, there isn't anything to wonder about. We know that it's not true that, in the fiction, that they have grandchildren, and it's also not true that, in the fiction, they do not have grandchildren. Intuitively, (@CoupleWhether) is true, but there isn't any sensible way to insert an _In the fiction_ operator that makes it true on Lewis's theory.

(@CoupleWhether) I don't know whether The Couple had grandchildren.

It isn't defective to wonder about this, in the way it is defective to wonder about things that are settled by the fiction.

(@CoupleWonder) I wonder whether The Couple had grandchildren.
(@HolmesWonder) #I wonder whether Sherlock Holmes met Napoleon.

For Lewis, once we know all there is to know about the fiction, all worlds are sorted into two buckets; those that are consistent with the fiction and those that are not. There is no way to make sense of relative likelihoods within those buckets. So we can't make sense of (@CoupleLikelyChildren), but it feels intuitively true.

(@CoupleLikelyChildren) The Couple might have had five grandchildren, and they might have had ten, but given the social norms at the time, and in the generation following, it's more likely they had five.

Blumberg and Holguín infer from facts like these that there is a fact of the matter about any question raised by the fiction. As they note, this strikes many people as absurd. I'm one of those people, so I'd like to set out a theory in which there need not be any such facts, without falling into the traps besetting Lewis's theory.

One might wonder whether we need such detail on trivial questions like the future of The Couple. This concern is in part a function of my choosing a trivial question; many questions more natural questions about fictions have the same shape. Who hasn't wondered what becomes of the broken hearted? More generally, the logical and epistemological issues that this topic raises have implications far beyond fiction. Any time we can coherently wonder about something without being certain whether there is a fact of the matter, the same issues will arise. Our subject is nothing less than the epistemology of the not clearly factual.

We can have graded uncertainty about questions where we aren't sure there is a fact of the matter. This raises questions about the rational constraints on this uncertainty. There are several familiar arguments that all uncertainty should, ultimately, be probabilistic. I'll argue that these arguments rest on an assumption that all the questions we're uncertain about are (certainly) about matters of fact. When there might be no fact of the matter, it is rational for one's uncertainty to be represented not by a probability function, but by a Dempster-Shafer belief function. (This is the 'New Work' for these functions the title promised.)

This paper has a snake-like structure. In sections [1](#sec-sec1) and [5](#sec-sec5) I discuss _possibility frames_. This is a system, introduced by Lloyd @Humberstone1981a and recently discussed in detail by Wesley @Holliday2025, which lets us preserve something like classical logic while allowing that there might not be a fact of the matter about some questions. I'll introduce the theory in section [1](#sec-sec1), and return to the slightly vexed question of whether this is really _classical_ logic in section [5](#sec-sec5). In sections [2](#sec-sec2) and [4](#sec-sec4) I'll discuss Dempster-Shafer functions. In section [2](#sec-sec2) I'll set out what they are, and the standard arguments against using them. In section [4](#sec-sec4) I'll come back to why these arguments aren't compelling when the subject matter might be non-factual. In the middle, I'll come back to Blumberg and Holguìn's arguments about fiction, and defend the position already sketched, that while their objections to Lewis are successful, their proposed remedy is implausible and should be rejected.

# Possibility Frames {#sec-sec1}

A Humberstone possibility frame (hereafter, just _possibility frame_) is a triple $\langle W, \leqslant, \mathbb{R}, V\rangle$, where $W$ is a set of possibilities, $\leqslant$ is a _refinement_ relation on them, $\mathbb{R}$ is a countable family of accesibility relations (with $R_i$ as the $i$'the member), and $V$ is a valuation function.^[One might expand frames even further, e.g., by adding a selection function that enters into the semantics for counterfactuals. Counterfactuals will be sitting just under the surface at many points in this paper, but to keep things focussed I'll defer discussion of counterfactuals to another day.] 

One way to think about the possibilities in $W$, suggested by @Humberstone1981a and used extensively by @Holliday2025, is that they are sets of possible worlds. I prefer to think of them as _stories_, at least on the assumption that stories are incomplete. A possibility, like a story, is something which settles some facts, while possibly leaving others open.

Following Humberstone, I'll write $x \leqslant y$ to mean that $y$ is a **refinement** of $x$.^[$y \geqslant x$ will just mean the same thing as $x \leqslant y$.] To say $y$ refines $x$ is to say that $y$ makes true everything that $x$ makes true, and possibly some more things besides. If possibilities are sets of possible worlds, then $y$ is a subset of $x$. (This makes the notation here confusing, which is why @Holliday2025 prefers to write $y \sqsubseteq x$ when $y$ is a refinement of $x$.) If possibilities are stories, then $y$ is a refinement of $x$ if $y$ fills in part of what $x$ leaves open. This is how I'll, intuitively, think of refinements.

$V$ is a **valuation** function. It tells us where the atomics are true. Formally, it is a function from $\mathcal{P}$, the set of atomics, to $\wp(W)$, , satisfying these two constraints:

- For all $x$, if $x \in V(p)$ and $x \leqslant y$, then $y \in V(p)$. Intuitively, truth for atomics is **persistent** across refinements.
- For all $x$, if $\forall y \geqslant x\;\, \exists z \geqslant y: z \in V(p)$, then $x \in V(p)$. This is what @Humberstone2011 [900] calls **refinability**. It means that $p$ only fails to be true at $x$ if there is some refinement of $x$ where it is settled as being untrue.

That's enough to provide a theory of truth for the language of propositional logic, and Humberstone proposes the following clauses.

\begin{align*}
[\text{Vbls}] \quad & \mathcal{M} \models_x p_i \text{ iff } x \in V(p_i); \\
[\neg] \quad & \mathcal{M} \models_x \neg A \text{ iff } \forall y \geqslant x, \, \mathcal{M} \nmodels_y  A; \\
[\wedge] \quad & \mathcal{M} \models_x A \wedge B \text{ iff } \mathcal{M} \models_x A \text{ and } \mathcal{M} \models_x B; \\
[\vee] \quad & \mathcal{M} \models_x A \vee B \text{ iff } \forall y \geqslant x \;\, \exists z \geqslant y : \mathcal{M} \models_z A \text{ or } \mathcal{M} \models_z B. \\
[\rightarrow] \quad & \mathcal{M} \models_x A \rightarrow B \text{ iff } \mathcal{M} \models_x \neg(A \wedge \neg B)
\end{align*}

The first two clauses are familiar, and the third looks much like the intuitionist treatment of negation. The final clause amounts to treating $\rightarrow$ as a defined connective. The surprising one is $[\vee]$. It says that a disjunction is true iff at any refinement, at least one of the disjuncts could become true. This is not the most obvious understanding of $\vee$, but it allows Humberstone to prove three striking results.

First, every sentence in the language is persistent. If $\mathcal{M} \models_x A$ and $x \leqslant y$, then $\mathcal{M} \models_y A$. For any sentence, truth is always preserved when moving to a refinement. 

Second, refinability holds for all sentences in the language. Once we've added negation to the language, we can restate refinability as the condition that, for any $A,$ if $\mathcal{M} \nmodels_x A$, there is some refinement $y$ of $x$ such that $\mathcal{M} \models_y \neg A$. Intuitively, if a sentence is not true, then at some refinement its negation is true.

Third, if we define validity on possibility frames, written as $\vDash_{pf}$, as truth preservation, then we get a very classical theory. It's not just that, within this language, $\vdash_{CL}$ and $\vDash_{pf}$ exactly overlap. It's also that, in any expanded language, as long as persistence and refinability hold, the introduction and elimination rules for $\vdash_{CL}$ also hold for $\vDash_{pf}$.

It's useful to work through one of these rules to show how the system works. Because it will play a role in what follows, I'll show that disjunction elimination holds for $\vDash_{pf}$. One natural formulation^[There are other formulations which make weaker structural assumptions, but this one will do to show that we're preserving classical logic.] of disjunction elimination says that $\Gamma \cup \{A\} \vdash_{CL} C$, $\Delta \cup \{B\} \vdash_{CL} C$, and $\Phi \vdash_{CL} A \vee B$ together imply $\Gamma \cup \Delta \cup Phi \vdash_{CL} C$. Let's show that the same principle holds for $\vDash_{pf}$.

Assume that $\Gamma \cup \{A\} \vDash_{pf} C$, $\Delta \cup \{B\} \vDash_{pf} C$, and $\Phi \vDash_{pf} A \vee B$, and assume for reduction that for some possibility $x$ where all members of $\Gamma \cup \Delta \cup \Phi$ are true,  $\mathcal{M} \nmodels_x C$. By refinability, there is some $y \geqslant x$ such that $\mathcal{M} \models_y \neg C$, i.e., for all $z \geqslant y,$ $\mathcal{M} \nmodels_z C$. By persistence, all members of $\Gamma \cup \Delta \cup \Phi$ are true at $y$. Since all of $\Phi$ is true at $y$, we have $\mathcal{M} \models_y A \vee B$. By $[\vee]$, there is some $z \geqslant y$ such that $\mathcal{M} \models_z A$ or $\mathcal{M} \models_z B$. By persistence again, all members of $\Gamma \cup \Delta$ are true at $z$. If $\mathcal{M} \models_z A$, then all of $\Gamma \cup \{A\}$ are true at $z$, so $\mathcal{M} \models_z C$. If $\mathcal{M} \models_z B$, then all of $\Delta \cup \{B\}$ is true at $z$, so $\mathcal{M} \models_z C$. Either way, $\mathcal{M} \models_z C$. But $z \geqslant y$ and $\mathcal{M} \models_y \neg C$, so $\mathcal{M} \nmodels_z C$. Contradiction.

Humberstone's system looks non-classical. It includes points that make true neither $A$ nor $\neg A$ for some $A$. It includes a rule for negation that looks more like intuitionistic negation than classical negation. But looks are misleading; the system is still classical. All the sequents, and all the admissible rules on sequents, carry over from classical logic. We have a non-standard semantics for a very standard logic. 

Possibility frames have attracted some attention recently as an interesting classical alternative to possible worlds semantics. We've already mentioned @Holliday2025, and his work will come up extensively in what follows. Matthew @HarrisonTrainor2019 has shown how to extent the semantics to first-order logic. Brian @WeathersonHoPF applies possibility frame semantics to a puzzle about counterfactuals. And Fabrizio @CarianiUnpub uses possibility frames to model the open future. This paper extends that list; I'm going to use them to provide a better way of talking about fictional truth.

Since we need modal operators, we need to say more about $\mathbb{R}$. First we'll talk about modals. We start a familiar truth condition for $\Box_i$:

\begin{align*}
[\Box_i] \quad & \mathcal{M} \models_x \Box_i A \text{ iff } \forall y \, (x R_i y \Rightarrow \mathcal{M} \models_y A)
\end{align*}

In words, $\Box_i A$ is true at $x$ iff $A$ is true at every $R_i$-accessible possibility. Humberstone treats $\Diamond$ as a defined connective, $\Diamond_i A$ just means $\neg \Box_i \neg A$, and I'll do the same. 

That alone isn't enough to guarantee that boxed sentences are persistent and refinable. There are a few ways to constrain how $\mathbb{R}$ and $\leq$ relate to get that guarantee; I'll use one suggested by Holliday. He calls this constraint **R-Win**.

**R-Win**
:    $xR_iy \leftrightarrow \forall y' \geqslant y \exists x' \geqslant x \forall x'' \geqslant x' \exists y'' \geqslant y': x''R_iy''$

It is easy to show that if each $R_i$ satisfies **R-Win**, then even after adding $\Box_i$ and $\Diamond_i$ to the language, all sentences will satisfy persistence and refinability. It is a little stronger than what's needed for these conditions, but the extra strength turns out to be a helpful simplification. 

One important consequence of **R-Win** is that each $R_i$ is carried downwards along refinement. That is, if $x R_i y$ and $y \leqslant y'$, then $x R_i y'$. More colloquially, if *a* can access *b*, *a* can access any refinement of *b*. This will be important when we get to epistemic modality.

@Holliday2025 [§6.3] notes that one upside of adding **R-Win** is that it means we get back _some_ familiar results from the traditional possible worlds semantics for modal logic. A possibility frame validates $\Box_i \Phi \rightarrow \Phi$ iff $R_i$ is reflexive; it validates $\Box_i \Phi \rightarrow \Box_i \Box_i \Phi$ iff $R_i$ is transitive; and it validates $\Diamond_i \top$ iff $R_i$ is serial. What's more important here, and what Holliday also notes, is that we don't get the same parallel for all axioms. 

In possible world semantics, the frame condition for $\Box_i \Phi \vee \Box_i \neg \Phi$, or equivalently, $\Diamond_i \Phi \rightarrow \Box_i \Phi$, is that each point accesses at most one point. That is, $\forall x, y, z ((xRy \wedge xRz) \rightarrow y = z)$. But in a possibility frame semantics, @Holliday2025 [229] shows that what it takes to validate $\Diamond_i \Phi \rightarrow \Box_i \Phi$ is (@FunctionalConstraint):

(@FunctionalConstraint) $\forall x, y (xR_iy \rightarrow \exists x^\prime \geq x \forall z (x^\prime \geq z \rightarrow \exists x^{\prime\prime} (x^{\prime\prime} \geq y \wedge x^{\prime\prime} \geq z)))$



In @fig-simple-frame, I've displayed a simple frame that validates $\Box_i \Phi \vee \Box_i \neg \Phi$ without being functional. The solid lines represet $R$-accessibility; the dotted lines represent refinements. From $x_1$ all the $y_i$ are accessible. So neither $\Box p$ nor $\Box \neg p$ are true at $x_1.$ But the disjunction $\Box p \vee \Box \neg p$ is true, since every refinement chain coming out of $x_1$ eventually validates either $\Box p$ (on the chain going to $x_2$) or $\Box \neg p$ (on the chain going to $x_3$).^[A similar construction shows that we can add a counterfactual that validates Conditional Excluded Middle without assuming that for each possibility $x$ and possibly true proposition $\Phi$, there is a unique nearest possibility where $\Phi$ is true.]

```{r}
#| echo: FALSE
#| output: FALSE
if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = 'tikz')
}
options(tinytex.engine = "xelatex")
font_opts <- list(extra.preamble = c("\\usepackage{fontspec}",
                                     "\\setmainfont{Scala Sans Pro}"))
```

```{r engine='tikz', engine.opts=font_opts}
#| label: fig-simple-frame
#| fig.cap: "Possibility frame with refinement (dashed, $\\geq$) and $R$-accessibility (solid arrows) relations"
#| fig.ext: 'jpg'
#| fig.align: center
#| cache: FALSE
#| echo: FALSE

\usetikzlibrary{arrows.meta, positioning, calc}
\begin{tikzpicture}[
    >=stealth,
    node distance=2cm,
    poss/.style={circle, draw, inner sep=1.5pt, minimum size=6mm, font=\small},
    Rarrow/.style={->, thick},
    refine/.style={dashed, thick, -},
]

% x-possibilities on the left
\node[poss] (x1) at (0, 2.5) {$x_1$};
\node[poss] (x2) at (-1.2, 0) {$x_2$};
\node[poss] (x3) at (1.2, 0) {$x_3$};

% y-possibilities on the right
\node[poss] (y1) at (6, 2.5) {$y_1$};
\node[poss, label=below:{\small $p$}] (y2) at (4.8, 0) {$y_2$};
\node[poss] (y3) at (7.2, 0) {$y_3$};

% Refinement relations (dashed, no arrowheads)
\draw[refine] (x1) -- (x2);
\draw[refine] (x1) -- (x3);
\draw[refine] (y1) -- (y2);
\draw[refine] (y1) -- (y3);

% R-relations (solid arrows).  The bends keep the bottom-row arrows from
% slicing through intermediate nodes — tweak the `bend` numbers to taste.
\draw[Rarrow] (x1) -- (y1);
\draw[Rarrow] (x1) to[bend left=10] (y2);
\draw[Rarrow] (x1) to[bend left=20] (y3);
\draw[Rarrow] (x2) to[bend right=20] (y2);
\draw[Rarrow] (x3) to[bend right=35] (y3);

\end{tikzpicture}
```

# Dempster-Shafer Functions {#sec-sec2}

Orthodox opinion in philosophy is that if a thinker's uncertainty can be measured numerically, so there is some function $Bel$ from propositions to numbers representing the agent's degree of belief in each proposition, $Bel$ must be a probability function. This view is usually called _probabilism_. Assume, for simplicity for now, that there is a finite set $\mathcal{F}$ of maximally specific relevant possibilities, and each proposition the thinker has an attitude towards is a subset of $\mathcal{F}$. Saying that $Bel$ is a probability function is equivalent to saying there is some mass function $m$ from singletons of members of $\mathcal{F}$ to non-negative reals such that:

1. $\sum_{x \in \mathcal{F}} m(\{x\}) = 1$
2. $Bel(A) = \sum_{x \in A} m(\{x\})$

The most widely endorsed alternative to probabilism is that $Bel$ only needs to satisfy the slightly weaker constraints of *Dempster-Shafer belief functions* [@Dempster1967; @Shafer1976]. I'll call these _belief functions_ from here on. Belief functions are such that there is a mass function $m$ from non-empty subsets of $\mathcal{F}$ to non-negative reals such that:

1. $\sum_{X \subseteq \mathcal{F}} m(A) = 1$
2. $Bel(A) = \sum_{X \subseteq A} m(X)$

If $m$ only assigns positive mass to singletons, then $Bel$ will be a probability function, so all belief functions are probability functions. But the converse is not true. The simplest case is where there are just two possibilities: $a, b$, and $m$ assigns mass ⅓ to each of $\{a\}, \{b\}$, and $\{a, b\}$. Then $Bel\{a\} = Bel\{b\} = \frac{1}{3}$, while $Bel(\{a, b\}) = 1$. We could state the rules on belief functions axiomatically, but this more semantic presentation is both more intuitive, and connects more smoothly to the applications we'll be interested in.

What motivates the more restrictive orthodox view, that $Bel$ has to be probabilistic? In the twentieth century, the primary motivations were largely pragmatic: Dutch Book arguments, and arguments from the representation of preferences over gambles. There were two problems with these arguments. One was that they were pragmatic, and hence the wrong kind of thing to ground a purely epistemic constraint. The other, as Patrick @Maher1997 pointed out, was that they were question-begging against the most important opponent, the proponent of belief functions. David @Christensen1996 solved the first problem by developing 'depragmatised' Dutch Book arguments, but this (a) made the other problem worse, and (b) did not generalise to provide constraints on updating degree of beliefs.

So these days the key argument for orthodoxy is some kind of accuracy based argument. The canonical such argument, due to James @Joyce1998, says that if $Bel$ is not a probability function, then for any plausible measure of the accuracy of one's degrees of belief, there is some alternative $Bel^\prime$ which is guaranteed to be more accuracte. 

The _guarantee_ here is broadly modal. It means that $Bel^\prime$ is more accurate than $Bel$ in every possible world, where worlds are understood to be sets of sentences which are complete (every sentence is either true or false) and closed under classical entailment. These assumptions are load-bearing. J. Robert G. @Williams2016prob shows that if we drop replace classical entailment with intuitionistic entailment then the constraint is not that $Bel$ is a probability function, but that it's a certain kind of intuitionistic probability function. Here we want to look at what happens if we keep the idea that we're using classical entailment, but drop the assumption of completeness.

In particular, consider what happens if the thinker knows they are in some possibility in a possibility frame, but does not know which one. For example, consider someone who knows that they are in one of the $x_i$ in @fig-simple-frame. To connect it to the earlier discussion, let the $R$ relation be accessibility for $\box_{ER}$, the operator meaning _It's true in Eleanor Rigby that_, and let $p$ be that The Couple has grandchildren. Then $\box_{ER} p$ is true at $x_2$, $\neg \box_{ER} p$ is true at $x_3$, as is (almost equivalently) $\box_{ER} \neg p$, while none of these are true at $x_1$. (Though both $\box_{ER} p \vee \neg \box_{ER} p$ and $\box_{ER} p \vee \box_{ER} \neg p$ are true at $x_1$.) 

Now imagine the thinker has $Bel(\box_{ER} p) = Bel(\neg \box_{ER} p) = $⅓. At any possible _world_, the function $Bel^\prime$, which has $Bel(\box_{ER} p) = Bel(\neg \box_{ER} p) = $1/2, is guaranteed to be more accurate. But at $x_1$, $Bel$ is more accurate than $Bel^\prime$. After all, both $\box_{ER} p$ and $\neg \box_{ER} p$ fail to be true, so it's more accurate to have lower credences in them. And $Bel$ is lower than $Bel^\prime$ on each proposition.

I conclude that an assumption that's needed to make the accuracy-dominance argument for probabilism work is that every question the thinker is uncertain about is guaranteed to be factual. That is, it only works if the thinker is certain they are not in possibilities like $x_1$ where there is no fact of the matter about whether $\box_{ER} p$ is true. (Or that they are in $y_1$, where there is no fact of the matter about whether $p$ is true; but usually we have more evidence we are not in such sparse possibilities as $y_1$.)

There are two very natural responses the proponent of accuracy dominance arguments might make here. One is to simply accept this result, and say that they argument was only meant to apply to questions known to be factual. That's still a lot of questions, and if we have to qualify our probabilism when thinking about the non-factual, well there's still a lot of factual questions about which probabilism is correct. If that's the next move, the obvious next question is just how wide the realm of the factual is known to be, but I'll set that aside here. An alternative response is to argue that this restriction to the factual is no restriction at all, since all questions which can be sensibly asked are known to have factual answers. In the next section, I'll argue that questions about fiction show this isn't right.

# Fictional Reality {#sec-sec3}

Let's go back to (@HusbandVincentOp), repeated here.

(@HusbandVincentOp) In the fiction, The Husband's name is Vincent.

We can wonder about whether this is true. Intuitively, it is more likely that his name is Vincent than that it's Vaibhav. We could get even clearer about just how likely it is to be Vincent by looking up frequency of names for newly married men around where and when the story is set. (That's not to say we can specify those details; but it seems clear the story is set somewhere in the UK, probably Liverpool or Greater London, sometime after WWII.)

If all questions we can wonder about are factual, there seem to be two live options. One, defended by @Lewis1978b, is that we know (@HusbandVincentOp) is false. In the introduction I surveyed some arguments from @BlumbergHolguin2025 against that view. Here's one more argument I didn't mention there. If we know (@HusbandVincentOp) is false, then everything I said in the last paragraph is false. It's not true that his name is more likely Vincent than Vaibhav, or that the story is probably set in Liverpool or Greater London. That is, at least, seriously revisionary.

Blumberg and Holguín conclude from this that there is an unknown fact of the matter about whether (@HusbandVincentOp) is true. As they note, this view is widely held to be "absurd". That's for the excellent reason that it is, in fact, absurd! How could Paul McCartney writing a few lines settle all the questions we could ask about the characters, from what grade Father MacKenzie got in his last high school English exam, to how many eggs The Wife ate in her lifetime? What could ground those facts? Those intuitive arguments seem compelling to me, but rather than rest on them, I'll note that their view has fairly revisionary consequences for how we think about the relationship between fictions. 

These days, the bulk of fictions produced are fan fictions (or _fanfics_); stories produced by fans recycling characters from established works. Sometimes these don't bother with consistency with the underlying source material, as if the writer had put Julius Caesar into the Korean War. But a large body of fanfics are, or at least attempt to be, 'canon-compliant'. That is, they aim to write stories which do not contradict any truths in the source material. If Blumberg and Holguín are right, then no two fanfics which contradict each other can be canon-compliant. Since the source settles all questions, at most one of the disagreeing fanfics can agree with the source.

This doesn't just affect fanfics; the same issue comes up with sequels. It is usually taken to be a constraint on sequels that they should agree with what was true in the prequel, or if not explain the divergence. If Blumberg and Holguín are correct, approximately no sequels satisfy this constraint. If we take _A Study in Scarlet_ to be a self-contained fiction, then it is incredibly unlikely that the protagonist of it will one day solve a murder in Dartmoor, have a fight to the death above the Reichenbach Falls, protect a woman whose stepfather tries to murder her by passing a snake through a heating vent, and so on. On their view, there is a fact at the end of _A Study in Scarlet_ about which (if any) of these things Holmes will one day do, and it seems improbable he will do all of them. So it's not just Watson's war wound which changes from one thing to another over the Holmes stories, it's Holmes's entire life trajectory.

Perhaps we could deny the assumption that _A Study in Scarlet_ is self-contained; what's true in a book which has a sequel is determined by what happens in later books. That too, however, would be revisionary. We don't think that the later descriptions of where the wound is get to be correct solely in virtue of being later.

It's implausible that all fictions are complete in the sense that Blumberg and Holguín suggest, and assuming that they are requires making massive changes to how we think about the relationship between fictions. So we should try something else. My suggestion is that the logic of _In the fiction_ is a modal logic where the underlying semantics is a possibility frame. For the reasons Blumberg and Holguín give, it's plausible that this logic is functional, i.e., it satisfies $\diamond \Phi \rightarrow \Box \Phi$. But as long as we use possibility frames, this does not require that there is a particular world that the fiction picks out.

Blumberg and Holguín are aware of the option that one could deny that the fiction is complete in this way, and they offer a series of objections to it. The most pressing is that if the fiction is incomplete, then (@objection) will be true, when *p* is replaced by any claim that lacks a truth value in the fiction.

(@objection) I know whether $p$ is true, but I don’t know whether $p$.

That would be very bad, but fortunately it isn’t a consequence of the view that the fiction is incomplete. For (@objection) to be true, it would not merely have to be the case that some claims in the fiction lack truth values. It would also have to be the case that it is known that $p$ is one such proposition about which the fiction is incomplete. This isn't just an aspect of the objection based on (@objection); all of Blumberg and Holguín's objections make this further assumption.

Somewhat surprisingly, if we represent incompleteness with possibility frames, then it is never knowable that the fiction is incomplete with respect to $p$. So this further assumption of the objection isn't correct, and the view defended here is not committed to implausible claims like (@objection). To see why this is so, we need to return to a point I flagged earlier about the nature of epistemic modality in possibility frames.

Assume that _S knows_ is a normal modal operator, so there is some relation $R_k$ such that _S knows that_ $\Phi$ is true at $x$ iff for all $y$ such that $xR_ky$, $\Phi$ is true at $y$. Since knowledge is factive, this $R_k$ will have to be reflexive.^[This isn't quite as obvious a point as it is in the possible worlds framework. But as noted above, Holliday proves that if we assume **R-Win**, then all and only reflexive frames validate $\Box \Phi \rightarrow \Phi$.] If, as is standard, we assume that $xRy$ and $y \geq y^\prime$ imply that $xRy^\prime$, it follows that whenever $x \geq x^\prime$, then $xR_kx^\prime$. By refinability, if neither $\Phi$ nor $\neg \Phi$ are true at $x$, then there are successor points to $x$ where $\Phi$ is true, and where $\neg \Phi$ is true. Crucially, this means it won't be the case that _It is not true that_ $\Phi$ holds at all points $y$ such that $xR_ky$. So it won't be _known_ that $\Phi$ is not true. 

A special case of this is where $\Phi$ is $\box_{ER}p$, for some claim $p$ that is intuitively unsettled by the text of _Eleanor Rigby_. There might be no fact of the matter about whether, in _Eleanor Rigby_, _p_ is true; but we can never know that. So, among other things, (@objection) is never true, defanging the objection.

This might seem like a rather Pyrrhic victory, however. There are several reasons we might worry about a view that says the fiction is incomplete, but we can never know where it is incomplete. Here are three immediate worries. First, this move looks ad hoc. Second, it looks implausible, given how sparse _Eleanor Rigby_ is. Third, we might worry that once we go down this route, it will be impossible to say what is different about the possibility frame view as compared to Blumberg and Holguín's fictional reality view. Let's take these in turn.

It's certainly true that if we simply stipulated that the fictional can't be known to be incomplete in a respect, that would be implausibly ad hoc. But that isn't what happened. The lack of knowledge follows from general principles relating $\geq$ and $\Box_{ER}$, which Humberstone and Holliday defend on independent grounds. It's a surprising consequence of those principles, but the principles weren't engineered to get this result.

The implausibility worry is more pressing. I would have thought offhand that it's obviously true, and hence known, that _Eleanor Rigby_ is incomplete in several respects. If we think possibility frames are the best way to represent incompleteness, and they say this incompleteness is unknowable, then maybe that's some argument against this intuition, but hardly a strong one. The best response, I feel, is that (@objection) seems obviously bad, but if there was a knowable incompleteness it would be true, so maybe we should live with all incompleteness being unknowable.

There are two different worries about expressibility, and I'll just address one here. 

One worry, which @Carianims addresses at length, is that we can't add to the language a way of saying anything is incomplete without messing up the persistence and refinability conditions. If you could say, truly, that $p$ is incomplete, that would have to be true on all refinements, which it plainly can't be given refinability. As Cariani notes, there are various ways to finesse this using indexicals. Roughly, you can have something in the language which means that $p$ is *actually* incomplete. The details here are messy, but ultimately manageable. But they don't, I think, help with the deeper worry about inexpressibility.

That worry is that we want some way of saying we are pretty sure that there is no fact of the matter about whether The Couple have grandchildren. In the next section, I'll address this concern. The short version is that while we can't know there is no fact of the matter about $\Box_{ER}p$, we can rationally have arbitrarily low credence in both $\Box_{ER}p$ and $\neg \Box_{ER}p$. What's distinctive about realms featuring incompleteness is that these pairs of low credences can be rational.


# Uncertainty about the Non-Factual {#sec-sec4}

# What is Classical Logic? {#sec-sec5}

Hello sunshine.
