---
title: "Persuasion in Daylight"
abstract: |
  Recent models of industry propaganda show that an interested party can lead an audience to false beliefs by sharing only true results. But the audiences in those models update on the content of what they are shown and not on the fact that they were shown it; they are, in the economists' term, cursed. I ask what survives when the audience is not. The answer divides the strategy in two. *Selection*, choosing which existing results to pass on, is neutralised by an audience that knows what was generated; its power depends on the audience's ignorance of the process, and transparency reforms remove that ignorance. *Design*, choosing which experiments come into existence, is not neutralised. An audience that knows everything about the process and updates correctly on it is still moved, and in the simplest case, a receiver with two options, moved as far as she can be: whatever her payoffs, the designer's best experiment leaves her with exactly the expected utility she would have had with no evidence at all, while her beliefs remain calibrated throughout. Nothing false is believed, nothing is hidden, and reason is engaged rather than bypassed, so on accounts that locate the wrong of deception or manipulation in the target's state there is no wrong to find; accounts that locate it in the influencer's attitude can classify design as manipulation, but the attitude is the same whether or not anything is taken. I argue that the wrong that varies with the terms is exploitation: the designer uses the audience's dependence on him for evidence, and her lack of power over the terms on which it is produced, to take for himself as much of the value of information as the available experiments allow. The fairness baseline the exploitation claim needs is supplied by the purpose the institution assigns to the evidence. Two institutional consequences follow. Registration and disclosure, which kill selection, make design commitment credible, so taken alone they relocate the problem rather than solving it. And the counter-moves that work against design, reducing the audience's dependence, giving her authority over what gets studied, and committing her in advance to a standard above the one her own payoffs dictate, are available only to receivers with institutional power, which is where the exploitation account says the remedy has to lie.
author:
  - name: Claude
    note: "Draft written by Claude (Fable 5.1) for Brian Weatherson's in-house blog experiment. Not for circulation."
date: 29 September 2026
categories:
  - epistemology
  - ethics
  - philosophy of science
  - claude-draft
draft: true
execute:
  echo: false
  warning: false
  message: false
bibliography:
  - ../../brian-quarto.bib
  - daylight.bib
citation: false
format:
  html:
    css: ../trad_defn.css
  pdf:
    output-file: "Persuasion in Daylight"
    include-in-header:
      - file: ../quarto2024.tex
      - text: |
         \cehead{
                 Persuasion in Daylight
                 }
    include-after-body:
        text: |
          \noindent Draft of September 2026.
---

```{r setup}
suppressMessages({library(dplyr); library(tidyr); library(purrr); library(ggplot2); library(knitr)})
mu <- 0.3; t0 <- 0.5
sens <- 0.8; fpr <- 0.3; N <- 4
```

# Introduction

In the early 1950s the American tobacco industry decided to fight science with science. Rather than deny that smoking caused cancer, it funded research, promoted the studies that happened to go its way, and let a growing body of contrary evidence be met with a manufactured sense that the question remained open [@OreskesConway2010]. Nobody had to lie. The studies that were promoted were real studies. The strategy worked for decades.

A series of recent models from philosophy of science explains why. In @WeatherallOConnorBruner2020, a propagandist who forwards to policymakers only those results, produced by honest scientists, that favour the industry's position can drive the policymakers to near-certainty in the wrong theory while the scientists converge on the right one. @Mohseni2022 show that a journalist who curates studies according to ordinary newsroom norms produces the same distortion without meaning to; @HolmanBruner2017 that an industry which funds the scientists whose methods happen to yield favourable results can bias a community's consensus without corrupting any individual; @OConnorFreeborn2025 that funding accurate research on *other* causes of a harm shifts blame away from the industrial cause. The common lesson, which the authors draw explicitly, is that fraud is unnecessary. True results suffice.

There is something these models share that their authors also note, but which has not received the attention it deserves. Their audiences are rational about what they are told and irrational about the fact that they are being told it. A policymaker in the Weatherall–O'Connor–Bruner model receives a study from the propagandist and conditionalises on its content exactly as she would had the study come to her at random. She does not ask what the propagandist's forwarding it tells her about the studies he did not forward. In the language of @EysterRabin2005, she is *cursed*: she correctly predicts what the propagandist does but ignores the correlation between what he does and what he knows. The authors flag as future work the question of what happens when the audience can "adjust their updating rule to accommodate the possibility that some of the evidence they receive is exaggerated, filtered, or otherwise intended to mislead" [@WeatherallOConnorBruner2020].

This paper takes up that question. The answer, I will argue, splits the tobacco strategy down the middle. One half of it, which I will call *selection*, consists in choosing which already-existing results to pass on. Against an audience that reasons about the process, selection is neutralised: this is the unravelling result of @Grossman1981 and @Milgrom1981, on which a sceptical audience treats silence as bad news and the sender ends up revealing everything or being treated as if he had. Selection's power depends on the audience's ignorance of what exists to be selected from, and the transparency reforms of the last two decades are devices for removing that ignorance. The other half, which I will call *design*, consists in choosing which experiments come into existence: what to measure, whom to enrol, what to compare against, how long to run. Against an audience that reasons about the process, design is not neutralised. This is the central result of @KamenicaGentzkow2011. A sender who commits in advance to an experiment, whose design the audience sees and knows to have been chosen in the sender's interest, can still move the audience's decisions in his favour, without inducing a single belief the audience should not hold. Her posterior after each result is exactly what the evidence warrants. What changes is not the accuracy of her beliefs but the frequency with which she decides as he wants.

The economics is not new, and I will present it briskly. What I add to it is, first, a diagnosis: that the philosophical models of persuasion-by-true-results are models of cursed audiences, and that removing the curse divides the phenomenon into two mechanisms that behave differently under every reform that has been proposed. In presenting the design mechanism I will lean on a feature of it that the persuasion literature knows but the philosophical literature has not used: for a receiver with two options, the designer's best experiment leaves her with *exactly* the expected utility she would have had with no evidence at all, whatever her payoffs. Second, an argument about what is wrong with that. Design is not lying or deception in any sense that requires a false belief, not misleading in the sense the literature on misleading with truths has analysed, and not manipulation on accounts that require covertness, bypassing reason, or a defective mental state. Some accounts do classify it as manipulation, on the strength of the designer's attitude, and I will not pretend otherwise; but the attitude is the same whether or not the designer takes anything, and what the receiver has a complaint about is the taking. The right category, I will argue, is exploitation, in the form that @Wertheimer1996 calls mutually advantageous exploitation: the audience is no worse off than with no evidence, consents to rely, and is nonetheless wronged, because the sender uses her dependence on him for evidence, and her lack of power over the terms on which it is produced, to take for himself the value the evidence could have had for her. The baseline of fair terms that every exploitation claim needs is supplied by the purpose the institution assigns to the evidence, which is what fixes what a cooperative experiment would be. Third, an institutional reading. Registration and disclosure, the reforms that defeat selection, make design commitment credible, so taken alone they relocate the problem rather than solving it, and make the residue harder to see because everything is now by the book. The counter-moves that work against design, reducing the receiver's dependence, giving her authority over what gets studied, and committing her in advance to a standard *above* the one her own payoffs dictate, are available only to receivers with institutional power. That is what the exploitation account predicts: the wrong lies in an imbalance of power over the terms, and the remedy lies with receivers who have such power, not with the rationality of receivers who do not.

# Two ways to bias a body of evidence

Fix an audience with a question and a decision that turns on it: a regulator deciding whether to approve a drug, a judge deciding guilt, an editor deciding whether a result is real. In each case there is a party with an interest in the decision going one way regardless of the answer, and that party has some control over the evidence the audience sees. There are two points at which that control can be exercised.

The first is after results exist. The sender has a stack of studies and decides which to hand over. The file drawer, cherry-picking, "selective sharing" in the sense of @WeatherallOConnorBruner2020, the journalist who finds one study for each side: all of these are choices about which existing results to transmit. Call this *selection*.

The second is before results exist. The sender decides which experiments to run: the endpoint (a surrogate marker or the outcome that matters), the comparator (placebo, or the rival drug at a dose chosen to disadvantage it), the population, the duration, the sample size. Every one of these is a choice about what the world will be asked, and therefore about what it can answer. Call this *design*.

The distinction is not between honest and dishonest experiments; everything I say about design assumes the experiments are competently run and reported in full. It is a distinction in the timing and the object of the sender's choice: selection is a choice among realised results; design is a choice among experiments, made before any result is known.

Real cases mix the two, and some of the most striking documented findings about industry-sponsored research are design findings. @Heres2006 examined head-to-head trials of second-generation antipsychotics and found that ninety percent favoured the sponsor's drug, so that olanzapine beat risperidone in trials sponsored by olanzapine's maker, risperidone beat quetiapine in trials sponsored by risperidone's, and quetiapine beat olanzapine in trials sponsored by quetiapine's; the mechanism was dose selection, comparator choice, and the choice of outcome measures [see also @Safer2002; @Sismondo2008]. The Cochrane review of industry sponsorship [@Lundh2017] finds that industry-funded studies reach favourable conclusions more often than independently funded ones without scoring worse on the standard risk-of-bias measures; its authors list comparator choice among the candidate explanations, alongside selective publication, and comparator choice is design. @Stegenga2018 calls the general phenomenon the malleability of medical research; the design channel is one species of it. The case @HolmanBruner2017 use to introduce industrial selection is a design case: trials of anti-arrhythmic drugs that measured arrhythmia suppression showed benefit, and only trials that measured mortality revealed the drugs were killing people [@Echt1991; see @FlemingDeMets1996 on surrogate endpoints].

My question is which of these two channels survives an audience that is not cursed. To answer it I need to say what an uncursed audience is.

# Cursed audiences

Here is a case that will serve throughout. A regulator must decide whether to approve a drug. Her prior probability that the drug works is $0.3$, and she approves if and only if her posterior probability that it works is at least $0.5$: she gets one unit of value from a correct decision and nothing from an incorrect one, so this is the threshold at which approval is the better bet. (Nothing depends on the symmetry; I relax it in §5.) The sponsor wants approval whether or not the drug works.

Suppose first that the sponsor runs four identical studies. Each study returns a positive result with probability $0.8$ if the drug works and with probability $0.3$ if it does not, and the studies are independent conditional on whether the drug works. The sponsor then reports every positive result and files away every negative one.

A regulator who sees $k$ positive reports and treats them as the whole record computes the posterior odds that the drug works as the prior odds times $(0.8/0.3)^k$. A single positive report takes her to a posterior of $0.53$, over her threshold, and at least one of four studies is positive with probability $0.9984$ if the drug works and $0.76$ if it does not. So she approves with probability $0.83$, and her probability of making the correct decision is $0.47$: worse than the $0.7$ she would achieve by ignoring the sponsor and rejecting everything. This is the Weatherall–O'Connor–Bruner phenomenon in miniature: a rational updater who sees a selected sample and treats it as unselected ends up worse off than with no evidence at all.

The regulator's mistake has a precise description, and two literatures have given it. @GrunwaldHalpern2003, building on @Shafer1985, distinguish conditioning in a *naive space*, whose points are the possible contents of an observation, from conditioning in a *sophisticated space*, whose points also specify the protocol by which the observation was produced; naive conditioning is correct only when the protocol satisfies a condition they call "coarsening at random", roughly that the probability of being shown a piece of evidence not depend on the state beyond what the evidence itself says. The sponsor's protocol violates that condition as badly as a protocol can. The regulator's total evidence is not "study 3 was positive" but "the sponsor showed me study 3, and it was positive, and he showed me nothing else" [see @Good1967 on total evidence, and @Sober2009; @Kotzen2012 on observation selection effects]. @EysterRabin2005 give the same mistake a game-theoretic name: a *cursed* player correctly forecasts the distribution of the other players' actions but underestimates, and in the fully cursed case ignores, the extent to which those actions depend on the other players' private information. The regulator forecasts that the sponsor will forward studies; she fails to condition on the fact that which studies he forwards depends on what all the studies said. The policymakers in the philosophy of science models have no model of the propagandist at all, which is the limiting case of the same failure, and I will use "cursed" for it in that extended sense.

This is not a criticism of those models. Real audiences are cursed. In laboratory tests of disclosure games, receivers are systematically insufficiently sceptical about what is not disclosed [@JinLucaMartin2021; see also @Frechette2022], and the historical record that motivates the models is a record of real policymakers being moved. If the question is how the tobacco strategy worked on the audiences it actually faced, the models answer it. My question is different. It is whether rationality protects an audience from being moved by true evidence, and to answer that one has to remove the curse and see what remains.

# Selection in daylight

Uncurse the regulator. She knows that four studies were run. She knows the sponsor's reporting policy. She sees $k$ positive reports and infers that the other $4-k$ were negative. Her posterior is now the one she would have reached had all four studies been laid in front of her: the prior odds times $(0.8/0.3)^k (0.2/0.7)^{4-k}$. She approves only when at least three of the four studies are positive. The sponsor's approval rate falls from $0.83$ to $0.30$, and her accuracy rises from $0.47$ to $0.89$, which is exactly the accuracy she would achieve from four honestly reported studies. Selection has bought the sponsor nothing.

This is the unravelling argument [@Grossman1981; @Milgrom1981]: when a sender holds verifiable information, so that he can withhold but not fabricate, and the receiver interprets what is not shown as the worst thing consistent with what is, the sender's best response is to show everything, because at every stage the sender with the best undisclosed news prefers to disclose it rather than be pooled with those who have worse. @MilgromRoberts1986 showed the same obtains even with a naive receiver if competing senders with opposed interests each reveal what the other conceals. Against a sceptical receiver, or between adversarial senders, choosing what to reveal is not a lever.

There is one condition that matters enormously, because it is the condition the transparency reforms target. Unravelling requires that the receiver know, or be able to infer, what exists to be revealed. If she does not know whether the sender ran four studies or none, silence pools "I ran studies and they were negative" with "I ran no studies", and the sender with bad news can hide behind the second [@Dye1985; @JungKwon1988]. Selection then retains some power, and the power grows with the receiver's uncertainty about the sender's evidential endowment. @Henry2009 models a researcher who chooses how many experiments to run and which to disclose to a receiver who does not observe the count, and finds that the researcher must sometimes reveal unfavourable results to establish credibility. @ArieliStewart2025 show that if the receiver is sufficiently uncertain about the sender's capacity to experiment, selective disclosure can achieve everything that design achieves. So the claim that selection is neutralised needs stating carefully: selection's power is a function of the receiver's ignorance of the process, and it goes to zero as that ignorance does.^[The Weatherall–O'Connor–Bruner model has a second treatment, "biased production", in which the propagandist runs his own studies and publishes only the favourable ones, and a striking finding within it: the propagandist does best by splitting his budget into the smallest possible studies. This looks like a design result but is not. The small studies do their work only because the unfavourable ones are withheld from a receiver who does not know how many were run. Against a receiver who knows the count and sees every draw, the partition of the draws into studies makes no difference to her total evidence.]

That is why the reforms of the last twenty years take the form they do. Trial registration requires the sponsor to declare a study before it is run, so that the regulator knows it exists whatever its result; pre-registration of analysis plans fixes the endpoint and the test before the data arrive [@Nosek2018]; registered reports commit a journal to publishing a study on the strength of its design, before results, so that the file drawer has nothing in it [@Chambers2013]. Each is a device for making the count known, which is to say for restoring the condition under which unravelling works [@Felgenhauer2021 models pre-registration as exactly this; for the philosophy of science case for these instruments see @Romero2016; @Heesen2018].

# Design in daylight

Now suppose the regulator is as sophisticated as one could wish. She knows what experiment the sponsor will run before he runs it. She sees every result. She knows the sponsor chose the experiment to maximise the chance of approval. She updates by conditionalisation in the sophisticated space, on the full protocol. There is nothing hidden from her.

Suppose the sponsor may choose any experiment whose outcome depends only on whether the drug works: a test, of any design, whose statistical properties the regulator will know. In particular he may choose a test with a single pass/fail outcome, such that every working drug passes and a drug that does not work passes with probability $q$. Think of a surrogate endpoint chosen for its sensitivity: a marker that every effective drug moves, and that a certain fraction of ineffective drugs also move. Choosing the question to ask, the surrogate rather than the outcome that matters, is choosing an experiment about the decision-relevant state, with likelihoods fixed by how well the surrogate tracks it.

The sponsor chooses $q$. If he sets $q = 0$ the test is perfectly informative: the regulator learns exactly whether the drug works, approves with probability $0.3$, and is never wrong. If he sets $q = 1$ the test is uninformative, the regulator's posterior stays at $0.3$, and she never approves. In between, a pass takes the regulator's posterior to $0.3/(0.3 + 0.7q)$, and she approves on a pass if and only if this is at least $0.5$, which is to say if and only if $q \le 3/7$. The sponsor sets $q = 3/7$. Now every working drug passes, and $43$% of the drugs that do not work pass too. The regulator, seeing a pass, computes a posterior of exactly $0.5$, and approves. Seeing a fail, she computes a posterior of $0$ and rejects. She approves $60$% of drugs, though only $30$% work.

Nothing here is hidden, and nothing she believes is false or ill-founded. Among the drugs she approves, exactly half work, which is what she believes when she approves. Her credences are calibrated in the strict sense: conditional on each thing she does, the frequency with which she is right is the credence on which she acted. Her expected accuracy is $0.7$. That is the same accuracy she would achieve with no evidence at all, since with no evidence she rejects everything and is right $70$% of the time. (This uses the convention that she approves when exactly indifferent; if she does not, the sponsor sets $q$ just below $3/7$ and leaves her with as little as he likes.) The sponsor has chosen an experiment that delivers to the regulator, in expectation, nothing, while delivering to himself twice the approvals he would get from an honest and informative test.

This is the "Bayesian persuasion" result of @KamenicaGentzkow2011, with the numbers of their prosecutor example. Their general theorem says a sender who commits to an experiment benefits whenever the concave closure of his payoff, as a function of the receiver's belief, lies strictly above that payoff at the prior. In the binary case the receiver's decision is a step function of her belief, so the sender pushes her belief just over the step as often as possible and lets it fall as far as it likes otherwise: the optimal experiment makes her exactly indifferent whenever she does what he wants, and certain whenever she does not [see @Kamenica2019; @BergemannMorris2019].

I want to draw out one consequence of that structure, because it is the one that matters for the ethics. It is natural to suppose the example is fragile: the regulator has symmetric payoffs, so her threshold sits at $0.5$, and a real regulator who weighted the approval of useless drugs more heavily than the rejection of useful ones would have a higher threshold and be harder to exploit. She would not. Whatever the regulator's payoffs, they fix some threshold $t^\ast$ at which she is indifferent between approving and rejecting, and the sponsor's optimal test puts her posterior at exactly $t^\ast$ after a pass and at $0$ after a fail. At $t^\ast$ she is indifferent, so approving is worth to her exactly what rejecting would be; so her expected utility is what she would get by rejecting at every posterior the experiment induces, and since the value of rejecting is linear in her belief and the induced posteriors average to her prior, that is exactly what rejecting at her prior is worth. Her expected utility under the sponsor's best experiment is her expected utility with no evidence, for every specification of her payoffs. This is a corollary of Kamenica and Gentzkow's characterisation, in which the receiver's indifference at the persuaded action is the whole mechanism, and it is familiar in the persuasion literature [@Kamenica2019]; the appendix gives the two-line proof. It holds for a receiver with two options, a sender who cares only about which option is taken, and an unrestricted set of experiments. Relax any of these and the receiver keeps some of the surplus: with three or more options the sender cannot make her indifferent at every step at once, and with a bounded set of experiments he may be unable to reach her threshold exactly. What survives relaxation is the direction of the result. The value of information, the difference between what she gets with the fully informative experiment and what she gets with none, goes to the sponsor to the extent that the structure of her options and the available experiments allow, and how much she cares about the two kinds of error affects only the shape of the experiment that takes it from her.

@tbl-twobytwo assembles the numbers for the four cases. The rows are the two channels; the columns are the two audiences.

```{r twobytwo}
#| label: tbl-twobytwo
#| tbl-cap: "The sponsor's approval rate and the regulator's accuracy (probability of a correct decision) under each channel and each kind of receiver. Prior that the drug works: 0.3; approval threshold: 0.5. Selection: four studies each with sensitivity 0.8 and false-positive rate 0.3, only positives reported. Design: the sponsor's optimal single-outcome test. With no evidence the regulator's accuracy is 0.7."
post_full  <- function(k) { lg <- mu * dbinom(k, N, sens); lb <- (1 - mu) * dbinom(k, N, fpr); lg / (lg + lb) }
post_naive <- function(k) { lg <- mu * sens^k; lb <- (1 - mu) * fpr^k; lg / (lg + lb) }
sel <- expand_grid(state = c("G", "B"), k = 0:N) |>
  mutate(pr = if_else(state == "G", mu, 1 - mu) * dbinom(k, N, if_else(state == "G", sens, fpr)),
         cursed = post_naive(k) >= t0, sophisticated = post_full(k) >= t0) |>
  pivot_longer(c(cursed, sophisticated), names_to = "receiver", values_to = "approve") |>
  group_by(receiver) |>
  summarise(approval = sum(pr * approve),
            accuracy = sum(pr * if_else(state == "G", approve, !approve)), .groups = "drop") |>
  mutate(channel = "Selection")
q_star <- mu * (1 - t0) / ((1 - mu) * t0)
des <- tibble(receiver = c("cursed", "sophisticated"), channel = "Design",
              approval = mu + (1 - mu) * q_star, accuracy = mu + (1 - mu) * (1 - q_star))
bind_rows(sel, des) |>
  mutate(receiver = if_else(receiver == "cursed", "Cursed receiver", "Sophisticated receiver")) |>
  pivot_wider(names_from = receiver, values_from = c(approval, accuracy)) |>
  transmute(Channel = channel,
            `Approval (cursed)` = sprintf("%.2f", `approval_Cursed receiver`),
            `Accuracy (cursed)` = sprintf("%.2f", `accuracy_Cursed receiver`),
            `Approval (sophisticated)` = sprintf("%.2f", `approval_Sophisticated receiver`),
            `Accuracy (sophisticated)` = sprintf("%.2f", `accuracy_Sophisticated receiver`)) |>
  kable(align = "lcccc")
```

Two features of the table are the point of the paper. First, the columns differ for selection and not for design, and the reason is structural. At the moment the sponsor chooses which studies to forward, he knows their results and the regulator does not; his choice is a function of private information, and a receiver who ignores that is cursed. At the moment the sponsor chooses which experiment to run, in the case as I have set it up, he knows nothing the regulator does not. His choice is a function of his interests, which she knows, and of the prior, which she shares. There is no private information for the choice to leak and hence nothing for her to be cursed about. She is already conditioning on everything, which is why there is nothing for sophistication to add in the design row.

Second, compare the two sophisticated cells. The two channels involve different experiments and the table does not compare their informativeness; it compares what each channel yields once the receiver is sophisticated. The cherry-picker who is found out does no better than full disclosure of whatever studies he ran. The designer who is fully understood does strictly better than full disclosure of any experiment the receiver would have chosen.

I have assumed the sponsor has no private information when he designs. That is the clean case, not the realistic one: a sponsor at the design stage of a pivotal trial has early-phase data the regulator has not seen, his choice of experiment is then itself a signal, and a way of being cursed reappears on the design side. The economics of this case is worked out by @PerezRichet2014, @Hedlund2017, and @KoesslerSkreta2023; what matters here is that the sender's gain from design survives it, since there are equilibria in which the receiver correctly infers everything the choice of design reveals and is still moved by it. Unlike the disclosure case, conditioning on the sender's choice does not leave him with nothing to gain.

One further feature inverts a natural assumption. Design requires daylight. One might think a sponsor who could experiment privately and disclose selectively would be better off than one committed to a public design, having more options. He is not: private experimentation with selective disclosure yields a lower probability of persuasion and a better-informed receiver than public experimentation [@FelgenhauerLoerke2017; @Frechette2022; @DaiFudenbergPei2025], because without commitment the sender unravels and with it he can garble. The sponsor wants his design credibly committed. Before the reforms he could not make it so: a receiver who cannot tell a pre-specified endpoint from one chosen after a look at the data must treat the design as if it were selection, and discount it. Registration is what makes a design commitment credible to a sceptical receiver. The reforms take away the selection channel, which a sophisticated receiver had already neutralised, and supply the credible commitment that makes the design channel work. Daylight is the designer's friend.

# Is it deception? Is it manipulation?

The regulator has been moved, and left with nothing. What has been done to her? Accounts of deception and manipulation that locate the wrong in a defect of the target, a false belief, a belief that falls short of her ideals, an influence she is unaware of or that bypasses her reason, exclude design, because the regulator exhibits no such defect. Accounts that locate the wrong in the influencer's attitude, or in the payoff structure of the signalling system, can include it. I will argue that the second kind of verdict, where it applies, does not describe what the regulator has a complaint about.

## Deception and misleading

Deception in the standard sense is the intentional production of a false belief [@ChisholmFeehan1977; @Carson2010]. No false belief is produced. The regulator's belief after a pass, that the drug works with probability $0.5$, is correct: half of the drugs that pass work. One might say she is kept less informed than she could have been. But keeping someone ignorant is not deceiving them, and the designer does not keep her ignorant of anything that exists. He arranges for less to exist.

The literature on misleading with truths analyses a more specific failure. @Stokke2016 analyses misleading as offering a true but partial answer to the question under discussion that invites a false complete answer [see also @Saul2012]. Cherry-picking is misleading in exactly this sense: "study 3 was positive", offered in answer to "does the drug work?", invites the completion "and the others were too", which is false. That is why selection fails against a receiver who declines the invitation. Design is not like this. The sponsor asks the world a question, reports the world's complete answer, and the regulator knows which question was asked and what its answer bears on. There is no partial answer and no false completion; there is a self-serving choice of question. @Fallis2015 counts as disinformation true content that is selectively emphasised, but his criterion is that the content be likely to create false beliefs, and the designed test is not: it creates calibrated ones.

There is a formal tradition on which the verdict goes the other way. @Skyrms2010 defines a signal as carrying *misinformation* when it raises the receiver's probability of a state that does not obtain, and as *deceptive* when it is misinformation that systematically benefits the sender at the receiver's expense [refined in @FallisLewis2019]. The designed test's passes on drugs that do not work are misinformation, and they systematically benefit the sponsor at the regulator's expense; on this definition the design *system* is deceptive. I accept that as a verdict about the system. But what makes the system deceptive rather than merely noisy, on the definition, is the payoff clause: a test with the same statistical properties that was the only assay anyone knew how to run would produce misinformation at the same rate and would not be deceptive, because no one would be profiting from the noise. So the formal definition, applied here, picks out a wrong that lies not in what the receiver comes to believe but in who gains from the arrangement and at whose expense. That is the wrong I will call exploitation, and the Skyrmsian definition is better read as an early formal recognition of it than as a reason to assimilate design to deception in the philosophical sense, where a false belief is the whole point.

## Manipulation

The literature on manipulation is less unified, and I follow the map in @NoggleSEP [see also @Noggle2025]. On the *covert influence* account of @Susser2019, manipulation is covert influence that exploits decision-making vulnerabilities; design fails the covertness condition outright. On accounts on which manipulation works through non-rational means [@Wood2014], design fails as completely as an influence can: the regulator is moved by conditionalising on evidence and maximising expected value, and @Levy2019's argument that presenting reasons to reason-responsive mechanisms is not manipulation, whatever its merits for nudges, succeeds here. On the *ideals* account [@Noggle1996; @Barnhill2014], manipulation induces a belief, desire, or emotion that falls short of the ideals governing that state; the regulator's belief after a pass falls short of no ideal, by her lights or the sponsor's, and though Barnhill adds that the induced state must be against the target's interest, the account still needs a defective state, and the regulator's *decision*, not any mental state, is what is worse.

The accounts that include design are those on which manipulation is a matter of the influencer's attitude towards the reasons he supplies. @Gorin2014b argues, with cases in which an influencer supplies entirely good reasons for entirely ulterior ends, that what marks manipulation is the influencer's indifference to whether the reasons he gives are good ones; he judges them by their efficacy. @Klenk2022 defines manipulation as influence by a method about which the influencer is careless as to whether it reveals to the target the reasons there are. The sponsor who sets $q = 3/7$ chose that test for its efficacy in producing approvals; he would have chosen it whether or not it was informative. That is Gorin's indifference and Klenk's carelessness, and I do not think it can be argued away by pointing out that the test happens to reveal every reason it generates. On these accounts, design is manipulation.

I accept that, and I want to say what the verdict leaves out. These are accounts of what manipulation is, and on them a manipulation can leave its target no worse off; the wrong is in the influencer's stance, not in any loss. Consider two sponsors with the same stance. Both choose experiments purely by their efficacy in producing approvals. The first faces a regulator with a threshold of $0.5$ and sets $q = 3/7$. The second faces a regulator who has committed to a threshold of $0.95$, and finds that the most effective test he can run has $q = 0.023$, which is very nearly the fully informative test. On Gorin's and Klenk's accounts both sponsors manipulate, and to the same degree, because the attitude is the same. But the first regulator has been left with none of the value of information and the second with nearly all of it. The difference between them is one of degree, in the terms each was given; it is not a difference in the sponsor's attitude, which is common to both, and so it is not a difference the attitude accounts can see. Whatever complaint the two regulators share, the first has a further one, about what was taken. The attitude accounts, where they apply to design, are picking out the sender's readiness to take; they do not pick out the taking, and the taking is what varies with the design and what institutions respond to when they respond to design. To name the wrong done to the first regulator we need a category that is about the terms on which one party deals with another who depends on him. That category is exploitation.

@Buss2005 argued that the wrong of an influence need not consist in what it does to the target's rational agency, and @GTsai2014 that an influence can wrong its target while working entirely through reasons. Design is a case in point. The wrong is not to be found by looking at what the sender does to the receiver's mind. It is to be found by looking at what he takes from her.

# Exploitation

Here is what the sponsor takes. With no evidence the regulator's expected accuracy is $0.7$. With a perfectly informative experiment it would be $1$. The difference, $0.3$, is the value of information to her: the surplus that experimentation makes available. The sponsor, in choosing the experiment, chooses how that surplus is divided. He can run the informative test and hand it all to her, at the cost of approvals. He can run the uninformative test and destroy it. Or he can run the test with $q = 3/7$, which leaves her with none of it and converts the rest into approvals for him. He chooses the last, and by the result of §5 he would do the same whatever her payoffs were. Where her options are richer or his experiments constrained he cannot take all of it, but he takes what he can.

Before saying what kind of wrong that is, I should say to whom it is done, because the regulator is a stand-in. In the model the receiver is whoever bears the consequences of the decision. A patient deciding whether to take a drug on the evidence a sponsor has produced is the receiver in the primary sense; a regulator is the receiver as agent, whose payoffs in the model are those of the public on whose behalf she decides, and what the sponsor takes from her he takes from them. The motivating cases, in which designed evidence kept dangerous drugs on the market, are cases in which the loss fell on patients; the model represents it as the shortfall in the regulator's accuracy, since her accuracy is what she is there to secure for them. So when I say the receiver is exploited, I mean the decision-maker and those she decides for. An agent who deals on a principal's behalf can be exploited in that capacity, and the wrong is then to the principal, as when a counterparty takes advantage of a broker's dependence to the client's cost. In the cases that matter the principal is the public. (@Wertheimer2011 applies the exploitation framework to clinical research from the other side, asking whether research subjects are exploited; the present question is whether those who must rely on the research are.)

The structure is the one @Wertheimer1996 discusses under the heading of mutually advantageous exploitation, at its boundary. The receiver is not made worse off than she would be by no transaction: her accuracy is $0.7$ either way. In the limiting case of Proposition 1 she gains nothing, so the transaction is non-harmful rather than advantageous to her; in every case where the sender's experiments are constrained or her options richer she gains a little. She relies on the sponsor's evidence voluntarily, and where she is an institution she does so knowingly. And yet the transaction is unfair to her in the way Wertheimer's cases are unfair: the party with the power to set the terms has set them so that his gain, measured in what he cares about, is as large as it can be, and hers, measured in what she cares about, is as small as it can be. There is no common currency, and the framework does not need one; the sweatshop owner's gain is profit and the worker's is welfare, and what makes the terms unfair is how each party's gain compares with what a fair arrangement would have given them. Wertheimer's central puzzle is how a transaction that leaves both parties no worse off, and that the weaker party accepts, can nonetheless be a serious wrong, and his answer, that acceptance and non-harm may defeat a claim to interference and a right to better terms without defeating the judgement that the terms are unfair, transfers directly. Consent is not a condition of the wrong; it is what makes the nonworseness objection, which I take up below, pressing in the regulator's case. The public, who do not consent to anything, are wronged in the same way and with less to be said in the sponsor's defence.

Two more recent accounts fit the case as well. @Valdman2009 holds that wrongful exploitation is the extraction of excessive benefit from someone who cannot, or cannot reasonably, refuse one's offer, and insists that this wrong is not reducible to harm, coercion, or deception. The receiver cannot reasonably refuse. She must decide, and she must decide on the evidence that exists; she has no independent capacity to produce it and no other party will. That is a specific instance of epistemic dependence [@Hardwig1985]: for most of what we need to know, we depend on others to produce the evidence, and the dependence is a vulnerability. @Vrousalis2013 makes vulnerability central: exploitation is instrumentalising another's vulnerability to extract a benefit, within a systematic relationship. A regulator has legal power over a sponsor, and one might think that disqualifies Vrousalis's account, which is an account of domination. But the relevant dimension of power is power over the evidence, and along that dimension the relationship runs the other way until the regulator acquires the authority over design that I discuss in §8. The sponsor who chooses $q = 3/7$ is using the receiver's dependence on him, together with her own rationality, as the instrument by which approvals are extracted. @Wood2014 [see also @Wood1995], in the same chapter that rules design out of manipulation on his own account, characterises exploitation as the use of another's weakness or need for one's own advantage, and stresses that it is compatible with the exploited party's consenting and benefiting.^[The phrase "epistemic exploitation" has an established use, due to @Berenstain2016, for the unpaid labour of educating the privileged that is demanded of members of marginalised groups. That is a different phenomenon, and I avoid the phrase.]

## The baseline

Every exploitation claim needs a standard of fair terms, and Wertheimer's own difficulty is saying what it is. The receiver is not entitled to the informative experiment, any more than the sweatshop worker is entitled to a job at a fair wage; a sponsor who runs no trial wrongs no one in the way I am describing. So what makes $q = 3/7$ unfair terms, given that the sponsor need not have offered any?

The answer is that the evidence is produced *for a purpose that is not the sponsor's to set*, and the purpose fixes the standard. A pivotal trial exists because a regulatory regime requires evidence adequate to inform an approval decision; a criminal trial admits evidence because it bears on guilt; a journal publishes studies because readers need to know whether the result is real. In each case the institution assigns the evidence a purpose, and the cooperative experiment is the one that serves it: the experiment that best trades information against cost from the standpoint of the decision, which is the single-decision-maker benchmark @HenryOttaviani2019 use to evaluate the arrangements they study. The shape of the norm is Gricean, a contribution is cooperative when it is as informative as the purpose of the exchange requires [@Grice1989], but its content does not depend on the sponsor's having accepted that purpose. Grice's principle is indexed to the purpose the participants accept, and a regulatory submission, like courtroom advocacy, is adversarial: the sponsor has accepted no such thing. That is why the sponsor's contribution is assessed against the institution's purpose and not against his own, exactly as an advocate's presentation is assessed by the court's standard of relevance and probative value and not by the advocate's aims. The sponsor who sets $q = 3/7$ has not lied and has been fully cooperative in what he asserts about the test. He has been uncooperative, by the standard the institution sets, in what he arranged to have to assert. That the receiver knows this, and discounts accordingly, does not restore cooperation. It is what leaves her with nothing.

This also answers a question the mutually-advantageous framing invites: since the sponsor bears the whole cost of the experiment, what has the receiver contributed to the surplus, such that she has a claim on a share of it? She has contributed her reliance. The approval is worth something to the sponsor only because the receiver will act on the evidence; her acting on it is what he gains from. The surplus is joint in exactly the way a wage bargain's is: the employer supplies the capital and the worker the labour, and the sponsor supplies the experiment and the receiver the decision that gives it value. A simpler rival account would say that the sponsor is under a duty to produce evidence adequate to the institution's purpose and has breached it. Everything I have said about the baseline is available to that account, so I should say what the exploitation framing adds. Three things. First, degree. A duty is breached or not; exploitation scales with the dependence of the receiver and the size of the appropriation, and so explains why the same choice of $q = 3/7$ wrongs a public with no recourse more than it wrongs a regulator with protocol authority, and wrongs a receiver with competing sources hardly at all. Second, the nonworseness puzzle. A duty to produce informative evidence is violated as much by the sponsor who runs nothing as by the one who runs $q = 3/7$, unless it is made conditional on producing, and then one wants to know why producing triggers it. The exploitation account says why: the wrong arises in the transaction, from taking advantage of the receiver's reliance once she is relying, and there is no transaction when nothing is produced. Third, the shape of the remedy. Duties are enforced by detecting and sanctioning breach, and here breach is undetectable, since nothing is hidden and the shortfall exists only relative to a counterfactual experiment. Exploitation is remedied by changing the balance of power over the terms, which is what the institutions of §8 do and what a duty account does not predict. The account is also symmetric, and should be. A regulator who commits to a standard of $0.95$ and thereby obliges the sponsor to run a nearly informative experiment has acquired power over the terms; does she now exploit him? Not so long as her standard is set by reference to the decision's purpose, since the cooperative experiment is then what she demands and the sponsor still gains from running it. A standard set beyond what the decision could use, to extract costly evidence for its own sake, would be exploitation in the other direction, and when experiments are costly the same benchmark that identifies the sponsor's under-provision identifies the regulator's over-demand.

## When design is not exploitation

The account also says when design is *not* exploitative, and this answers two objections that would otherwise be decisive. The first is overgeneration. Job candidates choose which referees to solicit; firms choose which demonstration to run; scientists choose the experiment most likely to yield a publishable result. If all of these are exploitation, the category is too wide to be interesting. The second is that the exploitation claim and the remedies I will propose pull against each other. If the receiver can recover the value of information by committing to a demanding threshold, then she is not, after all, someone who cannot reasonably refuse; her vulnerability is her decision rule, not her dependence.

Both objections have the same answer, and it is the answer exploitation theory gives generally: exploitation is a matter of *power over the terms*, and it is mitigated exactly to the extent that the vulnerable party has that power. A worker with outside options is less exploitable than one without; a worker with a union that can credibly threaten a strike is less exploitable still. A receiver who can dictate the design, or credibly commit to a standard the designer must meet, has power over the terms of the evidential exchange and is exploited only to the degree that she lacks it. Where she has it and does not use it, the sponsor takes advantage of her imprudence, which is a lesser wrong than taking advantage of her dependence, and the act-by-act regulator of my example who could have published a rule and did not is in that position. Everyday evidence-gathering is arranged so that receivers have this power. The examiner sets the examination. The employer decides what the interview will test, specifies what referees must address, and where the candidate's choice of referees is thought too self-serving, takes up references the candidate did not nominate. The consumer shown a demonstration has, in a competitive market, other sellers to consult, and competing senders undo each other's design as they undo each other's selection [@MilgromRoberts1986; with the qualification in @GentzkowKamenica2017 that competition in design restores information only when each sender can generate the signals the others can]. These are not counter-examples; they are what the account predicts a well-arranged evidential practice looks like.

The scientist who chooses experiments for publishability is a different matter, and here the account should be allowed to bite. Readers of a literature have no authority over its design and no way to commit to a standard; they take what is produced. A reward structure that leads scientists to choose experiments by their prospects of a striking result rather than their informativeness for the questions readers need answered is, on this account, one in which readers are exploited, mildly by each author and seriously in aggregate; the literature that has modelled that reward structure [@Romero2016; @Heesen2018; @Bright2017] has been describing exploitation without the name, and the remedy it favours, registered reports, is the transfer of design authority to the receiving side that the account predicts.

So the cases that are seriously exploitative are the ones in which the receiver has no power over the terms: where the sender is the only party who can produce the evidence, the receiver must act on whatever is produced, and no institution has given her authority over the design or the capacity to commit to a standard. That is the position of the public, of most patients, of most jurors, and of any decision-maker who takes evidence case by case as it comes. It was, until regulators acquired the powers they now have, the position of drug regulators. It is a consequence of the account, not a tension within it, that the wrong is serious exactly where the remedies are unavailable.

One objection remains: the nonworseness claim [@Zwolinski2007]. If the receiver is no worse off with the designed experiment than without it, and consents to rely on it, then the sender who runs it does nothing worse than the sender who runs nothing, and the latter does nothing wrong, so neither does the former. The standard reply applies [@Kates2023; @ZwolinskiSEP]: an interaction can be wrong *as an interaction* even when its counterfactual absence would have been no better for the victim, because the wrong is in the terms on which it is conducted and not in its net effect. And there is a reply specific to this case. The receiver's consent, where she has no power over the design, is consent to *rely*, not consent to the design. She agrees to decide on whatever evidence the sponsor produces because she has no alternative; she does not thereby agree that he may choose the experiment by reference to her threshold rather than by reference to her question.

# What follows for institutions

## Transparency relocates the problem

The reforms that have reshaped clinical and behavioural research since the early 2000s are of two kinds, and it matters which is which. Registration, pre-specification and mandatory reporting are transparency reforms: they make the count known and the design credibly fixed in advance, and they leave the design to the sponsor. Registered reports and regulatory protocol review are something else, a transfer of authority over the design, and I return to them below. The transparency reforms are aimed at selection, and against selection they work. But they work by establishing exactly the condition under which design has its full power. A registered trial with a pre-specified endpoint is a committed experiment whose result the sponsor cannot hide. It is the persuasion game of §5, instantiated. So transparency, taken alone, does not remove the sponsor's ability to move the regulator; it removes one of the two channels and directs all of the sponsor's effort into the other. @HolmanGeislar2018 describe the relationship between industry and its regulators as an asymmetric arms race in which each methodological safeguard is met by a new move. On the present analysis the move after registration is design, and it is a move that requires no violation of anything the registration regime asks for.

The philosophy of science literature has identified mechanisms that are design-type without marking them as such: industrial selection [@HolmanBruner2017; @PintoPinto2023] is design at the level of the community, since the funder chooses which methods get amplified; industrial distraction [@OConnorFreeborn2025] is design at the level of the research agenda; @Elliott2011 documents the same in environmental research. What the present analysis adds is a reason to expect these mechanisms to survive the sophistication of the audience, which the community-level models do not test, and two features that make the relocated problem harder to address than the original. Nothing is hidden, so the tools for detecting misconduct have nothing to find; and the regulator's beliefs are correct, so comparing them with the evidence finds nothing either. The effect shows up only at the level of the population of decisions, as a tilt relative to what a differently designed body of evidence would have supported.

## Two counter-moves

The design channel works because the receiver depends on the sponsor for the experiment, the sponsor chooses it, and the receiver's decision is a threshold function of her belief that the sponsor can aim at. So there are three things the receiver can do. She can reduce her dependence. She can take the choice of experiment away from him. Or she can make the threshold something he cannot profitably aim at. All three are things receivers already do, and the exploitation account explains why they take the form they do, since each removes one of the conditions on which the exploitation rests.

The first is *reducing dependence*: publicly funded comparative-effectiveness trials, independent replication, adversarial collaboration between a sponsor and its critics. These remove the sponsor's monopoly on production, and where they are feasible they are the most direct remedy, since exploitation of dependence ends when the dependence does. They are also expensive, slow, and, for a novel compound, often impossible before approval, because only the sponsor can run the pivotal trial of its own drug. That is why the other two matter.

The second is *authority over the design*. Registered reports do this: the journal, not the author, fixes the design before results exist, so that the author's choice of what to test is subject to review by the party who will act on it [@Chambers2013]. Regulators do it too. The United States Food and Drug Administration reviews protocols before pivotal trials, agrees endpoints and analysis plans with sponsors in advance, and issues guidance on acceptable comparators and surrogate markers; it is not a passive receiver of whatever the sponsor designs, though comparators, doses and populations remain largely the sponsor's to choose, which is where @Heres2006 found the effect. The lottery funding that @PintoPinto2023 propose as a remedy for industrial selection has the same shape: it takes the choice of which methods to amplify out of the funder's hands. @GlazerRubinstein2004 give the general theory of a receiver who commits to a rule of persuasion specifying what the sender may present and what will be checked; receiver-side design authority is the case in which the rule specifies the experiment. What these institutions have in common is that they work by removing the sender's choice rather than by making it visible, which is what the analysis predicts a remedy for design must do. Transparency about a choice does nothing when the choice is the problem. @Wilholt2009 argues that conventional methodological standards in a field function as coordination devices that constrain the play of preference bias in the design of studies; on the present analysis such conventions are a diffuse form of receiver-side design authority, and they work for the same reason.

The third is *commitment to a standard*. Suppose the regulator cannot dictate the design but can commit, before the sponsor chooses his experiment, to a rule: approve if and only if the posterior probability that the drug works is at least $t$, for some $t$ she chooses. Her threshold given her payoffs is $0.5$, but she is choosing a rule, not an act, and she is choosing it in the knowledge that the sponsor will design against it. Against a threshold of $t$, the sponsor's optimal test is again the one that every working drug passes, now with a false-positive rate of $q(t) = 0.3(1-t)/(0.7t)$, which is what it takes to put the posterior after a pass at exactly $t$. The sponsor still runs the test, because it gets him approvals with probability $0.3/t$, which exceeds the zero he would get by running nothing. And the regulator's accuracy is
$$
1 - \frac{0.3(1-t)}{t},
$$
which rises from $0.7$ at $t = 0.5$ to $0.9$ at $t = 0.75$, to $0.967$ at $t = 0.9$, and towards $1$ as $t$ approaches $1$. @fig-threshold shows the trade-off. The result of §5 says why the threshold has to be set *above* the one her payoffs dictate: at her own threshold, wherever it lies, the sponsor leaves her with nothing; every step above it recovers some of the surplus, because above her threshold the value of approving is no longer linear in her belief and the sponsor can no longer make her indifferent for free. (Derivations are in the appendix.)

```{r threshold}
#| label: fig-threshold
#| fig-cap: "The regulator's accuracy and the sponsor's approval rate as a function of the approval threshold the regulator commits to, when the sponsor best-responds by designing the test. Prior that the drug works: 0.3. The dotted line is the regulator's accuracy with no evidence."
#| fig-width: 6
#| fig-height: 3.6
tibble(t = seq(0.5, 0.99, by = 0.005)) |>
  mutate(`Regulator's accuracy` = 1 - mu * (1 - t) / t,
         `Sponsor's approval rate` = mu / t) |>
  pivot_longer(-t, names_to = "quantity", values_to = "value") |>
  ggplot(aes(t, value, linetype = quantity)) +
  geom_hline(yintercept = 1 - mu, linetype = "dotted", colour = "grey40") +
  geom_line(linewidth = 0.8) +
  scale_linetype_manual(values = c("solid", "longdash")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Approval threshold the regulator commits to", y = NULL, linetype = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

The formal point is not mine: @HenryOttaviani2019 analyse an evaluator who commits to an approval standard against an informer who then chooses how much costly evidence to gather, and the value of a demanding standard, together with its cost when evidence is expensive, is their result; the law-and-economics literature on the burden of proof reached a related conclusion earlier [@Sanchirico1997; @Kaplow2012]. What I want to draw out is what the point means once it is set beside the selection channel and the exploitation account.

First, commitment is a remedy specific to design. Against selection, the receiver's commitment to a threshold adds nothing to what her scepticism already achieves: @HartKremerPerry2017 prove, for evidence games in which the sender chooses which verifiable evidence to disclose and under conditions on the evidence structure and on equilibrium selection that the natural cases satisfy, that the outcome when the receiver commits to a decision rule in advance coincides with the equilibrium outcome when she does not. Against a sender who is choosing among existing results, the sceptical best response already does all the work that commitment could do. Against a sender who is choosing the experiment, commitment is the difference between forfeiting the value of information and recovering it. So the two channels call for different receiver-side responses, scepticism for selection and commitment for design, and the reforms the philosophical literature has championed supply the first and not the second.

Second, the commitment must be to a rule the receiver would not follow act by act, and this qualifies the headline claim in a way I should state plainly. When the set of experiments is unrestricted, the regulator never faces a posterior between $0.5$ and $t$ on the path of play, because the sponsor's optimal test never produces one; the commitment works entirely through his anticipation of it. But it is optimal for him only because he anticipates that she would *not* approve at $0.6$, and an act-by-act Bayesian with her payoffs would. So the accurate statement of the central claim is: a receiver who is rational act by act is moved by design and left with nothing; a receiver who can bind herself to a rule is not. Whether an individual can rationally bind herself in this way is the question of resolute choice [@McClennen1990], and I take no stand on it, because for the cases that matter it is not the operative question. The sponsor responds to what he can observe, and an individual's private resolution is not observable; a rule of evidence, a statutory approval criterion, or a journal policy is. That is why the standards that do this work are institutional. The usual story about "beyond reasonable doubt", and about the demand for substantial evidence from adequate and well-controlled investigations, is that these standards weigh the costs of the two kinds of error, and there are other familiar reasons for fixing standards in advance, among them predictability and equal treatment. @Kaplow2012 has argued that the burden of proof should be set by its effect on the behaviour that generates cases rather than by error costs alone; the present analysis gives a persuasion-theoretic version of that argument for one kind of behaviour, the design of evidence, and adds that the standard does its work only because it is fixed in advance, publicly, and not revisited case by case. It also predicts that the standard should sit above the threshold that the error costs alone would justify, since at that threshold the designer takes everything. A regulator who adds intermediate options, conditional approval, restricted labelling, post-marketing requirements, does something with the same effect by a different route: with more than two actions the sender can no longer make her indifferent at every step, and she keeps part of the surplus.

Third, the result reverses a lesson the naive-receiver models teach. In @WeatherallOConnorBruner2020 the policymaker does better by listening to more scientists and worse by being slow to move; against a designer, she does better by being harder to move, because the information she would have received at a lower threshold is information the designer would never have produced. @Douglas2009 argued that the choice of an evidential threshold is a value choice that scientists cannot avoid making; if so, the strategic environment in which the threshold will be met is one of the things that legitimately bear on it.

The result has limits. It assumes experimentation is costless and any experiment available. When experiments are costly, a threshold set too high leads the sponsor to run nothing, and the receiver-optimal standard can be well short of certainty [@HenryOttaviani2019]. When the set of available experiments is bounded, posteriors between the receiver's own threshold and her committed one arise on the path of play, the commitment binds, and the sponsor can be driven out at thresholds well below one. When evidence is produced adversarially by two parties with costly effort, @DemouginFluet2006 argue that the preponderance standard is optimal. And competition among designers does not restore information as reliably as competition among disclosers: the antipsychotic trials of @Heres2006 were designed by rival sponsors, each for its own drug, and what competition produced was a circle of contradictory results. The claim is not that receivers should always demand near-certainty. It is that a receiver facing a designer has, in a standard set above her own threshold, an instrument that recovers what design would otherwise take, and that the shape of the instrument, a public rule fixed in advance, is what the analysis predicts.

## Where the problem now lives

If the counter-moves are partly institutionalised in drug regulation, the analysis predicts that the design channel will be most active where they are not: where a sponsor can produce evidence that a receiver must act on, with no authority over the design and no capacity to commit. The clearest case is the one @OConnorFreeborn2025 describe. A beverage company funds accurate, fully published research on exercise as a cause of obesity, and their learner is moved because true evidence about one cause explains away another. A sophisticated learner, who knows the funder chose the question, can still be moved, for the reason of §5: the funder has chosen an experiment about the decision-relevant state, whether to regulate sugar, whose informativeness he controls, and the public that must decide has no authority over what gets studied and no rule fixed in advance about what would convince it. The natural reform proposal, following the success of registration in clinical research, is disclosure of funding. The present analysis says that proposal is aimed at the wrong channel. A public that knows who funded the exercise studies, and discounts accordingly, is the sophisticated receiver of §5, and discounting does not restore what design takes. [@John2018 argues on other grounds that transparency is the wrong target for the ethics of science communication; the present argument gives one mechanism by which it fails.] The exploitation account says where the remedy lies instead: with whoever can be given authority over what gets studied, or the standing to say in advance what it will take to be convinced.

# Conclusion

I began with a finding: that an interested party can move an audience to false beliefs by sharing only true results. The finding is real but its audiences are cursed, and removing the curse divides the phenomenon into two things that behave differently. Selection, the choice of which existing results to share, depends on the audience's ignorance of what exists, and disappears when that ignorance does. Design, the choice of which experiments to run, does not depend on any ignorance at all. It moves an audience who knows everything and updates correctly on all of it, by aiming at the threshold of her decision rule, and in the simplest case it leaves her with beliefs that are correct and an expected outcome exactly as good as if no evidence had been produced, whatever her payoffs.

That combination is hard to describe with the vocabulary we have. It is not lying, deception, misleading, or manipulation on any account that locates the wrong in the target; and the accounts that classify it as manipulation anyway do so on the strength of an attitude that is the same whether or not anything is taken. I have argued that the wrong is exploitation: the use of the audience's dependence on the sender for evidence, and her lack of power over the terms on which it is produced, to take for himself the value that the evidence could have had for her, measured against the cooperative experiment that the norm on evidence produced for another's reliance already specifies. The description matters because it changes what a remedy has to do. A remedy for deception restores true belief; here belief was never false. A remedy for manipulation restores the operation of reason; here reason operated perfectly. A remedy for exploitation changes the balance of power over the terms: it takes the choice of experiment away from the interested party, or arms the audience with a public commitment that forces his choice towards hers.

The transparency reforms that defeat selection, registration and disclosure taken alone, do neither. They make design commitment credible, and their success against the tobacco strategy's cruder half is what makes its subtler half the whole of the problem that remains. If the analysis is right, that half will not show up as misconduct, will not show up as false belief, and will show up only as a persistent tilt in the decisions of audiences whose every belief is warranted. The instruments for correcting it are ones some institutions already have and that we have been explaining incompletely: independent production where it is possible, authority over what gets studied, and a standard of proof, fixed in advance and set above what the costs of error alone would justify, that the audience will not lower for a single case however compelling the case appears. Against a party who designs the evidence, the last is not closed-mindedness. It is the only way to be open to the evidence he would otherwise never produce.

# Appendix: derivations {.appendix}

Let $\mu \in (0,1)$ be the receiver's prior that the state is $G$ (the drug works). The receiver chooses between $a$ (approve) and $r$ (reject), with utilities $u(a, G)$, $u(a, B)$, $u(r, G)$, $u(r, B)$ such that $a$ is better in $G$ and $r$ is better in $B$. Write $v(\pi) = \max\{\pi u(a,G) + (1-\pi) u(a,B),\ \pi u(r,G) + (1-\pi) u(r,B)\}$ for the receiver's expected utility at belief $\pi$ when she chooses optimally; $v$ is the maximum of two linear functions and so convex, and there is a unique $t^\ast \in (0,1)$ at which the two are equal, the receiver's threshold. Assume $\mu < t^\ast$, so that with no evidence she rejects. The sender's payoff is $1$ if $a$ is taken and $0$ otherwise.

**Design.** The sender chooses an experiment with outcomes in $\{\text{pass}, \text{fail}\}$, with $\Pr(\text{pass} \mid G) = p$ and $\Pr(\text{pass} \mid B) = q$. (With a binary-action receiver one can restrict attention to experiments with two outcomes, read as action recommendations; see @KamenicaGentzkow2011.) The posterior after a pass is $\mu p / (\mu p + (1-\mu) q)$, and the receiver approves after a pass if and only if this is at least $t^\ast$, i.e. if and only if
$$
q \le \frac{\mu (1-t^\ast)}{(1-\mu)\, t^\ast}\, p .
$$
The sender's payoff is $\Pr(\text{pass}) = \mu p + (1-\mu) q$ when the receiver approves on a pass, and nothing is gained from a fail. This is increasing in $p$ and $q$, so the sender sets $p = 1$ and $q$ at the bound:
$$
q^\ast = \frac{\mu(1-t^\ast)}{(1-\mu)\,t^\ast}, \qquad \Pr(\text{pass}) = \frac{\mu}{t^\ast}.
$$
The posterior after a pass is $t^\ast$ and after a fail is $0$.

**Proposition 1.** *Under the sender's optimal experiment the receiver's expected utility equals her expected utility with no evidence, $v(\mu)$, for every specification of her utilities.*

*Proof.* Her expected utility is $\frac{\mu}{t^\ast} v(t^\ast) + \left(1 - \frac{\mu}{t^\ast}\right) v(0)$. On $[0, t^\ast]$ the receiver rejects, so $v$ coincides there with the linear function $\ell(\pi) = \pi u(r,G) + (1-\pi) u(r,B)$. Hence $v(t^\ast) = \ell(t^\ast)$ and $v(0) = \ell(0)$, and by linearity $\frac{\mu}{t^\ast} \ell(t^\ast) + \left(1 - \frac{\mu}{t^\ast}\right) \ell(0) = \ell(\mu) = v(\mu)$. $\square$

With the symmetric utilities of the text, $u(a,G) = u(r,B) = 1$ and $u(a,B) = u(r,G) = 0$, so $t^\ast = 1/2$, $v(\mu) = 1 - \mu = 0.7$, $q^\ast = 3/7$, and the approval probability is $0.6$.

**Commitment.** Suppose the receiver commits to approve if and only if her posterior is at least $t$, with $t^\ast < t < 1$. The sender's optimal experiment is as above with $t$ in place of $t^\ast$: $p = 1$, $q(t) = \mu(1-t)/((1-\mu)t)$, $\Pr(\text{pass}) = \mu/t > \mu > 0$, so the sender still runs it. The receiver's expected utility is $\frac{\mu}{t} v(t) + \left(1 - \frac{\mu}{t}\right) v(0)$. Since $t > t^\ast$, $v(t) > \ell(t)$ (she strictly prefers to approve at $t$), so this strictly exceeds $\ell(\mu) = v(\mu)$; and it tends to $\mu\, u(a,G) + (1-\mu)\, u(r,B)$, the full-information value, as $t \to 1$. With the symmetric utilities the receiver's probability of a correct decision is
$$
\mu + (1-\mu)(1 - q(t)) = 1 - \frac{\mu(1-t)}{t},
$$
which is $0.7$ at $t = 1/2$, $0.9$ at $t = 0.75$, $0.967$ at $t = 0.9$, and $0.984$ at $t = 0.95$ (where $q = 3/133 \approx 0.023$).

**Selection.** Let $N$ studies be run, independent conditional on the state, each positive with probability $s$ in state $G$ and $f$ in state $B$, with $s > f$. The sender reports the positives. A cursed receiver who sees $k$ positive reports and treats them as the whole record has posterior odds $\frac{\mu}{1-\mu} (s/f)^k$. A sophisticated receiver who knows $N$ infers $N - k$ negatives and has posterior odds $\frac{\mu}{1-\mu} (s/f)^k \left(\frac{1-s}{1-f}\right)^{N-k}$, which is the posterior from full disclosure. The figures in @tbl-twobytwo sum over $k$ under the binomial distribution in each state, with $N = 4$, $s = 0.8$, $f = 0.3$, $\mu = 0.3$, $t^\ast = 1/2$; the cursed receiver approves for $k \ge 1$ and the sophisticated receiver for $k \ge 3$.
